### 2016-03-08 RoughDraft/ElMayor.tex
initial commit

\documentclass[12pt]{article}

\usepackage{amssymb,amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{fancyhdr} % required for custom header
\usepackage{graphicx}
\usepackage{listings}
\usepackage{courier}
\usepackage[usenames,dvipsnames]{color}

%set up the header
\pagestyle{fancy}
\lhead{Trever Hines}
\chead{El Mayor Postseismic}
\rhead{\today}

\setlength{\headheight}{15pt}
\renewcommand\headrulewidth{1.0pt} % Size of the header rule

%% Title
%%------------------------------------------------------------------------------
\title{	
El Mayor Postseismic
\author{Trever Hines}
\rule{\headwidth}{1.0pt}
}

\begin{document}
\maketitle
\section*{Introduction}

\section*{Data Processing}

  We use continuous GPS position time series provided by University
  Navstar Consortium (UNAVCO) for Plate Boundary Observatory (PBO)
  stations within a 400 km radius about the El Mayor-Cucapah
  epicenter. Our analysis is on the coseismic and postseismic
  deformation resulting from the EMC earthquake, which we collectively
  describe as $u(t)$. We consider GPS position time series,
  $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular
  tectonic deformation, annual and semi-annual fluctuations, and
  coseismic offsets from sigificant earthquakes over the time span of
  this study.  The June 14, 2010 Mw5.8 Ocotillo earthquake and the
  August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3
  event, are the only earthquakes after the EMC earthquake that
  produced noticeable offsets recorded by GPS. Although the Ocotillo
  earthquake had its own series of aftershocks (Haukson), neither
  earthquake produced transient deformation that is detectable with
  GPS. We thus model $u_\mathrm{obs}(t)$ as 
  \begin{equation}\label{TimeSeriesModel}
  \begin{split}  
    u_\mathrm{obs}(t) = &u(t) + c_0 + c_1t + \\
                       &c_2\sin(2\pi t) + c_3\cos(2\pi t) + c_4\sin(4\pi t) + c_5\cos(4\pi t) + \\
                       &c_6H(t-t_\mathrm{oc}) + c_7H(t-t_\mathrm{bs}) + \epsilon.
  \end{split}
  \end{equation}
  Where $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the
  Ocotillo earthquake and Brawley swarm respectively, $H(t)$ is the
  Heaviside function, $c_0$ through $c_7$ are unknown coefficients,
  and $\epsilon$ is noise with zero mean and variance that is assumed
  known.

  Stations which recorded signals that clearly cannot be described by
  the aforementioned processes are not included in our analysis. This
  includes stations in the Los Angeles basin, which record deformation
  that is largely anthropogenic. In order to ensure an accurate
  estimation of the secular deformation, we only use stations that
  were installed at least six months prior to El Mayor-Cucapah
  earthquake. While several stations were installed after the EMC
  earthquake to improve the spatial resolution of postseismic
  deformation \cite{S2015}, our inverse method uses postseismic
  displacements rather than velocities (e.g. Pollitz), which requires
  the knowledge of the stations preseismic position. Despite our
  inability to utilize potentially rich data, we prefer to use
  postseismic displacements rather than potentially dubious estimates
  of postseismic velocities.

  The October 16, 1999 Hector Mine earthquake, which occurred within
  our study region about 270 km north of the EMC epicenter, has
  produce transient postseismic deformation which we do not wish to
  model either mechanically or through empirical line fitting. We thus
  restrict our analysis to deformation observed six years after the
  Hector Mine earthquake, past which point postseismic deformation for
  nearfield sites occurs at an approximately steady rate
  \cite{SS2009}. When considering stations further away from the
  Hector Mine epicenter, postseismic transience persists for only
  about two years \cite{S2015}.

  We do not assume a parametric form for $u(t)$, (e.g. \cite{R2015}),
  but rather we model $u(t)$ as integrated Brownian motion, so that
  \begin{equation}
    \dot{u}(t) = \sigma^2\int_0^t w(s) ds.
  \end{equation}    
  where $w(t)$ is white noise and the variance of $\dot{u}(t)$
  increases linearly with time by a factor of $\sigma^2$. We use a
  Kalman filtering approach to estimate $u(t)$ and the unknown
  parameters in eq. \ref{TimeSeriesModel} which we describe now.

  In the context of Kalman filtering, our time varying state vector is
  \begin{equation}
    \mathbf{X}(t) = [u(t),\dot u(t), c_0, ..., c_7]
  \end{equation}
  and eq. \ref{TimeSeriesModel} is the observation function which maps
  the state vector to the GPS observations. We initiate the Kalman
  filter by assuming a prior estimate of $\mathbf{X}(t)$ at time $t_0$ which
  has a sufficiently large covariance to effectively make our prior
  uninformed.  For each time epoch, $t_i$, Bayesian linear regression
  is used to incorperate GPS derived estimates of displacement with
  our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a postserior
  estimate of the state, $\mathbf{X}_{i|i}$, which has covariance
  $\mathbf{\Sigma}_{i|i}$.

  We then use the posterior estimate of the state at time $t_i$ to
  form a prior estimate of the state at time $t_{i+1}$ through the
  transition function
  \begin{equation}\label{predict}
    \mathbf{X}_{i+1|i} = \mathbf{F}_{i+1}\mathbf{X}_{i|i} + \mathbf{\delta}_{i+1} 
  \end{equation}
  where 
  \begin{equation}
    \mathbf{F}_{i+1} = 
    \left[
    \begin{array}{ccc}
    1           & (t_{i+1} - t_i) & \mathbf{0}\\
    0           & 1              & \mathbf{0}\\
    \mathbf{0}  & \mathbf{0}     & \mathbf{I}
    \end{array}
    \right]
  \end{equation}
  and $\mathbf{\delta}_{i+1}$ is the process noise, which has zero
  mean and covariance described by
  \begin{equation}
    \mathbf{Q}_{i+1} = 
    \sigma^2 \left[
    \begin{array}{ccc}
    \frac{(t_{i+1} - t_i)^3}{3} & \frac{(t_{i+1} - t_{i})^2}{2} & \mathbf{0}\\
    \frac{(t_{i+1} - t_i)^2}{2} & (t_{i+1} - t_{i}) & \mathbf{0}\\ 
    \mathbf{0} & \mathbf{0} & \mathbf{0}
    \end{array}
    \right].
  \end{equation}

  The covariance of the new prior state, $\mathbf{X}_{i+1|i}$, is then described by
  \begin{equation}
    \mathbf{\Sigma}_{i+1|i} = \mathbf{F}_{i+1}\mathbf{\Sigma}_{i|i}\mathbf{F}^T_{i+1} + \mathbf{Q}_{i+1}.
  \end{equation}

  This process is repeated for each of the $N$ time epochs at which
  point we use Rauch-Tung-Striebel smoothing to find $X_{i|N}$, which
  is an estimate of the state at time $t_i$ that incorporates all $N$
  GPS observation.  Our final estimates of $u(t)$ are used in
  subsequent analysis, while the remaining components of of the state
  vector are considered nuisance parameters. In the interests of
  computational tractability, we downsample our smoothed time series
  from daily solutions down to weekly solutions.

  We illustrate the effect of filtering in figure ().  We assume a
  constant $\sigma^2$ for each station, which is chosen to be just
  large enough for the earliest transient deformation at the most
  nearfield site, P496?, to be faithfully described by the filtered
  solution.

  Cite Freed 2007 for far reaching postseismic after Landers/Hector Mine.

\section*{Observations}

\section*{Prior Studies}

\section*{Postseismic Modeling}
  We use a fault geometry from \cite{W2011}, which was determined
  using teleseismic, GPS, and InSAR data.

  After the El Mayor-Cucapah earthquake, additional GPS stations were
  installed In Baja California to record postseismic deformation with
  better spatial coverage.  Two of the stations PTAX and PHJX were
  installed near the epicenter in the Cucapah Mountains.  We do not
  include these two stations in our analysis because the geometry of
  the faults that ruptured during the earthquake is more complicated
  than our assumed fault geometry \cite{O2012} and the near field
  stations would be most sensitive to error in our geometry. We also
  leave of these near field stations in order to avoid any near field
  processes which we do not consider in this paper \cite{GO2014}.

  Numerous stations exhibit extraneous signals which can be at  
  \cite{A2007}

\section*{Rheological constraints}

\section*{Results}
\section*{Acknowledgements}
  This material is based on EarthScope Plate Boundary Observatory data
  services provided by UNAVCO through the GAGE Facility with support
  from the National Science Foundation (NSF) and National Aeronautics
  and Space Administration (NASA) under NSF Cooperative Agreement
  No. EAR-1261833.

\begin{thebibliography}{}

\bibitem[Freed et al. (2007)]{F2007} 1. Freed AM, Bürgmann R, Herring
  T. Far-reaching transient motions after Mojave earthquakes require
  broad mantle flow beneath a strong crust. Geophys Res
  Lett. 2007;34:1-5. doi:10.1029/2007GL030959.

\bibitem[Rollins et al. (2015)]{R2015} Rollins, C., Barbot, S.,
  Avouac, J.P. Postseismic Deformation Following the 2010 M7.2 El
  Mayor-Cucapah Earthquake: Observations, Kinematic Inversions, and
  Dynamic Models. 2015. \textit{Pure Appl Geophys.}
  doi:10.1007/s00024-014-1005-6.

\bibitem[Savage and Svarc (2009)]{SS2009} Savage, J.C. and Svarc,
  J.L. Postseismic relaxation following the 1992 M 7 . 3 Landers and
  1999 M 7.1 Hector Mine earthquakes, southern California. 2009. 114,
  1-12. doi:10.1029/2008JB005938.

\bibitem[Spliner et al. (2015)]{S2015} Spliner, J.C., Bennett, R.A.,
  Walls, C., Lawrence, S., Garcia, J.J.G. Assessing long-term
  postseismic deformation following the M7.2 April 2010, El
  Mayor-Cucapah earthquake with implications for lithospheric rheology
  in the Salton Trough. 2015. \textit{J Geophys Res.}
  2015. doi:10.1002/2014JB011613.Received.

\bibitem[Gonzalez-Ortega et al. (2014)]{GO2014} Gonzalez-Ortega A.,
  Fialko, Y., Sandwell D., et al. El Mayor-Cucapah (mw7.2) earthquake:
  Early near-field postseismic deformation from the InSAR and GPS
  observations. 2014. \textit{J Geophys Res.} 119,
  1482-1497. doi:10.1002/2013JB010193

\bibitem[Oskin et al. (2012)]{O2012} Oskin, M.E., Arrowsmith, R.,
  Corona A.H., et al. 2012. Near-Field Deformation from the El
  Mayor-Cucapah Earthquake Revealed by Differential
  LIDAR. \textit{Science}. February,
  702-705. doi:10.1126/science.1213778.

\bibitem[Wei et al. (2011)]{W2011} Wei, S., Fielding, E., Leprince,
  S., et al 2011. Superficial simplicity of the 2010 El Mayor–Cucapah
  earthquake of Baja California in Mexico. \textit{Nat
  Geosci}, 4, 615-618, doi: 10.1038/ngeo1213.

\bibitem[Aagard et al. (2013)]{A2007} Aagaard, B.T., Knepley, M.G. \&
  Williams, C.A., 2013. A domain decomposition approach to
  implementing fault slip in finite-element models of quasi-static and
  dynamic crustal deformation, \textit{J. Geophys.  Res. Solid Earth},
  118, doi: 10.1002/jgrb.50217.

\end{thebibliography}
\end{document}

### 2016-03-13 RoughDraft/ElMayor.tex
commit before push

@@
 \section*{Introduction}
+\begin{figure}
+\includegraphics[scale=0.2]{Figures/ContextMap}
+\centering
+\caption{test}
+\end{figure}
+  sdfdf
+
+Previous studies which have modeled postseismic deformation following the El Mayor-Cucapah earthquake include \cite{Pollitz2012}, \cite{Gonzalez-ortega2014}, \cite{Spinler2015}, and \cite{Rollins2015}.
+\cite{Gonzalez-ortega2014} was able to describe five months of near field ($\lesssim 50$ km from the epicenter) postseismic defomation observed by InSAR and campaign GPS with afterslip and fault contraction on the coseismically ruptured fault.
+\cite{Gonzalez-ortega2014} also noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
+Using continuous GPS stations within 200 km of the El Mayor-Cucapah epicent, which consists mostly of stations north of the US-Mexico border, \cite{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip in an elastic lithosphere, albeit with an implausibly large amount of afterslip inferred on the least constrained southern most fault segment which may be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
+In this paper, we reiterate this finding by \cite{Rollins2015} and note that a purely elastic dislocation model is incapable of describing deformation observed at GPS stations greater than ~200 km from the El Mayor-Cucapah epicenter.
+
+Given the inability to describe both near and far field deformation with fault slip in an elastic lithosphere, \cite{Pollitz2012}, \cite{Rollins2015} and \cite{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential deformation mechanism.
+The lithospheric rheology is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and find the best fitting model parameters, which is generally a computationally expensive nonlinear inverse problem.
+Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
+For example, it is commonly assumed that the lithosphere consits of only three homogeneously Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \cite{Hines2013}\cite{Riva2009}.
+Additionally, it is necessary to make simplifying assumptions about the nature of afterslip.
+For example \cite{Pollitz2012} and \cite{Spinler2015} assumed that afterslip does not persist beyond six months and one year respectively and subsequent displacements were assumed to be the result of only viscoelastic relaxation.
+However, numerous observations of interseismic fault creep has been recognized in this and similar tectonic settings and it has been speculated that such creep can be initiated as a postseismic process \cite{Cakir2012} \cite{Cetin2014}.
+We are unaware of any oIn this study, we therefore do not make to implicit assumption that afterslip terminates after a given amount of time.
+Indeed, the preferred viscoelastic model from \cite{Pollitz2012} underpredicts near field velocities, which could be indicative of unmodeled continued afterslip.
+
+All of the aforementioned studies model displacements observered at stations within 200 km of the El Mayor-Cucapah epicenter, while postseismic deformation in this region following previous earthquakes of similar magnitude has been observed at distances extended out to about 300 km \cite{Freed2007a}.
+In the present study we examine stations within 400 km of the El Mayor-Cucapah epicenter, which turns out to be crucial for discerning the postseismic deformation mechanism.
+
+Clearly, both afterslip and viscoelastic relaxation are involved in postseismic deformation neglecting to model one of these deformation mechanisms could result in a biased estimate of the other.
+In this paper we use the inverse method described in \cite{Hines2015} to estimate the afterslip an effective viscosity necessary to describe the transience postseismic deformation over the first ten months after the El Mayor-Cucapah earthquake.
+We then form a suite of models which have various lithospheric rheologies but viscosities that are consistent with the effective viscosity estimated from the early postseismic deformation.
+Of the suite of models tested, we find that five years of postseismic deformation can be explained by a combination of sustained afterslip on the coseismicly ruptured fault and a Zener rheology upper mantle with viscosity that decays from $4\times10^{18}$ to $1\times10^{18}$ Pa s.
 
@@
 
-  We use continuous GPS position time series provided by University
-  Navstar Consortium (UNAVCO) for Plate Boundary Observatory (PBO)
-  stations within a 400 km radius about the El Mayor-Cucapah
-  epicenter. Our analysis is on the coseismic and postseismic
-  deformation resulting from the EMC earthquake, which we collectively
-  describe as $u(t)$. We consider GPS position time series,
-  $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular
-  tectonic deformation, annual and semi-annual fluctuations, and
-  coseismic offsets from sigificant earthquakes over the time span of
-  this study.  The June 14, 2010 Mw5.8 Ocotillo earthquake and the
-  August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3
-  event, are the only earthquakes after the EMC earthquake that
-  produced noticeable offsets recorded by GPS. Although the Ocotillo
-  earthquake had its own series of aftershocks (Haukson), neither
-  earthquake produced transient deformation that is detectable with
-  GPS. We thus model $u_\mathrm{obs}(t)$ as 
+We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for Plate Boundary Observatory (PBO) stations within a 400 km radius about the El Mayor-Cucapah epicenter.
+Our analysis is on the coseismic and postseismic deformation resulting from the EMC earthquake, which we collectively describe as $u(t)$.
+We consider GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular tectonic deformation, annual and semi-annual fluctuations, and coseismic offsets from sigificant earthquakes over the time span of this study.
+The June 14, 2010 Mw5.8 Ocotillo earthquake and the August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3 event, are the only earthquakes after the EMC earthquake that produced noticeable offsets recorded by GPS.
+Although the Ocotillo earthquake had its own series of aftershocks (Haukson), neither earthquake produced transient deformation that is detectable with GPS.
+We thus model $u_\mathrm{obs}(t)$ as
+
 \begin{equation}\label{TimeSeriesModel}
@@
 \end{equation}
-  Where $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the
-  Ocotillo earthquake and Brawley swarm respectively, $H(t)$ is the
-  Heaviside function, $c_0$ through $c_7$ are unknown coefficients,
-  and $\epsilon$ is noise with zero mean and variance that is assumed
-  known.
+Where $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the Ocotillo earthquake and Brawley swarm respectively, $H(t)$ is the Heaviside function, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is noise with zero mean and variance that is assumed known.
 
-  Stations which recorded signals that clearly cannot be described by
-  the aforementioned processes are not included in our analysis. This
-  includes stations in the Los Angeles basin, which record deformation
-  that is largely anthropogenic. In order to ensure an accurate
-  estimation of the secular deformation, we only use stations that
-  were installed at least six months prior to El Mayor-Cucapah
-  earthquake. While several stations were installed after the EMC
-  earthquake to improve the spatial resolution of postseismic
-  deformation \cite{S2015}, our inverse method uses postseismic
-  displacements rather than velocities (e.g. Pollitz), which requires
-  the knowledge of the stations preseismic position. Despite our
-  inability to utilize potentially rich data, we prefer to use
-  postseismic displacements rather than potentially dubious estimates
-  of postseismic velocities.
+Stations which recorded signals that clearly cannot be described by the aforementioned processes are not included in our analysis.
+This includes stations in the Los Angeles basin, which record deformation that is largely anthropogenic.
+In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
+While several stations were installed after the EMC earthquake to improve the spatial resolution of postseismic deformation \cite{Spinler2015}, our inverse method uses postseismic displacements rather than velocities (e.g.
+...), which requires the knowledge of the stations preseismic position.
+Despite our inability to utilize potentially rich data, we prefer to use postseismic displacements rather than potentially dubious estimates of postseismic velocities.
 
-  The October 16, 1999 Hector Mine earthquake, which occurred within
-  our study region about 270 km north of the EMC epicenter, has
-  produce transient postseismic deformation which we do not wish to
-  model either mechanically or through empirical line fitting. We thus
-  restrict our analysis to deformation observed six years after the
-  Hector Mine earthquake, past which point postseismic deformation for
-  nearfield sites occurs at an approximately steady rate
-  \cite{SS2009}. When considering stations further away from the
-  Hector Mine epicenter, postseismic transience persists for only
-  about two years \cite{S2015}.
+The October 16, 1999 Hector Mine earthquake, which occurred within our study region about 270 km north of the EMC epicenter, has produce transient postseismic deformation which we do not wish to model either mechanically or through empirical line fitting.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, past which point postseismic deformation for nearfield sites occurs at an approximately steady rate \cite{Savage2009}.
+When considering stations further away from the Hector Mine epicenter, postseismic transience persists for only about two years \cite{Spinler2015}.
 
-  We do not assume a parametric form for $u(t)$, (e.g. \cite{R2015}),
-  but rather we model $u(t)$ as integrated Brownian motion, so that
+We do not assume a parametric form for $u(t)$, (e.g. \cite{Rollins2015}), but rather we model $u(t)$ as integrated Brownian motion, so that 
 \begin{equation}
@@
 \end{equation}
-  where $w(t)$ is white noise and the variance of $\dot{u}(t)$
-  increases linearly with time by a factor of $\sigma^2$. We use a
-  Kalman filtering approach to estimate $u(t)$ and the unknown
-  parameters in eq. \ref{TimeSeriesModel} which we describe now.
 
-  In the context of Kalman filtering, our time varying state vector is
+where $w(t)$ is white noise and the variance of $\dot{u}(t)$ increases linearly with time by a factor of $\sigma^2$. We use a
+Kalman filtering approach to estimate $u(t)$ and the unknown parameters in eq. \ref{TimeSeriesModel} which we describe now.  In the context of Kalman filtering, our time varying state vector is
 \begin{equation}
@@
 \end{equation}
-  and eq. \ref{TimeSeriesModel} is the observation function which maps
-  the state vector to the GPS observations. We initiate the Kalman
-  filter by assuming a prior estimate of $\mathbf{X}(t)$ at time $t_0$ which
-  has a sufficiently large covariance to effectively make our prior
-  uninformed.  For each time epoch, $t_i$, Bayesian linear regression
-  is used to incorperate GPS derived estimates of displacement with
-  our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a postserior
-  estimate of the state, $\mathbf{X}_{i|i}$, which has covariance
-  $\mathbf{\Sigma}_{i|i}$.
+and eq.
+\ref{TimeSeriesModel} is the observation function which maps the state vector to the GPS observations.
+We initiate the Kalman filter by assuming a prior estimate of $\mathbf{X}(t)$ at time $t_0$ which has a sufficiently large covariance to effectively make our prior uninformed.
+For each time epoch, $t_i$, Bayesian linear regression is used to incorperate GPS derived estimates of displacement with our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a postserior estimate of the state, $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
 
-  We then use the posterior estimate of the state at time $t_i$ to
-  form a prior estimate of the state at time $t_{i+1}$ through the
-  transition function
+We then use the posterior estimate of the state at time $t_i$ to form a prior estimate of the state at time $t_{i+1}$ through the transition function
 \begin{equation}\label{predict}
@@
 \end{equation}
-  and $\mathbf{\delta}_{i+1}$ is the process noise, which has zero
-  mean and covariance described by
+and $\mathbf{\delta}_{i+1}$ is the process noise, which has zero mean and covariance described by
 \begin{equation}
@@
 
-  This process is repeated for each of the $N$ time epochs at which
-  point we use Rauch-Tung-Striebel smoothing to find $X_{i|N}$, which
-  is an estimate of the state at time $t_i$ that incorporates all $N$
-  GPS observation.  Our final estimates of $u(t)$ are used in
-  subsequent analysis, while the remaining components of of the state
-  vector are considered nuisance parameters. In the interests of
-  computational tractability, we downsample our smoothed time series
-  from daily solutions down to weekly solutions.
+This process is repeated for each of the $N$ time epochs at which point we use Rauch-Tung-Striebel smoothing to find $X_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates all $N$ GPS observation.
+Our final estimates of $u(t)$ are used in subsequent analysis, while the remaining components of of the state vector are considered nuisance parameters.
+In the interests of computational tractability, we down sample our smoothed time series from daily solutions down to weekly solutions.
 
-  We illustrate the effect of filtering in figure ().  We assume a
-  constant $\sigma^2$ for each station, which is chosen to be just
-  large enough for the earliest transient deformation at the most
-  nearfield site, P496?, to be faithfully described by the filtered
-  solution.
+The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
+As one endmember, setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line.
+The other endmember, where $\sigma^2$ is infinitely large, will result in $u(t)$ fitting what is obviously noise in the data.
+While one can use a maximum likelihood based approach to picking $\sigma^2$ (e.g.
+\cite{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
+This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signla.
+Figure 1 shows the ....
+While formal errors are estimated for $u(t)$ it is important to know that the true uncertainty in $u(t)$ is much larger due to assumptions made in formulating eq.
+(1).
+For example, we assume that the background rate of tectonic deformation can be approximated a linear rate, while is appears to hold true based on inspection of the time series, mechanical models would suggest this to not be true on earthquake cycle timescales
+
+We illustrate the effect of filtering in figure ().
+We assume a constant $\sigma^2$ for each station, which is chosen to be just large enough for the earliest transient deformation at the most nearfield site, P496?, to be faithfully described by the filtered solution.
 
@@
 \section*{Postseismic Modeling}
-  We use a fault geometry from \cite{W2011}, which was determined
-  using teleseismic, GPS, and InSAR data.
 
-  After the El Mayor-Cucapah earthquake, additional GPS stations were
-  installed In Baja California to record postseismic deformation with
-  better spatial coverage.  Two of the stations PTAX and PHJX were
-  installed near the epicenter in the Cucapah Mountains.  We do not
-  include these two stations in our analysis because the geometry of
-  the faults that ruptured during the earthquake is more complicated
-  than our assumed fault geometry \cite{O2012} and the near field
-  stations would be most sensitive to error in our geometry. We also
-  leave of these near field stations in order to avoid any near field
-  processes which we do not consider in this paper \cite{GO2014}.
+We use a fault geometry from \cite{Wei2011}, which was determined using teleseismic, GPS, and InSAR data.
 
-  Numerous stations exhibit extraneous signals which can be at  
-  \cite{A2007}
+After the El Mayor-Cucapah earthquake, additional GPS stations were installed In Baja California to record postseismic deformation with better spatial coverage.
+Two of the stations PTAX and PHJX were installed near the epicenter in the Cucapah Mountains.
+We do not include these two stations in our analysis because the geometry of the faults that ruptured during the earthquake is more complicated than our assumed fault geometry \cite{Oskin2012} \cite{Fletcher2014} and the near field stations would be most sensitive to error in our geometry.
+We also leave of these near field stations in order to avoid any near field processes which we do not consider in this paper \cite{Gonzalez-ortega2014}.
+Numerous stations exhibit extraneous signals which can be
 
@@
 \section*{Acknowledgements}
-  This material is based on EarthScope Plate Boundary Observatory data
-  services provided by UNAVCO through the GAGE Facility with support
-  from the National Science Foundation (NSF) and National Aeronautics
-  and Space Administration (NASA) under NSF Cooperative Agreement
-  No. EAR-1261833.
 
-\begin{thebibliography}{}
+This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.
+EAR-1261833.
 
-\bibitem[Freed et al. (2007)]{F2007} 1. Freed AM, Bürgmann R, Herring
-  T. Far-reaching transient motions after Mojave earthquakes require
-  broad mantle flow beneath a strong crust. Geophys Res
-  Lett. 2007;34:1-5. doi:10.1029/2007GL030959.
+\bibliographystyle{apalike}
+\bibliography{mybib}
 
-\bibitem[Rollins et al. (2015)]{R2015} Rollins, C., Barbot, S.,
-  Avouac, J.P. Postseismic Deformation Following the 2010 M7.2 El
-  Mayor-Cucapah Earthquake: Observations, Kinematic Inversions, and
-  Dynamic Models. 2015. \textit{Pure Appl Geophys.}
-  doi:10.1007/s00024-014-1005-6.
-
-\bibitem[Savage and Svarc (2009)]{SS2009} Savage, J.C. and Svarc,
-  J.L. Postseismic relaxation following the 1992 M 7 . 3 Landers and
-  1999 M 7.1 Hector Mine earthquakes, southern California. 2009. 114,
-  1-12. doi:10.1029/2008JB005938.
-
-\bibitem[Spliner et al. (2015)]{S2015} Spliner, J.C., Bennett, R.A.,
-  Walls, C., Lawrence, S., Garcia, J.J.G. Assessing long-term
-  postseismic deformation following the M7.2 April 2010, El
-  Mayor-Cucapah earthquake with implications for lithospheric rheology
-  in the Salton Trough. 2015. \textit{J Geophys Res.}
-  2015. doi:10.1002/2014JB011613.Received.
-
-\bibitem[Gonzalez-Ortega et al. (2014)]{GO2014} Gonzalez-Ortega A.,
-  Fialko, Y., Sandwell D., et al. El Mayor-Cucapah (mw7.2) earthquake:
-  Early near-field postseismic deformation from the InSAR and GPS
-  observations. 2014. \textit{J Geophys Res.} 119,
-  1482-1497. doi:10.1002/2013JB010193
-
-\bibitem[Oskin et al. (2012)]{O2012} Oskin, M.E., Arrowsmith, R.,
-  Corona A.H., et al. 2012. Near-Field Deformation from the El
-  Mayor-Cucapah Earthquake Revealed by Differential
-  LIDAR. \textit{Science}. February,
-  702-705. doi:10.1126/science.1213778.
-
-\bibitem[Wei et al. (2011)]{W2011} Wei, S., Fielding, E., Leprince,
-  S., et al 2011. Superficial simplicity of the 2010 El Mayor–Cucapah
-  earthquake of Baja California in Mexico. \textit{Nat
-  Geosci}, 4, 615-618, doi: 10.1038/ngeo1213.
-
-\bibitem[Aagard et al. (2013)]{A2007} Aagaard, B.T., Knepley, M.G. \&
-  Williams, C.A., 2013. A domain decomposition approach to
-  implementing fault slip in finite-element models of quasi-static and
-  dynamic crustal deformation, \textit{J. Geophys.  Res. Solid Earth},
-  118, doi: 10.1002/jgrb.50217.
-
-\end{thebibliography}
 \end{document}

### 2016-03-14 RoughDraft/ElMayor.tex
commit before push

@@
 \section*{Introduction}
-\begin{figure}
-\includegraphics[scale=0.2]{Figures/ContextMap}
-\centering
-\caption{test}
-\end{figure}
-  sdfdf
 
@@
 
+\begin{equation}
+  u_\mathrm{obs}(t) = u_\mathrm{pred}(t) + \epsilon
+\end{equation}
+where
 \begin{equation}\label{TimeSeriesModel}
   \begin{split}  
-    u_\mathrm{obs}(t) = &u(t) + c_0 + c_1t + \\
+    u_\mathrm{pred}(t) = &u(t) + c_0 + c_1t + \\
                          &c_2\sin(2\pi t) + c_3\cos(2\pi t) + c_4\sin(4\pi t) + c_5\cos(4\pi t) + \\
-                       &c_6H(t-t_\mathrm{oc}) + c_7H(t-t_\mathrm{bs}) + \epsilon.
+                         &c_6H(t-t_\mathrm{oc}) + c_7H(t-t_\mathrm{bs}).
   \end{split}
 \end{equation}
-Where $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the Ocotillo earthquake and Brawley swarm respectively, $H(t)$ is the Heaviside function, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is noise with zero mean and variance that is assumed known.
+In the above equations, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the Ocotillo earthquake and Brawley swarm respectively, $H(t)$ is the Heaviside function, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is noise with zero mean and variance that assumed known.
 
@@
 
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/figure_1}
+\centering
+\caption{GPS displacement solution from UNAVCO (black) and predicted displacements after applying a Kalman filter where $\sigma^2=0.05 \mathrm{m}^2/\mathrm{yr}^3$.
+Red line indicates the time of the Ocotillo earthquake where a jump in the time series is estimated}
+\label{P496Fit}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/figure_2}
+\centering
+\caption{Postseismic displacements estimated after applying a Kalman filter to the GPS displacement solution from UNAVCO.
+Displacements shown have had a background secular trend removed as well as an estimated seasonal signal.}
+\label{P496PS}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/figure_3}
+\centering
+\caption{GPS displacement solution from UNAVCO (black) and predicted displacements after applying a Kalman filter where $\sigma^2=0.05 \mathrm{m}^2/\mathrm{yr}^3$.
+Red line indicates the time of the Ocotillo earthquake where a jump in the time series is estimated}
+\label{P619Fit}
+\end{figure}
+
+\begin{figure}
+
+\includegraphics[scale=0.6]{Figures/figure_4}
+\centering
+\caption{Postseismic displacements estimated after applying a Kalman filter to the GPS displacement solution from UNAVCO.
+Displacements shown do not include the estimated secular trend, seasonal signals, and displacements resulting from the Ocotillo earthquake.}
+\label{P619PS}
+\end{figure}
+
 The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
-As one endmember, setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line.
-The other endmember, where $\sigma^2$ is infinitely large, will result in $u(t)$ fitting what is obviously noise in the data.
+Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation \cite{Savage2005a}.
+The other endmember, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
 While one can use a maximum likelihood based approach to picking $\sigma^2$ (e.g.
 \cite{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
-This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signla.
-Figure 1 shows the ....
-While formal errors are estimated for $u(t)$ it is important to know that the true uncertainty in $u(t)$ is much larger due to assumptions made in formulating eq.
-(1).
-For example, we assume that the background rate of tectonic deformation can be approximated a linear rate, while is appears to hold true based on inspection of the time series, mechanical models would suggest this to not be true on earthquake cycle timescales
+This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal.
+We find that when using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$, we are able to adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{P496Fit}).
+Since we assume that the first week of deformation is overwhelmingly the result of afterslip, any unmodeled afterslip over the first week following the El Mayor-Cucapah earthquake will be added into our estimates of coseismic slip in section ().
+Figure \ref{P496PS} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with its formal uncertainties.
 
-We illustrate the effect of filtering in figure ().
-We assume a constant $\sigma^2$ for each station, which is chosen to be just large enough for the earliest transient deformation at the most nearfield site, P496?, to be faithfully described by the filtered solution.
+It is important to note that the shown uncertainties in $u(t)$ do not account for our uncertainty in eq.
+\ref{TimeSeriesModel}.
+For example, we assume that the background rate of deformation can be approximated as having a constant rate, while mechanical models would suggest this to not be true on earthquake cycle timescales \cite{Thatcher1983}.
+Although based on inspection,  assuming a constant rate of background deformation appears to be appropriate for all stations except for perhaps the stations closest to the Hector Mine epicenter, where postseismic deformation persists.
+Also, our model for seasonal deformation in eq.
+\ref{TimeSeriesModel} assumes a constant amplitude over time, which means that years of particularly heavy or light rainfall cannot be adequately described.
+This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (figure \ref{P619PS}).
+
+note that stations jumps are only estimated for stations within 40 km of BS or OC
 
@@
 
-\section*{Observations}
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/near_field_data_1}
+\centering 
+\caption{near field coseismic}
+\label{nearfield1}
+\end{figure}
 
-\section*{Prior Studies}
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/near_field_data_2}
+\centering 
+\caption{near field coseismic}
+\label{nearfield2}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/near_field_data_3}
+\centering 
+\caption{near field coseismic}
+\label{nearfield3}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/near_field_data_4}
+\centering 
+\caption{near field coseismic}
+\label{nearfield4}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/far_field_data_1}
+\centering 
+\caption{near field coseismic}
+\label{farfield1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/far_field_data_2}
+\centering 
+\caption{near field coseismic}
+\label{farfield2}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/far_field_data_3}
+\centering 
+\caption{near field coseismic}
+\label{farfield3}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6]{Figures/far_field_data_4}
+\centering 
+\caption{near field coseismic}
+\label{farfield4}
+\end{figure}
+
+We show the difference in $u(t)$ for each station from 0 to 0.8 years (figure \ref{nearfield2} and \ref{farfield2}), 0.8 to 3.2 years (figure \ref{nearfield3} and \ref{farfield3}), and from 3.2 to 5.0 years (figure \ref{nearfield4} and \ref{farfield4}).
+For far field stations (figure \ref{farfield2}, \ref{farfield3}, and \ref{farfield4}), we can see a clear south trending displacement throughout the first 3.2 years in stations as far as 400 km from of the El Mayor Cucapah epicenter.
+These displacements are most pronounced along the direction of the El Mayor-Cucapah P and S axis, as would be expected for postseismic deformation.
+Beyond 3.2 years, The southward trending far field postseismic deformation is barely perceptible.
+There is however, an eastward trend in far field stations just west of the Hector Mine epicenter.
+We suspect this this deformation, which is inconsistent with the pattern expected for El Mayor-Postseismic, is the result of continued transient postseismic deformation following the Hector Mine earthquake.
+The vertical deformation in the far field is difficult to attribute to postseismic processes.
+Most far field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
+This trend in vertical deformation can be observed in all three of the qaudrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
+Although we use vertical deformation in our subsequent analysis, we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
+
+Near field deformation is show in figures \ref{nearfield2}, \ref{nearfield3}, and \ref{nearfield4}.
+The near field deformation is notably sustained when compared to the far field deformation.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of ~1.4 cm/yr to the south five years after the El Mayor-Cucapah earthquake.
+Vertical postseismic deformation in the near field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
+However, the vertical postseismic deformation signal is only apparent in the early postseismic period (figure \ref{nearfield2}).
+As with the far field deformation, there is a general trend of uplift in the near field one year after the earthquake which we do not consider to be related to postseismic processes.
 
 \section*{Postseismic Modeling}
+
+outline:
+
+-dismiss poroelastic rebound
+
+-Discuss justification of afterslip as a mechanism
+ -vertical deformation argument
+ -Kayla's paper and Haukson
+ -discuss fault geometry
+
+-Discuss viscoelastic relaxation
+  - discuss rheologic models and parameters needed to estimate
+
+-Discuss approximation, implications for all rheologic models
+-discretization of the lithosphere
+-discuss the nitty gritty inverse method
+
+- issue with nonuniqueness of deep afterslip and crustal flow
+
+-discuss fault geometry and modeling assumptions. including elastic properties. and Kayla's paper
+
+-Discuss discretization of slip and viscosity
+
+-discuss early postseismic approximation
+
+In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah.
+We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechansism.
+Poroelastic has also been used to model postseismic deformation (cite); however, the analysis of \cite{Gonzalez-ortega2014} suggests found that any contribution to postseismic deformation from poroelastic rebound would be negligable.
+Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
+
+In this study we estimate coseismic and time dependent postseismic fault slip, both which are assumed to occur on the fault geometry estimated by \cite{Wei2011a} with some modifications.
+Field studies and other coseismic slip models have found a significantly more complicated geometry for the coseismically ruptured fault \cite{Fletcher2009} \cite{Oskin2012}; however, the relatively simple coseismic fault geometry from \cite{Wei2011a} is sufficient to describe the data in this study because most of the stations used here are sufficiently far from the epicenter that they are insensitive to the detailed fault geometry found by \cite{Fletcher2009} and \cite{Oskin2012}.
+We do, however, modify the fault geometry from \cite{Wei2011a} by extending segment 2 northward by 40 km which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
+This extended fault segment was also found to be necessary by \cite{Rollins2015} and \cite{Pollitz2012} for describing postseismic deformation.
+
+To model postseismic deformation we must first assume a rheologic model.
+The simplest viscoelastic rheologic model would be a Maxwell model, where shear stresses and strains can be described with the mechanical analogy of a spring and dashpot connected in series.
+If coseismic and postseismic slip, described by $s(\xi,t)$, occurs on a fault $F$, and viscoelastic relaxation of subsequent stresses occurs in a Maxwell viscoelastic medium $L$, which has a spatially variable viscosity, $\eta(\zeta)$, then coseismic and postseismic deformation can be described by
+\begin{equation}\label{GeneralForward}
+  u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
+           \int_0^t\int_F s(\tau,\xi) f(t-\tau,x,\xi) d\xi d\tau
+\end{equation}
+where $g(x,\xi)$ is the elastic Green's function relating slip at $\xi$ to instantaneous displacement at $x$ and $f(t,x,\xi)$ describes the rate of deformation at $x$ and time $t$ resulting from viscoelastic relaxation of stresses induced by slip  at $\xi$.
+The variables which we are primarily concerned with estimating in this study are $s(\xi,t)$ and $\eta(\zeta)$.
+Numerous experimental and geophysical studies suggest that a Maxwell rheology is inappropriate to describe the behaviour of the uppermost mantle \cite{Chopra1997} \cite{Pollitz2003} \cite{Freed2004} and so we do not limit ourselves to exploring Maxwell viscolesticity.
+When considering other stress-linear viscoelastic models, such as a Zener or Burgers model, the description of displacements remains unchanged from eq \ref{GeneralForward} except that $f$ is parameterized by additional rheologic parameters which must also be estimated.
+The difficulty in  determining an appropriate rheologic model and then estimating $s(\xi,t)$ and the unkown rheologic parameters from observations of $u(x,t)$ is that it is a nonlinear inverse problem with many unknown parameters and a computationally expensive forward problem.
+We can greatly simplify the inverse problem by first considering the early postseismic period where we can approximate $u(x,t)$ for any stress-linear viscoelastic rheology as
+\begin{equation}\label{ApproxForward}
+  u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
+           \int_0^t\int_F\int_L \frac{s(\tau,\xi)}{\eta_\mathrm{eff}(\zeta)} h(x,\xi,\zeta) d\zeta d\xi d\tau
+\end{equation}
+
+It can be shown (\cite{Hines2015}),
+
+other rheologic models in this study      viscoelasticity is We also test rheologic models other than viscoelasticity to describe
+
+There are numerous other parameters which are not known, but will be considered known in this study.
+
+   Inherent in f is also a stress-linear viscoelastic model.   In this study we will be be known while try to consider
+
+Numerous researchers have used vertical deformation   
+as a discriminant for discerning whether afterslip or viscoelastic relaxation is the dominant postseismic mechanism (\cite{Hetland2014}, \cite{Pollitz2012} \cite{Rollins2015}).
+As noted by \cite{Rollins2015} the uplift just north of the epicenter is suggestive of afterslip at seismogenic depths, as opposed to deeper afterslip which would predict subsidence north of the fault.
+
+   The early near field postseismic vertical deformation does show a quadrant pattern and is also consistent with the coseismic vertical deformation.  Given
+
+that would not becomes there is no longer a coherent far field deformation signal.
+This is in contrast to near field displacements which persists for the entire 5.0 years of data used in this study.
+Figure () further illustrates the difference in deformation regimes between near field and far field station.
 

### 2016-03-18 RoughDraft/ElMayor.tex
commit before push

@@
 Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
-For example, it is commonly assumed that the lithosphere consits of only three homogeneously Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \cite{Hines2013}\cite{Riva2009}.
+For example, it is commonly assumed that the lithosphere consists of only three homogeneously Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \cite{Hines2013}\cite{Riva2009}.
 Additionally, it is necessary to make simplifying assumptions about the nature of afterslip.
-For example \cite{Pollitz2012} and \cite{Spinler2015} assumed that afterslip does not persist beyond six months and one year respectively and subsequent displacements were assumed to be the result of only viscoelastic relaxation.
+For example, one can assume a frictional model for afterslip and parameterize afterslip in terms its the unkown rheologic properties (e.g.
+\cite{Johnson2009} \cite{Johnson2004}).
+Additionally, one can assume that afterslip only dominates the first year of deformation (e.g.
+\cite{Pollitz2012} and \cite{Spinler2015}) and that viscoelastic relaxation is the dominant mechanism in later years.
 However, numerous observations of interseismic fault creep has been recognized in this and similar tectonic settings and it has been speculated that such creep can be initiated as a postseismic process \cite{Cakir2012} \cite{Cetin2014}.
@@
 
-We do not assume a parametric form for $u(t)$, (e.g. \cite{Rollins2015}), but rather we model $u(t)$ as integrated Brownian motion, so that 
+Studies of postseismic deformation typically assume a parametric form for $u(t)$ such as such as a logarithmic or exponential function.
+Such functions have been found empirically e.g.
+\cite{Savage2005a} and theoretically \cite{Marone1991} to adequately describe deformation resulting from postseismic deformation.
+However, by assuming a logarithmic or exponential form of $u(t)$ we run the risk of overfitting the GPS time series and inferring a nonexistent postseismic signal.
+We therefore do not assume any parameteric form for $u(t)$ and rather treat it as integrated Brownian motion, so that
 \begin{equation}
@@
 Most far field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
-This trend in vertical deformation can be observed in all three of the qaudrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
+This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
 Although we use vertical deformation in our subsequent analysis, we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
@@
 
-In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah.
-We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechansism.
-Poroelastic has also been used to model postseismic deformation (cite); however, the analysis of \cite{Gonzalez-ortega2014} suggests found that any contribution to postseismic deformation from poroelastic rebound would be negligable.
+In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake.
+We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechanisms.
+Poroelastic rebound has also been used to model postseismic deformation (cite); however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligable.
 Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
 
-In this study we estimate coseismic and time dependent postseismic fault slip, both which are assumed to occur on the fault geometry estimated by \cite{Wei2011a} with some modifications.
-Field studies and other coseismic slip models have found a significantly more complicated geometry for the coseismically ruptured fault \cite{Fletcher2009} \cite{Oskin2012}; however, the relatively simple coseismic fault geometry from \cite{Wei2011a} is sufficient to describe the data in this study because most of the stations used here are sufficiently far from the epicenter that they are insensitive to the detailed fault geometry found by \cite{Fletcher2009} and \cite{Oskin2012}.
+In this study we estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \cite{Wei2011a} with some modifications.
+Field studies \cite{Fletcher2014} and LIDAR observations \cite{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \cite{Wei2011a}, especially within the Sierra Cucapah.
+However, we find the relatively simple coseismic fault geometry from \cite{Wei2011a} to be sufficient because most of the stations used in this station are sufficiently far from the El Mayor-Cucapah epicenter that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
 We do, however, modify the fault geometry from \cite{Wei2011a} by extending segment 2 northward by 40 km which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
@@
 
+We consider a variety of rheologic models for the lithosphere and asthenosphere in this study.
+The simplest rheologic model would be to consider the lithospere and asthenosphere to be effectively elastic.
+In such case, the rheologic parameters, consisting of the Lame parameters, $\lambda$ and $\mu$, and density, $\rho$, are reasonably well known, leaving the only unknowns to be the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
+\cite{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be well explained with afterslip on the coseismicly ruptured fault, which has been extended down to the lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}, and they did not require any viscoelastic relaxation to describe the observations.
+They did however, find that the amount of afterslip required for the southernmost fault segment to be unrealistically large, equivalent to a Mw7.2 earthquake.
+Since most of the GPS data is located north of the rupture zone, slip on the Indiviso fault segment is least constrained and could be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
+
+It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, and so in the interest of preventing a non-unique solution, we assuming afterslip to occur only at seismogenic depths (<15 km), and allow for viscoelastic relaxation in the lower crust (15-30 km) depth and the upper mantle.We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
+Additionally, as noted by \cite{Rollins2015} the postseismic uplift just north of the rupture zone can be well described with slip at seismogenic depths, while afterslip which is constrained to depths beneath 15 km predicts subsidence in that region.
+
+A third reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and trying to simultaneously estimate deep afterslip and a lower crustal viscosity leads creates a significant null space.
+The reason for this is because viscoelastic relaxation within the lower crust of resulting from slip that is also within the lower crust will produce surface deformation in the direction opposite of slip.
+That is to say, the predicted viscoelastic deformation will cancel out the elastic deformation resulting in a trade off where a viscoelastic relaxation within a weak lower crust can be canceled out by slip at lower crustal depths.
+
+With afterslip constrained to shallow depths, we must now select a viscoelastic rheology for the lower crust and upper mantle.
+Maxwell viscoelasticity, which can be schematically illustrated as a spring and dashpot connected in series, is the simplest and commonly used rheologic model for studies on postseismic deformation NUR IS SLS!
+(e.g.
+\cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
+Assuming Maxwell viscoelasticity introduces a single the unknown rheologic parameter.
+A Maxwell viscoelastic model of the lithosphere would predict deformation that decays steadily over time, which fails to describe the multiple timescales of relaxation observed in postseismic deformation \cite{Savage1997}.
+An additional deficiency in modeling the lithosphere with a Maxwell rheology is that inferred viscosities tend to depend on the the timescale of the geophysical process being modelled \cite{Peltier1981}.
+When assuming Maxwell viscoselasticity, upper mantle viscosities for Southern California inferred from postseismic deformation tend to be on the order of $10^{18}$ Pa s (\cite{Pollitz2000}, \cite{Thatcher2008}, \cite{Spinler2015}.
+However, studies of interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+
+To account for the apparently multiple timescales of relaxation, \cite{Pollitz2003} used a Burgers rheology upper mantle to model postseismic deformation following the Hector Mine earthquake and inferred a transient viscosity of $1.6\times10^{17}$ Pa s and a steady state viscosity of $4.6\times10^{18}$ Pa s, which still falls short of the steady state viscosity required for longer term geophysical processes.
+The particularly weak transient viscosity was found to be necessary to describe the early rapid postseismic deformation, although other researchers have successfully described the early postseismic deformation for the same earthquake with fault creep and poroelastic rebound.
+Nevertheless, laboratory experiments have demonstrated that mantle rock exhibits two phases of relaxation which can be adequately described with a Burgers rheology \cite{Chopra1997} and we should expect to see some postseismic signal resulting from transience viscoelasticity.
+
+The third linear viscoelastic rheology which we consider is the Zener model, often referred to as a standard linear solid, whose mechanical analogue consists of a spring connected in series with a Kelvin element.
+A generalization of the Zener model, consisting of a series of Kelvin elements connected in series each of which representing a distinct deformation mechanism, is commonly used to describe the spectrum of frequency dependent attenuation \cite{Liu1976}.
+The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982}, which is too weak to be perceptible in the GPS data used in the present study.
+
+As an exploratory step, we also perform a slip inversion, assuming an elastic lithosphere and asthenosphere.
+The difference between the analysis in  \cite{Rollins2015} and the present study is that we include a wider range of GPS stations in our inversion and we also perform a temporal estimation of afterslip, as opposed to estimating slip at a single epoch.
+The material properties used in our inversion are given in table 1 and are consistent with the properties used by \cite{Wei2011a} and the 1D SCEC background velocity model.
+We discretize the
+
+ and the constrained and the only para.  where the rheologic parameters       
+In order to model postseismic deformation we must ddetermine an appropriate rheologic model for the lithosphere and asthenosphere.  
 To model postseismic deformation we must first assume a rheologic model.
@@
 
+what this gives us is a prior constraint on lithospheric viscosity initial that is unbiased by neglecting the contribution of afterslip!
+
 It can be shown (\cite{Hines2015}),
@@
    Inherent in f is also a stress-linear viscoelastic model.   In this study we will be be known while try to consider
-
-Numerous researchers have used vertical deformation   
-as a discriminant for discerning whether afterslip or viscoelastic relaxation is the dominant postseismic mechanism (\cite{Hetland2014}, \cite{Pollitz2012} \cite{Rollins2015}).
-As noted by \cite{Rollins2015} the uplift just north of the epicenter is suggestive of afterslip at seismogenic depths, as opposed to deeper afterslip which would predict subsidence north of the fault.
 

### 2016-03-24 RoughDraft/ElMayor.tex
new commit

@@
 \usepackage[usenames,dvipsnames]{color}
+\usepackage[maxfloats=50]{morefloats}
 
@@
 \maketitle
+\section*{Abstract}
+we propose a anelastic phase of deformation in the mantle distinct from phases associated with attenuation
+
 \section*{Introduction}
@@
 While several stations were installed after the EMC earthquake to improve the spatial resolution of postseismic deformation \cite{Spinler2015}, our inverse method uses postseismic displacements rather than velocities (e.g.
-...), which requires the knowledge of the stations preseismic position.
+...)
+ELABORATE ON VELOCITY VS DISPLACEMENT
+, which requires the knowledge of the stations preseismic position.
 Despite our inability to utilize potentially rich data, we prefer to use postseismic displacements rather than potentially dubious estimates of postseismic velocities.
@@
 
+The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
+Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation \cite{Savage2005a}.
+The other endmember, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
+While one can use a maximum likelihood based approach to picking $\sigma^2$ (e.g.
+\cite{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
+This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal.
+We find that when using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$, we are able to adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{P496Fit}).
+Since we assume that the first week of deformation is overwhelmingly the result of afterslip, any unmodeled afterslip over the first week following the El Mayor-Cucapah earthquake will be added into our estimates of coseismic slip in section ().
+Figure \ref{P496PS} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with its formal uncertainties.
+
+It is important to note that the shown uncertainties in $u(t)$ do not account for the non-negligible epistemic uncertainty in eq.
+\ref{TimeSeriesModel}.
+For example, we assume that the background rate of deformation can be approximated as having a constant rate, while mechanical models would suggest this to not be true on earthquake cycle timescales \cite{Thatcher1983}.
+Although based on inspection,  assuming a constant rate of background deformation appears to be appropriate for all stations except for perhaps the stations closest to the Hector Mine epicenter, where postseismic deformation persists.
+Also, our model for seasonal deformation in eq.
+\ref{TimeSeriesModel} assumes a constant amplitude over time, which means that years of particularly heavy or light rainfall cannot be adequately described.
+This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (figure \ref{P619PS}).
+
+note that stations jumps are only estimated for stations within 40 km of BS or OC
+
+Cite Freed 2007 for far reaching postseismic after Landers/Hector Mine.
+
+We show the difference in $u(t)$ for each station from 0 to 0.8 years (figure \ref{nearfield2} and \ref{farfield2}), 0.8 to 3.2 years (figure \ref{nearfield3} and \ref{farfield3}), and from 3.2 to 5.0 years (figure \ref{nearfield4} and \ref{farfield4}).
+For far field stations (figure \ref{farfield2}, \ref{farfield3}, and \ref{farfield4}), we can see a clear south trending displacement throughout the first 3.2 years in stations as far as 400 km from of the El Mayor Cucapah epicenter.
+These displacements are most pronounced along the direction of the El Mayor-Cucapah P and S axis, as would be expected for postseismic deformation.
+Beyond 3.2 years, The southward trending far field postseismic deformation is barely perceptible.
+There is however, an eastward trend in far field stations just west of the Hector Mine epicenter.
+We suspect this this deformation, which is inconsistent with the pattern expected for El Mayor-Postseismic, is the result of continued transient postseismic deformation following the Hector Mine earthquake.
+The vertical deformation in the far field is difficult to attribute to postseismic processes.
+Most far field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
+This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
+Although we use vertical deformation in our subsequent analysis, we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
+
+Near field deformation is show in figures \ref{nearfield2}, \ref{nearfield3}, and \ref{nearfield4}.
+The near field deformation is notably sustained when compared to the far field deformation.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of ~1.4 cm/yr to the south five years after the El Mayor-Cucapah earthquake.
+Vertical postseismic deformation in the near field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
+However, the vertical postseismic deformation signal is only apparent in the early postseismic period (figure \ref{nearfield2}).
+As with the far field deformation, there is a general trend of uplift in the near field one year after the earthquake which we do not consider to be related to postseismic processes.
+
+\section*{Postseismic Modeling}
+
+outline:
+
+-dismiss poroelastic rebound
+
+-Discuss justification of afterslip as a mechanism
+ -vertical deformation argument
+ -Kayla's paper and Haukson
+ -discuss fault geometry
+
+-Discuss viscoelastic relaxation
+  - discuss rheologic models and parameters needed to estimate
+
+-Discuss approximation, implications for all rheologic models
+-discretization of the lithosphere
+-discuss the nitty gritty inverse method
+
+- issue with nonuniqueness of deep afterslip and crustal flow
+
+-discuss fault geometry and modeling assumptions. including elastic properties. and Kayla's paper
+
+-Discuss discretization of slip and viscosity
+
+-discuss early postseismic approximation
+
+In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake.
+We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechanisms.
+Poroelastic rebound has also been used to model postseismic deformation \cite{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligable.
+Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
+
+\subsection{Fault Geometry}
+In this study we estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \cite{Wei2011a} with some modifications.
+Field studies \cite{Fletcher2014} and LIDAR observations \cite{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \cite{Wei2011a}, especially within the Sierra Cucapah.
+However, we find the relatively simple coseismic fault geometry from \cite{Wei2011a} to be sufficient because most of the stations used in this station are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
+We do, however, modify the fault geometry from \cite{Wei2011a} by extending segment 2 northward by 40 km which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
+This extended fault segment was also found to be necessary by \cite{Rollins2015} and \cite{Pollitz2012} for describing postseismic deformation.
+
+We consider a variety of rheologic models for the lithosphere and asthenosphere in this study.
+The simplest rheologic model would be to consider the lithospere and asthenosphere to be effectively elastic and isotropic.
+In such case, the rheologic parameters, consisting of the Lame parameters, $\lambda$ and $\mu$, and density, $\rho$, are reasonably well known, leaving the only unknowns to be the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
+\cite{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be well explained with afterslip on the coseismicly ruptured fault, which has been extended down to the lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}, and they did not require any viscoelastic relaxation to describe the observations.
+They did however, find that the amount of afterslip required for the southernmost fault segment to be unrealistically large, equivalent to a Mw7.2 earthquake.
+Since most of the GPS data is located north of the rupture zone, slip on the Indiviso fault segment is least constrained and could be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
+
+It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, at least in 2D earthquake models.
+In the interest of preventing a non-unique solution, we assuming afterslip to occur only at seismogenic depths (<15 km), and allow for viscoelastic relaxation in the lower crust (15-30 km) depth and the upper mantle.We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
+Additionally, as noted by \cite{Rollins2015} the postseismic uplift just north of the rupture zone can be well described with slip at seismogenic depths, while afterslip which is constrained to depths beneath 15 km predicts subsidence in that region.
+
+A third reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and trying to simultaneously estimate deep afterslip and a lower crustal viscosity leads creates a significant null space.
+The reason for this is because viscoelastic relaxation within the lower crust of resulting from slip that is also within the lower crust will produce surface deformation in the direction opposite of slip.
+That is to say, the predicted viscoelastic deformation will cancel out the elastic deformation resulting in a trade off where a viscoelastic relaxation within a weak lower crust can be canceled out by slip at lower crustal depths.
+
+\subsection{Rheologic Models}
+With afterslip constrained to shallow depths, we must now select a viscoelastic rheology for the lower crust and upper mantle.
+Maxwell viscoelasticity, which can be schematically illustrated as a spring and dashpot connected in series, is the simplest and commonly used rheologic model for studies on postseismic deformation (e.g.
+\cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
+The Maxwell model describes both an instantaneously elastic and fluid-like phase of deformation.
+Assuming Maxwell viscoelasticity introduces the additional rheologic parameter, $\eta_M$, which is typically estimated for the lower crust and upper mantle as an inverse problem, where the viscosities are chosen to minimize the difference between the observed postseismic deformation and deformation predicted by a mechanical model.
+A Maxwell viscoelastic model of the lithosphere would predict deformation that decays steadily over time, which fails to describe the observable deformation which exhibits transient deformation which decays rapidly within the first year of an earthquake followed by a relatively steady rate of deformaiton \cite{Savage1997}.
+An additional deficiency in describing postseismic deformation with viscoelastic relaxation in a Maxwell viscoselastic lithosphere is that inferred viscosities tend to be considerably lower than viscosities inferred from geophysical processes that occur over longer timescales.
+For example, postseismic studies in Southern California following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have all inferred a Maxwell viscoselastic upper mantle with a viscosities ranging from $10^{17}$ to $10^{18}$ Pa s; however, studies on interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+
+We also consider the Zener viscoelastic model whose mechanical analogue consists of a spring connected in series with a Kelvin element.
+The Zener model is used to describe both an instantaneous and delayed phase of elasticity.
+A generalization of the Zener model, consisting of numerous Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \cite{Liu1976}.
+The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982} and the largest characteristic relaxation time would be on the order of days, which is too short to be perceptible in the GPS data used in the present study.
+We therefor ignore the delayed elasticity associated with seismic attenuation models, and consider such models to be effectively instantaneously elastic.
+Nevertheless, we still explore the possibility of describing postseismic deformation with a Zener model that has relaxation timescales of months to years.
+
+Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid behaviour required for mantle dynamics on geologic time scales.
+\cite{Yuen1982} proposed a Burgers rheology with a low viscosity ($\approx 10^{16}$ Pa s) in the Kelvin element and high viscosity ($\approx 10^{21}$ Pa s) in the Maxwell element which is capable of describing both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
+The justification of a Burger's rheology mantle is further supported by laboratory experments on the strength of olivine \cite{Chopra1997}.
+\cite{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
+While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \cite{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \cite{Lundgren2009} and \cite{Luttrell2007}.
+Additionally, the transient viscosity inferred by \cite{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, while \cite{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \cite{Jacobs2002}.
+In this paper we seek to constrain the rheologic parameters describing a Burgers upper mantle that are consistent with postseismic deformation and long term geophysical processes, while also accounting  for shallow afterslip, which perhaps biased the solution from \cite{Pollitz2003}.
+
+\subsection{Constraint on Effective Viscosity}\label{InitialInversion}
+For the three linear viscoelastic rheologies described above, Maxwell, Zener, and Burgers, postseismic displacement resulting from time dependent fault slip, $s(\xi,t)$, on a fault $F$ can be described as
+\begin{equation}\label{GeneralForward}
+  u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
+           \int_0^t\int_F s(\tau,\xi) f(t-\tau,x,\xi) d\xi d\tau
+\end{equation}
+where $g(x,\xi)$ describes the instantaneous elastic displacements at $x$ resulting from a unit of slip at $\xi$, and $f(t,x,\xi)$ describes the velocity at $x$ resulting from viscoelastic relaxation of stresses induced by slip at $\xi$.
+$f$ is a function of the properties of the chosen rheologic model, which are generally not well known.
+The parameters controlling the instantaneous elastic behaviour of the lithosphere and asthenosphere, $\mu$, $\lambda$, and density $\rho$, are relatively well known and we use the values listed in table 1, which are consistent with the properties used in the coseismic model by \cite{Wei2011a} and the 1D SCEC background velocity model.
+The remaining rheologic parameter, which we will assume to have a depth dependence, are estimated to optimize the predicted fit to observable postseismic displacement.
+
+In order greatly simplify the posed inverse problem we use to method describe in \cite{Hines2015} to constrain the effective lithospheric viscosity structure for the early postseismic period.
+The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere, denoted at $L$, are controlled by the relatively well known instantaneous elastic properties.
+This means that the rate of deformation in each parcel of the lithosphere will deform at a rate that is inversely proportional to its effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$, and independent of $\eta_{\mathrm{eff}}$ elsewhere.
+Then, as a consequently of linear elasticity, the initial rate of surface deformation resulting from viscoelastic relaxation is a linear combination of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's viscosity.
+That is to say
+\begin{equation}\label{InitialRate}
+  f(0,x,\xi) = \int_L \frac{h(x,\xi,\zeta)}{\eta_\mathrm{eff}(\zeta)} d\zeta, 
+\end{equation}
+where $h(x,\xi,\zeta)$ describes the initial rate of deformation resultion from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and, most importantly, $h$ is independent of all rheologic properties other than those that control the instantaneous elastic behaviour, $\mu$, $\lambda$ and $\rho$.
+Subsitution eq.
+\ref{InitialRate} into \ref{GeneralForward} gives us an approximation for early postseismic deformation,
+\begin{equation}\label{ApproxForward}
+  u(x,t) \approx \int_F s(\xi,t)g(x,\xi)d\xi + 
+           \int_0^t\int_F\int_L \frac{s(\tau,\xi)}{\eta_\mathrm{eff}(\zeta)} h(x,\xi,\zeta) d\zeta d\xi d\tau,
+\end{equation}
+which is valid for as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
+Although eq.
+\ref{ApproxForward} may only valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are functions of the fault geometry and instantaneous elastic properties, which are fairly well known, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem, eq.
+\ref{ApproxForward}, can be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
+This is in contrast to evaluating the full forward problem, eq.
+\ref{GeneralForward}, numerically for each realization of $s$ and $\eta_{\mathrm{eff}}$ which is far more computationally demanding.
+
+We perform an initial inversion of postseismic displacements using eq.
+\ref{ApproxForward} as out forward problem.
+As noted, we use the fault geometry from \cite{Wei2011}, except that each segment extends to 15 km depth and segment 2 is extended 40 km northward.
+Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
+We estimate coseismic slip as well as a rate of afterslip which is constant over the time intervals spanning 0.0-0.125, 0.125-0.25, and 0.5-1.0 years following the earthquake, as well as over 1.0 year intervals for the remaining postseismic period.
+We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip for all segments except for segment 1, where slip is constrained be within $45^\circ$ of normal.
+We estimate $\eta_{\mathrm{eff}}$ within 6 vertically stratified layers which have depths ranging from 0-15 km, 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain, 800 km.
+Details of the inverse method are described in \cite{Hines2015}.
+We note that a nonlinear Kalman filter based inverse method can be employed to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \cite{Segall1997} or \cite{McGuire2003}, where we do not have to explicitly impose a time dependent parameterization of $s$.
+Indeed we have thoroughly explored that possibility but we ultimately prefer the method described in \cite{Hines2015} because of its relative simplicity and because we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general.
+
+The first step in our inverse method is to determine the time during the postseismic period at which point the early postseismic approximation, eq.
+\ref{ApproxForward}, is no longer approriate, which we will denote as $t_{\mathrm{end}}$.
+As noted, it is valid for approximately as long as the rate of deformation resulting for viscoelastic relaxation is approximately constant.
+We can almost certainly assume that deformation at the most far field stations which are ~400 km away from the El Mayor-Cucapah is the result of viscoelastic relaxation.
+Then the approximation should be valid for as long as a linear trend adequately approximates the far field deformation.
+Using this logic, it would appear that $t_{\mathrm{end}}$ is $\sim1$ year after the El Mayor-Cucapah earthquake.
+Another way to determine $t_{\mathrm{end}}$ is to find the best fitting prediction of eq.
+\ref{ApproxForward} to various durations of the postseismic timeseries and determine when eq.
+\ref{ApproxForward} is not longer capable of describing the deformation without incurring systematic misfits.
+This is illustrated in figures \ref{NearFieldRS} and \ref{FarFieldRS}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
+When using eq.
+\ref{ApproxForward} to fit the entire five years of postseismic displacement we see that the near field displacements, eg.
+station P501, are accurately predicted, as was also the case when modelling postseismic deformation with an elastic lithosphere.
+When looking at displacement in the far field, eg.
+station P621, we see that eq.
+\ref{ApproxForward} overestimates the rate of deformation in the later postseismic and underestimates the rate of deformation in the near field.
+As we progressively decrease the length of the postseismic timeseries used in the inversion, we see improved fit to the early postseismic period.
+Due to the low signal to noise ratio for far field stations, it is difficult to determine at what point eq.
+\ref{ApproxForward} is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{end}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
+As noted in \cite{Hines2015}, overestimating $t_{\mathrm{end}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{end}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$; although the uncertainties would be larger.
+We can then consider our subsequent inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the lithospheric strength needed to describe the far field rate of deformation during the first 0.8 years of postseismic deformation.
+
+We want to find the discretize parameters describing coseismic slip and the rate of afterslip, $\mathbf{s}$, and viscosity, $\mathbf{\eta_{\mathrm{eff}}}$, that minimize the difference between the each discrete observation of postseismic deformation over the first 0.8 years following the El Mayor-Cucapah earthquake, which is here denoted $\mathbf{u_\mathrm{obs}}$, and the discrete observations predicted in eq.
+\ref{ApproxForward}, $\mathbf{u_\mathrm{pred}}$.
+That is, we want to solve
+
+\begin{equation}\label{ObjectiveFunction}
+ \mathrm{min}_{\mathbf{s},\mathbf{\eta_\mathrm{eff}}} \left|\left|
+ \frac{\mathbf{u_\mathrm{pred}}(s,\eta_\mathrm{eff}) - \mathbf{u_\mathrm{obs}}}
+ {\mathbf{\sigma_\mathrm{obs}}}\right|\right|_2^2.
+\end{equation} 
+Due to inherent nonuniqueness in the solution to eq. \ref{ObjectiveFunction}, we add zeroth order Tikhonov regularization to estimates of slip,
+\begin{equation}\label{Misfit}
+||\lambda_s \mathbf{s}||_2^2=0,
+\end{equation}
+and second order Tikhonov regularization to estimates of effective fluidity, 
+\begin{equation}
+||\lambda_v \nabla \mathbf{\eta_{\mathrm{eff}}}^{-1}||_2^2=0.
+\end{equation}
+The degree to which we impose the regularization on slip and viscosity is controlled by the penalty parameters $\lambda_s$ and $\lambda_v$.
+The penalty parameters are chosen with two L-curve tests, where $\lambda_s$ is first chosen assuming $\lambda_v=0$, and then $\lambda_v$ is determined while keeping $\lambda_s$ at the chosen value.
+We note that our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do in a model space where eq.
+\ref{GeneralForward} is our forward problem in section \ref{FullInversion}.
+Estimates of $\mathbf{s}$ made here will not be used in section \ref{FullInversion}, and so the motivation behind even adding regularization to $\mathbf{s}$ is to ensure that the slip driving viscoelastic relaxation in eq.
+\ref{ApproxForward} are sensible.
+
+Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
+Although fluidities is a sparesly used metric, it is more natural to use fludities rather than viscosity since eq.
+\ref{InitialRate} is linear with respect to fluidity and so the fluidity represents the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere.
+We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_v$, and our choice our $\lambda_v$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
+It is therefore difficult to interpret the magnitude of uncertainties on viscosity shown in figure \ref{EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
+The uncertainties in fluidities increases with depth, as would be expected due to decreased sensitivity with depth.
+Nevertheless, a robust feature that we see in this that the viscosity below 60 km depth needs to be $\sim 10^{18}$ Pa s to describe the early rate of postseismic deformation for stations greater than $\sim 200$ km from the epicenter.
+The viscosity of the lower crust is the least well constrained as there is effectively no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years of postseismic, $> 10^{19}$ Pa s.
+Our inference of a mantle viscosity of $\sim 10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady state viscosities from \cite{Pollitz2000}, \cite{Pollitz2003}, \cite{Johnson2007}, \cite{Spinler2015}, and \cite{Rollins2015}.
+
+Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figures \ref{InitialCoseismic} and \ref{InitialAfterslip} respectively.
+To show the how our slip solution is influenced by allowing for a viscoelastic lithopshere, we have also show a coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but while assuming the lithosphere and ashthenosphere are elastic.
+In both coseismic inversion, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
+This is consistent with field studies, \cite{Fletcher2014} as well as coseismic slip models \cite{Wei2011}.
+The potency of inferred coseismic slip is $3.32\times 10^{9} \mathrm{m}^3$, which is equivalent to a moment magnitude of 7.28 when assuming a shear modulus of $3.2\times10^{10}$ Pa.
+The potency of the inferred coseismic slip model when assuming an elastic lithosphere is not significantly different, $3.55\times 10^9 \mathrm{m}^3$.
+The striking difference between the two models is that the inferred afterslip on the Indiviso fault segment is significantly larger when not accounting for viscoelasticity.
+The potency of afterslip in the elastic model is $2.7\times 10^9 \mathrm{m}^3$, compared to $0.85\times 10^9 \mathrm{m}^3$.
+The former is comparable to the size of the mainshock which, as noted by \cite{Rollins2015}, is implausibly large.
+The significant amount of afterslip on the Indiviso fault inferred by \cite{Rollins2015}, which is predicts broadscale deformation for the GPS stations used in this study, seems to be compensating for unmodeled viscoelastic relaxation at depths of $>60$ km.
+This inferred transitional depth is consistent with the regionally averaged lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}.
+The fact that there is still a substantial amount of deep afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than we allow for since we only estimate depth dependent variations in viscosity.
+
+\subsection{Full Inversion}\label{FullInversion}
+
+In the previous section we used the efficient inverse method described by \cite{Hines2015} to constrain the effective lithospheric viscosity required to explain the first 0.8 years of postseismic deformation.
+In this section we use the inferred effective lithospheric viscosities as a prior constraint when searching for rheologic models of the lithosphere which are capable of describing the available 5 years of postseismic data.
+
+Table 1 describes how the inferred effective viscosities from section \ref{InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
+In this section we perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from \ref{InitialInversion}.
+Our forward problem is now eq.
+\ref{GeneralForward} rather than the approximation given by eq.
+\ref{ApproxForward}.
+As a reference, we compare the best fit solution for each assumed lithospheric model to a the best fit solution assuming an entirely elastic lithosphere.
+One intuitive criterion for a viscoelastic lithospheric model to be plausible is that it should be able to predict observable deformation better than a lithospheric model which is elastic.
+
+We first assume that the crust and mantle can be described with a Maxwell rheology, and so inferences of $\eta_{\mathrm{eff}}$ are equivalent to inferences of $\eta_{\mathrm{M}}$.
+We compute $f$ and $g$ from eq.
+\ref{GeneralForward} using Pylith \cite{Aagaard2009} and assume the same spatial and temporal discretization of $s$ as in section \ref{InitialInversion}.
+The misfit, defined by eq.
+\ref{Misfit}, is X which significantly higher than that of the elastic model, X.
+It is apparent that most of the misfit comes from the Maxwell model significantly overestimating the rate of deformation after $\sim 3$ years following the earthquake.
+Although, the numerous studies have described postseismic deformation in Southern California using a Maxwell visocolatic rheology with viscosities consistent with ours, it is clear that such a model is incapable of describing the entire postseismic time series.
+As previously noted, \cite{Pollitz2001}, recognized this deficiency in a Maxwell rheology which motivated their exploration of a Burgers rheology upper mantle \cite{Pollitz2003}.
+
+Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener model, which only introduces the unknown paremeter $\mu_{k}$.
+We assume that the lower crust still has a Maxwell viscosity and $\eta_{M}$ is set equal to $\eta_{\mathrm{eff}}$.
+For a Zener model, the effective initial viscosity is $\eta_{K}$ and so we set $\eta_K$ equal to $\eta_{\mathrm{eff}}$ inferred from above.
+The unknown rheologic parameter which we estimate is the ratio of shear moduli, $\nu=\frac{\mu_K}{\mu_M}$.
+We compute nine different sets of Green's functions, $f$ and $g$, using Pylith where we assume different values of $\nu$ ranging from 0 to 1.
+The former being a degenerate case when the Zener model becomes the Maxwell model from above and the later being a Jeffreys solid.
+The misfit of the best fit models to the observed postseismic data when varying $\nu$ is shown in figure \ref{ShearRatio}.
+The optimal value of $\nu$ is found to be $0.375$ which decreases the misfit by only about \%10; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years.
+This significant improvement is seen for all shear modulus  ratios greater than $0.125$.
+
+Because we are able to adequately  describe the available 5 years of postseismic seismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
+However, since Zener model can be thought of as the limit when the steady state viscosity in a Burgers rheology is infinite, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in \ref{InitialInversion} and an effectively infinite steady state viscosity on the timescale of five years, $>10^{20}$ Pa s, would be also be able to satisfactorily describe the observable postseismic deformation.
+
+Satisfied with a Zener rheology for the mantle with shear modulus ratio of 0.375, our final step is to choose a damping parameter for out estimates of coseismic slip and afterslip, which has been fixed at 0 until now.
+We estimate the damping parameter, again enforcing smallness on our model, using another L-curve test.
+Our preferred model for coseismic slip and afterslip is shown in figure ?
+?
+and ?.
+
+\section{Discussion}
+
+what this gives us is a prior constraint on lithospheric viscosity initial that is unbiased by neglecting the contribution of afterslip!
+
+It can be shown (\cite{Hines2015}),
+
+other rheologic models in this study      viscoelasticity is We also test rheologic models other than viscoelasticity to describe
+
+There are numerous other parameters which are not known, but will be considered known in this study.
+
+   Inherent in f is also a stress-linear viscoelastic model.   In this study we will be be known while try to consider
+
+   give table of assumed and estimated material properties
+
+   The early near field postseismic vertical deformation does show a quadrant pattern and is also consistent with the coseismic vertical deformation.  Given
+
+that would not becomes there is no longer a coherent far field deformation signal.
+This is in contrast to near field displacements which persists for the entire 5.0 years of data used in this study.
+Figure () further illustrates the difference in deformation regimes between near field and far field station.
+
+note that subsidence in the peninsular range can be explained with either a localized weakness or conitnued afterslip at seismogenic depths
+
+We use a fault geometry from \cite{Wei2011}, which was determined using teleseismic, GPS, and InSAR data.
+
+make note of \cite{Yamagiwa2014}
+
+note that creep in Brawley is probably the main source of error
+
+After the El Mayor-Cucapah earthquake, additional GPS stations were installed In Baja California to record postseismic deformation with better spatial coverage.
+Two of the stations PTAX and PHJX were installed near the epicenter in the Cucapah Mountains.
+We do not include these two stations in our analysis because the geometry of the faults that ruptured during the earthquake is more complicated than our assumed fault geometry \cite{Oskin2012} \cite{Fletcher2014} and the near field stations would be most sensitive to error in our geometry.
+We also leave of these near field stations in order to avoid any near field processes which we do not consider in this paper \cite{Gonzalez-ortega2014}.
+Numerous stations exhibit extraneous signals which can be
+
+\section*{Acknowledgements}
+We are grateful to Andy Freed for an illuminating discussion on the material in this manuscript.
+
+This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.
+EAR-1261833.
+
+\bibliographystyle{apalike}
+\bibliography{mybib}
+
 \begin{figure}
@@
 \end{figure}
-
-The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
-Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation \cite{Savage2005a}.
-The other endmember, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
-While one can use a maximum likelihood based approach to picking $\sigma^2$ (e.g.
-\cite{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
-This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal.
-We find that when using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$, we are able to adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{P496Fit}).
-Since we assume that the first week of deformation is overwhelmingly the result of afterslip, any unmodeled afterslip over the first week following the El Mayor-Cucapah earthquake will be added into our estimates of coseismic slip in section ().
-Figure \ref{P496PS} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with its formal uncertainties.
-
-It is important to note that the shown uncertainties in $u(t)$ do not account for our uncertainty in eq.
-\ref{TimeSeriesModel}.
-For example, we assume that the background rate of deformation can be approximated as having a constant rate, while mechanical models would suggest this to not be true on earthquake cycle timescales \cite{Thatcher1983}.
-Although based on inspection,  assuming a constant rate of background deformation appears to be appropriate for all stations except for perhaps the stations closest to the Hector Mine epicenter, where postseismic deformation persists.
-Also, our model for seasonal deformation in eq.
-\ref{TimeSeriesModel} assumes a constant amplitude over time, which means that years of particularly heavy or light rainfall cannot be adequately described.
-This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (figure \ref{P619PS}).
-
-note that stations jumps are only estimated for stations within 40 km of BS or OC
-
-Cite Freed 2007 for far reaching postseismic after Landers/Hector Mine.
 
@@
 
-We show the difference in $u(t)$ for each station from 0 to 0.8 years (figure \ref{nearfield2} and \ref{farfield2}), 0.8 to 3.2 years (figure \ref{nearfield3} and \ref{farfield3}), and from 3.2 to 5.0 years (figure \ref{nearfield4} and \ref{farfield4}).
-For far field stations (figure \ref{farfield2}, \ref{farfield3}, and \ref{farfield4}), we can see a clear south trending displacement throughout the first 3.2 years in stations as far as 400 km from of the El Mayor Cucapah epicenter.
-These displacements are most pronounced along the direction of the El Mayor-Cucapah P and S axis, as would be expected for postseismic deformation.
-Beyond 3.2 years, The southward trending far field postseismic deformation is barely perceptible.
-There is however, an eastward trend in far field stations just west of the Hector Mine epicenter.
-We suspect this this deformation, which is inconsistent with the pattern expected for El Mayor-Postseismic, is the result of continued transient postseismic deformation following the Hector Mine earthquake.
-The vertical deformation in the far field is difficult to attribute to postseismic processes.
-Most far field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
-This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
-Although we use vertical deformation in our subsequent analysis, we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
+\begin{figure}
+\includegraphics[scale=0.8]{Figures/near_field_record_section}
+\centering 
+\caption{near field record section}
+\label{NearFieldRS}
+\end{figure}
+\begin{figure}
+\includegraphics[scale=0.8]{Figures/far_field_record_section}
+\centering 
+\caption{far field record section}
+\label{FarFieldRS}
+\end{figure}        
+\begin{figure}
 
-Near field deformation is show in figures \ref{nearfield2}, \ref{nearfield3}, and \ref{nearfield4}.
-The near field deformation is notably sustained when compared to the far field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of ~1.4 cm/yr to the south five years after the El Mayor-Cucapah earthquake.
-Vertical postseismic deformation in the near field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
-However, the vertical postseismic deformation signal is only apparent in the early postseismic period (figure \ref{nearfield2}).
-As with the far field deformation, there is a general trend of uplift in the near field one year after the earthquake which we do not consider to be related to postseismic processes.
+\includegraphics[scale=1.0]{Figures/slip_lcurve}
+\centering 
+\caption{near field record section}
+\label{SlipLCurve}
+\end{figure}
 
-\section*{Postseismic Modeling}
+\begin{figure}
+\includegraphics[scale=1.0]{Figures/fluidity_lcurve}
+\centering 
+\caption{far field record section}
+\label{FluidityLCurve}
+\end{figure}
 
-outline:
+\begin{figure}
+\includegraphics[scale=1.0]{Figures/effective_viscosity}
+\centering 
+\caption{effective viscosity}
+\label{EffectiveViscosity}
+\end{figure}
 
--dismiss poroelastic rebound
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/initial_coseismic}
+\caption{coseismic slip from initial inversion}
+\label{InitialCoseismic}
+\end{figure}
 
--Discuss justification of afterslip as a mechanism
- -vertical deformation argument
- -Kayla's paper and Haukson
- -discuss fault geometry
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/initial_afterslip}
+\centering 
+\caption{afterslip from initial inversion}
+\label{InitialAfterslip}
+\end{figure}
 
--Discuss viscoelastic relaxation
-  - discuss rheologic models and parameters needed to estimate
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/initial_elastic_coseismic}
+\centering 
+\caption{coseismic slip from elastic inversion}
+\label{InitialElasticCoseismic}
+\end{figure}
 
--Discuss approximation, implications for all rheologic models
--discretization of the lithosphere
--discuss the nitty gritty inverse method
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/initial_elastic_afterslip}
+\centering 
+\caption{afterslip from elastic inversion}
+\label{FluidityLCurve}
+\end{figure}
 
-- issue with nonuniqueness of deep afterslip and crustal flow
+\begin{figure}
+\includegraphics[scale=1.0]{Figures/shear_ratio}
+\centering 
+\caption{misfit with different shear modulus ratios}
+\label{ShearRatio}
+\end{figure}
 
--discuss fault geometry and modeling assumptions. including elastic properties. and Kayla's paper
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/final_coseismic}
+\centering 
+\caption{misfit with different shear modulus ratios}
+\label{ShearRatio}
+\end{figure}
 
--Discuss discretization of slip and viscosity
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/final_afterslip_0-1}
+\centering 
+\caption{misfit with different shear modulus ratios}
+\label{ShearRatio}
+\end{figure}
 
--discuss early postseismic approximation
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/final_afterslip_1-3}
+\centering 
+\caption{misfit with different shear modulus ratios}
+\label{ShearRatio}
+\end{figure}
 
-In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechanisms.
-Poroelastic rebound has also been used to model postseismic deformation (cite); however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligable.
-Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
-
-In this study we estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \cite{Wei2011a} with some modifications.
-Field studies \cite{Fletcher2014} and LIDAR observations \cite{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \cite{Wei2011a}, especially within the Sierra Cucapah.
-However, we find the relatively simple coseismic fault geometry from \cite{Wei2011a} to be sufficient because most of the stations used in this station are sufficiently far from the El Mayor-Cucapah epicenter that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
-We do, however, modify the fault geometry from \cite{Wei2011a} by extending segment 2 northward by 40 km which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
-This extended fault segment was also found to be necessary by \cite{Rollins2015} and \cite{Pollitz2012} for describing postseismic deformation.
-
-We consider a variety of rheologic models for the lithosphere and asthenosphere in this study.
-The simplest rheologic model would be to consider the lithospere and asthenosphere to be effectively elastic.
-In such case, the rheologic parameters, consisting of the Lame parameters, $\lambda$ and $\mu$, and density, $\rho$, are reasonably well known, leaving the only unknowns to be the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
-\cite{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be well explained with afterslip on the coseismicly ruptured fault, which has been extended down to the lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}, and they did not require any viscoelastic relaxation to describe the observations.
-They did however, find that the amount of afterslip required for the southernmost fault segment to be unrealistically large, equivalent to a Mw7.2 earthquake.
-Since most of the GPS data is located north of the rupture zone, slip on the Indiviso fault segment is least constrained and could be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
-
-It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, and so in the interest of preventing a non-unique solution, we assuming afterslip to occur only at seismogenic depths (<15 km), and allow for viscoelastic relaxation in the lower crust (15-30 km) depth and the upper mantle.We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
-Additionally, as noted by \cite{Rollins2015} the postseismic uplift just north of the rupture zone can be well described with slip at seismogenic depths, while afterslip which is constrained to depths beneath 15 km predicts subsidence in that region.
-
-A third reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and trying to simultaneously estimate deep afterslip and a lower crustal viscosity leads creates a significant null space.
-The reason for this is because viscoelastic relaxation within the lower crust of resulting from slip that is also within the lower crust will produce surface deformation in the direction opposite of slip.
-That is to say, the predicted viscoelastic deformation will cancel out the elastic deformation resulting in a trade off where a viscoelastic relaxation within a weak lower crust can be canceled out by slip at lower crustal depths.
-
-With afterslip constrained to shallow depths, we must now select a viscoelastic rheology for the lower crust and upper mantle.
-Maxwell viscoelasticity, which can be schematically illustrated as a spring and dashpot connected in series, is the simplest and commonly used rheologic model for studies on postseismic deformation NUR IS SLS!
-(e.g.
-\cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
-Assuming Maxwell viscoelasticity introduces a single the unknown rheologic parameter.
-A Maxwell viscoelastic model of the lithosphere would predict deformation that decays steadily over time, which fails to describe the multiple timescales of relaxation observed in postseismic deformation \cite{Savage1997}.
-An additional deficiency in modeling the lithosphere with a Maxwell rheology is that inferred viscosities tend to depend on the the timescale of the geophysical process being modelled \cite{Peltier1981}.
-When assuming Maxwell viscoselasticity, upper mantle viscosities for Southern California inferred from postseismic deformation tend to be on the order of $10^{18}$ Pa s (\cite{Pollitz2000}, \cite{Thatcher2008}, \cite{Spinler2015}.
-However, studies of interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
-
-To account for the apparently multiple timescales of relaxation, \cite{Pollitz2003} used a Burgers rheology upper mantle to model postseismic deformation following the Hector Mine earthquake and inferred a transient viscosity of $1.6\times10^{17}$ Pa s and a steady state viscosity of $4.6\times10^{18}$ Pa s, which still falls short of the steady state viscosity required for longer term geophysical processes.
-The particularly weak transient viscosity was found to be necessary to describe the early rapid postseismic deformation, although other researchers have successfully described the early postseismic deformation for the same earthquake with fault creep and poroelastic rebound.
-Nevertheless, laboratory experiments have demonstrated that mantle rock exhibits two phases of relaxation which can be adequately described with a Burgers rheology \cite{Chopra1997} and we should expect to see some postseismic signal resulting from transience viscoelasticity.
-
-The third linear viscoelastic rheology which we consider is the Zener model, often referred to as a standard linear solid, whose mechanical analogue consists of a spring connected in series with a Kelvin element.
-A generalization of the Zener model, consisting of a series of Kelvin elements connected in series each of which representing a distinct deformation mechanism, is commonly used to describe the spectrum of frequency dependent attenuation \cite{Liu1976}.
-The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982}, which is too weak to be perceptible in the GPS data used in the present study.
-
-As an exploratory step, we also perform a slip inversion, assuming an elastic lithosphere and asthenosphere.
-The difference between the analysis in  \cite{Rollins2015} and the present study is that we include a wider range of GPS stations in our inversion and we also perform a temporal estimation of afterslip, as opposed to estimating slip at a single epoch.
-The material properties used in our inversion are given in table 1 and are consistent with the properties used by \cite{Wei2011a} and the 1D SCEC background velocity model.
-We discretize the
-
- and the constrained and the only para.  where the rheologic parameters       
-In order to model postseismic deformation we must ddetermine an appropriate rheologic model for the lithosphere and asthenosphere.  
-To model postseismic deformation we must first assume a rheologic model.
-The simplest viscoelastic rheologic model would be a Maxwell model, where shear stresses and strains can be described with the mechanical analogy of a spring and dashpot connected in series.
-If coseismic and postseismic slip, described by $s(\xi,t)$, occurs on a fault $F$, and viscoelastic relaxation of subsequent stresses occurs in a Maxwell viscoelastic medium $L$, which has a spatially variable viscosity, $\eta(\zeta)$, then coseismic and postseismic deformation can be described by
-\begin{equation}\label{GeneralForward}
-  u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
-           \int_0^t\int_F s(\tau,\xi) f(t-\tau,x,\xi) d\xi d\tau
-\end{equation}
-where $g(x,\xi)$ is the elastic Green's function relating slip at $\xi$ to instantaneous displacement at $x$ and $f(t,x,\xi)$ describes the rate of deformation at $x$ and time $t$ resulting from viscoelastic relaxation of stresses induced by slip  at $\xi$.
-The variables which we are primarily concerned with estimating in this study are $s(\xi,t)$ and $\eta(\zeta)$.
-Numerous experimental and geophysical studies suggest that a Maxwell rheology is inappropriate to describe the behaviour of the uppermost mantle \cite{Chopra1997} \cite{Pollitz2003} \cite{Freed2004} and so we do not limit ourselves to exploring Maxwell viscolesticity.
-When considering other stress-linear viscoelastic models, such as a Zener or Burgers model, the description of displacements remains unchanged from eq \ref{GeneralForward} except that $f$ is parameterized by additional rheologic parameters which must also be estimated.
-The difficulty in  determining an appropriate rheologic model and then estimating $s(\xi,t)$ and the unkown rheologic parameters from observations of $u(x,t)$ is that it is a nonlinear inverse problem with many unknown parameters and a computationally expensive forward problem.
-We can greatly simplify the inverse problem by first considering the early postseismic period where we can approximate $u(x,t)$ for any stress-linear viscoelastic rheology as
-\begin{equation}\label{ApproxForward}
-  u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
-           \int_0^t\int_F\int_L \frac{s(\tau,\xi)}{\eta_\mathrm{eff}(\zeta)} h(x,\xi,\zeta) d\zeta d\xi d\tau
-\end{equation}
-
-what this gives us is a prior constraint on lithospheric viscosity initial that is unbiased by neglecting the contribution of afterslip!
-
-It can be shown (\cite{Hines2015}),
-
-other rheologic models in this study      viscoelasticity is We also test rheologic models other than viscoelasticity to describe
-
-There are numerous other parameters which are not known, but will be considered known in this study.
-
-   Inherent in f is also a stress-linear viscoelastic model.   In this study we will be be known while try to consider
-
-   The early near field postseismic vertical deformation does show a quadrant pattern and is also consistent with the coseismic vertical deformation.  Given
-
-that would not becomes there is no longer a coherent far field deformation signal.
-This is in contrast to near field displacements which persists for the entire 5.0 years of data used in this study.
-Figure () further illustrates the difference in deformation regimes between near field and far field station.
-
-We use a fault geometry from \cite{Wei2011}, which was determined using teleseismic, GPS, and InSAR data.
-
-After the El Mayor-Cucapah earthquake, additional GPS stations were installed In Baja California to record postseismic deformation with better spatial coverage.
-Two of the stations PTAX and PHJX were installed near the epicenter in the Cucapah Mountains.
-We do not include these two stations in our analysis because the geometry of the faults that ruptured during the earthquake is more complicated than our assumed fault geometry \cite{Oskin2012} \cite{Fletcher2014} and the near field stations would be most sensitive to error in our geometry.
-We also leave of these near field stations in order to avoid any near field processes which we do not consider in this paper \cite{Gonzalez-ortega2014}.
-Numerous stations exhibit extraneous signals which can be
-
-\section*{Rheological constraints}
-
-\section*{Results}
-\section*{Acknowledgements}
-
-This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.
-EAR-1261833.
-
-\bibliographystyle{apalike}
-\bibliography{mybib}
+\begin{figure}
+\includegraphics[scale=0.1]{Figures/final_afterslip_3-5}
+\centering 
+\caption{misfit with different shear modulus ratios}
+\label{ShearRatio}
+\end{figure}
 

### 2016-03-27 RoughDraft/ElMayor.tex
commit before push

@@
 \usepackage[usenames,dvipsnames]{color}
-\usepackage[maxfloats=50]{morefloats}
+\usepackage[maxfloats=30]{morefloats}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 \begin{figure}
+\includegraphics[scale=0.9]{Figures/context_map}
+\centering 
+\caption{}
+\label{ContextMap}
+\end{figure}
+
+\begin{figure}
 \includegraphics[scale=0.6]{Figures/figure_1}
@@
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{nearfield1}
 \end{figure}
-
 \begin{figure}
@@
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{nearfield2}
 \end{figure}
-
 \begin{figure}
@@
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{nearfield3}
 \end{figure}
-
 \begin{figure}
@@
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{nearfield4}
@@
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/far_field_data_1}
+\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_1}
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{farfield1}
 \end{figure}
-
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/far_field_data_2}
+\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_2}
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{farfield2}
 \end{figure}
-
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/far_field_data_3}
+\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_3}
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{farfield3}
 \end{figure}
-
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/far_field_data_4}
+\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_4}
 \centering 
-\caption{near field coseismic}
+\caption{}
 \label{farfield4}
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/near_field_record_section}
+\includegraphics[scale=0.9]{Figures/near_field_record_section}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/far_field_record_section}
+\includegraphics[scale=0.9]{Figures/far_field_record_section}
 \centering 
@@
 \centering 
-\caption{misfit with different shear modulus ratios}
-\label{ShearRatio}
+\caption{}
+\label{FinalCoseismic}
 \end{figure}
@@
 \centering 
-\caption{misfit with different shear modulus ratios}
+\caption{}
 \label{ShearRatio}
@@
 \centering 
-\caption{misfit with different shear modulus ratios}
+\caption{}
+\label{ShearRatio}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.9]{Figures/near_field_final_record_section}
+\centering 
+\caption{}
+\label{ShearRatio}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.9]{Figures/far_field_final_record_section}
+\centering 
+\caption{}
 \label{ShearRatio}

### 2016-03-27 RoughDraft/ElMayor.tex
commit before push

@@
 
-outline:
-
--dismiss poroelastic rebound
-
--Discuss justification of afterslip as a mechanism
- -vertical deformation argument
- -Kayla's paper and Haukson
- -discuss fault geometry
-
--Discuss viscoelastic relaxation
-  - discuss rheologic models and parameters needed to estimate
-
--Discuss approximation, implications for all rheologic models
--discretization of the lithosphere
--discuss the nitty gritty inverse method
-
-- issue with nonuniqueness of deep afterslip and crustal flow
-
--discuss fault geometry and modeling assumptions. including elastic properties. and Kayla's paper
-
--Discuss discretization of slip and viscosity
-
--discuss early postseismic approximation
-
 In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake.
 We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechanisms.
-Poroelastic rebound has also been used to model postseismic deformation \cite{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligable.
+Poroelastic rebound has also been used to model postseismic deformation \cite{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
 Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
 
-\subsection{Fault Geometry}
-In this study we estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \cite{Wei2011a} with some modifications.
-Field studies \cite{Fletcher2014} and LIDAR observations \cite{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \cite{Wei2011a}, especially within the Sierra Cucapah.
-However, we find the relatively simple coseismic fault geometry from \cite{Wei2011a} to be sufficient because most of the stations used in this station are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
-We do, however, modify the fault geometry from \cite{Wei2011a} by extending segment 2 northward by 40 km which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
+\subsection*{model design}
+We estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \cite{Wei2011} with some modifications.
+Field studies \cite{Fletcher2014} and LIDAR observations \cite{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \cite{Wei2011}, especially within the Sierra Cucapah.
+However, we find the relatively simple coseismic fault geometry from \cite{Wei2011a} to be sufficient because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
+The fault geometry used in this study (figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \cite{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
+Additionally, We extend the northern segment by 40 km to the northwest which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
 This extended fault segment was also found to be necessary by \cite{Rollins2015} and \cite{Pollitz2012} for describing postseismic deformation.
@@
 We consider a variety of rheologic models for the lithosphere and asthenosphere in this study.
-The simplest rheologic model would be to consider the lithospere and asthenosphere to be effectively elastic and isotropic.
-In such case, the rheologic parameters, consisting of the Lame parameters, $\lambda$ and $\mu$, and density, $\rho$, are reasonably well known, leaving the only unknowns to be the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
+The simplest rheologic model is to consider the lithospere and asthenosphere to be effectively elastic and isotropic.
+In such case, the rheologic parameters, consisting of the Lame parameters, $\lambda$ and $\mu$, and density, $\rho$, are reasonably well known.
+The only unknowns are then the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
 \cite{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be well explained with afterslip on the coseismicly ruptured fault, which has been extended down to the lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}, and they did not require any viscoelastic relaxation to describe the observations.
-They did however, find that the amount of afterslip required for the southernmost fault segment to be unrealistically large, equivalent to a Mw7.2 earthquake.
-Since most of the GPS data is located north of the rupture zone, slip on the Indiviso fault segment is least constrained and could be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
+They did however, find that an unrealistically large amount of afterslip is required on the Indiviso fault, equivalent to a Mw7.2 earthquake.
+Since most of the GPS data is located north of the rupture zone, slip on the Indiviso fault segment is not well constrained and it could be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
+It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, at least in 2D earthquake models.
+In the interest of eliminating null space in our inverse problem,  we assuming afterslip occurs only at seismogenic depths ($<15$ km), and we allow for viscoelastic relaxation in the lower crust (15-30 km) and the upper mantle.
+We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
+Additionally, as noted by \cite{Rollins2015} the postseismic uplift just north of the rupture zone can be well described with slip at seismogenic depths, while afterslip which is constrained to depths below 15 km predicts subsidence in that region.
 
-It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, at least in 2D earthquake models.
-In the interest of preventing a non-unique solution, we assuming afterslip to occur only at seismogenic depths (<15 km), and allow for viscoelastic relaxation in the lower crust (15-30 km) depth and the upper mantle.We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
-Additionally, as noted by \cite{Rollins2015} the postseismic uplift just north of the rupture zone can be well described with slip at seismogenic depths, while afterslip which is constrained to depths beneath 15 km predicts subsidence in that region.
+Another reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and the inverse problem becomes particularly ill-posed when trying to simultaneously estimate afterslip and a lithospheric viscosity at the same depths.
+This ill-posedness is illustrated in figure (TBD), which shows the displacement resulting from a meter of slip on a fault extending from 15 to 30 km depth as well as the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+The horizontal displacement from fault slip is in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
+This means that displacement resulting from afterslip at lower crustal depths can be cancelled out by a low viscosity lower crust.
+We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
+Aside from the issue of nonuniqueness, it is also nonsensical to allow for both brittle and ductile deformation mechanisms at the same depth.
 
-A third reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and trying to simultaneously estimate deep afterslip and a lower crustal viscosity leads creates a significant null space.
-The reason for this is because viscoelastic relaxation within the lower crust of resulting from slip that is also within the lower crust will produce surface deformation in the direction opposite of slip.
-That is to say, the predicted viscoelastic deformation will cancel out the elastic deformation resulting in a trade off where a viscoelastic relaxation within a weak lower crust can be canceled out by slip at lower crustal depths.
+A schematic representation of the viscoelastic rheologic models considered in this study for the lower crust and upper mantle are shown in figure (TBD).
+We consider Maxwell viscoelasticity, where the steady state viscosity $\eta_M$ is unknown; Zener viscoelasticty, where the transient viscosity $\eta_K$ and transient shear modulus $\mu_K$ are unknown; and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all largely unknown.
+We further discuss these rheologic models and their use in geophysical studies in the discussion.
 
-\subsection{Rheologic Models}
-With afterslip constrained to shallow depths, we must now select a viscoelastic rheology for the lower crust and upper mantle.
-Maxwell viscoelasticity, which can be schematically illustrated as a spring and dashpot connected in series, is the simplest and commonly used rheologic model for studies on postseismic deformation (e.g.
-\cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
-The Maxwell model describes both an instantaneously elastic and fluid-like phase of deformation.
-Assuming Maxwell viscoelasticity introduces the additional rheologic parameter, $\eta_M$, which is typically estimated for the lower crust and upper mantle as an inverse problem, where the viscosities are chosen to minimize the difference between the observed postseismic deformation and deformation predicted by a mechanical model.
-A Maxwell viscoelastic model of the lithosphere would predict deformation that decays steadily over time, which fails to describe the observable deformation which exhibits transient deformation which decays rapidly within the first year of an earthquake followed by a relatively steady rate of deformaiton \cite{Savage1997}.
-An additional deficiency in describing postseismic deformation with viscoelastic relaxation in a Maxwell viscoselastic lithosphere is that inferred viscosities tend to be considerably lower than viscosities inferred from geophysical processes that occur over longer timescales.
-For example, postseismic studies in Southern California following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have all inferred a Maxwell viscoselastic upper mantle with a viscosities ranging from $10^{17}$ to $10^{18}$ Pa s; however, studies on interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
-
-We also consider the Zener viscoelastic model whose mechanical analogue consists of a spring connected in series with a Kelvin element.
-The Zener model is used to describe both an instantaneous and delayed phase of elasticity.
-A generalization of the Zener model, consisting of numerous Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \cite{Liu1976}.
-The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982} and the largest characteristic relaxation time would be on the order of days, which is too short to be perceptible in the GPS data used in the present study.
-We therefor ignore the delayed elasticity associated with seismic attenuation models, and consider such models to be effectively instantaneously elastic.
-Nevertheless, we still explore the possibility of describing postseismic deformation with a Zener model that has relaxation timescales of months to years.
-
-Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid behaviour required for mantle dynamics on geologic time scales.
-\cite{Yuen1982} proposed a Burgers rheology with a low viscosity ($\approx 10^{16}$ Pa s) in the Kelvin element and high viscosity ($\approx 10^{21}$ Pa s) in the Maxwell element which is capable of describing both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
-The justification of a Burger's rheology mantle is further supported by laboratory experments on the strength of olivine \cite{Chopra1997}.
-\cite{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
-While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \cite{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \cite{Lundgren2009} and \cite{Luttrell2007}.
-Additionally, the transient viscosity inferred by \cite{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, while \cite{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \cite{Jacobs2002}.
-In this paper we seek to constrain the rheologic parameters describing a Burgers upper mantle that are consistent with postseismic deformation and long term geophysical processes, while also accounting  for shallow afterslip, which perhaps biased the solution from \cite{Pollitz2003}.
-
-\subsection{Constraint on Effective Viscosity}\label{InitialInversion}
-For the three linear viscoelastic rheologies described above, Maxwell, Zener, and Burgers, postseismic displacement resulting from time dependent fault slip, $s(\xi,t)$, on a fault $F$ can be described as
+\subsection*{constraint on effective viscosity}\label{InitialInversion}
+For any linear viscoelastic rheology of the lithosphere and asthenosphere, postseismic displacement resulting from time dependent fault slip, $s(\xi,t)$, on a fault $F$ can be described as  
 \begin{equation}\label{GeneralForward}
@@
 $f$ is a function of the properties of the chosen rheologic model, which are generally not well known.
-The parameters controlling the instantaneous elastic behaviour of the lithosphere and asthenosphere, $\mu$, $\lambda$, and density $\rho$, are relatively well known and we use the values listed in table 1, which are consistent with the properties used in the coseismic model by \cite{Wei2011a} and the 1D SCEC background velocity model.
+The parameters controlling the instantaneous elastic behaviour of the lithosphere and asthenosphere, $\mu$, $\lambda$, and density $\rho$, are relatively well known and we use the values listed in table (TBD), which are consistent with the properties used in the coseismic model by \cite{Wei2011} and the 1D SCEC background velocity model.
 The remaining rheologic parameter, which we will assume to have a depth dependence, are estimated to optimize the predicted fit to observable postseismic displacement.
 
-In order greatly simplify the posed inverse problem we use to method describe in \cite{Hines2015} to constrain the effective lithospheric viscosity structure for the early postseismic period.
-The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere, denoted at $L$, are controlled by the relatively well known instantaneous elastic properties.
+In order to greatly simplify the posed inverse problem, we use to method describe in \cite{Hines2015} to constrain the effective lithospheric viscosity structure for the early postseismic period.
+The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere are controlled by the relatively well known instantaneous elastic properties.
 This means that the rate of deformation in each parcel of the lithosphere will deform at a rate that is inversely proportional to its effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$, and independent of $\eta_{\mathrm{eff}}$ elsewhere.
-Then, as a consequently of linear elasticity, the initial rate of surface deformation resulting from viscoelastic relaxation is a linear combination of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's viscosity.
+Then, as a consequence of linear elasticity, the initial rate of surface deformation resulting from viscoelastic relaxation is a linear combination of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's viscosity.
 That is to say
@@
 \end{equation}
-where $h(x,\xi,\zeta)$ describes the initial rate of deformation resultion from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and, most importantly, $h$ is independent of all rheologic properties other than those that control the instantaneous elastic behaviour, $\mu$, $\lambda$ and $\rho$.
-Subsitution eq.
-\ref{InitialRate} into \ref{GeneralForward} gives us an approximation for early postseismic deformation,
+where $h(x,\xi,\zeta)$ describes the initial rate of deformation resultion from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and $L$ denotes the lithosphere and asthenosphere.
+Importantly, $h$ is independent of all rheologic properties other than those that control the instantaneous elastic behaviour, $\mu$, $\lambda$ and $\rho$.
+We can combine eq.
+\ref{InitialRate} with \ref{GeneralForward} to get a first order approximation for early postseismic deformation,
 \begin{equation}\label{ApproxForward}
@@
 This is in contrast to evaluating the full forward problem, eq.
-\ref{GeneralForward}, numerically for each realization of $s$ and $\eta_{\mathrm{eff}}$ which is far more computationally demanding.
+\ref{GeneralForward}, numerically for each realization of $s$ and unkown rheologic properties which is far more computationally demanding.
 
 We perform an initial inversion of postseismic displacements using eq.
-\ref{ApproxForward} as out forward problem.
-As noted, we use the fault geometry from \cite{Wei2011}, except that each segment extends to 15 km depth and segment 2 is extended 40 km northward.
+\ref{ApproxForward} as our forward problem.
+As noted, we use the fault geometry from \cite{Wei2011}, except that each segment extends to 15 km depth and the north segment is extended 40 km northward.
 Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
 We estimate coseismic slip as well as a rate of afterslip which is constant over the time intervals spanning 0.0-0.125, 0.125-0.25, and 0.5-1.0 years following the earthquake, as well as over 1.0 year intervals for the remaining postseismic period.
-We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip for all segments except for segment 1, where slip is constrained be within $45^\circ$ of normal.
-We estimate $\eta_{\mathrm{eff}}$ within 6 vertically stratified layers which have depths ranging from 0-15 km, 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain, 800 km.
+We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip.
+We estimate $\eta_{\mathrm{eff}}$ within 6 vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain, 800 km.
 Details of the inverse method are described in \cite{Hines2015}.
@@
 
-The first step in our inverse method is to determine the time during the postseismic period at which point the early postseismic approximation, eq.
+The first step in our inverse method is to determine at which point the early postseismic approximation, eq.
 \ref{ApproxForward}, is no longer approriate, which we will denote as $t_{\mathrm{end}}$.
-As noted, it is valid for approximately as long as the rate of deformation resulting for viscoelastic relaxation is approximately constant.
-We can almost certainly assume that deformation at the most far field stations which are ~400 km away from the El Mayor-Cucapah is the result of viscoelastic relaxation.
-Then the approximation should be valid for as long as a linear trend adequately approximates the far field deformation.
+As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
+We can almost certainly assume that deformation at the most far field stations which are ~400 km away from the El Mayor-Cucapah epicenter is the result of viscoelastic relaxation.
+The approximation should then be valid for as long as a linear trend adequately approximates the far field deformation.
 Using this logic, it would appear that $t_{\mathrm{end}}$ is $\sim1$ year after the El Mayor-Cucapah earthquake.
 Another way to determine $t_{\mathrm{end}}$ is to find the best fitting prediction of eq.
-\ref{ApproxForward} to various durations of the postseismic timeseries and determine when eq.
-\ref{ApproxForward} is not longer capable of describing the deformation without incurring systematic misfits.
-This is illustrated in figures \ref{NearFieldRS} and \ref{FarFieldRS}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
+\ref{ApproxForward} to observed deformation using increasing durations of the postseismic timeseries.
+$t_\mathrm{end}$ should be the point when eq.
+\ref{ApproxForward} is not longer capable of describing the observed deformation without incurring systematic misfits.
+This is illustrated in figures \ref{fig:NearFieldRS} and \ref{fig:FarFieldRS}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
 When using eq.
 \ref{ApproxForward} to fit the entire five years of postseismic displacement we see that the near field displacements, eg.
-station P501, are accurately predicted, as was also the case when modelling postseismic deformation with an elastic lithosphere.
-When looking at displacement in the far field, eg.
+station P501, are accurately predicted but when looking at displacement in the far field, eg.
 station P621, we see that eq.
-\ref{ApproxForward} overestimates the rate of deformation in the later postseismic and underestimates the rate of deformation in the near field.
-As we progressively decrease the length of the postseismic timeseries used in the inversion, we see improved fit to the early postseismic period.
+\ref{ApproxForward} overestimates the rate of deformation in the later postseismic and underestimates the rate of deformation in the early period.
 Due to the low signal to noise ratio for far field stations, it is difficult to determine at what point eq.
@@
 
-Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
+Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
 Although fluidities is a sparesly used metric, it is more natural to use fludities rather than viscosity since eq.
@@
 We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_v$, and our choice our $\lambda_v$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
-It is therefore difficult to interpret the magnitude of uncertainties on viscosity shown in figure \ref{EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
+It is therefore difficult to interpret the magnitude of uncertainties on viscosity shown in figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
 The uncertainties in fluidities increases with depth, as would be expected due to decreased sensitivity with depth.
@@
 
-Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figures \ref{InitialCoseismic} and \ref{InitialAfterslip} respectively.
-To show the how our slip solution is influenced by allowing for a viscoelastic lithopshere, we have also show a coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but while assuming the lithosphere and ashthenosphere are elastic.
+Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figures \ref{fig:InitialCoseismic} and \ref{fig:InitialAfterslip} respectively.
+To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show a coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but while assuming the lithosphere and ashthenosphere are elastic.
 In both coseismic inversion, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
@@
 
-Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener model, which only introduces the unknown paremeter $\mu_{k}$.
+Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener model, which only introduces the unknown parameter $\mu_{k}$.
 We assume that the lower crust still has a Maxwell viscosity and $\eta_{M}$ is set equal to $\eta_{\mathrm{eff}}$.
@@
 The former being a degenerate case when the Zener model becomes the Maxwell model from above and the later being a Jeffreys solid.
-The misfit of the best fit models to the observed postseismic data when varying $\nu$ is shown in figure \ref{ShearRatio}.
-The optimal value of $\nu$ is found to be $0.375$ which decreases the misfit by only about \%10; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years.
-This significant improvement is seen for all shear modulus  ratios greater than $0.125$.
+The misfit of the best fit models to the observed postseismic data when varying $\nu$ is shown in figure \ref{fig:ShearModulusRatio}.
+The optimal value of $\nu$ is found to be $0.375$ which decreases the misfit by only about \%10; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (\ref{fig:FinalFarFieldRS}).
+This significant improvement is seen for all shear modulus  ratios greater than about $0.125$.
 
 Because we are able to adequately  describe the available 5 years of postseismic seismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since Zener model can be thought of as the limit when the steady state viscosity in a Burgers rheology is infinite, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in \ref{InitialInversion} and an effectively infinite steady state viscosity on the timescale of five years, $>10^{20}$ Pa s, would be also be able to satisfactorily describe the observable postseismic deformation.
+However, since Zener model can be thought of as the limit when the steady state viscosity in a Burgers rheology is infinite, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in \ref{InitialInversion} and an effectively infinite steady state viscosity on the timescale of five years, $>10^{20}$ Pa s, would also be able to satisfactorily describe the observable postseismic deformation.
 
@@
 We estimate the damping parameter, again enforcing smallness on our model, using another L-curve test.
-Our preferred model for coseismic slip and afterslip is shown in figure ?
-?
-and ?.
+Our preferred model for coseismic slip and afterslip is shown in figures \ref{fig:FinalCoseismic} through \ref{fig:FinalAfterslip3}.
+
+The postseismic displacements predicted for our preferred slip model and rheologic model of the lithospheric are shown in figures \ref{fig:NearField1} through \ref{fig:FarField4} as well as \ref{fig:FinalNearFieldRS} and \ref{fig:FinalFarFieldRS}.
+Additionally we show the predicted postseismic deformation broken down into an elastic and viscoelastic component (figure (TBD)).
+Overall, the trend in the near field and far field transient deformation is accurately described by our preferred model.
+In particular, the trend in far field deformation is much better described by our preferred model, which has a Zener rheology mantle, than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:FinalFarFieldRS}).
+There are a few areas where we have notable misfit.
+Most of our misfit is for the near field stations in the Imperial Valley and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \cite{Wei2011} and Wei 2015.
+Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
+Lastly, there are clear discrepancies between the observed and predicted vertical deformation following the first year after the El Mayor Cucapah earthquake.
+We observe a general uplift throughout Southern California, which is inconsistent with any postseismic model, which would produce a quadrant pattern of deformation.
+
+The cumulative potency of slip over time is shown in figure (TBD).
+The inferred coseismic potency is $3.1\times10^{9} \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of five years of afterslip is $1.2\times10^{9} \mathrm{m}^3$.
+While most of the afterslip is inferred to be within the first couple months of the earthquake, accounting for the most rapid near field transient deformation, we infer that afterslip in the vicinity of the Sierra Cucapah, where most slip occurred during the main shock, is necessary to explain the sustained rate of deformation in the near field.
+We emphasize, that the GPS station closest to where we infer there to be sustained afterslip, P496, is still about 30 km away, which we believe is too distil for us to conclusively argue for sustained brittle deformation rather ductile deformation in a shear zone, especially for the last two years where afterslip is inferred to be on the deepest patches.
+Although we do note that it is not unheard of for afterslip to persists for years or decades following an earthquake \cite{Cakir2012}.
+Either way, we can conclusively say a localized deformation mechanism is required to explain the available five years of near field deformation.
 
 \section{Discussion}
+
+With afterslip constrained to shallow depths, we must now select a viscoelastic rheology for the lower crust and upper mantle.
+Maxwell viscoelasticity, which can be schematically illustrated as a spring and dashpot connected in series, is the simplest and commonly used rheologic model for studies on postseismic deformation (e.g.
+\cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
+The Maxwell model describes both an instantaneously elastic and fluid-like phase of deformation.
+Assuming Maxwell viscoelasticity introduces the additional rheologic parameter, $\eta_M$, which is typically estimated for the lower crust and upper mantle as an inverse problem, where the viscosities are chosen to minimize the difference between the observed postseismic deformation and deformation predicted by a mechanical model.
+A Maxwell viscoelastic model of the lithosphere would predict deformation that decays steadily over time, which fails to describe the observable deformation which exhibits transient deformation which decays rapidly within the first year of an earthquake followed by a relatively steady rate of deformaiton \cite{Savage1997}.
+An additional deficiency in describing postseismic deformation with viscoelastic relaxation in a Maxwell viscoselastic lithosphere is that inferred viscosities tend to be considerably lower than viscosities inferred from geophysical processes that occur over longer timescales.
+For example, postseismic studies in Southern California following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have all inferred a Maxwell viscoselastic upper mantle with a viscosities ranging from $10^{17}$ to $10^{18}$ Pa s; however, studies on interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+
+We also consider the Zener viscoelastic model whose mechanical analogue consists of a spring connected in series with a Kelvin element.
+The Zener model is used to describe both an instantaneous and delayed phase of elasticity.
+A generalization of the Zener model, consisting of numerous Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \cite{Liu1976}.
+The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982} and the largest characteristic relaxation time would be on the order of days, which is too short to be perceptible in the GPS data used in the present study.
+We therefor ignore the delayed elasticity associated with seismic attenuation models, and consider such models to be effectively instantaneously elastic.
+Nevertheless, we still explore the possibility of describing postseismic deformation with a Zener model that has relaxation timescales of months to years.
+
+Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid behaviour required for mantle dynamics on geologic time scales.
+\cite{Yuen1982} proposed a Burgers rheology with a low viscosity ($\approx 10^{16}$ Pa s) in the Kelvin element and high viscosity ($\approx 10^{21}$ Pa s) in the Maxwell element which is capable of describing both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
+The justification of a Burger's rheology mantle is further supported by laboratory experments on the strength of olivine \cite{Chopra1997}.
+\cite{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
+While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \cite{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \cite{Lundgren2009} and \cite{Luttrell2007}.
+Additionally, the transient viscosity inferred by \cite{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, while \cite{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \cite{Jacobs2002}.
+In this paper we seek to constrain the rheologic parameters describing a Burgers upper mantle that are consistent with postseismic deformation and long term geophysical processes, while also accounting  for shallow afterslip, which perhaps biased the solution from \cite{Pollitz2003}.
 
@@
 \caption{}
-\label{ContextMap}
+\label{fig:ContextMap}
 \end{figure}
@@
 Red line indicates the time of the Ocotillo earthquake where a jump in the time series is estimated}
-\label{P496Fit}
+\label{fig:P496Fit}
 \end{figure}
@@
 Displacements shown have had a background secular trend removed as well as an estimated seasonal signal.}
-\label{P496PS}
+\label{fig:P496PS}
 \end{figure}
@@
 Red line indicates the time of the Ocotillo earthquake where a jump in the time series is estimated}
-\label{P619Fit}
+\label{fig:P619Fit}
 \end{figure}
@@
 Displacements shown do not include the estimated secular trend, seasonal signals, and displacements resulting from the Ocotillo earthquake.}
-\label{P619PS}
+\label{fig:P619PS}
 \end{figure}
@@
 \caption{}
-\label{nearfield1}
+\label{fig:NearField1}
 \end{figure}
@@
 \caption{}
-\label{nearfield2}
+\label{fig:NearField2}
 \end{figure}
@@
 \caption{}
-\label{nearfield3}
+\label{fig:NearField3}
 \end{figure}
@@
 \caption{}
-\label{nearfield4}
+\label{fig:NearField4}
 \end{figure}
@@
 \caption{}
-\label{farfield1}
+\label{fig:FarField1}
 \end{figure}
@@
 \caption{}
-\label{farfield2}
+\label{fig:FarField2}
 \end{figure}
@@
 \caption{}
-\label{farfield3}
+\label{fig:FarField3}
 \end{figure}
@@
 \caption{}
-\label{farfield4}
+\label{fig:FarField4}
 \end{figure}
@@
 \caption{near field record section}
-\label{NearFieldRS}
+\label{fig:NearFieldRS}
 \end{figure}
@@
 \caption{far field record section}
-\label{FarFieldRS}
+\label{fig:FarFieldRS}
 \end{figure}        
@@
 \caption{near field record section}
-\label{SlipLCurve}
+\label{fig:SlipLCurve}
 \end{figure}
@@
 \caption{far field record section}
-\label{FluidityLCurve}
+\label{fig:FluidityLCurve}
 \end{figure}
@@
 \caption{effective viscosity}
-\label{EffectiveViscosity}
+\label{fig:EffectiveViscosity}
 \end{figure}
@@
 \caption{coseismic slip from initial inversion}
-\label{InitialCoseismic}
+\label{fig:InitialCoseismic}
 \end{figure}
@@
 \caption{afterslip from initial inversion}
-\label{InitialAfterslip}
+\label{fig:InitialAfterslip}
 \end{figure}
@@
 \caption{coseismic slip from elastic inversion}
-\label{InitialElasticCoseismic}
+\label{fig:InitialElasticCoseismic}
 \end{figure}
@@
 \caption{afterslip from elastic inversion}
-\label{FluidityLCurve}
+\label{fig:InitialElasticAfterslip}
 \end{figure}
@@
 \caption{misfit with different shear modulus ratios}
-\label{ShearRatio}
+\label{fig:ShearModulusRatio}
 \end{figure}
@@
 \caption{}
-\label{FinalCoseismic}
+\label{fig:FinalCoseismic}
 \end{figure}
@@
 \caption{}
-\label{ShearRatio}
+\label{fig:FinalAfterslip1}
 \end{figure}
@@
 \caption{}
-\label{ShearRatio}
+\label{fig:FinalAfterslip2}
 \end{figure}
@@
 \caption{}
-\label{ShearRatio}
+\label{fig:FinalAfterslip3}
 \end{figure}
@@
 \caption{}
-\label{ShearRatio}
+\label{fig:FinalNearFieldRS}
 \end{figure}
@@
 \caption{}
-\label{ShearRatio}
+\label{fig:FinalFarFieldRS}
 \end{figure}

### 2016-03-29 RoughDraft/ElMayor.tex
commit before push

@@
 \usepackage[usenames,dvipsnames]{color}
-\usepackage[maxfloats=30]{morefloats}
+\usepackage[maxfloats=40]{morefloats}
 \usepackage{caption}
 \usepackage{subcaption}
+\usepackage{natbib}
 
@@
 
-Previous studies which have modeled postseismic deformation following the El Mayor-Cucapah earthquake include \cite{Pollitz2012}, \cite{Gonzalez-ortega2014}, \cite{Spinler2015}, and \cite{Rollins2015}.
-\cite{Gonzalez-ortega2014} was able to describe five months of near field ($\lesssim 50$ km from the epicenter) postseismic defomation observed by InSAR and campaign GPS with afterslip and fault contraction on the coseismically ruptured fault.
-\cite{Gonzalez-ortega2014} also noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
-Using continuous GPS stations within 200 km of the El Mayor-Cucapah epicent, which consists mostly of stations north of the US-Mexico border, \cite{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip in an elastic lithosphere, albeit with an implausibly large amount of afterslip inferred on the least constrained southern most fault segment which may be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
-In this paper, we reiterate this finding by \cite{Rollins2015} and note that a purely elastic dislocation model is incapable of describing deformation observed at GPS stations greater than ~200 km from the El Mayor-Cucapah epicenter.
+Previous studies which have modeled postseismic deformation following the El Mayor-Cucapah earthquake include \citet{Pollitz2012}, \citet{Gonzalez-ortega2014}, \citet{Spinler2015}, and \citet{Rollins2015}.
+\citet{Gonzalez-ortega2014} was able to describe five months of near field ($\lesssim 50$ km from the epicenter) postseismic defomation observed by InSAR and campaign GPS with afterslip and fault contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} also noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
+Using continuous GPS stations within 200 km of the El Mayor-Cucapah epicent, which consists mostly of stations north of the US-Mexico border, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip in an elastic lithosphere, albeit with an implausibly large amount of afterslip inferred on the least constrained southern most fault segment which may be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
+In this paper, we reiterate this finding by \citet{Rollins2015} and note that a purely elastic dislocation model is incapable of describing deformation observed at GPS stations greater than ~200 km from the El Mayor-Cucapah epicenter.
 
-Given the inability to describe both near and far field deformation with fault slip in an elastic lithosphere, \cite{Pollitz2012}, \cite{Rollins2015} and \cite{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential deformation mechanism.
+Given the inability to describe both near and far field deformation with fault slip in an elastic lithosphere, \citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential deformation mechanism.
 The lithospheric rheology is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and find the best fitting model parameters, which is generally a computationally expensive nonlinear inverse problem.
 Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
-For example, it is commonly assumed that the lithosphere consists of only three homogeneously Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \cite{Hines2013}\cite{Riva2009}.
+For example, it is commonly assumed that the lithosphere consists of only three homogeneously Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep[e.g.][]{Hines2013,Riva2009}.
 Additionally, it is necessary to make simplifying assumptions about the nature of afterslip.
-For example, one can assume a frictional model for afterslip and parameterize afterslip in terms its the unkown rheologic properties (e.g.
-\cite{Johnson2009} \cite{Johnson2004}).
-Additionally, one can assume that afterslip only dominates the first year of deformation (e.g.
-\cite{Pollitz2012} and \cite{Spinler2015}) and that viscoelastic relaxation is the dominant mechanism in later years.
-However, numerous observations of interseismic fault creep has been recognized in this and similar tectonic settings and it has been speculated that such creep can be initiated as a postseismic process \cite{Cakir2012} \cite{Cetin2014}.
-We are unaware of any oIn this study, we therefore do not make to implicit assumption that afterslip terminates after a given amount of time.
-Indeed, the preferred viscoelastic model from \cite{Pollitz2012} underpredicts near field velocities, which could be indicative of unmodeled continued afterslip.
+For example, one can assume a frictional model for afterslip and parameterize afterslip in terms its the unkown rheologic properties \citep[e.g.][]{Johnson2009,Johnson2004}.
+Additionally, one can assume that afterslip only dominates the first year of deformation \citep[e.g.][]{Pollitz2012,Spinler2015} and that viscoelastic relaxation is the dominant mechanism in later years.
+However, numerous observations of interseismic fault creep has been recognized in this and similar tectonic settings and it has been speculated that such creep can be initiated as a postseismic process \citep{Cakir2012,Cetin2014}.
+We therefore do not make to implicit assumption that afterslip terminates after a given amount of time.
+Indeed, the preferred viscoelastic model from \citet{Pollitz2012} underestimates near field velocities, which could be indicative of unmodeled continued afterslip.
 
-All of the aforementioned studies model displacements observered at stations within 200 km of the El Mayor-Cucapah epicenter, while postseismic deformation in this region following previous earthquakes of similar magnitude has been observed at distances extended out to about 300 km \cite{Freed2007a}.
+All of the aforementioned studies model displacements observered at stations within 200 km of the El Mayor-Cucapah epicenter, while postseismic deformation in this region following previous earthquakes of similar magnitude has been observed at distances extended out to about 300 km \citep{Freed2007a}.
 In the present study we examine stations within 400 km of the El Mayor-Cucapah epicenter, which turns out to be crucial for discerning the postseismic deformation mechanism.
@@
 Clearly, both afterslip and viscoelastic relaxation are involved in postseismic deformation neglecting to model one of these deformation mechanisms could result in a biased estimate of the other.
-In this paper we use the inverse method described in \cite{Hines2015} to estimate the afterslip an effective viscosity necessary to describe the transience postseismic deformation over the first ten months after the El Mayor-Cucapah earthquake.
+In this paper we use the inverse method described in \citet{Hines2015} to estimate the afterslip an effective viscosity necessary to describe the transience postseismic deformation over the first ten months after the El Mayor-Cucapah earthquake.
 We then form a suite of models which have various lithospheric rheologies but viscosities that are consistent with the effective viscosity estimated from the early postseismic deformation.
-Of the suite of models tested, we find that five years of postseismic deformation can be explained by a combination of sustained afterslip on the coseismicly ruptured fault and a Zener rheology upper mantle with viscosity that decays from $4\times10^{18}$ to $1\times10^{18}$ Pa s.
+Of the suite of models tested, we find that five years of postseismic deformation can be explained by a combination of sustained afterslip on the coseismicly ruptured fault and a Zener rheology upper mantle with viscosity that decays from $\sim5\times10^{18}$ to $\sim1\times10^{18}$ Pa s.
 
@@
 
-We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for Plate Boundary Observatory (PBO) stations within a 400 km radius about the El Mayor-Cucapah epicenter.
-Our analysis is on the coseismic and postseismic deformation resulting from the EMC earthquake, which we collectively describe as $u(t)$.
-We consider GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular tectonic deformation, annual and semi-annual fluctuations, and coseismic offsets from sigificant earthquakes over the time span of this study.
+We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) stations within a 400 km radius about the El Mayor-Cucapah epicenter.
+Our analysis is on the coseismic and postseismic deformation resulting from the El Mayor-Cucapah earthquake, which we collectively describe as $u(t)$.
+We consider GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular tectonic deformation, annual and semi-annual fluctuations, and coseismic offsets from significant earthquakes over the time span of this study.
 The June 14, 2010 Mw5.8 Ocotillo earthquake and the August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3 event, are the only earthquakes after the EMC earthquake that produced noticeable offsets recorded by GPS.
@@
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-While several stations were installed after the EMC earthquake to improve the spatial resolution of postseismic deformation \cite{Spinler2015}, our inverse method uses postseismic displacements rather than velocities (e.g.
+While several stations were installed after the EMC earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015}, our inverse method uses postseismic displacements rather than velocities (e.g.
 ...)
@@
 The October 16, 1999 Hector Mine earthquake, which occurred within our study region about 270 km north of the EMC epicenter, has produce transient postseismic deformation which we do not wish to model either mechanically or through empirical line fitting.
-We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, past which point postseismic deformation for nearfield sites occurs at an approximately steady rate \cite{Savage2009}.
-When considering stations further away from the Hector Mine epicenter, postseismic transience persists for only about two years \cite{Spinler2015}.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, past which point postseismic deformation for nearfield sites occurs at an approximately steady rate \citep{Savage2009}.
+When considering stations further away from the Hector Mine epicenter, postseismic transience persists for only about two years \citep{Spinler2015}.
 
@@
 Such functions have been found empirically e.g.
-\cite{Savage2005a} and theoretically \cite{Marone1991} to adequately describe deformation resulting from postseismic deformation.
+\citep{Savage2005a} and theoretically \citep{Marone1991} to adequately describe deformation resulting from postseismic deformation.
 However, by assuming a logarithmic or exponential form of $u(t)$ we run the risk of overfitting the GPS time series and inferring a nonexistent postseismic signal.
@@
 The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
-Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation \cite{Savage2005a}.
+Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation \citep{Savage2005a}.
 The other endmember, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
 While one can use a maximum likelihood based approach to picking $\sigma^2$ (e.g.
-\cite{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
+\citep{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal.
@@
 \ref{TimeSeriesModel}.
-For example, we assume that the background rate of deformation can be approximated as having a constant rate, while mechanical models would suggest this to not be true on earthquake cycle timescales \cite{Thatcher1983}.
+For example, we assume that the background rate of deformation can be approximated as having a constant rate, while mechanical models would suggest this to not be true on earthquake cycle timescales \citep{Thatcher1983}.
 Although based on inspection,  assuming a constant rate of background deformation appears to be appropriate for all stations except for perhaps the stations closest to the Hector Mine epicenter, where postseismic deformation persists.
@@
 Another reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and the inverse problem becomes particularly ill-posed when trying to simultaneously estimate afterslip and a lithospheric viscosity at the same depths.
-This ill-posedness is illustrated in figure (TBD), which shows the displacement resulting from a meter of slip on a fault extending from 15 to 30 km depth as well as the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+This ill-posedness is illustrated in figure (\ref{fig:LowerCrust}), which shows the displacement resulting from a meter of slip on a fault extending from 15 to 30 km depth as well as the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
 The horizontal displacement from fault slip is in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
@@
 
-With afterslip constrained to shallow depths, we must now select a viscoelastic rheology for the lower crust and upper mantle.
-Maxwell viscoelasticity, which can be schematically illustrated as a spring and dashpot connected in series, is the simplest and commonly used rheologic model for studies on postseismic deformation (e.g.
+Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle, which is the simplest viscoelastic rheologic model (e.g.
 \cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
-The Maxwell model describes both an instantaneously elastic and fluid-like phase of deformation.
-Assuming Maxwell viscoelasticity introduces the additional rheologic parameter, $\eta_M$, which is typically estimated for the lower crust and upper mantle as an inverse problem, where the viscosities are chosen to minimize the difference between the observed postseismic deformation and deformation predicted by a mechanical model.
-A Maxwell viscoelastic model of the lithosphere would predict deformation that decays steadily over time, which fails to describe the observable deformation which exhibits transient deformation which decays rapidly within the first year of an earthquake followed by a relatively steady rate of deformaiton \cite{Savage1997}.
-An additional deficiency in describing postseismic deformation with viscoelastic relaxation in a Maxwell viscoselastic lithosphere is that inferred viscosities tend to be considerably lower than viscosities inferred from geophysical processes that occur over longer timescales.
-For example, postseismic studies in Southern California following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have all inferred a Maxwell viscoselastic upper mantle with a viscosities ranging from $10^{17}$ to $10^{18}$ Pa s; however, studies on interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+In Southern California, postseismic studies following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s with a relatively stronger lower crust.
+While these inferences are consistent with our effective viscosities, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
+Studies on interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
 
-We also consider the Zener viscoelastic model whose mechanical analogue consists of a spring connected in series with a Kelvin element.
-The Zener model is used to describe both an instantaneous and delayed phase of elasticity.
-A generalization of the Zener model, consisting of numerous Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \cite{Liu1976}.
-The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982} and the largest characteristic relaxation time would be on the order of days, which is too short to be perceptible in the GPS data used in the present study.
-We therefor ignore the delayed elasticity associated with seismic attenuation models, and consider such models to be effectively instantaneously elastic.
-Nevertheless, we still explore the possibility of describing postseismic deformation with a Zener model that has relaxation timescales of months to years.
+An additional deficiency in the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate postseismic deformation.
+Early transient postseismic deformation can be attributed to fault creep \cite{Savage2005a} and the trend in postseismic deformation can then be explained with a combination of fault creep and relaxation in a Maxwell viscoelastic lithosphere, (e.g.
+\cite{Hearn2009}, \cite{Johnson2009}).
+However, the trend in postseismic deformation at distances greater than about 200 km from the El Mayor Cucapah epicenter, which can only be attributed to viscoelastic relaxation \cite{Freed2007a}, cannot be explained with a Maxwell viscoelastic lithosphere (figure \ref{fig:FinalFarFieldRS}).
+
+We found that a Zener rheology in the upper mantle with a transient viscosity of about $10^{18}$ Pa s does a noticeably better job at predicting far field postseismic deformation.
+A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \cite{Liu1976}.
+The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982} and the largest characteristic relaxation time would be on the order of days.
+Even though our inferred transient viscosity is orders of magnitude larger than that required for seismic attenuation models, the two models are not incompatible.
+Rather the delayed elasticity in seismic attenuation models occurs on such short timescales that it can be considered  part of the instantaneous elastic phase of deformation associated with the preferred Zener model in this study.
 
@@
 While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \cite{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \cite{Lundgren2009} and \cite{Luttrell2007}.
-Additionally, the transient viscosity inferred by \cite{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, while \cite{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \cite{Jacobs2002}.
-In this paper we seek to constrain the rheologic parameters describing a Burgers upper mantle that are consistent with postseismic deformation and long term geophysical processes, while also accounting  for shallow afterslip, which perhaps biased the solution from \cite{Pollitz2003}.
-
-what this gives us is a prior constraint on lithospheric viscosity initial that is unbiased by neglecting the contribution of afterslip!
-
-It can be shown (\cite{Hines2015}),
-
-other rheologic models in this study      viscoelasticity is We also test rheologic models other than viscoelasticity to describe
-
-There are numerous other parameters which are not known, but will be considered known in this study.
-
-   Inherent in f is also a stress-linear viscoelastic model.   In this study we will be be known while try to consider
-
-   give table of assumed and estimated material properties
-
-   The early near field postseismic vertical deformation does show a quadrant pattern and is also consistent with the coseismic vertical deformation.  Given
-
-that would not becomes there is no longer a coherent far field deformation signal.
-This is in contrast to near field displacements which persists for the entire 5.0 years of data used in this study.
-Figure () further illustrates the difference in deformation regimes between near field and far field station.
-
-note that subsidence in the peninsular range can be explained with either a localized weakness or conitnued afterslip at seismogenic depths
-
-We use a fault geometry from \cite{Wei2011}, which was determined using teleseismic, GPS, and InSAR data.
-
-make note of \cite{Yamagiwa2014}
-
-note that creep in Brawley is probably the main source of error
-
-After the El Mayor-Cucapah earthquake, additional GPS stations were installed In Baja California to record postseismic deformation with better spatial coverage.
-Two of the stations PTAX and PHJX were installed near the epicenter in the Cucapah Mountains.
-We do not include these two stations in our analysis because the geometry of the faults that ruptured during the earthquake is more complicated than our assumed fault geometry \cite{Oskin2012} \cite{Fletcher2014} and the near field stations would be most sensitive to error in our geometry.
-We also leave of these near field stations in order to avoid any near field processes which we do not consider in this paper \cite{Gonzalez-ortega2014}.
-Numerous stations exhibit extraneous signals which can be
+Additionally, the transient viscosity inferred by \cite{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, which may be the result of shallow afterslip.
+While \cite{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \cite{Jacobs2002}.
+It is then possible that the preferred rheologic model from \cite{Pollitz2003} was biased towards inferring a particularly low transient viscosity by neglecting to account for afterslip.
+This is in contrast to the present study, where we have inferred a lithospheric viscosity structure simultaneously with afterslip.
+While we also argue that a transient rheology is necessary to explain postseismic deformation, our preferred transient viscosity of $10^{18}$ Pa s is an order of magnitude larger than the transient viscosity found by \cite{Pollitz2003}.
+Since we found that A Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady state viscosity that is effectively infinite over five years, would also be able to describe postseismic deformation.
+Such a Burgers model would then be consistent with the steady state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.
 
@@
 \label{fig:ContextMap}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.9]{Figures/rheology}
+\centering 
+\caption{}
+\label{fig:Rheology}
 \end{figure}
@@
 \end{figure}
+
 \begin{figure}
+\includegraphics[scale=0.6]{Figures/lower_crust}
+\centering 
+\caption{afterslip and viscoelastic relaxation in lower crust}
+\label{fig:LowerCrust}
+\end{figure}
 
+\begin{figure}
 \includegraphics[scale=1.0]{Figures/slip_lcurve}

### 2016-03-29 RoughDraft/ElMayor.tex
commit before push

@@
 
-\section*{Introduction}
+\section{Introduction}
 
@@
 Additionally, it is necessary to make simplifying assumptions about the nature of afterslip.
-For example, one can assume a frictional model for afterslip and parameterize afterslip in terms its the unkown rheologic properties \citep[e.g.][]{Johnson2009,Johnson2004}.
+For example, one can assume a frictional model for afterslip and parameterize afterslip in terms its the unknown rheologic properties \citep[e.g.][]{Johnson2009,Johnson2004}.
 Additionally, one can assume that afterslip only dominates the first year of deformation \citep[e.g.][]{Pollitz2012,Spinler2015} and that viscoelastic relaxation is the dominant mechanism in later years.
@@
 
-\section*{Data Processing}
+\section{Data Processing}\label{sec:Data}
 
 We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) stations within a 400 km radius about the El Mayor-Cucapah epicenter.
-Our analysis is on the coseismic and postseismic deformation resulting from the El Mayor-Cucapah earthquake, which we collectively describe as $u(t)$.
-We consider GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular tectonic deformation, annual and semi-annual fluctuations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010 Mw5.8 Ocotillo earthquake and the August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3 event, are the only earthquakes after the EMC earthquake that produced noticeable offsets recorded by GPS.
-Although the Ocotillo earthquake had its own series of aftershocks (Haukson), neither earthquake produced transient deformation that is detectable with GPS.
+Our analysis is on the coseismic and postseismic displacement resulting from the El Mayor-Cucapah earthquake, which we collectively describe as $u(t)$.
+We consider GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
+The June 14, 2010 Mw5.8 Ocotillo earthquake and the August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3 event (figure \ref{fig:ContextMap}), are the only earthquakes after the El Mayor-Cucapah earthquake that produced noticeable offsets recorded by GPS.
+Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither earthquake produced detectable postseismic deformation of its own.
 We thus model $u_\mathrm{obs}(t)$ as
-
 \begin{equation}
@@
   \begin{split}  
-    u_\mathrm{pred}(t) = &u(t) + c_0 + c_1t + \\
+    u_\mathrm{pred}(t) = &u(t)H(t-t_\mathrm{emc}) + c_0 + c_1t + \\
                          &c_2\sin(2\pi t) + c_3\cos(2\pi t) + c_4\sin(4\pi t) + c_5\cos(4\pi t) + \\
@@
 \end{equation}
-In the above equations, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the Ocotillo earthquake and Brawley swarm respectively, $H(t)$ is the Heaviside function, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is noise with zero mean and variance that assumed known.
+In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthuqake, Ocotillo earthquake, and the Brawley swarm respectively, $H(t)$ is the Heaviside function, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
+We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicenters.
 
@@
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-While several stations were installed after the EMC earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015}, our inverse method uses postseismic displacements rather than velocities (e.g.
-...)
-ELABORATE ON VELOCITY VS DISPLACEMENT
-, which requires the knowledge of the stations preseismic position.
-Despite our inability to utilize potentially rich data, we prefer to use postseismic displacements rather than potentially dubious estimates of postseismic velocities.
+Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it is possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
+However, we use coseismic and postseismic displacements, rather than velocities, in our inverse method described in section \ref{sec:Model} because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertanties depending on exactly how the estimation is done.
+This modeling choice prevents us from using the newly installed stations in Baja California in our analysis.
 
-The October 16, 1999 Hector Mine earthquake, which occurred within our study region about 270 km north of the EMC epicenter, has produce transient postseismic deformation which we do not wish to model either mechanically or through empirical line fitting.
-We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, past which point postseismic deformation for nearfield sites occurs at an approximately steady rate \citep{Savage2009}.
-When considering stations further away from the Hector Mine epicenter, postseismic transience persists for only about two years \citep{Spinler2015}.
+The October 16, 1999 Hector Mine earthquake, which occurred within our study region about 270 km north of the El Mayor-Cucapah epicenter, has produce transient postseismic deformation which we do not wish to model either mechanically or through empirical line fitting.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, past which point postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
+When appraising our model fit in section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine, which may be the result of errors in this approximation.
 
-Studies of postseismic deformation typically assume a parametric form for $u(t)$ such as such as a logarithmic or exponential function.
-Such functions have been found empirically e.g.
-\citep{Savage2005a} and theoretically \citep{Marone1991} to adequately describe deformation resulting from postseismic deformation.
-However, by assuming a logarithmic or exponential form of $u(t)$ we run the risk of overfitting the GPS time series and inferring a nonexistent postseismic signal.
-We therefore do not assume any parameteric form for $u(t)$ and rather treat it as integrated Brownian motion, so that
+Studies of postseismic deformation typically assume a parametric form for $u(t)$, such as one with a logarithmic or exponential time dependence \citep[e.g.][]{Savage2005a}.
+However, by assuming a logarithmic or exponential form of $u(t)$ we run the risk of over fitting the GPS time series and inferring a nonexistent postseismic signal.
+We therefore do not assume any parametric form for $u(t)$ and rather treat it as integrated Brownian motion, so that
 \begin{equation}
@@
 \end{equation}    
-
-where $w(t)$ is white noise and the variance of $\dot{u}(t)$ increases linearly with time by a factor of $\sigma^2$. We use a
-Kalman filtering approach to estimate $u(t)$ and the unknown parameters in eq. \ref{TimeSeriesModel} which we describe now.  In the context of Kalman filtering, our time varying state vector is
+where $w(t)$ is white noise and the variance of $\dot{u}(t)$ increases linearly with time by a factor of $\sigma^2$.
+We use a Kalman filtering approach to estimate $u(t)$ and the unknown parameters in eq.
+\ref{TimeSeriesModel}.
+In the context of Kalman filtering, our time varying state vector is
 \begin{equation}
@@
 \ref{TimeSeriesModel} is the observation function which maps the state vector to the GPS observations.
-We initiate the Kalman filter by assuming a prior estimate of $\mathbf{X}(t)$ at time $t_0$ which has a sufficiently large covariance to effectively make our prior uninformed.
-For each time epoch, $t_i$, Bayesian linear regression is used to incorperate GPS derived estimates of displacement with our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a postserior estimate of the state, $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
+We initiate the Kalman filter by assuming a prior estimate of $\mathbf{X}(t)$ at the first time epoch, denoted $\mathbf{X}_{1|0}$, which has a sufficiently large covariance, denoted $\mathbf{\Sigma}_{1|0}$, to effectively make our prior uninformed.
+For each time epoch, $t_i$, Bayesian linear regression is used to incorporate GPS derived estimates of displacement with our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a posterior estimate of the state, $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
 
@@
 
-This process is repeated for each of the $N$ time epochs at which point we use Rauch-Tung-Striebel smoothing to find $X_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates all $N$ GPS observation.
-Our final estimates of $u(t)$ are used in subsequent analysis, while the remaining components of of the state vector are considered nuisance parameters.
+This process is repeated for each of the $N$ time epochs at which point we use Rauch-Tung-Striebel smoothing \citep{Rauch1965} to find $\mathbf{X}_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates GPS observation for all $N$ time epochs.
+Our final estimates of $u(t)$ are used in subsequent analysis, while the remaining components of the state vector are considered nuisance parameters.
 In the interests of computational tractability, we down sample our smoothed time series from daily solutions down to weekly solutions.
@@
 The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
-Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation \citep{Savage2005a}.
-The other endmember, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
-While one can use a maximum likelihood based approach to picking $\sigma^2$ (e.g.
-\citep{Segall1997}), we rather take a subjective approach and choose a value for $\sigma^2$, which is used when filtering time series for each station, that is just large enough to faithfully describes the early rapid rate of postseismic deformation at the most near field station in our study, P496.
-This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal.
-We find that when using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$, we are able to adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{P496Fit}).
-Since we assume that the first week of deformation is overwhelmingly the result of afterslip, any unmodeled afterslip over the first week following the El Mayor-Cucapah earthquake will be added into our estimates of coseismic slip in section ().
-Figure \ref{P496PS} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with its formal uncertainties.
+Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behaviour in postseismic deformation.
+The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
+While one can use a maximum likelihood based approach to picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the postseismic deformation at the most near field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
+We find that when using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$, we are able to adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{fig:P496Fit}).
+We assume that the first week of deformation is overwhelmingly the result of afterslip and any unmodeled afterslip over the first week following the El Mayor-Cucapah earthquake will be added into our estimates of coseismic slip in section \ref{sec:Model}.
+Figure \ref{fig:P496PS} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with the estimated uncertainties.
+\cite{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and indeed, after processing the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we see clear postseismic transient deformation (\ref{fig:P619Fit} and \ref{fig:P619PS}).
 
@@
 \ref{TimeSeriesModel}.
-For example, we assume that the background rate of deformation can be approximated as having a constant rate, while mechanical models would suggest this to not be true on earthquake cycle timescales \citep{Thatcher1983}.
-Although based on inspection,  assuming a constant rate of background deformation appears to be appropriate for all stations except for perhaps the stations closest to the Hector Mine epicenter, where postseismic deformation persists.
+For example, we assume a constant secular rate of deformation, while viscoelastic mechanical models of the earthquake cycle predict that the accumulation of tectonic deformation is nonlinear over time \citep{Thatcher1983}.
+Based on inspection, the rate of secular deformation does appear constant for all stations except for perhaps the stations closest to the Hector Mine epicenter, as noted aboved.
 Also, our model for seasonal deformation in eq.
 \ref{TimeSeriesModel} assumes a constant amplitude over time, which means that years of particularly heavy or light rainfall cannot be adequately described.
-This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (figure \ref{P619PS}).
+This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (e.g.
+figure \ref{fig:P619PS}).
 
-note that stations jumps are only estimated for stations within 40 km of BS or OC
-
-Cite Freed 2007 for far reaching postseismic after Landers/Hector Mine.
-
-We show the difference in $u(t)$ for each station from 0 to 0.8 years (figure \ref{nearfield2} and \ref{farfield2}), 0.8 to 3.2 years (figure \ref{nearfield3} and \ref{farfield3}), and from 3.2 to 5.0 years (figure \ref{nearfield4} and \ref{farfield4}).
-For far field stations (figure \ref{farfield2}, \ref{farfield3}, and \ref{farfield4}), we can see a clear south trending displacement throughout the first 3.2 years in stations as far as 400 km from of the El Mayor Cucapah epicenter.
-These displacements are most pronounced along the direction of the El Mayor-Cucapah P and S axis, as would be expected for postseismic deformation.
-Beyond 3.2 years, The southward trending far field postseismic deformation is barely perceptible.
-There is however, an eastward trend in far field stations just west of the Hector Mine epicenter.
-We suspect this this deformation, which is inconsistent with the pattern expected for El Mayor-Postseismic, is the result of continued transient postseismic deformation following the Hector Mine earthquake.
+We show the near and far field postseismic deformation accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as coseismic displacements in figures \ref{fig:NearField1} through \ref{fig:FarField4}.
+In the far field, we can see clear south trending displacement for the first 3.0 years following the earthquake at stations as far as 400 km from of the El Mayor Cucapah epicenter.
+These displacements are most pronounced along the direction of the El Mayor-Cucapah P and T axis, as would be expected for postseismic deformation.
+After 3.0 years, The southward trending far field postseismic deformation is barely perceptible.
 The vertical deformation in the far field is difficult to attribute to postseismic processes.
@@
 This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
-Although we use vertical deformation in our subsequent analysis, we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
+Although we use vertical deformation in our analysis in section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
 
-Near field deformation is show in figures \ref{nearfield2}, \ref{nearfield3}, and \ref{nearfield4}.
-The near field deformation is notably sustained when compared to the far field deformation.
+The near field postseismic deformation is notably sustained when compared to the far field deformation.
 Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of ~1.4 cm/yr to the south five years after the El Mayor-Cucapah earthquake.
 Vertical postseismic deformation in the near field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
-However, the vertical postseismic deformation signal is only apparent in the early postseismic period (figure \ref{nearfield2}).
+However, the vertical postseismic deformation signal is only apparent in the early postseismic period (figure \ref{fig:NearField2}).
 As with the far field deformation, there is a general trend of uplift in the near field one year after the earthquake which we do not consider to be related to postseismic processes.
 
-\section*{Postseismic Modeling}
+\section{Postseismic Modeling}\label{sec:Model}
 
@@
 We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechanisms.
-Poroelastic rebound has also been used to model postseismic deformation \cite{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
+Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
 Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
 
-\subsection*{model design}
-We estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \cite{Wei2011} with some modifications.
-Field studies \cite{Fletcher2014} and LIDAR observations \cite{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \cite{Wei2011}, especially within the Sierra Cucapah.
-However, we find the relatively simple coseismic fault geometry from \cite{Wei2011a} to be sufficient because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
+We estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \citet{Wei2011} with some modifications.
+Field studies \citep{Fletcher2014} and LIDAR observations \citep{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \citet{Wei2011}, especially within the Sierra Cucapah.
+However, we find the relatively simple coseismic fault geometry from \cite{Wei2011} to be sufficient because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
 The fault geometry used in this study (figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \cite{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
-Additionally, We extend the northern segment by 40 km to the northwest which is motivated by the clustering of aftershocks on the northern tip of coseismic rupture zone \cite{Kroll2013} \cite{Hauksson2011}.
+Additionally, We extend the northern segment by 40 km to the northwest which is motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
 This extended fault segment was also found to be necessary by \cite{Rollins2015} and \cite{Pollitz2012} for describing postseismic deformation.
@@
 It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, at least in 2D earthquake models.
-In the interest of eliminating null space in our inverse problem,  we assuming afterslip occurs only at seismogenic depths ($<15$ km), and we allow for viscoelastic relaxation in the lower crust (15-30 km) and the upper mantle.
+In the interest of eliminating null space in our inverse problem,  we assume that afterslip occurs only at seismogenic depths ($<15$ km), and we allow for viscoelastic relaxation in the lower crust (15-30 km) and the upper mantle.
 We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
@@
 The horizontal displacement from fault slip is in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
-This means that displacement resulting from afterslip at lower crustal depths can be cancelled out by a low viscosity lower crust.
+This means that displacement resulting from afterslip at lower crustal depths can be cancelled out, at least partially, by a low viscosity lower crust.
 We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
-Aside from the issue of nonuniqueness, it is also nonsensical to allow for both brittle and ductile deformation mechanisms at the same depth.
+Aside from the issue of non-uniqueness, it is also nonsensical to allow for both brittle and ductile deformation mechanisms at the same depth.
 
-A schematic representation of the viscoelastic rheologic models considered in this study for the lower crust and upper mantle are shown in figure (TBD).
+A schematic representation of the viscoelastic rheologic models considered in this study for the lower crust and upper mantle are shown in figure \ref{fig:Rheology}.
 We consider Maxwell viscoelasticity, where the steady state viscosity $\eta_M$ is unknown; Zener viscoelasticty, where the transient viscosity $\eta_K$ and transient shear modulus $\mu_K$ are unknown; and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all largely unknown.
@@
   u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
-           \int_0^t\int_F s(\tau,\xi) f(t-\tau,x,\xi) d\xi d\tau
+           \int_0^t\int_F s(\xi,\tau) f(t-\tau,x,\xi) d\xi d\tau
 \end{equation}
-where $g(x,\xi)$ describes the instantaneous elastic displacements at $x$ resulting from a unit of slip at $\xi$, and $f(t,x,\xi)$ describes the velocity at $x$ resulting from viscoelastic relaxation of stresses induced by slip at $\xi$.
+where $g(x,\xi)$ describes the instantaneous elastic displacements at $x$ resulting from a unit of slip at $\xi$, and $f(t,x,\xi)$ describes the time dependent velocity at $x$ resulting from viscoelastic relaxation of stresses induced by slip at $\xi$.
 $f$ is a function of the properties of the chosen rheologic model, which are generally not well known.
@@
 Although eq.
-\ref{ApproxForward} may only valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are functions of the fault geometry and instantaneous elastic properties, which are fairly well known, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem, eq.
+\ref{ApproxForward} may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are functions of the fault geometry and instantaneous elastic properties, which are fairly well known, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem, eq.
 \ref{ApproxForward}, can be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
@@
 \ref{GeneralForward}, numerically for each realization of $s$ and unkown rheologic properties which is far more computationally demanding.
+Figure \ref{fig:Rheology} shows how $\eta_\mathrm{eff}$ relates to the parameters for various linear viscoelastic rheologies.
 
@@
 \ref{ApproxForward} as our forward problem.
-As noted, we use the fault geometry from \cite{Wei2011}, except that each segment extends to 15 km depth and the north segment is extended 40 km northward.
+As noted, we use the fault geometry from \citet{Wei2011}, except that each segment extends to 15 km depth and the north segment is extended 40 km northward.
 Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
-We estimate coseismic slip as well as a rate of afterslip which is constant over the time intervals spanning 0.0-0.125, 0.125-0.25, and 0.5-1.0 years following the earthquake, as well as over 1.0 year intervals for the remaining postseismic period.
+We estimate coseismic slip as well as the rate of afterslip over time intervals spanning 0.0-0.125 years, 0.125-0.25 years, 0.5-1.0 years, and at 1.0 year intervals for the remaining five years.
 We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip.
-We estimate $\eta_{\mathrm{eff}}$ within 6 vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain, 800 km.
-Details of the inverse method are described in \cite{Hines2015}.
-We note that a nonlinear Kalman filter based inverse method can be employed to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \cite{Segall1997} or \cite{McGuire2003}, where we do not have to explicitly impose a time dependent parameterization of $s$.
-Indeed we have thoroughly explored that possibility but we ultimately prefer the method described in \cite{Hines2015} because of its relative simplicity and because we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general.
+We estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain, 800 km.
+Details of the inverse method are described in \citet{Hines2015}.
+We note that a nonlinear Kalman filter based inverse method can be employed to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, where we do not have to explicitly impose a time dependent parameterization of $s$.
+Indeed we have thoroughly explored that possibility but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity and because we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general.
 
@@
 As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
-We can almost certainly assume that deformation at the most far field stations which are ~400 km away from the El Mayor-Cucapah epicenter is the result of viscoelastic relaxation.
+We can almost certainly assume that deformation at the most far field stations which are $\sim400$ km away from the El Mayor-Cucapah epicenter is the result of viscoelastic relaxation.
 The approximation should then be valid for as long as a linear trend adequately approximates the far field deformation.
@@
 
-We want to find the discretize parameters describing coseismic slip and the rate of afterslip, $\mathbf{s}$, and viscosity, $\mathbf{\eta_{\mathrm{eff}}}$, that minimize the difference between the each discrete observation of postseismic deformation over the first 0.8 years following the El Mayor-Cucapah earthquake, which is here denoted $\mathbf{u_\mathrm{obs}}$, and the discrete observations predicted in eq.
+We want to find the discretized parameters describing coseismic slip and the rate of afterslip, $\mathbf{s}$, and viscosity, $\mathbf{\eta_{\mathrm{eff}}}$, that minimize the difference between the each discrete observation of postseismic deformation over the first 0.8 years following the El Mayor-Cucapah earthquake, which is here denoted $\mathbf{u_\mathrm{obs}}$, and the discrete observations predicted in eq.
 \ref{ApproxForward}, $\mathbf{u_\mathrm{pred}}$.
@@
 Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
-Although fluidities is a sparesly used metric, it is more natural to use fludities rather than viscosity since eq.
-\ref{InitialRate} is linear with respect to fluidity and so the fluidity represents the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere.
+Although fluidity is a sparsely used metric, it is more natural to use fludities rather than viscosity since eq.
+\ref{InitialRate} is linear with respect to fluidity and so the fluidity represents the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere and asthenosphere.
 We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_v$, and our choice our $\lambda_v$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
@@
 The uncertainties in fluidities increases with depth, as would be expected due to decreased sensitivity with depth.
-Nevertheless, a robust feature that we see in this that the viscosity below 60 km depth needs to be $\sim 10^{18}$ Pa s to describe the early rate of postseismic deformation for stations greater than $\sim 200$ km from the epicenter.
-The viscosity of the lower crust is the least well constrained as there is effectively no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years of postseismic, $> 10^{19}$ Pa s.
+Nevertheless, a robust feature that we see is that the viscosity below 60 km depth needs to be $\sim 10^{18}$ Pa s to describe the early rate of postseismic deformation for stations greater than $\sim200$ km from the epicenter (JUSTIFY THIS).
+This inferred transitional depth is consistent with the regionally averaged lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}.
+The viscosity of the lower crust is the least well constrained as there is effectively no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years of postseismic, $>10^{19}$ Pa s.
 Our inference of a mantle viscosity of $\sim 10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady state viscosities from \cite{Pollitz2000}, \cite{Pollitz2003}, \cite{Johnson2007}, \cite{Spinler2015}, and \cite{Rollins2015}.
@@
 Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figures \ref{fig:InitialCoseismic} and \ref{fig:InitialAfterslip} respectively.
-To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show a coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but while assuming the lithosphere and ashthenosphere are elastic.
+To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show a coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but we assume the lithosphere and ashthenosphere are elastic.
 In both coseismic inversion, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
-This is consistent with field studies, \cite{Fletcher2014} as well as coseismic slip models \cite{Wei2011}.
+This is consistent with field studies, \cite{Fletcher2014} as well as the coseismic slip model from \cite{Wei2011}.
 The potency of inferred coseismic slip is $3.32\times 10^{9} \mathrm{m}^3$, which is equivalent to a moment magnitude of 7.28 when assuming a shear modulus of $3.2\times10^{10}$ Pa.
@@
 The striking difference between the two models is that the inferred afterslip on the Indiviso fault segment is significantly larger when not accounting for viscoelasticity.
-The potency of afterslip in the elastic model is $2.7\times 10^9 \mathrm{m}^3$, compared to $0.85\times 10^9 \mathrm{m}^3$.
+The potency of afterslip in the elastic model is $2.7\times 10^9 \mathrm{m}^3$, compared to $0.85\times 10^9 \mathrm{m}^3$ for the viscoelastic model.
 The former is comparable to the size of the mainshock which, as noted by \cite{Rollins2015}, is implausibly large.
-The significant amount of afterslip on the Indiviso fault inferred by \cite{Rollins2015}, which is predicts broadscale deformation for the GPS stations used in this study, seems to be compensating for unmodeled viscoelastic relaxation at depths of $>60$ km.
-This inferred transitional depth is consistent with the regionally averaged lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}.
+The significant amount of afterslip inferred to be on the Indiviso fault by \cite{Rollins2015} seems to be compensating for unmodeled viscoelastic relaxation at depths of $>60$ km.
 The fact that there is still a substantial amount of deep afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than we allow for since we only estimate depth dependent variations in viscosity.
@@
 In the previous section we used the efficient inverse method described by \cite{Hines2015} to constrain the effective lithospheric viscosity required to explain the first 0.8 years of postseismic deformation.
-In this section we use the inferred effective lithospheric viscosities as a prior constraint when searching for rheologic models of the lithosphere which are capable of describing the available 5 years of postseismic data.
+In this section we use the inferred effective lithospheric viscosities as a prior constraint when searching for rheologic models of the lithosphere which are capable of describing the available five years of postseismic data.
 
-Table 1 describes how the inferred effective viscosities from section \ref{InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
+Figure \ref{fig:Rheology} describes how the inferred effective viscosities from section \ref{InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
 In this section we perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from \ref{InitialInversion}.
@@
 The misfit of the best fit models to the observed postseismic data when varying $\nu$ is shown in figure \ref{fig:ShearModulusRatio}.
-The optimal value of $\nu$ is found to be $0.375$ which decreases the misfit by only about \%10; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (\ref{fig:FinalFarFieldRS}).
+The optimal value of $\nu$ is found to be $0.375$ which decreases the misfit by only about 10\%; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (\ref{fig:FinalFarFieldRS}).
 This significant improvement is seen for all shear modulus  ratios greater than about $0.125$.
@@
 In Southern California, postseismic studies following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s with a relatively stronger lower crust.
+Our inference that the the crust and uppermost mantle are relatively strong compared to the underlying mantle is also consistent with that found by \cite{Freed2007a}.
 While these inferences are consistent with our effective viscosities, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
@@
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/figure_1}
+\includegraphics[scale=0.45]{Figures/filterP496}
 \centering
-\caption{GPS displacement solution from UNAVCO (black) and predicted displacements after applying a Kalman filter where $\sigma^2=0.05 \mathrm{m}^2/\mathrm{yr}^3$.
-Red line indicates the time of the Ocotillo earthquake where a jump in the time series is estimated}
-\label{fig:P496Fit}
+\caption{}
+\label{fig:P496}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/figure_2}
+\includegraphics[scale=0.45]{Figures/filterP619}
 \centering
-\caption{Postseismic displacements estimated after applying a Kalman filter to the GPS displacement solution from UNAVCO.
-Displacements shown have had a background secular trend removed as well as an estimated seasonal signal.}
-\label{fig:P496PS}
+\caption{} 
+\label{fig:P619}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/figure_3}
+\includegraphics[scale=0.4]{Figures/nearfield}
 \centering 
-\caption{GPS displacement solution from UNAVCO (black) and predicted displacements after applying a Kalman filter where $\sigma^2=0.05 \mathrm{m}^2/\mathrm{yr}^3$.
-Red line indicates the time of the Ocotillo earthquake where a jump in the time series is estimated}
-\label{fig:P619Fit}
+\caption{}
+\label{fig:NearField}
 \end{figure}
@@
 \begin{figure}
-
-\includegraphics[scale=0.6]{Figures/figure_4}
+\includegraphics[scale=0.4]{Figures/farfield}
 \centering 
-\caption{Postseismic displacements estimated after applying a Kalman filter to the GPS displacement solution from UNAVCO.
-Displacements shown do not include the estimated secular trend, seasonal signals, and displacements resulting from the Ocotillo earthquake.}
-\label{fig:P619PS}
+\caption{}
+\label{fig:FarField}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.6]{Figures/near_field_data_1}
+\includegraphics[scale=0.6]{Figures/recordsection1}
 \centering 
-\caption{}
-\label{fig:NearField1}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.6]{Figures/near_field_data_2}
-\centering 
-\caption{}
-\label{fig:NearField2}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.6]{Figures/near_field_data_3}
-\centering 
-\caption{}
-\label{fig:NearField3}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.6]{Figures/near_field_data_4}
-\centering 
-\caption{}
-\label{fig:NearField4}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_1}
-\centering 
-\caption{}
-\label{fig:FarField1}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_2}
-\centering 
-\caption{}
-\label{fig:FarField2}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_3}
-\centering 
-\caption{}
-\label{fig:FarField3}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_4}
-\centering 
-\caption{}
-\label{fig:FarField4}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.9]{Figures/near_field_record_section}
-\centering 
-\caption{near field record section}
-\label{fig:NearFieldRS}
-\end{figure}
-\begin{figure}
-\includegraphics[scale=0.9]{Figures/far_field_record_section}
-\centering 
-\caption{far field record section}
-\label{fig:FarFieldRS}
+\caption{record section}
+\label{fig:RecordSection1}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.1]{Figures/initial_coseismic}
-\caption{coseismic slip from initial inversion}
-\label{fig:InitialCoseismic}
+\includegraphics[scale=0.09]{Figures/initialslip}
+\caption{}
+\label{fig:InitialSlip}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.1]{Figures/initial_afterslip}
-\centering 
-\caption{afterslip from initial inversion}
-\label{fig:InitialAfterslip}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.1]{Figures/initial_elastic_coseismic}
-\centering 
-\caption{coseismic slip from elastic inversion}
-\label{fig:InitialElasticCoseismic}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.1]{Figures/initial_elastic_afterslip}
-\centering 
-\caption{afterslip from elastic inversion}
-\label{fig:InitialElasticAfterslip}
+\includegraphics[scale=0.09]{Figures/elasticslip}
+\caption{}
+\label{fig:InitialSlip}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.1]{Figures/final_coseismic}
+\includegraphics[scale=0.09]{Figures/finalslip}
 \centering 
 \caption{}
-\label{fig:FinalCoseismic}
+\label{fig:FinalSlip}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.1]{Figures/final_afterslip_0-1}
+\includegraphics[scale=0.6]{Figures/recordsection2}
 \centering 
 \caption{}
-\label{fig:FinalAfterslip1}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.1]{Figures/final_afterslip_1-3}
-\centering 
-\caption{}
-\label{fig:FinalAfterslip2}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.1]{Figures/final_afterslip_3-5}
-\centering 
-\caption{}
-\label{fig:FinalAfterslip3}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.9]{Figures/near_field_final_record_section}
-\centering 
-\caption{}
-\label{fig:FinalNearFieldRS}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.9]{Figures/far_field_final_record_section}
-\centering 
-\caption{}
-\label{fig:FinalFarFieldRS}
+\label{fig:RecordSection2}
 \end{figure}

### 2016-04-04 RoughDraft/ElMayor.tex
commit before push

@@
-\documentclass[12pt]{article}
+\documentclass[1p]{elsarticle}
 
-\usepackage{amssymb,amsmath}
-\usepackage[margin=1.0in]{geometry}
-\usepackage{fancyhdr} % required for custom header
-\usepackage{graphicx}
-\usepackage{listings}
-\usepackage{courier}
-\usepackage[usenames,dvipsnames]{color}
+\usepackage{amssymb,amsmath,amsthm,amsfonts}
+%\usepackage[margin=1.0in]{geometry}
+%\usepackage{fancyhdr} % required for custom header
+%\usepackage{graphicx}
+%\usepackage{listings}
+%\usepackage{courier}
+%\usepackage[usenames,dvipsnames]{color}
 \usepackage[maxfloats=40]{morefloats}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{natbib}
+%\usepackage{caption}
+%\usepackage{subcaption}
+%\usepackage{natbib}
+%\usepackage{setspace}
+%\doublespacing
 
 %set up the header
-\pagestyle{fancy}
-\lhead{Trever Hines}
-\chead{El Mayor Postseismic}
-\rhead{\today}
+%\pagestyle{fancy}
+%\lhead{Trever Hines}
+%\chead{El Mayor Postseismic}
+%\rhead{\today}
 
-\setlength{\headheight}{15pt}
-\renewcommand\headrulewidth{1.0pt} % Size of the header rule
+%\setlength{\headheight}{15pt}
+%\renewcommand\headrulewidth{1.0pt} % Size of the header rule
 
@@
 \title{	
-El Mayor Postseismic
-\author{Trever Hines}
-\rule{\headwidth}{1.0pt}
-}
+Rheologic contraints on the Lithosphere and Asthenosphere from five years of Postseismic deformation following the El Mayor-Cucapah earthquake}
+\author{T. T. Hines\fnref{fn}}
+\author{E. A. Hetland\fnref{fn}}
+\fntext[fn]{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, MI, USA}
 
 \begin{document}
+\begin{abstract}
+foo bar
+\end{abstract}
 \maketitle
-\section*{Abstract}
-we propose a anelastic phase of deformation in the mantle distinct from phases associated with attenuation
 
 \section{Introduction}
+Ground deformation in the years following a large ($>$Mw7) earthquake provides insight into the mechanical behaviour of the lithosphere.
+It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions (e.g.
+\cite{Savage1990}).
+Thanks to the dense geodetic network deployed throughout the 2000's as part of the Plate Boundary Observatory, the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California produced observable postseismic deformation at more GPS stations than any other earthquake in California to date.
+With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake, where we consider both afterslip and viscoelastic relaxation in lithosphere and asthenosphere as candidate mechanisms.
 
 Previous studies which have modeled postseismic deformation following the El Mayor-Cucapah earthquake include \citet{Pollitz2012}, \citet{Gonzalez-ortega2014}, \citet{Spinler2015}, and \citet{Rollins2015}.
-\citet{Gonzalez-ortega2014} was able to describe five months of near field ($\lesssim 50$ km from the epicenter) postseismic defomation observed by InSAR and campaign GPS with afterslip and fault contraction on the coseismically ruptured fault.
-\citet{Gonzalez-ortega2014} also noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
-Using continuous GPS stations within 200 km of the El Mayor-Cucapah epicent, which consists mostly of stations north of the US-Mexico border, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip in an elastic lithosphere, albeit with an implausibly large amount of afterslip inferred on the least constrained southern most fault segment which may be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
-In this paper, we reiterate this finding by \citet{Rollins2015} and note that a purely elastic dislocation model is incapable of describing deformation observed at GPS stations greater than ~200 km from the El Mayor-Cucapah epicenter.
+Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the observations with afterslip in an entirely elastic lithosphere and asthenosphere.
+\citet{Gonzalez-ortega2014} described five months of postseismic deformation observed by nearfield ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR with afterslip and contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
+Using continuous GPS stations, which are mostly north of rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of afterslip inferred on the least constrained, southern most fault segment.
+Here, we suggest this inferred afterslip may have been acting as a proxy for distributed relaxation in the upper mantle.
 
-Given the inability to describe both near and far field deformation with fault slip in an elastic lithosphere, \citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential deformation mechanism.
-The lithospheric rheology is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and find the best fitting model parameters, which is generally a computationally expensive nonlinear inverse problem.
+\citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential postseismic deformation mechanism.
+The lithospheric rheology is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and then find the best fitting rheologic parameters.
+The inference of these rheologic parameters is a computationally expensive nonlinear inverse problem which is typically approached with a forward modeling grid search method.
 Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
-For example, it is commonly assumed that the lithosphere consists of only three homogeneously Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep[e.g.][]{Hines2013,Riva2009}.
-Additionally, it is necessary to make simplifying assumptions about the nature of afterslip.
-For example, one can assume a frictional model for afterslip and parameterize afterslip in terms its the unknown rheologic properties \citep[e.g.][]{Johnson2009,Johnson2004}.
-Additionally, one can assume that afterslip only dominates the first year of deformation \citep[e.g.][]{Pollitz2012,Spinler2015} and that viscoelastic relaxation is the dominant mechanism in later years.
-However, numerous observations of interseismic fault creep has been recognized in this and similar tectonic settings and it has been speculated that such creep can be initiated as a postseismic process \citep{Cakir2012,Cetin2014}.
-We therefore do not make to implicit assumption that afterslip terminates after a given amount of time.
-Indeed, the preferred viscoelastic model from \citet{Pollitz2012} underestimates near field velocities, which could be indicative of unmodeled continued afterslip.
+For example, it is commonly assumed that the lithosphere consists of only three homogeneous, Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep[e.g.][]{Riva2009,Hines2013}.
+To further reduce the model space dimensions being search, it is also necessary to make simplifying assumptions about the nature of afterslip.
+For example, one can assume a frictional model for afterslip and parameterize afterslip in terms of the unknown rheologic properties of the fault \citep[e.g.][]{Johnson2009,Johnson2004}.
+One can also assume that afterslip does not persist for more than a few months or a year and then model the later postseismic deformation assuming it to be the result of only viscoelastic relaxation \citep[e.g.][]{Pollitz2012,Spinler2015}.
+However, postseismic afterslip in similar tectonic settings has been observed to persist for decades following earthquakes \citep{Cakir2012,Cetin2014}.
+Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to a biased inference of lithospheric viscosity.
+Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near field deformation, which could be indicative of unmodeled continued afterslip.
 
-All of the aforementioned studies model displacements observered at stations within 200 km of the El Mayor-Cucapah epicenter, while postseismic deformation in this region following previous earthquakes of similar magnitude has been observed at distances extended out to about 300 km \citep{Freed2007a}.
-In the present study we examine stations within 400 km of the El Mayor-Cucapah epicenter, which turns out to be crucial for discerning the postseismic deformation mechanism.
+In this study, we assume that both afterslip and viscoelastic relaxation can contribute to postseismic deformation.
+Modeling both of these mechanisms creates a high dimensional model space that must be searched with nonlinear optimization methods.
+We first develop an initial postseismic model using the method described in \citet{Hines2015}.
+This method simultaneously estimate the afterslip and effective lithospheric viscosity structure necessary to describe the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
+We then use the inferred effective viscosity structure to create a suite of postseismic models which are tested against available five years of postseismic data.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of sustained afterslip beneath the Sierra Cucapah and a Zener rheology upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s at 30 km depth to $1\times10^{18}$ Pa s at 120 km depth.
 
-Clearly, both afterslip and viscoelastic relaxation are involved in postseismic deformation neglecting to model one of these deformation mechanisms could result in a biased estimate of the other.
-In this paper we use the inverse method described in \citet{Hines2015} to estimate the afterslip an effective viscosity necessary to describe the transience postseismic deformation over the first ten months after the El Mayor-Cucapah earthquake.
-We then form a suite of models which have various lithospheric rheologies but viscosities that are consistent with the effective viscosity estimated from the early postseismic deformation.
-Of the suite of models tested, we find that five years of postseismic deformation can be explained by a combination of sustained afterslip on the coseismicly ruptured fault and a Zener rheology upper mantle with viscosity that decays from $\sim5\times10^{18}$ to $\sim1\times10^{18}$ Pa s.
+\begin{figure}
+\includegraphics[scale=0.8]{Figures/context_map} 
+\caption{Map of the area where postseismic deformation following the El Mayor-Cucapah earthquake can be observed geodetically.
+The large focal mechanism is for the El Mayor Cucapah earthquake and the three small focal mechanisms are for the Octotillo earthquake and the two main shocks during the Brawley swarm.
+The black dots indicate the locations of GPS stations used in this study.
+The fault geometry used in this study is shown in cyan where dashed lines indicate buried edges of the fault segments.
+The green and red boxes denote the extent of the near and far field displacement maps.
+The blue sector highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis and stations within this sector are used in the record sections in figures \ref{fig:RecordSection1} and \ref{fig:RecordSection2}}
+\label{fig:ContextMap}
+\end{figure}
 
@@
 
-We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) stations within a 400 km radius about the El Mayor-Cucapah epicenter.
-Our analysis is on the coseismic and postseismic displacement resulting from the El Mayor-Cucapah earthquake, which we collectively describe as $u(t)$.
-We consider GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010 Mw5.8 Ocotillo earthquake and the August 26, 2012 Brawley swarm, which consisted of a Mw5.5 and Mw5.3 event (figure \ref{fig:ContextMap}), are the only earthquakes after the El Mayor-Cucapah earthquake that produced noticeable offsets recorded by GPS.
-Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither earthquake produced detectable postseismic deformation of its own.
-We thus model $u_\mathrm{obs}(t)$ as
+We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicenter.
+We describe the coseismic and postseismic displacement resulting from the El Mayor-Cucapah earthquake collectively as $u_\mathrm{post}(t)$ and we consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
+The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.3 event on August 26, 2012, (figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the GPS position timeseries.
+We treat the displacements resulting from the Brawley swarm as a single event because the position time series are provided by UNAVCO as daily solutions.
+Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation and we model displacements resulting from these events with a Heaviside function, $H(t)$.
+We then model $u_\mathrm{obs}(t)$ as
 \begin{equation}
@@
   \begin{split}  
-    u_\mathrm{pred}(t) = &u(t)H(t-t_\mathrm{emc}) + c_0 + c_1t + \\
+    u_\mathrm{pred}(t) = &u_\mathrm{post}(t)H(t-t_\mathrm{emc}) + c_0 + c_1t + \\
                          &c_2\sin(2\pi t) + c_3\cos(2\pi t) + c_4\sin(4\pi t) + c_5\cos(4\pi t) + \\
@@
 \end{equation}
-In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthuqake, Ocotillo earthquake, and the Brawley swarm respectively, $H(t)$ is the Heaviside function, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
+In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthuqake, Ocotillo earthquake, and the Brawley swarm, respectively, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
 We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicenters.
 
-Stations which recorded signals that clearly cannot be described by the aforementioned processes are not included in our analysis.
-This includes stations in the Los Angeles basin, which record deformation that is largely anthropogenic.
+Stations which recorded displacements that clearly cannot be described by the aforementioned processes are not included in our analysis.
+This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Argus2005} .
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it is possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
-However, we use coseismic and postseismic displacements, rather than velocities, in our inverse method described in section \ref{sec:Model} because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertanties depending on exactly how the estimation is done.
+Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it would be possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
+However, we use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
+We use displacements because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertanties depending on exactly how the estimation is done (REF).
 This modeling choice prevents us from using the newly installed stations in Baja California in our analysis.
 
-The October 16, 1999 Hector Mine earthquake, which occurred within our study region about 270 km north of the El Mayor-Cucapah epicenter, has produce transient postseismic deformation which we do not wish to model either mechanically or through empirical line fitting.
-We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, past which point postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
-When appraising our model fit in section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine, which may be the result of errors in this approximation.
+The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred about 270 km north of the El Mayor-Cucapah epicenter, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
+When appraising our model fit in Section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine epicenter, which may be the result of errors in the assumption that the trend in Hector Mine postseismic deformation is linear after six years.
 
-Studies of postseismic deformation typically assume a parametric form for $u(t)$, such as one with a logarithmic or exponential time dependence \citep[e.g.][]{Savage2005a}.
-However, by assuming a logarithmic or exponential form of $u(t)$ we run the risk of over fitting the GPS time series and inferring a nonexistent postseismic signal.
-We therefore do not assume any parametric form for $u(t)$ and rather treat it as integrated Brownian motion, so that
+Studies of postseismic deformation typically assume a parametric form for $u_\mathrm{post}(t)$, such as one with a logarithmic or exponential time dependence \citep[e.g.][]{Savage2005a}.
+However, by assuming a logarithmic or exponential form of $u_\mathrm{post}(t)$ we run the risk of over fitting the GPS time series and inferring a nonexistent postseismic signal.
+We therefore do not assume any parametric form for $u_\mathrm{post}(t)$ and rather treat it as integrated Brownian motion, so that
 \begin{equation}
-    \dot{u}(t) = \sigma^2\int_0^t w(s) ds.
+    \dot{u}_\mathrm{post}(t) = \sigma^2\int_0^t w(s) ds,
 \end{equation}    
-where $w(t)$ is white noise and the variance of $\dot{u}(t)$ increases linearly with time by a factor of $\sigma^2$.
-We use a Kalman filtering approach to estimate $u(t)$ and the unknown parameters in eq.
+where $w(t)$ is white noise and the variance of $\dot{u}_\mathrm{post}(t)$ increases linearly with time by a factor of $\sigma^2$.
+We use a Kalman filtering approach to estimate $u_\mathrm{post}(t)$ and the unknown parameters in eq.
 \ref{TimeSeriesModel}.
@@
 \begin{equation}
-    \mathbf{X}(t) = [u(t),\dot u(t), c_0, ..., c_7]
+    \mathbf{X}(t) = [u_\mathrm{post}(t),\dot u_\mathrm{post}(t), c_0, ..., c_7]
 \end{equation}
@@
 This process is repeated for each of the $N$ time epochs at which point we use Rauch-Tung-Striebel smoothing \citep{Rauch1965} to find $\mathbf{X}_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates GPS observation for all $N$ time epochs.
-Our final estimates of $u(t)$ are used in subsequent analysis, while the remaining components of the state vector are considered nuisance parameters.
+Our final estimates of $u_\mathrm{post}(t)$ are used in subsequent analysis, while the remaining components of the state vector are considered nuisance parameters.
 In the interests of computational tractability, we down sample our smoothed time series from daily solutions down to weekly solutions.
 
-The smoothness of $u(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect the postseismic signal to vary over time.
-Setting $\sigma^2$ equal to zero will effectively result in modeling $u(t)$ as a straight line which is insufficient to describe the expected transient behaviour in postseismic deformation.
-The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ fitting what is obviously noise in the data.
-While one can use a maximum likelihood based approach to picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the postseismic deformation at the most near field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
-This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
-We find that when using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$, we are able to adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{fig:P496Fit}).
-We assume that the first week of deformation is overwhelmingly the result of afterslip and any unmodeled afterslip over the first week following the El Mayor-Cucapah earthquake will be added into our estimates of coseismic slip in section \ref{sec:Model}.
-Figure \ref{fig:P496PS} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with the estimated uncertainties.
-\cite{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and indeed, after processing the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we see clear postseismic transient deformation (\ref{fig:P619Fit} and \ref{fig:P619PS}).
+The smoothness of $u_\mathrm{post}(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect postseismic displacements to vary over time.
+Setting $\sigma^2$ equal to zero will effectively result in modeling $u_\mathrm{post}(t)$ as a straight line which is insufficient to describe the expected transient behaviour in postseismic deformation.
+The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ overfitting the data.
+While one can use a maximum likelihood based approach to picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
+We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{fig:P496}).
+By down sampling, we implicitly assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
+Figure \ref{fig:P496} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with the estimated uncertainties.
+\cite{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and indeed, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we also clearly see far reaching postseismic transient deformation (figure \ref{fig:P619}).
 
-It is important to note that the shown uncertainties in $u(t)$ do not account for the non-negligible epistemic uncertainty in eq.
+It is important to note that the shown uncertainties in $u_\mathrm{post}(t)$ do not account for the non-negligible epistemic uncertainty in eq.
 \ref{TimeSeriesModel}.
@@
 This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (e.g.
-figure \ref{fig:P619PS}).
+figure \ref{fig:P619}).
 
-We show the near and far field postseismic deformation accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as coseismic displacements in figures \ref{fig:NearField1} through \ref{fig:FarField4}.
+We show the near and far field postseismic deformation accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as coseismic displacements in figures \ref{fig:NearField} and \ref{fig:FarField}.
 In the far field, we can see clear south trending displacement for the first 3.0 years following the earthquake at stations as far as 400 km from of the El Mayor Cucapah epicenter.
@@
 The near field postseismic deformation is notably sustained when compared to the far field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of ~1.4 cm/yr to the south five years after the El Mayor-Cucapah earthquake.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of $\sim1.4$ cm/yr to the south five years after the El Mayor-Cucapah earthquake.
 Vertical postseismic deformation in the near field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
-However, the vertical postseismic deformation signal is only apparent in the early postseismic period (figure \ref{fig:NearField2}).
+However, the vertical postseismic deformation signal is only apparent for the first year after the earthquake (figure \ref{fig:NearField}).
 As with the far field deformation, there is a general trend of uplift in the near field one year after the earthquake which we do not consider to be related to postseismic processes.
@@
 
+\begin{table}\label{tab:MaterialProperties}
+\begin{tabular} {l l l l l l}
+depth (km) &$\lambda$ (GPa)&$\mu$ (Gpa)&$\rho$ (kg/m$^3$)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
+0-5 & 24.0 & 24.3 & 2400 & - & -\\
+5-15 & 35.2 & 35.4 & 2670 & - & -\\
+15-30 & 41.8 & 41.9 & 2800 & 44.3 & 0.0\\
+30-60 & 61.0 & 60.8 & 3000 & 5.91 & 0.375\\
+60-90 & 61.0 & 60.8 & 3000 & 1.99 & 0.375\\
+90-120 & 61.0 & 60.8 & 3000 & 1.31 & 0.375\\
+120-150 & 61.0 & 60.8 & 3000 & 1.10 & 0.375\\
+150-$\infty$ & 61.0 & 60.8 & 3000 & 1.07 & 0.375\\
+\end{tabular}
+\caption{Assumed and estimated material properties.
+$\lambda$, $\mu$, and $\rho$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in section \ref{sec:InitialInversion} and $\mu_k/\mu$ are the optimal shear moduli ratios found in section \ref{sec:FullInversion} for a Zener rheology.}
+
+\end{table}
 In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We consider afterslip and viscoelastic relaxation in the lithosphere and/or asthenosphere as candidate mechanisms.
+We consider afterslip and viscoelastic relaxation in the lithosphere and asthenosphere as candidate mechanisms.
 Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
@@
 Field studies \citep{Fletcher2014} and LIDAR observations \citep{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \citet{Wei2011}, especially within the Sierra Cucapah.
-However, we find the relatively simple coseismic fault geometry from \cite{Wei2011} to be sufficient because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
+However, we find the relatively simple coseismic fault geometry from \cite{Wei2011} to be adequate because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
 The fault geometry used in this study (figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \cite{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
@@
 
-\subsection*{constraint on effective viscosity}\label{InitialInversion}
+\subsection{constraint on effective viscosity}\label{sec:InitialInversion}
 For any linear viscoelastic rheology of the lithosphere and asthenosphere, postseismic displacement resulting from time dependent fault slip, $s(\xi,t)$, on a fault $F$ can be described as  
@@
 $f$ is a function of the properties of the chosen rheologic model, which are generally not well known.
-The parameters controlling the instantaneous elastic behaviour of the lithosphere and asthenosphere, $\mu$, $\lambda$, and density $\rho$, are relatively well known and we use the values listed in table (TBD), which are consistent with the properties used in the coseismic model by \cite{Wei2011} and the 1D SCEC background velocity model.
+The parameters in $g$ which control the instantaneous elastic displacements, $\mu$, $\lambda$, and density $\rho$, are relatively well known and we use the values listed in table \ref{tab:MaterialProperties}, which are consistent with the properties used in the coseismic model by \cite{Wei2011} and the 1D SCEC background velocity model.
 The remaining rheologic parameter, which we will assume to have a depth dependence, are estimated to optimize the predicted fit to observable postseismic displacement.
 
-In order to greatly simplify the posed inverse problem, we use to method describe in \cite{Hines2015} to constrain the effective lithospheric viscosity structure for the early postseismic period.
-The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere are controlled by the relatively well known instantaneous elastic properties.
+In order to greatly simplify the posed inverse problem, we use the method describe in \cite{Hines2015} to constrain an effective lithospheric viscosity structure for the early postseismic period.
+The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere are only controlled by the relatively well known instantaneous elastic properties.
 This means that the rate of deformation in each parcel of the lithosphere will deform at a rate that is inversely proportional to its effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$, and independent of $\eta_{\mathrm{eff}}$ elsewhere.
@@
 where $h(x,\xi,\zeta)$ describes the initial rate of deformation resultion from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and $L$ denotes the lithosphere and asthenosphere.
-Importantly, $h$ is independent of all rheologic properties other than those that control the instantaneous elastic behaviour, $\mu$, $\lambda$ and $\rho$.
 We can combine eq.
@@
 We note that a nonlinear Kalman filter based inverse method can be employed to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, where we do not have to explicitly impose a time dependent parameterization of $s$.
-Indeed we have thoroughly explored that possibility but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity and because we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general.
+We have thoroughly explored this possibility but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity and because we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general.
 
@@
 \ref{ApproxForward} is not longer capable of describing the observed deformation without incurring systematic misfits.
-This is illustrated in figures \ref{fig:NearFieldRS} and \ref{fig:FarFieldRS}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
+This is illustrated in figure \ref{fig:RecordSection1}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
 When using eq.
@@
 
-We want to find the discretized parameters describing coseismic slip and the rate of afterslip, $\mathbf{s}$, and viscosity, $\mathbf{\eta_{\mathrm{eff}}}$, that minimize the difference between the each discrete observation of postseismic deformation over the first 0.8 years following the El Mayor-Cucapah earthquake, which is here denoted $\mathbf{u_\mathrm{obs}}$, and the discrete observations predicted in eq.
-\ref{ApproxForward}, $\mathbf{u_\mathrm{pred}}$.
-That is, we want to solve
-
+We estimate the discretized parameters describing coseismic slip, afterslip, and effective viscosity by solving 
 \begin{equation}\label{ObjectiveFunction}
- \mathrm{min}_{\mathbf{s},\mathbf{\eta_\mathrm{eff}}} \left|\left|
+ \mathrm{min}_{s,\eta_\mathrm{eff}} \left|\left|
  \frac{\mathbf{u_\mathrm{pred}}(s,\eta_\mathrm{eff}) - \mathbf{u_\mathrm{obs}}}
@@
 \end{equation} 
-Due to inherent nonuniqueness in the solution to eq. \ref{ObjectiveFunction}, we add zeroth order Tikhonov regularization to estimates of slip,
+where $\mathbf{u_\mathrm{obs}}$ are the discrete observations of the first 0.8 years of postseismic displacements for each station, $\mathbf{\sigma_\mathrm{obs}}$ are the observation uncertainties, and $\mathbf{u_\mathrm{pred}}$ are predicted displacements from eq \ref{ApproxForward}.
+Due to inherent nonuniqueness in the solution to eq.
+\ref{ObjectiveFunction}, we add zeroth order Tikhonov regularization to estimates of slip,
 \begin{equation}\label{Misfit}
-||\lambda_s \mathbf{s}||_2^2=0,
+||\lambda_s s||_2^2=0,
 \end{equation}
@@
 \begin{equation}
-||\lambda_v \nabla \mathbf{\eta_{\mathrm{eff}}}^{-1}||_2^2=0.
+||\lambda_v \nabla \eta_{\mathrm{eff}}^{-1}||_2^2=0.
 \end{equation}
@@
 We note that our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do in a model space where eq.
-\ref{GeneralForward} is our forward problem in section \ref{FullInversion}.
-Estimates of $\mathbf{s}$ made here will not be used in section \ref{FullInversion}, and so the motivation behind even adding regularization to $\mathbf{s}$ is to ensure that the slip driving viscoelastic relaxation in eq.
+\ref{GeneralForward} is our forward problem in section \ref{sec:FullInversion}.
+Estimates of $s$ made here will not be used in section \ref{sec:FullInversion}, and so the motivation behind even adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
 \ref{ApproxForward} are sensible.
@@
 The uncertainties in fluidities increases with depth, as would be expected due to decreased sensitivity with depth.
-Nevertheless, a robust feature that we see is that the viscosity below 60 km depth needs to be $\sim 10^{18}$ Pa s to describe the early rate of postseismic deformation for stations greater than $\sim200$ km from the epicenter (JUSTIFY THIS).
-This inferred transitional depth is consistent with the regionally averaged lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}.
-The viscosity of the lower crust is the least well constrained as there is effectively no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years of postseismic, $>10^{19}$ Pa s.
-Our inference of a mantle viscosity of $\sim 10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady state viscosities from \cite{Pollitz2000}, \cite{Pollitz2003}, \cite{Johnson2007}, \cite{Spinler2015}, and \cite{Rollins2015}.
+Nevertheless, a robust feature that we see is that the viscosity below 60 km depth needs to be $\sim 1\times10^{18}$ Pa s to describe the early rate of postseismic deformation for stations further than $\sim200$ km from the epicenter.
+This depth where we require low viscosity is consistent with the regionally averaged lithosphere-asthenosphere boundary inferred by \citet{Lekic2011}.
+The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years after the El Mayor-Cucapah earthquake.
+Our inference of a mantle viscosity on the order of $10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady state viscosities from \citet{Pollitz2000}, \citet{Pollitz2003}, \citet{Johnson2007}, \citet{Spinler2015}, and \citet{Rollins2015}.
 
-Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figures \ref{fig:InitialCoseismic} and \ref{fig:InitialAfterslip} respectively.
-To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show a coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but we assume the lithosphere and ashthenosphere are elastic.
+Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figure \ref{fig:InitialSlip}.
+To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show the coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but we assume the lithosphere and asthenosphere are elastic.
 In both coseismic inversion, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
 This is consistent with field studies, \cite{Fletcher2014} as well as the coseismic slip model from \cite{Wei2011}.
-The potency of inferred coseismic slip is $3.32\times 10^{9} \mathrm{m}^3$, which is equivalent to a moment magnitude of 7.28 when assuming a shear modulus of $3.2\times10^{10}$ Pa.
+The potency of inferred coseismic slip is $3.32\times 10^{9} \mathrm{m}^3$, which is equivalent to a moment magnitude of 7.28 when assuming a shear modulus of 32 GPa.
 The potency of the inferred coseismic slip model when assuming an elastic lithosphere is not significantly different, $3.55\times 10^9 \mathrm{m}^3$.
@@
 The former is comparable to the size of the mainshock which, as noted by \cite{Rollins2015}, is implausibly large.
-The significant amount of afterslip inferred to be on the Indiviso fault by \cite{Rollins2015} seems to be compensating for unmodeled viscoelastic relaxation at depths of $>60$ km.
-The fact that there is still a substantial amount of deep afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than we allow for since we only estimate depth dependent variations in viscosity.
+The significant amount of afterslip inferred to be on the Indiviso fault by \cite{Rollins2015} seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
+The fact that there is still an appreciable amount of deep afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than we allow for since we only estimate depth dependent variations in viscosity.
 
-\subsection{Full Inversion}\label{FullInversion}
+\subsection{Full Inversion}\label{sec:FullInversion}
 
@@
 
-Figure \ref{fig:Rheology} describes how the inferred effective viscosities from section \ref{InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
-In this section we perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from \ref{InitialInversion}.
+Figure \ref{fig:Rheology} describes how the inferred effective viscosities from section \ref{sec:InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
+In this section we perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from \ref{sec:InitialInversion}.
 Our forward problem is now eq.
@@
 We compute $f$ and $g$ from eq.
-\ref{GeneralForward} using Pylith \cite{Aagaard2009} and assume the same spatial and temporal discretization of $s$ as in section \ref{InitialInversion}.
-The misfit, defined by eq.
-\ref{Misfit}, is X which significantly higher than that of the elastic model, X.
+\ref{GeneralForward} using Pylith \citep{Aagaard2009} and assume the same spatial and temporal discretization of $s$ as in section \ref{sec:InitialInversion}.
+The misfit for the Maxwell model, defined by eq.
+\ref{Misfit}, is 62.0 which is significantly higher than that of the elastic model, 47.5.
+As noted, our estimates of $\eta_\mathrm{eff}$ can be thought of as an upper limit, and we have tried using viscoelastic Green's functions, $f$, with lower viscosities but that only increases the misfit.
 It is apparent that most of the misfit comes from the Maxwell model significantly overestimating the rate of deformation after $\sim 3$ years following the earthquake.
-Although, the numerous studies have described postseismic deformation in Southern California using a Maxwell visocolatic rheology with viscosities consistent with ours, it is clear that such a model is incapable of describing the entire postseismic time series.
-As previously noted, \cite{Pollitz2001}, recognized this deficiency in a Maxwell rheology which motivated their exploration of a Burgers rheology upper mantle \cite{Pollitz2003}.
+Although, numerous studies have described postseismic deformation in Southern California using a Maxwell viscoelastic rheology with viscosities consistent with ours, it is clear that such a model is incapable of describing the entire postseismic time series.
+As previously noted, \cite{Pollitz2001}, recognized this deficiency in a Maxwell rheology which motivated their exploration of a Burgers rheology upper mantle \citep{Pollitz2003}.
 
-Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener model, which only introduces the unknown parameter $\mu_{k}$.
-We assume that the lower crust still has a Maxwell viscosity and $\eta_{M}$ is set equal to $\eta_{\mathrm{eff}}$.
-For a Zener model, the effective initial viscosity is $\eta_{K}$ and so we set $\eta_K$ equal to $\eta_{\mathrm{eff}}$ inferred from above.
+Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces the unknown parameter $\mu_{k}$.
+We assume that the lower crust still has a Maxwell rheology.
+The steady state viscosity, $\eta_{M}$, in the crust and the transient viscosity, $\eta_\mathrm{K}$, in the mantle are set equal to the inferred effective viscosities.
 The unknown rheologic parameter which we estimate is the ratio of shear moduli, $\nu=\frac{\mu_K}{\mu_M}$.
@@
 The former being a degenerate case when the Zener model becomes the Maxwell model from above and the later being a Jeffreys solid.
-The misfit of the best fit models to the observed postseismic data when varying $\nu$ is shown in figure \ref{fig:ShearModulusRatio}.
-The optimal value of $\nu$ is found to be $0.375$ which decreases the misfit by only about 10\%; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (\ref{fig:FinalFarFieldRS}).
+We estimate coseismic slip and afterslip for each realization of $\nu$.
+The misfit as a function of $\nu$ is shown in figure \ref{fig:ShearModulusRatio}.
+The optimal value of $\nu$ is found to be $0.375$, which has a misfit of 44.9,  which seems like a modest improvement from the elastic model; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (figure \ref{fig:RecordSection2}).
 This significant improvement is seen for all shear modulus ratios greater than about $0.125$.
 
-Because we are able to adequately  describe the available 5 years of postseismic seismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since Zener model can be thought of as the limit when the steady state viscosity in a Burgers rheology is infinite, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in \ref{InitialInversion} and an effectively infinite steady state viscosity on the timescale of five years, $>10^{20}$ Pa s, would also be able to satisfactorily describe the observable postseismic deformation.
+Because we are able to adequately  describe the available five years of postseismic seismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
+However, since the Zener model can be thought of as the limit when the steady state viscosity in a Burgers rheology is infinite, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in \ref{sec:InitialInversion} and an effectively infinite steady state viscosity on the timescale of five years, $>10^{20}$ Pa s, would also be able to satisfactorily describe the observable postseismic deformation.
 
@@
 We estimate the damping parameter, again enforcing smallness on our model, using another L-curve test.
-Our preferred model for coseismic slip and afterslip is shown in figures \ref{fig:FinalCoseismic} through \ref{fig:FinalAfterslip3}.
+Our preferred model for coseismic slip and afterslip is shown in figure \ref{fig:FinalSlip}.
 
-The postseismic displacements predicted for our preferred slip model and rheologic model of the lithospheric are shown in figures \ref{fig:NearField1} through \ref{fig:FarField4} as well as \ref{fig:FinalNearFieldRS} and \ref{fig:FinalFarFieldRS}.
-Additionally we show the predicted postseismic deformation broken down into an elastic and viscoelastic component (figure (TBD)).
+The postseismic displacements predicted for our preferred slip model and rheologic model of the lithospheric are shown in figures \ref{fig:NearField} and \ref{fig:FarField} as well as \ref{fig:RecordSection2}.
+Additionally, we show the predicted postseismic deformation broken down into an elastic and viscoelastic component (figure (TBD)).
 Overall, the trend in the near field and far field transient deformation is accurately described by our preferred model.
-In particular, the trend in far field deformation is much better described by our preferred model, which has a Zener rheology mantle, than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:FinalFarFieldRS}).
+In particular, the trend in far field deformation is much better described by our preferred model, which has a Zener rheology mantle, than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:RecordSection2}).
 There are a few areas where we have notable misfit.
-Most of our misfit is for the near field stations in the Imperial Valley and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \cite{Wei2011} and Wei 2015.
+Most of our misfit is for the near field stations in the Imperial Valley and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \citep{Wei2011a,Wei2015}.
 Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
@@
 We emphasize, that the GPS station closest to where we infer there to be sustained afterslip, P496, is still about 30 km away, which we believe is too distil for us to conclusively argue for sustained brittle deformation rather ductile deformation in a shear zone, especially for the last two years where afterslip is inferred to be on the deepest patches.
-Although we do note that it is not unheard of for afterslip to persists for years or decades following an earthquake \cite{Cakir2012}.
+Although we do note that it is not unheard of for afterslip to persists for years or decades following an earthquake \citep{Cakir2012}.
 Either way, we can conclusively say a localized deformation mechanism is required to explain the available five years of near field deformation.
@@
 
-Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle, which is the simplest viscoelastic rheologic model (e.g.
-\cite{Nur1974}, \cite{Pollitz2000}, \cite{Hetland2003},\cite{Freed2006a}, \cite{Johnson2009}, \cite{Hearn2009}).
-In Southern California, postseismic studies following the Landers \cite{Pollitz2000}, Hector Mine \cite{Pollitz2001}, and El Mayor-Cucuapah earthquake \cite{Spinler2015}, \cite{Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s with a relatively stronger lower crust.
-Our inference that the the crust and uppermost mantle are relatively strong compared to the underlying mantle is also consistent with that found by \cite{Freed2007a}.
+Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle, which is the simplest viscoelastic rheologic model \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}.
+In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucuapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s with a relatively stronger lower crust.
+Our inference that the the crust and uppermost mantle are relatively strong compared to the underlying mantle is also consistent with that found by \citet{Freed2007a}.
 While these inferences are consistent with our effective viscosities, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
-Studies on interseismic deformation \cite{Lundgren2009} and lake loading \cite{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+Studies on interseismic deformation \citep{Lundgren2009} and lake loading \citep{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
 
 An additional deficiency in the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate postseismic deformation.
-Early transient postseismic deformation can be attributed to fault creep \cite{Savage2005a} and the trend in postseismic deformation can then be explained with a combination of fault creep and relaxation in a Maxwell viscoelastic lithosphere, (e.g.
-\cite{Hearn2009}, \cite{Johnson2009}).
-However, the trend in postseismic deformation at distances greater than about 200 km from the El Mayor Cucapah epicenter, which can only be attributed to viscoelastic relaxation \cite{Freed2007a}, cannot be explained with a Maxwell viscoelastic lithosphere (figure \ref{fig:FinalFarFieldRS}).
+One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
+However, the trend in postseismic deformation at distances greater than about 200 km from the El Mayor Cucapah epicenter, which can only be attributed to viscoelastic relaxation \citep{Freed2007a}, cannot be explained with a Maxwell viscoelastic lithosphere (figure \ref{fig:RecordSection2}).
 
 We found that a Zener rheology in the upper mantle with a transient viscosity of about $10^{18}$ Pa s does a noticeably better job at predicting far field postseismic deformation.
-A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \cite{Liu1976}.
-The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \cite{Yuen1982} and the largest characteristic relaxation time would be on the order of days.
+A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \citep{Liu1976}.
+The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \citep{Yuen1982} and the largest characteristic relaxation time would be on the order of days.
 Even though our inferred transient viscosity is orders of magnitude larger than that required for seismic attenuation models, the two models are not incompatible.
-Rather the delayed elasticity in seismic attenuation models occurs on such short timescales that it can be considered  part of the instantaneous elastic phase of deformation associated with the preferred Zener model in this study.
+Rather the delayed elasticity in seismic attenuation models occurs on such short time scales that it can be considered  part of the instantaneous elastic phase of deformation associated with the preferred Zener model in this study.
 
 Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid behaviour required for mantle dynamics on geologic time scales.
-\cite{Yuen1982} proposed a Burgers rheology with a low viscosity ($\approx 10^{16}$ Pa s) in the Kelvin element and high viscosity ($\approx 10^{21}$ Pa s) in the Maxwell element which is capable of describing both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
-The justification of a Burger's rheology mantle is further supported by laboratory experments on the strength of olivine \cite{Chopra1997}.
-\cite{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
-While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \cite{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \cite{Lundgren2009} and \cite{Luttrell2007}.
-Additionally, the transient viscosity inferred by \cite{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, which may be the result of shallow afterslip.
-While \cite{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \cite{Jacobs2002}.
-It is then possible that the preferred rheologic model from \cite{Pollitz2003} was biased towards inferring a particularly low transient viscosity by neglecting to account for afterslip.
+\citet{Yuen1982} proposed a Burgers rheology with a low viscosity ($\approx 10^{16}$ Pa s) in the Kelvin element and high viscosity ($\approx 10^{21}$ Pa s) in the Maxwell element which is capable of describing both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
+The justification of a Burger's rheology mantle is further supported by laboratory experiments on the strength of olivine \citep{Chopra1997}.
+\citet{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
+While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \citet{Lundgren2009} and \citet{Luttrell2007}.
+Additionally, the transient viscosity inferred by \citet{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, which may be the result of shallow afterslip.
+While \citet{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \citep{Jacobs2002}.
+It is then possible that the preferred rheologic model from \citet{Pollitz2003} was biased towards inferring a particularly low transient viscosity by neglecting to account for afterslip.
 This is in contrast to the present study, where we have inferred a lithospheric viscosity structure simultaneously with afterslip.
@@
 
+This research was funded by X
+
 \bibliographystyle{apalike}
 \bibliography{mybib}
-
-\begin{figure}
-\includegraphics[scale=0.9]{Figures/context_map}
-\centering 
-\caption{}
-\label{fig:ContextMap}
-\end{figure}
 

### 2016-04-06 RoughDraft/ElMayor.tex
commit before push

@@
 Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to a biased inference of lithospheric viscosity.
-Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near field deformation, which could be indicative of unmodeled continued afterslip.
+Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near-field deformation, which could be indicative of unmodeled continued afterslip.
 
@@
 The fault geometry used in this study is shown in cyan where dashed lines indicate buried edges of the fault segments.
-The green and red boxes denote the extent of the near and far field displacement maps.
+The green and red boxes denote the extent of the near and far-field displacement maps.
 The blue sector highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis and stations within this sector are used in the record sections in figures \ref{fig:RecordSection1} and \ref{fig:RecordSection2}}
@@
 Stations which recorded displacements that clearly cannot be described by the aforementioned processes are not included in our analysis.
-This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Argus2005} .
+This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Bawden2001,Argus2005} .
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
@@
 The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ overfitting the data.
-While one can use a maximum likelihood based approach to picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+While one can use a maximum likelihood based approach to picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
@@
 By down sampling, we implicitly assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
-Figure \ref{fig:P496} shows the estimate of coseismic and postseismic deformation, $u(t)$, for station P496 along with the estimated uncertainties.
+Figure \ref{fig:P496} shows the estimate of coseismic and postseismic deformation, $u_\mathrm{post}(t)$, for station P496 along with the estimated uncertainties.
 \cite{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and indeed, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we also clearly see far reaching postseismic transient deformation (figure \ref{fig:P619}).
+
+\begin{figure}
+\includegraphics[scale=0.37]{Figures/filterP496}
+\centering
+\caption{}
+\label{fig:P496}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.37]{Figures/filterP619}
+\centering
+\caption{} 
+\label{fig:P619}
+\end{figure}
 
@@
 \ref{TimeSeriesModel}.
-For example, we assume a constant secular rate of deformation, while viscoelastic mechanical models of the earthquake cycle predict that the accumulation of tectonic deformation is nonlinear over time \citep{Thatcher1983}.
-Based on inspection, the rate of secular deformation does appear constant for all stations except for perhaps the stations closest to the Hector Mine epicenter, as noted aboved.
+For example, we assume a constant rate of secular deformation, which appears to be an appropriate approximation for all but perhaps the stations closest to the Hector Mine epicenter, as noted aboved.
 Also, our model for seasonal deformation in eq.
-\ref{TimeSeriesModel} assumes a constant amplitude over time, which means that years of particularly heavy or light rainfall cannot be adequately described.
-This deficiency in our seasonal model causes our estimate of $u(t)$ to describe some of the unmodeled oscillations (e.g.
+\ref{TimeSeriesModel} assumes a constant amplitude over time, which means that any yearly variability in the climatic conditions could introduce systematic residuals \citep{Davis2012}.
+Indeed, it would be more appropriate to consider the seasonal amplitudes $c_2-c_5$ in eq.
+\ref{TimeSeriesModel} as stochastic variables \citep{Murray2005}.
+By using constant seasonal amplitudes our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodeled oscillations (e.g.
 figure \ref{fig:P619}).
 
-We show the near and far field postseismic deformation accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as coseismic displacements in figures \ref{fig:NearField} and \ref{fig:FarField}.
-In the far field, we can see clear south trending displacement for the first 3.0 years following the earthquake at stations as far as 400 km from of the El Mayor Cucapah epicenter.
-These displacements are most pronounced along the direction of the El Mayor-Cucapah P and T axis, as would be expected for postseismic deformation.
-After 3.0 years, The southward trending far field postseismic deformation is barely perceptible.
-The vertical deformation in the far field is difficult to attribute to postseismic processes.
-Most far field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
+We show in figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic deformation accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as the coseismic displacements.
+In the far-field to the north, we can see south trending displacements for the first 3.0 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicenter.
+These displacements are most pronounced along the direction of the El Mayor-Cucapah P axis.
+A similar eastward trend can be seen in the few far-field stations along the T axis in Arizona.
+After 3.0 years, The trend in far-field postseismic deformation is barely perceptible.
+The vertical deformation in the far-field is difficult to attribute to postseismic processes.
+Most far-field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
 This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
-Although we use vertical deformation in our analysis in section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation as it likely has non-tectonic origins.
+Although we use vertical deformation in our analysis in section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation as it likely does not have postseismic origins.
 
-The near field postseismic deformation is notably sustained when compared to the far field deformation.
+\begin{figure}
+\includegraphics[scale=0.32]{Figures/nearfield}
+\centering 
+\caption{}
+\label{fig:NearField}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.32]{Figures/farfield}
+\centering 
+\caption{}
+\label{fig:FarField}
+\end{figure}
+
+The near-field postseismic deformation is notably sustained when compared to the far-field deformation.
 Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of $\sim1.4$ cm/yr to the south five years after the El Mayor-Cucapah earthquake.
-Vertical postseismic deformation in the near field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
+Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
 However, the vertical postseismic deformation signal is only apparent for the first year after the earthquake (figure \ref{fig:NearField}).
-As with the far field deformation, there is a general trend of uplift in the near field one year after the earthquake which we do not consider to be related to postseismic processes.
+As with the far-field deformation, there is a general trend of uplift in the near-field one year after the earthquake which we do not consider to be related to postseismic processes.
 
@@
 We consider afterslip and viscoelastic relaxation in the lithosphere and asthenosphere as candidate mechanisms.
-Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \cite{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
-Additionally, we are considering stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
+Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
+Furthermore, we consider stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
 
-We estimate coseismic and time dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \citet{Wei2011} with some modifications.
+We estimate coseismic and time-dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \citet{Wei2011} with some modifications.
 Field studies \citep{Fletcher2014} and LIDAR observations \citep{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \citet{Wei2011}, especially within the Sierra Cucapah.
-However, we find the relatively simple coseismic fault geometry from \cite{Wei2011} to be adequate because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \cite{Fletcher2014} and \cite{Oskin2012}.
-The fault geometry used in this study (figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \cite{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
-Additionally, We extend the northern segment by 40 km to the northwest which is motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
-This extended fault segment was also found to be necessary by \cite{Rollins2015} and \cite{Pollitz2012} for describing postseismic deformation.
+However, we find that a relatively simple coseismic fault geometry based on \citep{Wei2011} is adequate because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \citet{Fletcher2014} and \citet{Oskin2012}.
+The fault geometry used in this study (figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \citet{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
+Both segments extend from the surface to 15 km depth.
+We extend the northern segment by 40 km to the northwest, motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
+This extended fault segment was also found to be necessary by \citet{Rollins2015} and \citet{Pollitz2012} in order to describe the postseismic deformation.
+\subsection{elastic inversion}\label{sec:ElasticInversion}    
+We consider a variety of rheologic models for the lithosphere and asthenosphere.
+The simplest rheologic model is to consider the lithospere and asthenosphere to be effectively elastic and isotropic.
+In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the values listed in table \ref{tab:MaterialProperties} throughout this paper.
+The values for $\lambda$ and $\mu$ are consistent with the properties used in the coseismic model by \cite{Wei2011} and the 1D SCEC velocity model.
+The only unknowns are then the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
+Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane and they did not require any viscoelastic relaxation to describe the observations.
+We also perform an elastic slip inversion but we use GPS stations within a larger radius about the El Mayor-Cucapah epicenter (400 km instead of $\sim$200 km).
+Our forward problem describing predicted postseismic deformation $u_\mathrm{pred}$ in terms of time dependent fault slip $s$ is
+\begin{equation}\label{eq:ElasticForward}
+  u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi 
+\end{equation}           
+where $g(x,\xi)$ is an elastic Green's function describing the displacement at position $x$ resulting from a unit of slip at $\xi$ on the fault, denoted by $F$.
+We estimate coseismic slip, as well as the rate of afterslip over time intervals spanning 0.0-0.125 years, 0.125-0.25 years, 0.5-1.0 years, and at 1.0 year intervals for the remaining five years.
+Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
+We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip.
+We also add zeroth order Tikhonov regularization so that our slip solution satisfies
+\begin{equation}\label{eq:ElasticObjective}
+  \min_s \left(\left|\left|\frac{u_\mathrm{pred}(s) - u_\mathrm{post}}                
+                                {\sigma_\mathrm{obs}}\right|\right|_2^2 + 
+                                \lambda_s||s||_2^2\right). 
+\end{equation}
+The penalty parameters, $\lambda_s$, is chosen with a trade-off curve.
 
-We consider a variety of rheologic models for the lithosphere and asthenosphere in this study.
-The simplest rheologic model is to consider the lithospere and asthenosphere to be effectively elastic and isotropic.
-In such case, the rheologic parameters, consisting of the Lame parameters, $\lambda$ and $\mu$, and density, $\rho$, are reasonably well known.
-The only unknowns are then the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
-\cite{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be well explained with afterslip on the coseismicly ruptured fault, which has been extended down to the lithosphere-asthenosphere boundary inferred by \cite{Lekic2011}, and they did not require any viscoelastic relaxation to describe the observations.
-They did however, find that an unrealistically large amount of afterslip is required on the Indiviso fault, equivalent to a Mw7.2 earthquake.
-Since most of the GPS data is located north of the rupture zone, slip on the Indiviso fault segment is not well constrained and it could be acting as a proxy for distributed relaxation in the lower crust or upper mantle.
-It is well understood that afterslip at sufficiently great depths can explain postseismic deformation resulting from viscoelastic relaxation \cite{Savage1990}, at least in 2D earthquake models.
-In the interest of eliminating null space in our inverse problem,  we assume that afterslip occurs only at seismogenic depths ($<15$ km), and we allow for viscoelastic relaxation in the lower crust (15-30 km) and the upper mantle.
-We choose such shallow constraints on afterslip because rate-state friction based models would suggest afterslip to occur at shallow depths to accommodate a coseismic slip deficit \cite{Marone1991}, which is indeed inferred in the coseismic models by \cite{Wei2011a} and (Fialko 2010).
-Additionally, as noted by \cite{Rollins2015} the postseismic uplift just north of the rupture zone can be well described with slip at seismogenic depths, while afterslip which is constrained to depths below 15 km predicts subsidence in that region.
+Our coseismic and afterslip solutions are shown in figure (TBD).
+As with \citet{Rollins2015}, we find that a significant amount of afterslip on the southern segment is required to explain the observations.
+Figure (TBD) is a scaled record section of observed and predicted postseismic displacements for stations along the El Mayor-Cucapah P axis.
+It is evident from figure (TBD) that the near-field stations ($\lesssim200$ km) can be well described by afterslip in an entirely elastic medium while there is a systematic underestimation and inability to reproduce the transient deformation in the far-field stations ($\gtrsim200$ km).
+When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
+In the following sections we seek to better describe the far-field postseismic deformation using viscoelastic models.
 
-Another reason for constraining slip to be shallower than 15 km depth is because we seek to estimate a lower crustal viscosity and the inverse problem becomes particularly ill-posed when trying to simultaneously estimate afterslip and a lithospheric viscosity at the same depths.
-This ill-posedness is illustrated in figure (\ref{fig:LowerCrust}), which shows the displacement resulting from a meter of slip on a fault extending from 15 to 30 km depth as well as the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
-The horizontal displacement from fault slip is in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
-This means that displacement resulting from afterslip at lower crustal depths can be cancelled out, at least partially, by a low viscosity lower crust.
-We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
-Aside from the issue of non-uniqueness, it is also nonsensical to allow for both brittle and ductile deformation mechanisms at the same depth.
+\subsection{constraints on effective viscosity}\label{sec:InitialInversion}
 
-A schematic representation of the viscoelastic rheologic models considered in this study for the lower crust and upper mantle are shown in figure \ref{fig:Rheology}.
-We consider Maxwell viscoelasticity, where the steady state viscosity $\eta_M$ is unknown; Zener viscoelasticty, where the transient viscosity $\eta_K$ and transient shear modulus $\mu_K$ are unknown; and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all largely unknown.
+For any linear viscoelastic rheology of the lithosphere and asthenosphere, postseismic displacement resulting from time dependent fault slip can be described as  
+\begin{equation}\label{GeneralForward}
+  u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
+           \int_0^t\int_F s(\xi,\tau) f(t-\tau,x,\xi) d\xi d\tau
+\end{equation}
+where $f(t,x,\xi)$ describes the time-dependent velocity at $x$ resulting from viscoelastic relaxation of stresses induced by slip at $\xi$.
+$f$ is a function of $\lambda$, $\mu$, and any additional rheologic parameters controlling the viscoelastic response, which are generally not well known.
+Schematic representations of the viscoelastic rheologic models considered in this study for the lower crust and upper mantle are shown in figure \ref{fig:Rheology}.
+We consider Maxwell viscoelasticity, where the steady state viscosity $\eta_M$ is unknown, Zener viscoelasticty, where the transient viscosity $\eta_K$ and transient shear modulus $\mu_K$ are unknown, and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all unknown.
 We further discuss these rheologic models and their use in geophysical studies in the discussion.
 
-\subsection{constraint on effective viscosity}\label{sec:InitialInversion}
-For any linear viscoelastic rheology of the lithosphere and asthenosphere, postseismic displacement resulting from time dependent fault slip, $s(\xi,t)$, on a fault $F$ can be described as  
-\begin{equation}\label{GeneralForward}
-  u(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
-           \int_0^t\int_F s(\xi,\tau) f(t-\tau,x,\xi) d\xi d\tau
-\end{equation}
-where $g(x,\xi)$ describes the instantaneous elastic displacements at $x$ resulting from a unit of slip at $\xi$, and $f(t,x,\xi)$ describes the time dependent velocity at $x$ resulting from viscoelastic relaxation of stresses induced by slip at $\xi$.
-$f$ is a function of the properties of the chosen rheologic model, which are generally not well known.
-The parameters in $g$ which control the instantaneous elastic displacements, $\mu$, $\lambda$, and density $\rho$, are relatively well known and we use the values listed in table \ref{tab:MaterialProperties}, which are consistent with the properties used in the coseismic model by \cite{Wei2011} and the 1D SCEC background velocity model.
-The remaining rheologic parameter, which we will assume to have a depth dependence, are estimated to optimize the predicted fit to observable postseismic displacement.
+\begin{figure}
+\includegraphics[scale=0.9]{Figures/rheology}
+\centering 
+\caption{}
+\label{fig:Rheology}
+\end{figure}
 
-In order to greatly simplify the posed inverse problem, we use the method describe in \cite{Hines2015} to constrain an effective lithospheric viscosity structure for the early postseismic period.
+In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2015} to constrain an initial effective lithospheric viscosity structure from the early postseismic deformation.
 The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere are only controlled by the relatively well known instantaneous elastic properties.
 This means that the rate of deformation in each parcel of the lithosphere will deform at a rate that is inversely proportional to its effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$, and independent of $\eta_{\mathrm{eff}}$ elsewhere.
-Then, as a consequence of linear elasticity, the initial rate of surface deformation resulting from viscoelastic relaxation is a linear combination of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's viscosity.
+Then, through linear superposition, we can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's viscosity.
 That is to say
@@
 \begin{equation}\label{ApproxForward}
-  u(x,t) \approx \int_F s(\xi,t)g(x,\xi)d\xi + 
+  u_\mathrm{pred}(x,t) \approx \int_F s(\xi,t)g(x,\xi)d\xi + 
            \int_0^t\int_F\int_L \frac{s(\tau,\xi)}{\eta_\mathrm{eff}(\zeta)} h(x,\xi,\zeta) d\zeta d\xi d\tau,
@@
 Although eq.
-\ref{ApproxForward} may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are functions of the fault geometry and instantaneous elastic properties, which are fairly well known, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem, eq.
-\ref{ApproxForward}, can be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
+(\ref{ApproxForward}) may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are only functions of the fault geometry and instantaneous elastic properties, $\lambda$ and $\mu$, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem in eq.
+(\ref{ApproxForward}) can be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
 This is in contrast to evaluating the full forward problem, eq.
-\ref{GeneralForward}, numerically for each realization of $s$ and unkown rheologic properties which is far more computationally demanding.
-Figure \ref{fig:Rheology} shows how $\eta_\mathrm{eff}$ relates to the parameters for various linear viscoelastic rheologies.
+(\ref{GeneralForward}), numerically for each realization of $s$ and unknown rheologic properties.
+Figure \ref{fig:Rheology} shows how estimates of $\eta_\mathrm{eff}$ can then be used as a constraint on the unknown parameters for various linear viscoelastic rheologies.
 
-We perform an initial inversion of postseismic displacements using eq.
-\ref{ApproxForward} as our forward problem.
-As noted, we use the fault geometry from \citet{Wei2011}, except that each segment extends to 15 km depth and the north segment is extended 40 km northward.
-Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
-We estimate coseismic slip as well as the rate of afterslip over time intervals spanning 0.0-0.125 years, 0.125-0.25 years, 0.5-1.0 years, and at 1.0 year intervals for the remaining five years.
-We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip.
-We estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain, 800 km.
-Details of the inverse method are described in \citet{Hines2015}.
-We note that a nonlinear Kalman filter based inverse method can be employed to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, where we do not have to explicitly impose a time dependent parameterization of $s$.
-We have thoroughly explored this possibility but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity and because we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general.
+We perform an initial inversion of postseismic displacements using the approximation in eq.
+\ref{ApproxForward}.
+We estimate coseismic slip and afterslip with the same spatial and temporal discretization as in section \ref{sec:ElasticInversion}.
+Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain at 800 km.
+We again restrict fault slip to occur between 0 and 15 km depth and we made this choice to help eliminate inevitable non uniqueness.
+It has long been recognized that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional models \citep{Savage1990}.
+Since we are trying to simultaneously model these two processes, it is necessary to put sensible constraints on the depth of fault slip.
+Additionally, we note that when simultaneously estimating afterslip in the lower crust and a lower crustal viscosity, the inverse problem becomes particularly ill-posed.
+This ill-posedness is illustrated in figure (\ref{fig:LowerCrust}), which shows the displacement resulting from a meter of slip on a fault extending from 15 to 30 km depth as well as the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+The horizontal displacement from fault slip is in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
+This means that surface displacements resulting from afterslip at lower crustal depths can be cancelled out, at least partially, by a low viscosity lower crust.
+We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
+This is not to say that we do not believe deep afterslip to be a possibility, rather we restrict slip to seismogenic depths as a modeling necessity.
+Although, it has been noted that the pattern of vertical postseismic deformation following the El Mayor-Cucpah earthquake indicates that a significant amount of afterslip must be shallow \cite{Rollins2015}.
+
+\begin{figure}
+\includegraphics[scale=0.5]{Figures/lower_crust}
+\caption{afterslip and viscoelastic relaxation in lower crust}
+\label{fig:LowerCrust}
+\end{figure}
+
+Further details of how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2015}.
+We note that a nonlinear Kalman filter based inverse method can be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parameterization of $s$.
+We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity.
+Moreover, we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general for the respoving power of these GPS data.
 
 The first step in our inverse method is to determine at which point the early postseismic approximation, eq.
-\ref{ApproxForward}, is no longer approriate, which we will denote as $t_{\mathrm{end}}$.
+\ref{ApproxForward} breaks down, which we will denote as $t_{\mathrm{bd}}$.
 As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
-We can almost certainly assume that deformation at the most far field stations which are $\sim400$ km away from the El Mayor-Cucapah epicenter is the result of viscoelastic relaxation.
-The approximation should then be valid for as long as a linear trend adequately approximates the far field deformation.
-Using this logic, it would appear that $t_{\mathrm{end}}$ is $\sim1$ year after the El Mayor-Cucapah earthquake.
-Another way to determine $t_{\mathrm{end}}$ is to find the best fitting prediction of eq.
+We can almost certainly assume that deformation at the most far-field stations, which are $\sim400$ km away from the El Mayor-Cucapah epicenter, is the result of viscoelastic relaxation.
+The approximation should then be valid for as long as a linear trend adequately approximates the far-field deformation.
+Using this logic, it would appear that $t_{\mathrm{bd}}\approx1$ year after the El Mayor-Cucapah earthquake.
+Another way to determine $t_{\mathrm{bd}}$ is to find the best fitting prediction of eq.
 \ref{ApproxForward} to observed deformation using increasing durations of the postseismic timeseries.
-$t_\mathrm{end}$ should be the point when eq.
-\ref{ApproxForward} is not longer capable of describing the observed deformation without incurring systematic misfits.
+$t_\mathrm{bd}$ should be the point when eq.
+\ref{ApproxForward} is no longer capable of describing the observed deformation without incurring systematic misfits.
 This is illustrated in figure \ref{fig:RecordSection1}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
 When using eq.
-\ref{ApproxForward} to fit the entire five years of postseismic displacement we see that the near field displacements, eg.
-station P501, are accurately predicted but when looking at displacement in the far field, eg.
+\ref{ApproxForward} to fit the entire five years of postseismic displacement we see that the near-field displacements, eg.
+station P501, are accurately predicted but when looking at displacement in the far-field, eg.
 station P621, we see that eq.
 \ref{ApproxForward} overestimates the rate of deformation in the later postseismic and underestimates the rate of deformation in the early period.
-Due to the low signal to noise ratio for far field stations, it is difficult to determine at what point eq.
-\ref{ApproxForward} is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{end}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
-As noted in \cite{Hines2015}, overestimating $t_{\mathrm{end}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{end}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$; although the uncertainties would be larger.
-We can then consider our subsequent inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the lithospheric strength needed to describe the far field rate of deformation during the first 0.8 years of postseismic deformation.
+Due to the low signal-to-noise ratios for far-field stations, it is difficult to determine at what point eq.
+\ref{ApproxForward} is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{bd}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
+As noted in \cite{Hines2015}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$; although the uncertainties would be larger.
+We can then consider our subsequent inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the lithospheric strength needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
 
-We estimate the discretized parameters describing coseismic slip, afterslip, and effective viscosity by solving 
+\begin{figure}
+\includegraphics[scale=0.5]{Figures/recordsection1}
+\centering 
+\caption{record section}
+\label{fig:RecordSection1}
+\end{figure}
+
+We estimate coseismic slip, afterslip, and effective viscosity by solving 
 \begin{equation}\label{ObjectiveFunction}
- \mathrm{min}_{s,\eta_\mathrm{eff}} \left|\left|
- \frac{\mathbf{u_\mathrm{pred}}(s,\eta_\mathrm{eff}) - \mathbf{u_\mathrm{obs}}}
- {\mathbf{\sigma_\mathrm{obs}}}\right|\right|_2^2.
+ \mathrm{min}_{s,\eta_\mathrm{eff}} \left(\left|\left|
+ \frac{u_\mathrm{pred}(s,\eta_\mathrm{eff}) - u_\mathrm{obs}}
+ {\mathbf{\sigma_\mathrm{obs}}}\right|\right|_2^2 + 
+ \lambda_s||s||_2^2 + 
+ \lambda_\eta||\nabla \eta_{\mathrm{eff}}^{-1}||_2^2\right)
 \end{equation} 
-where $\mathbf{u_\mathrm{obs}}$ are the discrete observations of the first 0.8 years of postseismic displacements for each station, $\mathbf{\sigma_\mathrm{obs}}$ are the observation uncertainties, and $\mathbf{u_\mathrm{pred}}$ are predicted displacements from eq \ref{ApproxForward}.
-Due to inherent nonuniqueness in the solution to eq.
-\ref{ObjectiveFunction}, we add zeroth order Tikhonov regularization to estimates of slip,
-\begin{equation}\label{Misfit}
-||\lambda_s s||_2^2=0,
-\end{equation}
-and second order Tikhonov regularization to estimates of effective fluidity, 
-\begin{equation}
-||\lambda_v \nabla \eta_{\mathrm{eff}}^{-1}||_2^2=0.
-\end{equation}
-The degree to which we impose the regularization on slip and viscosity is controlled by the penalty parameters $\lambda_s$ and $\lambda_v$.
-The penalty parameters are chosen with two L-curve tests, where $\lambda_s$ is first chosen assuming $\lambda_v=0$, and then $\lambda_v$ is determined while keeping $\lambda_s$ at the chosen value.
-We note that our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do in a model space where eq.
-\ref{GeneralForward} is our forward problem in section \ref{sec:FullInversion}.
+where $u_\mathrm{obs}$ consists of the first 0.8 years of postseismic deformation and $u_\mathrm{pred}$ are the predicted displacements from eq.
+\ref{ApproxForward}.
+Due to inherent nonuniqueness, we have added zeroth order Tikhonov regularization to estimates of $s$, and second order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^-1$.
+The degree to which we impose the regularization on slip and viscosity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$.
+The penalty parameters are chosen with two trade-off curves.
+We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then $\lambda_\eta$ is determined while fixing $\lambda_s$ at the chosen value.
+We note that our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in section \ref{sec:FullInversion}.
 Estimates of $s$ made here will not be used in section \ref{sec:FullInversion}, and so the motivation behind even adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
-\ref{ApproxForward} are sensible.
+\ref{ApproxForward} is sensible.
 
 Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
-Although fluidity is a sparsely used metric, it is more natural to use fludities rather than viscosity since eq.
-\ref{InitialRate} is linear with respect to fluidity and so the fluidity represents the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere and asthenosphere.
-We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_v$, and our choice our $\lambda_v$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
-It is therefore difficult to interpret the magnitude of uncertainties on viscosity shown in figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
+Although fluidity is rarely used in geophysical literature, it is more natural to consider fludities rather than viscosities since eq.
+\ref{InitialRate} is linear with respect to fluidity and so the fluidity is proportional to the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere and asthenosphere.
+We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_\eta$.
+Our choice our $\lambda_\eta$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
+It is therefore difficult to interpret the magnitude of uncertainties on viscosities shown in figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
 The uncertainties in fluidities increases with depth, as would be expected due to decreased sensitivity with depth.
-Nevertheless, a robust feature that we see is that the viscosity below 60 km depth needs to be $\sim 1\times10^{18}$ Pa s to describe the early rate of postseismic deformation for stations further than $\sim200$ km from the epicenter.
-This depth where we require low viscosity is consistent with the regionally averaged lithosphere-asthenosphere boundary inferred by \citet{Lekic2011}.
+Nevertheless, a robust feature that we see is that the viscosity below 60 km depth needs to be on order of $10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations.
+Our inference that the lower crust and mantle from 30 to 60 km depth are appreciable stronger than the underlying mantle is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
 The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years after the El Mayor-Cucapah earthquake.
-Our inference of a mantle viscosity on the order of $10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady state viscosities from \citet{Pollitz2000}, \citet{Pollitz2003}, \citet{Johnson2007}, \citet{Spinler2015}, and \citet{Rollins2015}.
+Our inference of a mantle viscosity on the order of $10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady-state viscosities from \citet{Pollitz2000}, \citet{Pollitz2003}, \citet{Johnson2007}, \citet{Spinler2015}, and \citet{Rollins2015}.
+
+\begin{figure}
+\includegraphics[scale=0.7]{Figures/effective_viscosity}
+\centering 
+\caption{effective viscosity}
+\label{fig:EffectiveViscosity}
+\end{figure}
 
@@
 To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show the coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but we assume the lithosphere and asthenosphere are elastic.
-In both coseismic inversion, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
-This is consistent with field studies, \cite{Fletcher2014} as well as the coseismic slip model from \cite{Wei2011}.
+In both coseismic inversions, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
+This is consistent with field studies, \cite{Fletcher2014} as well as the coseismic slip from \cite{Wei2011}.
 The potency of inferred coseismic slip is $3.32\times 10^{9} \mathrm{m}^3$, which is equivalent to a moment magnitude of 7.28 when assuming a shear modulus of 32 GPa.
@@
 The fact that there is still an appreciable amount of deep afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than we allow for since we only estimate depth dependent variations in viscosity.
+
+\begin{figure}
+\includegraphics[scale=0.09]{Figures/initialslip}
+\caption{}
+\label{fig:InitialSlip}
+\end{figure}
 
@@
 The misfit as a function of $\nu$ is shown in figure \ref{fig:ShearModulusRatio}.
-The optimal value of $\nu$ is found to be $0.375$, which has a misfit of 44.9,  which seems like a modest improvement from the elastic model; however, the improvement can be clearly seen in the fit to the far field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (figure \ref{fig:RecordSection2}).
+The optimal value of $\nu$ is found to be $0.375$, which has a misfit of 44.9,  which seems like a modest improvement from the elastic model; however, the improvement can be clearly seen in the fit to the far-field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (figure \ref{fig:RecordSection2}).
 This significant improvement is seen for all shear modulus ratios greater than about $0.125$.
@@
 Additionally, we show the predicted postseismic deformation broken down into an elastic and viscoelastic component (figure (TBD)).
-Overall, the trend in the near field and far field transient deformation is accurately described by our preferred model.
-In particular, the trend in far field deformation is much better described by our preferred model, which has a Zener rheology mantle, than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:RecordSection2}).
+Overall, the trend in the near-field and far-field transient deformation is accurately described by our preferred model.
+In particular, the trend in far-field deformation is much better described by our preferred model, which has a Zener rheology mantle, than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:RecordSection2}).
 There are a few areas where we have notable misfit.
-Most of our misfit is for the near field stations in the Imperial Valley and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \citep{Wei2011a,Wei2015}.
+Most of our misfit is for the near-field stations in the Imperial Valley and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \citep{Wei2011a,Wei2015}.
 Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
@@
 The inferred coseismic potency is $3.1\times10^{9} \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of five years of afterslip is $1.2\times10^{9} \mathrm{m}^3$.
-While most of the afterslip is inferred to be within the first couple months of the earthquake, accounting for the most rapid near field transient deformation, we infer that afterslip in the vicinity of the Sierra Cucapah, where most slip occurred during the main shock, is necessary to explain the sustained rate of deformation in the near field.
+While most of the afterslip is inferred to be within the first couple months of the earthquake, accounting for the most rapid near-field transient deformation, we infer that afterslip in the vicinity of the Sierra Cucapah, where most slip occurred during the main shock, is necessary to explain the sustained rate of deformation in the near-field.
 We emphasize, that the GPS station closest to where we infer there to be sustained afterslip, P496, is still about 30 km away, which we believe is too distil for us to conclusively argue for sustained brittle deformation rather ductile deformation in a shear zone, especially for the last two years where afterslip is inferred to be on the deepest patches.
 Although we do note that it is not unheard of for afterslip to persists for years or decades following an earthquake \citep{Cakir2012}.
-Either way, we can conclusively say a localized deformation mechanism is required to explain the available five years of near field deformation.
+Either way, we can conclusively say a localized deformation mechanism is required to explain the available five years of near-field deformation.
 
@@
 
-We found that a Zener rheology in the upper mantle with a transient viscosity of about $10^{18}$ Pa s does a noticeably better job at predicting far field postseismic deformation.
+We found that a Zener rheology in the upper mantle with a transient viscosity of about $10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
 A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \citep{Liu1976}.
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/rheology}
-\centering 
-\caption{}
-\label{fig:Rheology}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.45]{Figures/filterP496}
-\centering
-\caption{}
-\label{fig:P496}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.45]{Figures/filterP619}
-\centering
-\caption{} 
-\label{fig:P619}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.4]{Figures/nearfield}
-\centering 
-\caption{}
-\label{fig:NearField}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.4]{Figures/farfield}
-\centering 
-\caption{}
-\label{fig:FarField}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6]{Figures/recordsection1}
-\centering 
-\caption{record section}
-\label{fig:RecordSection1}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6]{Figures/lower_crust}
-\centering 
-\caption{afterslip and viscoelastic relaxation in lower crust}
-\label{fig:LowerCrust}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=1.0]{Figures/slip_lcurve}
-\centering 
-\caption{near field record section}
-\label{fig:SlipLCurve}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=1.0]{Figures/fluidity_lcurve}
-\centering 
-\caption{far field record section}
-\label{fig:FluidityLCurve}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=1.0]{Figures/effective_viscosity}
-\centering 
-\caption{effective viscosity}
-\label{fig:EffectiveViscosity}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.09]{Figures/initialslip}
-\caption{}
-\label{fig:InitialSlip}
-\end{figure}
-
-\begin{figure}
 \includegraphics[scale=0.09]{Figures/elasticslip}

### 2016-04-08 RoughDraft/ElMayor.tex
commit before push

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/context_map} 
+\includegraphics[scale=0.7]{Figures/ContextMap} 
 \caption{Map of the area where postseismic deformation following the El Mayor-Cucapah earthquake can be observed geodetically.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data Processing}\label{sec:Data}
@@
 \begin{figure}
-\includegraphics[scale=0.37]{Figures/filterP496}
+\includegraphics[scale=0.7]{Figures/FilterP496}
 \centering
@@
 \begin{figure}
-\includegraphics[scale=0.37]{Figures/filterP619}
+\includegraphics[scale=0.7]{Figures/FilterP619}
 \centering
@@
 \begin{figure}
-\includegraphics[scale=0.32]{Figures/nearfield}
+\includegraphics[scale=0.7]{Figures/MapViewNearField}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.32]{Figures/farfield}
+\includegraphics[scale=0.7]{Figures/MapViewFarField}
 \centering 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Postseismic Modeling}\label{sec:Model}
@@
 This extended fault segment was also found to be necessary by \citet{Rollins2015} and \citet{Pollitz2012} in order to describe the postseismic deformation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{elastic inversion}\label{sec:ElasticInversion}    
@@
 In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the values listed in table \ref{tab:MaterialProperties} throughout this paper.
-The values for $\lambda$ and $\mu$ are consistent with the properties used in the coseismic model by \cite{Wei2011} and the 1D SCEC velocity model.
-The only unknowns are then the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
+The values for $\lambda$ and $\mu$ are consistent with the properties used in the coseismic model by \citet{Wei2011} and the 1D SCEC velocity model.
+The only unknown is the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
 Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane and they did not require any viscoelastic relaxation to describe the observations.
@@
 \end{equation}           
-where $g(x,\xi)$ is an elastic Green's function describing the displacement at position $x$ resulting from a unit of slip at $\xi$ on the fault, denoted by $F$.
+where $g(x,\xi)$ is an elastic Green's function describing the displacement at surface position $x$ resulting from a unit of slip at $\xi$ on the fault, denoted by $F$.
 We estimate coseismic slip, as well as the rate of afterslip over time intervals spanning 0.0-0.125 years, 0.125-0.25 years, 0.5-1.0 years, and at 1.0 year intervals for the remaining five years.
 Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
-We impose that the coseismic slip and rates of afterslip are within 45$^\circ$ of right-lateral slip.
-We also add zeroth order Tikhonov regularization so that our slip solution satisfies
+We impose that direction slip and slip rate are within 45$^\circ$ of right-lateral.
+We also add zeroth order Tikhonov regularization so that our solution for $s$ satisfies
 \begin{equation}\label{eq:ElasticObjective}
@@
 
-Our coseismic and afterslip solutions are shown in figure (TBD).
-As with \citet{Rollins2015}, we find that a significant amount of afterslip on the southern segment is required to explain the observations.
-Figure (TBD) is a scaled record section of observed and predicted postseismic displacements for stations along the El Mayor-Cucapah P axis.
-It is evident from figure (TBD) that the near-field stations ($\lesssim200$ km) can be well described by afterslip in an entirely elastic medium while there is a systematic underestimation and inability to reproduce the transient deformation in the far-field stations ($\gtrsim200$ km).
+Our coseismic and afterslip solutions are shown in figure \ref{fig:ElasticSlip}.
+As with \citet{Rollins2015}, we find that a large amount of afterslip on the southern fault segment is required to explain the observations.
+The potency of our inferred coseismic slip is $3.2\times10^9 \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPS.
+The potency of our inferred cumulative five years of afterslip is $6.1\times10^9 \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to the result of relaxation of coseismicly induced stresses.
+Our slip model accurately describes near field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicenter (figure \ref{fig:RecordSectionElastic}).
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
-In the following sections we seek to better describe the far-field postseismic deformation using viscoelastic models.
+Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next section.
 
+\begin{figure}
+\includegraphics[scale=0.7]{Figures/ElasticSlip}
+\caption{}
+\label{fig:ElasticSlip}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.7]{Figures/RecordSectionElastic}
+\caption{}
+\label{fig:RecordSectionElastic}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{constraints on effective viscosity}\label{sec:InitialInversion}
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/rheology}
+\includegraphics[scale=0.7]{Figures/rheology}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.5]{Figures/lower_crust}
+\includegraphics[scale=0.5]{Figures/Cancellation}
 \caption{afterslip and viscoelastic relaxation in lower crust}
@@
 We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity.
-Moreover, we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general for the respoving power of these GPS data.
+Moreover, we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
 
@@
 \begin{figure}
-\includegraphics[scale=0.5]{Figures/recordsection1}
+\includegraphics[scale=0.7]{Figures/RecordSectionDuration}
 \centering 
@@
 Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
-Although fluidity is rarely used in geophysical literature, it is more natural to consider fludities rather than viscosities since eq.
-\ref{InitialRate} is linear with respect to fluidity and so the fluidity is proportional to the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere and asthenosphere.
+Although fluidity is rarely used in geophysical literature, eq.
+\ref{InitialRate} is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere and asthenosphere.
 We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_\eta$.
@@
 It is therefore difficult to interpret the magnitude of uncertainties on viscosities shown in figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
-The uncertainties in fluidities increases with depth, as would be expected due to decreased sensitivity with depth.
-Nevertheless, a robust feature that we see is that the viscosity below 60 km depth needs to be on order of $10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations.
-Our inference that the lower crust and mantle from 30 to 60 km depth are appreciable stronger than the underlying mantle is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
-The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that the viscosity is effectively infinite during the first 0.8 years after the El Mayor-Cucapah earthquake.
+A robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
+The viscosity below $\sim60$ km depth needs to be $~1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
+The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
 Our inference of a mantle viscosity on the order of $10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady-state viscosities from \citet{Pollitz2000}, \citet{Pollitz2003}, \citet{Johnson2007}, \citet{Spinler2015}, and \citet{Rollins2015}.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/effective_viscosity}
+\includegraphics[scale=0.7]{Figures/EffectiveViscosity}
 \centering 
@@
 Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figure \ref{fig:InitialSlip}.
-To show how our slip solution is influenced by allowing for a viscoelastic lithopshere, we also show the coseismic slip and afterslip inferred using the same geometry, discretization, and regularization, but we assume the lithosphere and asthenosphere are elastic.
-In both coseismic inversions, most of the slip is inferred to be in the Sierra Cucapah and is right lateral with a significant normal component.
-This is consistent with field studies, \cite{Fletcher2014} as well as the coseismic slip from \cite{Wei2011}.
-The potency of inferred coseismic slip is $3.32\times 10^{9} \mathrm{m}^3$, which is equivalent to a moment magnitude of 7.28 when assuming a shear modulus of 32 GPa.
-The potency of the inferred coseismic slip model when assuming an elastic lithosphere is not significantly different, $3.55\times 10^9 \mathrm{m}^3$.
-The striking difference between the two models is that the inferred afterslip on the Indiviso fault segment is significantly larger when not accounting for viscoelasticity.
-The potency of afterslip in the elastic model is $2.7\times 10^9 \mathrm{m}^3$, compared to $0.85\times 10^9 \mathrm{m}^3$ for the viscoelastic model.
-The former is comparable to the size of the mainshock which, as noted by \cite{Rollins2015}, is implausibly large.
-The significant amount of afterslip inferred to be on the Indiviso fault by \cite{Rollins2015} seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
-The fact that there is still an appreciable amount of deep afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than we allow for since we only estimate depth dependent variations in viscosity.
+Similar to our elastic slip model from section \ref{sec:ElasticInversion}, coseismic slip is inferred to be in the Sierra Cucapah and it is right lateral with a significant normal component.
+This is consistent with field studies \cite{Fletcher2014}, as well as the coseismic slip from \cite{Wei2011}.
+The potency of inferred coseismic slip is $3.3\times 10^{9} \mathrm{m}^3$, which is also about the same as that inferred from section \ref{sec:ElasticInversion}.
+The present inference of afterslip on the Indiviso fault is significantly less than what was found in the section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
+When fault slip is simultaneously estimated with a lithospheric and asthenospheric viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9 \mathrm{m}^3$, compared to $3.46\times10^{9} \mathrm{m}^3$ when we assume the lithosphere and asthenosphere are elastic.
+The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
+The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
 
 \begin{figure}
-\includegraphics[scale=0.09]{Figures/initialslip}
+\includegraphics[scale=0.7]{Figures/InitialSlip}
 \caption{}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Full Inversion}\label{sec:FullInversion}
 
-In the previous section we used the efficient inverse method described by \cite{Hines2015} to constrain the effective lithospheric viscosity required to explain the first 0.8 years of postseismic deformation.
-In this section we use the inferred effective lithospheric viscosities as a prior constraint when searching for rheologic models of the lithosphere which are capable of describing the available five years of postseismic data.
+In the previous section, we used the efficient inverse method described by \citet{Hines2015} to constrain the effective lithospheric viscosity required to explain the first 0.8 years of postseismic deformation.
+In this section, we use the effective lithospheric viscosities inferred above as a prior constraint when searching for rheologic models of the lithosphere which are capable of describing the available five years of postseismic data.
+Figure \ref{fig:Rheology} describes how the inferred effective viscosities from section \ref{sec:InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
+We perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from section \ref{sec:InitialInversion}.
+Our forward problem is now eq.
+(\ref{GeneralForward}) rather than the approximation given by eq.
+(\ref{ApproxForward}).
 
-Figure \ref{fig:Rheology} describes how the inferred effective viscosities from section \ref{sec:InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
-In this section we perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from \ref{sec:InitialInversion}.
-Our forward problem is now eq.
-\ref{GeneralForward} rather than the approximation given by eq.
-\ref{ApproxForward}.
-As a reference, we compare the best fit solution for each assumed lithospheric model to a the best fit solution assuming an entirely elastic lithosphere.
+%As a reference, we compare the best fit solution for each assumed lithospheric model to a the best fit solution assuming an entirely elastic lithosphere.
 One intuitive criterion for a viscoelastic lithospheric model to be plausible is that it should be able to predict observable deformation better than a lithospheric model which is elastic.
 
-We first assume that the crust and mantle can be described with a Maxwell rheology, and so inferences of $\eta_{\mathrm{eff}}$ are equivalent to inferences of $\eta_{\mathrm{M}}$.
+We first assume that the crust and mantle can be described with a Maxwell rheology, and we use $\eta_{\mathrm{eff}}$ from section \ref{sec:InitialInversion} for our assumed value of $\eta_{\mathrm{M}}$.
 We compute $f$ and $g$ from eq.
-\ref{GeneralForward} using Pylith \citep{Aagaard2009} and assume the same spatial and temporal discretization of $s$ as in section \ref{sec:InitialInversion}.
-The misfit for the Maxwell model, defined by eq.
-\ref{Misfit}, is 62.0 which is significantly higher than that of the elastic model, 47.5.
-As noted, our estimates of $\eta_\mathrm{eff}$ can be thought of as an upper limit, and we have tried using viscoelastic Green's functions, $f$, with lower viscosities but that only increases the misfit.
-It is apparent that most of the misfit comes from the Maxwell model significantly overestimating the rate of deformation after $\sim 3$ years following the earthquake.
-Although, numerous studies have described postseismic deformation in Southern California using a Maxwell viscoelastic rheology with viscosities consistent with ours, it is clear that such a model is incapable of describing the entire postseismic time series.
-As previously noted, \cite{Pollitz2001}, recognized this deficiency in a Maxwell rheology which motivated their exploration of a Burgers rheology upper mantle \citep{Pollitz2003}.
+(\ref{GeneralForward}) using the finite element software, Pylith \citep{Aagaard2009}, and assume the same spatial and temporal discretization of $s$ as in sections \ref{sec:ElasticInversion} and \ref{sec:InitialInversion}.
+We estimate $s$ using linear least squares and we find the mean chi squared value,
+\begin{equation}\label{eq:Misfit}
+  \bar\chi^2 = \frac{1}{N}\left|\left|\frac{u_\mathrm{pred} - u_\mathrm{obs}}{\sigma_\mathrm{obs}}\right|\right|_2^2,
+\end{equation}
+is 37.4.
+For comparison, $\bar\chi^2=35.3$ for the elastic model from section \ref{sec:ElasticInversion}.
+The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years.
+As noted, our estimates of $\eta_\mathrm{eff}$ can be thought of as an upper limit, and we have tried using Maxwell viscoelastic Green's functions with lower viscosities; however, that only increases the misfit.
+Although, the viscosities used here are consistent with the successful Maxwell viscoelastic models found by \citet{Rollins2015} and \citet{Spinler2015}, which had mantle viscosities on the order of $10^{18}$ Pa s, we find that such a model is incapable of describing the entire postseismic time series.
+\citet{Pollitz2001} similarly recognized this deficiency in a Maxwell rheology, which then motivated their exploration of a Burgers rheology upper mantle \citep{Pollitz2003}.
 
-Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces the unknown parameter $\mu_{k}$.
+Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces the unknown parameter $\mu_{K}$.
 We assume that the lower crust still has a Maxwell rheology.
 The steady state viscosity, $\eta_{M}$, in the crust and the transient viscosity, $\eta_\mathrm{K}$, in the mantle are set equal to the inferred effective viscosities.
-The unknown rheologic parameter which we estimate is the ratio of shear moduli, $\nu=\frac{\mu_K}{\mu_M}$.
-We compute nine different sets of Green's functions, $f$ and $g$, using Pylith where we assume different values of $\nu$ ranging from 0 to 1.
-The former being a degenerate case when the Zener model becomes the Maxwell model from above and the later being a Jeffreys solid.
-We estimate coseismic slip and afterslip for each realization of $\nu$.
-The misfit as a function of $\nu$ is shown in figure \ref{fig:ShearModulusRatio}.
-The optimal value of $\nu$ is found to be $0.375$, which has a misfit of 44.9,  which seems like a modest improvement from the elastic model; however, the improvement can be clearly seen in the fit to the far-field data which does a significantly better job at explaining the rate of deformation throughout the 5 years (figure \ref{fig:RecordSection2}).
-This significant improvement is seen for all shear modulus ratios greater than about $0.125$.
+We then estimate the ratio of shear moduli, $\frac{\mu_K}{\mu}$.
+We compute nine different sets of Green's functions, $f$ and $g$, using Pylith, where we assume values of $\frac{\mu_K}{\mu}$ ranging from 0 to 1.
+The former being a degenerate case when the Zener model becomes the Maxwell model.
+We estimate coseismic slip and afterslip for each realization of $\frac{\mu_K}{\mu}$.
+The optimal shear moduli ratio is found to be $0.375$ which has a misfit of $\bar\chi^2=31.2$ (figure \ref{fig:ShearModulusRatio}).
+The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (figure \ref{fig:RecordSection2}).
+The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the 5 years.
 
-Because we are able to adequately  describe the available five years of postseismic seismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since the Zener model can be thought of as the limit when the steady state viscosity in a Burgers rheology is infinite, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in \ref{sec:InitialInversion} and an effectively infinite steady state viscosity on the timescale of five years, $>10^{20}$ Pa s, would also be able to satisfactorily describe the observable postseismic deformation.
+\begin{figure}
+\includegraphics[scale=0.8]{Figures/RatioMisfit}
+\centering 
+\caption{misfit with different shear modulus ratios}
+\label{fig:ShearModulusRatio}
+\end{figure}
 
-Satisfied with a Zener rheology for the mantle with shear modulus ratio of 0.375, our final step is to choose a damping parameter for out estimates of coseismic slip and afterslip, which has been fixed at 0 until now.
-We estimate the damping parameter, again enforcing smallness on our model, using another L-curve test.
-Our preferred model for coseismic slip and afterslip is shown in figure \ref{fig:FinalSlip}.
+\begin{figure}
+\includegraphics[scale=0.8]{Figures/RecordSectionFinal}
+\centering 
+\caption{}
+\label{fig:RecordSection2}
+\end{figure}
 
-The postseismic displacements predicted for our preferred slip model and rheologic model of the lithospheric are shown in figures \ref{fig:NearField} and \ref{fig:FarField} as well as \ref{fig:RecordSection2}.
-Additionally, we show the predicted postseismic deformation broken down into an elastic and viscoelastic component (figure (TBD)).
-Overall, the trend in the near-field and far-field transient deformation is accurately described by our preferred model.
-In particular, the trend in far-field deformation is much better described by our preferred model, which has a Zener rheology mantle, than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:RecordSection2}).
+Because we are able to adequately describe the available five years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
+However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in section \ref{sec:InitialInversion} and a steady state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
+
+The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in figure \ref{fig:FinalSlip} and the predicted postiseismic displacements are shown figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
+Overall, the trends in the near-field and far-field transient deformation are accurately described by our preferred model.
+In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:RecordSection2}).
 There are a few areas where we have notable misfit.
-Most of our misfit is for the near-field stations in the Imperial Valley and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \citep{Wei2011a,Wei2015}.
+Most of our misfit is for the near-field stations in the Imperial Valley, and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \citep{Wei2011a,Wei2015}.
+In particular, we are unable to model the sustained rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
 Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
@@
 
+\begin{figure}
+\includegraphics[scale=0.8]{Figures/FinalSlip}
+\centering 
+\caption{}
+\label{fig:FinalSlip}
+\end{figure}
+
 The cumulative potency of slip over time is shown in figure (TBD).
-The inferred coseismic potency is $3.1\times10^{9} \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of five years of afterslip is $1.2\times10^{9} \mathrm{m}^3$.
-While most of the afterslip is inferred to be within the first couple months of the earthquake, accounting for the most rapid near-field transient deformation, we infer that afterslip in the vicinity of the Sierra Cucapah, where most slip occurred during the main shock, is necessary to explain the sustained rate of deformation in the near-field.
-We emphasize, that the GPS station closest to where we infer there to be sustained afterslip, P496, is still about 30 km away, which we believe is too distil for us to conclusively argue for sustained brittle deformation rather ductile deformation in a shear zone, especially for the last two years where afterslip is inferred to be on the deepest patches.
-Although we do note that it is not unheard of for afterslip to persists for years or decades following an earthquake \citep{Cakir2012}.
-Either way, we can conclusively say a localized deformation mechanism is required to explain the available five years of near-field deformation.
+The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of five years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
+Most of the afterslip in our preferred model occurs within the first year after the earthquake with a significant amount inferred to be shallow and in the Sierra Cucapah.
+The afterslip within the first year is accounting for the most rapid near-field transient deformation.
+After one year, afterslip is inferred to be deeper and under the Sierra Cucapah, which is describing much of the sustained near-field postseismic deformation.
+We emphasize, that the GPS station closest to our inferred afterslip, P496, is still about 30 km away, which is too far away for us to conclusively argue for sustained brittle deformation rather shallow ductile deformation.
+The deep afterslip inferred after one year could potentially be describing deformation resulting from lower crustal flow.
+Indeed, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from section \ref{sec:InitialInversion}, and we find that such a model adequately describes the observations without any afterslip after one year.
+Our model with a weaker lower crust still requires about the same amount of afterslip over the first year.
+We do believe that the early shallow afterslip is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
 
-Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle, which is the simplest viscoelastic rheologic model \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}.
-In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucuapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s with a relatively stronger lower crust.
+Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}, which is the simplest viscoelastic rheologic model.
+In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucuapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s, with a relatively stronger lower crust.
 Our inference that the the crust and uppermost mantle are relatively strong compared to the underlying mantle is also consistent with that found by \citet{Freed2007a}.
-While these inferences are consistent with our effective viscosities, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
-Studies on interseismic deformation \citep{Lundgren2009} and lake loading \citep{Luttrell2007}, which are both processes that occur on the timescale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+While these studies found viscosities that are consistent with our effective viscosities from section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
+Studies on the earthquake cycle \citep{Lundgren2009} and lake loading \citep{Luttrell2007} in Southern California, which are both processes that occur on the time scale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
 
-An additional deficiency in the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate postseismic deformation.
+An additional deficiency in the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate of postseismic deformation.
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
-However, the trend in postseismic deformation at distances greater than about 200 km from the El Mayor Cucapah epicenter, which can only be attributed to viscoelastic relaxation \citep{Freed2007a}, cannot be explained with a Maxwell viscoelastic lithosphere (figure \ref{fig:RecordSection2}).
+However, postseismic deformation at distances greater than $\sim200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep{Freed2007a} but we have demonstrated that it cannot be explained with a Maxwell rheology (figure \ref{fig:RecordSection2}).
 
-We found that a Zener rheology in the upper mantle with a transient viscosity of about $10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
-A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe the spectrum of frequencies where seismic attenuation is observed \citep{Liu1976}.
-The highest viscosity needed to describe attenuation of earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \citep{Yuen1982} and the largest characteristic relaxation time would be on the order of days.
+We found that a Zener rheology in the upper mantle with a transient viscosity of $\sim10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
+A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe seismic attenuation \citep{Liu1976}.
+The highest viscosity needed to describe attenuation of Earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \citep{Yuen1982} and the largest characteristic relaxation time would be on the order of days.
 Even though our inferred transient viscosity is orders of magnitude larger than that required for seismic attenuation models, the two models are not incompatible.
-Rather the delayed elasticity in seismic attenuation models occurs on such short time scales that it can be considered  part of the instantaneous elastic phase of deformation associated with the preferred Zener model in this study.
+Rather, the delayed elasticity in seismic attenuation models occurs on such short time scales that it can be considered  part of the instantaneous elastic phase of deformation associated with the preferred Zener model in this study.
 
 Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid behaviour required for mantle dynamics on geologic time scales.
-\citet{Yuen1982} proposed a Burgers rheology with a low viscosity ($\approx 10^{16}$ Pa s) in the Kelvin element and high viscosity ($\approx 10^{21}$ Pa s) in the Maxwell element which is capable of describing both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
-The justification of a Burger's rheology mantle is further supported by laboratory experiments on the strength of olivine \citep{Chopra1997}.
+\citet{Yuen1982} proposed a Burgers rheology with a low transient viscosity ($\mu_K\approx10^{16}$ Pa s) and high steady-state viscosity ($\eta_M\approx10^{21}$ Pa s) to describe both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
+The justification of a Burger's rheology mantle is further supported by laboratory experiments on olivine \citep{Chopra1997}.
 \citet{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
-While the Burgers rheology was introduced as a means of bridging to gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \citet{Lundgren2009} and \citet{Luttrell2007}.
+While the Burgers rheology was introduced as a means of bridging the gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \citet{Lundgren2009} and \citet{Luttrell2007}.
 Additionally, the transient viscosity inferred by \citet{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, which may be the result of shallow afterslip.
@@
 While we also argue that a transient rheology is necessary to explain postseismic deformation, our preferred transient viscosity of $10^{18}$ Pa s is an order of magnitude larger than the transient viscosity found by \cite{Pollitz2003}.
-Since we found that A Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady state viscosity that is effectively infinite over five years, would also be able to describe postseismic deformation.
-Such a Burgers model would then be consistent with the steady state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.
+Since we found that a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over five years, would also be able to describe the postseismic deformation.
+Such a Burgers model might then be consistent with the steady state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.
 
@@
 
-This research was funded by X
+This material is based upon work supported by the National Science
+Foundation under Grant Numbers EAR 1045372 and EAR 1245263.
 
@@
 
-\begin{figure}
-\includegraphics[scale=0.09]{Figures/elasticslip}
-\caption{}
-\label{fig:InitialSlip}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=1.0]{Figures/shear_ratio}
-\centering 
-\caption{misfit with different shear modulus ratios}
-\label{fig:ShearModulusRatio}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.09]{Figures/finalslip}
-\centering 
-\caption{}
-\label{fig:FinalSlip}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6]{Figures/recordsection2}
-\centering 
-\caption{}
-\label{fig:RecordSection2}
-\end{figure}
-
 \end{document}

### 2016-04-09 RoughDraft/ElMayor.tex
commit before push

@@
 \title{	
-Rheologic contraints on the Lithosphere and Asthenosphere from five years of Postseismic deformation following the El Mayor-Cucapah earthquake}
+Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
 \author{T. T. Hines\fnref{fn}}
@@
 \begin{abstract}
-foo bar
 \end{abstract}
@@
 \section{Introduction}
-Ground deformation in the years following a large ($>$Mw7) earthquake provides insight into the mechanical behaviour of the lithosphere.
-It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions (e.g.
-\cite{Savage1990}).
-Thanks to the dense geodetic network deployed throughout the 2000's as part of the Plate Boundary Observatory, the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California produced observable postseismic deformation at more GPS stations than any other earthquake in California to date.
-With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake, where we consider both afterslip and viscoelastic relaxation in lithosphere and asthenosphere as candidate mechanisms.
+Ground deformation in the years following a large ($gtrsim$Mw7) earthquake provides insight into the mechanical behaviour of the crust and upper mantle.
+It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
+Thanks to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California produced observable postseismic deformation at more GPS stations than any other earthquake in California to date.
+With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake, where we consider both afterslip and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
 
-Previous studies which have modeled postseismic deformation following the El Mayor-Cucapah earthquake include \citet{Pollitz2012}, \citet{Gonzalez-ortega2014}, \citet{Spinler2015}, and \citet{Rollins2015}.
-Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the observations with afterslip in an entirely elastic lithosphere and asthenosphere.
-\citet{Gonzalez-ortega2014} described five months of postseismic deformation observed by nearfield ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR with afterslip and contraction on the coseismically ruptured fault.
-\citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
-Using continuous GPS stations, which are mostly north of rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of afterslip inferred on the least constrained, southern most fault segment.
-Here, we suggest this inferred afterslip may have been acting as a proxy for distributed relaxation in the upper mantle.
+Previous studies which have modelled postseismic deformation following the El Mayor-Cucapah earthquake include \citet{Pollitz2012}, \citet{Gonzalez-ortega2014}, \citet{Spinler2015}, and \citet{Rollins2015}.
+Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the postseismic deformation with afterslip in an elastic half-space.
+\citet{Gonzalez-ortega2014} described five months of postseismic deformation observed by near-field ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR with afterslip and contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodelled viscoelastic relaxation.
+Using continuous GPS stations, which are mostly north of rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of slip inferred on the least constrained, southern-most fault segment.
+Here, we suggest the afterslip inferred by \cite{Rollins2015} may have been acting as a proxy for distributed relaxation in the upper mantle.
 
 \citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential postseismic deformation mechanism.
-The lithospheric rheology is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and then find the best fitting rheologic parameters.
-The inference of these rheologic parameters is a computationally expensive nonlinear inverse problem which is typically approached with a forward modeling grid search method.
+The rheology of the crust and mantle is largely unknown and so modelling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and then find the best fitting rheologic parameters.
+The inference of these rheologic parameters is a computationally expensive non-linear inverse problem which is typically approached with a forward modelling grid search method.
 Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
@@
 To further reduce the model space dimensions being search, it is also necessary to make simplifying assumptions about the nature of afterslip.
-For example, one can assume a frictional model for afterslip and parameterize afterslip in terms of the unknown rheologic properties of the fault \citep[e.g.][]{Johnson2009,Johnson2004}.
-One can also assume that afterslip does not persist for more than a few months or a year and then model the later postseismic deformation assuming it to be the result of only viscoelastic relaxation \citep[e.g.][]{Pollitz2012,Spinler2015}.
+For example, one can assume a frictional model for afterslip and parametrize afterslip in terms of the unknown rheologic properties of the fault \citep[e.g.][]{Johnson2009,Johnson2004}.
+One can also assume that afterslip does not persist for more than a few months and then model the later postseismic deformation assuming it to be the result of only viscoelastic relaxation \citep[e.g.][]{Pollitz2012,Spinler2015}.
 However, postseismic afterslip in similar tectonic settings has been observed to persist for decades following earthquakes \citep{Cakir2012,Cetin2014}.
 Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to a biased inference of lithospheric viscosity.
-Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near-field deformation, which could be indicative of unmodeled continued afterslip.
+Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near-field deformation, which could be indicative of unmodelled continued afterslip.
 
 In this study, we assume that both afterslip and viscoelastic relaxation can contribute to postseismic deformation.
-Modeling both of these mechanisms creates a high dimensional model space that must be searched with nonlinear optimization methods.
+Modelling both of these mechanisms creates a high dimensional model space that must be searched with non-linear optimization methods.
 We first develop an initial postseismic model using the method described in \citet{Hines2015}.
 This method simultaneously estimate the afterslip and effective lithospheric viscosity structure necessary to describe the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We then use the inferred effective viscosity structure to create a suite of postseismic models which are tested against available five years of postseismic data.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of sustained afterslip beneath the Sierra Cucapah and a Zener rheology upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s at 30 km depth to $1\times10^{18}$ Pa s at 120 km depth.
+We then use the inferred effective viscosity structure to create a suite of postseismic models which are tested against the available 5 years of postseismic data.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip beneath the Sierra Cucapah, a Zener rheology upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
 
@@
 \caption{Map of the area where postseismic deformation following the El Mayor-Cucapah earthquake can be observed geodetically.
-The large focal mechanism is for the El Mayor Cucapah earthquake and the three small focal mechanisms are for the Octotillo earthquake and the two main shocks during the Brawley swarm.
+The large focal mechanism is for the El Mayor Cucapah earthquake and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
 The black dots indicate the locations of GPS stations used in this study.
@@
 The green and red boxes denote the extent of the near and far-field displacement maps.
-The blue sector highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis and stations within this sector are used in the record sections in figures \ref{fig:RecordSection1} and \ref{fig:RecordSection2}}
+The blue sector highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis and stations within this sector are used in the record Sections in Figures \ref{fig:RecordSection1} and \ref{fig:RecordSection2}}
 \label{fig:ContextMap}
@@
 
-We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicenter.
-We describe the coseismic and postseismic displacement resulting from the El Mayor-Cucapah earthquake collectively as $u_\mathrm{post}(t)$ and we consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.3 event on August 26, 2012, (figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the GPS position timeseries.
-We treat the displacements resulting from the Brawley swarm as a single event because the position time series are provided by UNAVCO as daily solutions.
+We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicentre.
+We collectively describe the coseismic and postseismic displacements resulting from the El Mayor-Cucapah earthquake as $u_\mathrm{post}(t)$.
+We consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
+The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.3 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
+We treat the displacements resulting from the Brawley swarm as a single event because the time series are provided by UNAVCO as daily solutions.
 Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation and we model displacements resulting from these events with a Heaviside function, $H(t)$.
@@
 \end{equation}
-In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthuqake, Ocotillo earthquake, and the Brawley swarm, respectively, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
-We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicenters.
+In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthquake, Ocotillo earthquake, and the Brawley swarm, respectively, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
+We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicentres.
 
@@
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it would be possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
+Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it is possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
 However, we use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
-We use displacements because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertanties depending on exactly how the estimation is done (REF).
-This modeling choice prevents us from using the newly installed stations in Baja California in our analysis.
+We use displacements because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertainties depending on exactly how the estimation is done.
+This modelling choice prevents us from using the newly installed stations in Baja California for our analysis.
 
-The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred about 270 km north of the El Mayor-Cucapah epicenter, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
-We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
-When appraising our model fit in Section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine epicenter, which may be the result of errors in the assumption that the trend in Hector Mine postseismic deformation is linear after six years.
+The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred about 270 km north of the El Mayor-Cucapah epicentre, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicentre are approximately constant \citep{Savage2009}.
+When appraising our model fit in Section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine epicentre, which may be the result of errors in the assumption that the trend in Hector Mine postseismic deformation is linear after six years.
 
 Studies of postseismic deformation typically assume a parametric form for $u_\mathrm{post}(t)$, such as one with a logarithmic or exponential time dependence \citep[e.g.][]{Savage2005a}.
-However, by assuming a logarithmic or exponential form of $u_\mathrm{post}(t)$ we run the risk of over fitting the GPS time series and inferring a nonexistent postseismic signal.
+However, by assuming a logarithmic or exponential form of $u_\mathrm{post}(t)$ we run the risk of over fitting the GPS time series and inferring a non-existent postseismic signal.
 We therefore do not assume any parametric form for $u_\mathrm{post}(t)$ and rather treat it as integrated Brownian motion, so that
@@
 We use a Kalman filtering approach to estimate $u_\mathrm{post}(t)$ and the unknown parameters in eq.
-\ref{TimeSeriesModel}.
+(\ref{TimeSeriesModel}).
 In the context of Kalman filtering, our time varying state vector is
@@
 and eq.
-\ref{TimeSeriesModel} is the observation function which maps the state vector to the GPS observations.
+(\ref{TimeSeriesModel}) is the observation function which maps the state vector to the GPS observations.
 We initiate the Kalman filter by assuming a prior estimate of $\mathbf{X}(t)$ at the first time epoch, denoted $\mathbf{X}_{1|0}$, which has a sufficiently large covariance, denoted $\mathbf{\Sigma}_{1|0}$, to effectively make our prior uninformed.
@@
 The smoothness of $u_\mathrm{post}(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect postseismic displacements to vary over time.
-Setting $\sigma^2$ equal to zero will effectively result in modeling $u_\mathrm{post}(t)$ as a straight line which is insufficient to describe the expected transient behaviour in postseismic deformation.
-The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ overfitting the data.
-While one can use a maximum likelihood based approach to picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+Setting $\sigma^2$ equal to zero will effectively result in modelling $u_\mathrm{post}(t)$ as a straight line which is insufficient to describe the expected transient behaviour in postseismic deformation.
+The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ over fitting the data.
+While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
-We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (figure \ref{fig:P496}).
+We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (Figure \ref{fig:P496}).
 By down sampling, we implicitly assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
-Figure \ref{fig:P496} shows the estimate of coseismic and postseismic deformation, $u_\mathrm{post}(t)$, for station P496 along with the estimated uncertainties.
-\cite{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and indeed, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we also clearly see far reaching postseismic transient deformation (figure \ref{fig:P619}).
+\citet{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicentre, we also clearly see far reaching postseismic transient deformation (Figure \ref{fig:P619}).
 
@@
 It is important to note that the shown uncertainties in $u_\mathrm{post}(t)$ do not account for the non-negligible epistemic uncertainty in eq.
-\ref{TimeSeriesModel}.
-For example, we assume a constant rate of secular deformation, which appears to be an appropriate approximation for all but perhaps the stations closest to the Hector Mine epicenter, as noted aboved.
+(\ref{TimeSeriesModel}).
+For example, we assume a constant rate of secular deformation, which appears to be an appropriate approximation for all but perhaps the stations closest to the Hector Mine epicentre, as noted above.
 Also, our model for seasonal deformation in eq.
-\ref{TimeSeriesModel} assumes a constant amplitude over time, which means that any yearly variability in the climatic conditions could introduce systematic residuals \citep{Davis2012}.
+(\ref{TimeSeriesModel}) assumes a constant amplitude over time, which means that any yearly variability in the climatic conditions could introduce systematic residuals \citep{Davis2012}.
 Indeed, it would be more appropriate to consider the seasonal amplitudes $c_2-c_5$ in eq.
-\ref{TimeSeriesModel} as stochastic variables \citep{Murray2005}.
-By using constant seasonal amplitudes our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodeled oscillations (e.g.
-figure \ref{fig:P619}).
+(\ref{TimeSeriesModel}) as stochastic variables \citep{Murray2005}.
+By using constant seasonal amplitudes our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodelled annual and semi-annual oscillations (e.g.
+Figure \ref{fig:P619}).
 
-We show in figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic deformation accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as the coseismic displacements.
-In the far-field to the north, we can see south trending displacements for the first 3.0 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicenter.
+We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as the coseismic displacements.
+In the far-field to the north, we can see south trending displacements for the first 3.0 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicentre.
 These displacements are most pronounced along the direction of the El Mayor-Cucapah P axis.
 A similar eastward trend can be seen in the few far-field stations along the T axis in Arizona.
-After 3.0 years, The trend in far-field postseismic deformation is barely perceptible.
+After 3 years, the trend in far-field postseismic deformation is barely perceptible.
 The vertical deformation in the far-field is difficult to attribute to postseismic processes.
 Most far-field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
-This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symetric quadrant pattern, as would be expected for postseismic processes.
-Although we use vertical deformation in our analysis in section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation as it likely does not have postseismic origins.
+This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symmetric quadrant pattern, as would be expected for postseismic processes.
+Although we use vertical deformation in our analysis in Section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation as it likely does not have postseismic origins.
 
@@
 The near-field postseismic deformation is notably sustained when compared to the far-field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, is moving at a steady rate of $\sim1.4$ cm/yr to the south five years after the El Mayor-Cucapah earthquake.
-Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is indeed resulting from tectonic processes.
-However, the vertical postseismic deformation signal is only apparent for the first year after the earthquake (figure \ref{fig:NearField}).
-As with the far-field deformation, there is a general trend of uplift in the near-field one year after the earthquake which we do not consider to be related to postseismic processes.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicentre, P496, has been moving at a steady rate of $\sim1.5$ cm/yr to the south since $\sim1$ year after the El Mayor-Cucapah earthquake.
+Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from tectonic processes.
+However, the vertical postseismic signal is only apparent for the first year after the earthquake (Figure \ref{fig:NearField}).
+As with the far-field deformation, there is a general trend of uplift in the near-field after $\sim1$ year, which we do not consider to be related to postseismic processes.
 
@@
 \begin{table}\label{tab:MaterialProperties}
-\begin{tabular} {l l l l l l}
-depth (km) &$\lambda$ (GPa)&$\mu$ (Gpa)&$\rho$ (kg/m$^3$)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
-0-5 & 24.0 & 24.3 & 2400 & - & -\\
-5-15 & 35.2 & 35.4 & 2670 & - & -\\
-15-30 & 41.8 & 41.9 & 2800 & 44.3 & 0.0\\
-30-60 & 61.0 & 60.8 & 3000 & 5.91 & 0.375\\
-60-90 & 61.0 & 60.8 & 3000 & 1.99 & 0.375\\
-90-120 & 61.0 & 60.8 & 3000 & 1.31 & 0.375\\
-120-150 & 61.0 & 60.8 & 3000 & 1.10 & 0.375\\
-150-$\infty$ & 61.0 & 60.8 & 3000 & 1.07 & 0.375\\
+\begin{tabular} {l l l l l}
+depth (km) &$\lambda$ (GPa)&$\mu$ (GPa)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
+0-5 & 24.0 & 24.3 & - & -\\
+5-15 & 35.2 & 35.4 & - & -\\
+15-30 & 41.8 & 41.9 & 44.3 & 0.0\\
+30-60 & 61.0 & 60.8 & 5.91 & 0.375\\
+60-90 & 61.0 & 60.8 & 1.99 & 0.375\\
+90-120 & 61.0 & 60.8 & 1.31 & 0.375\\
+120-150 & 61.0 & 60.8 & 1.10 & 0.375\\
+150-$\infty$ & 61.0 & 60.8 & 1.07 & 0.375\\
 \end{tabular}
 \caption{Assumed and estimated material properties.
-$\lambda$, $\mu$, and $\rho$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in section \ref{sec:InitialInversion} and $\mu_k/\mu$ are the optimal shear moduli ratios found in section \ref{sec:FullInversion} for a Zener rheology.}
+$\lambda$, $\mu$, and $\rho$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in Section \ref{sec:InitialInversion} and $\mu_k/\mu$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology.}
 
 \end{table}
-In this paper, we seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake.
+In this paper, we seek to find the mechanisms driving 5 years of postseismic deformation following the El Mayor-Cucapah earthquake.
 We consider afterslip and viscoelastic relaxation in the lithosphere and asthenosphere as candidate mechanisms.
@@
 
-We estimate coseismic and time-dependent postseismic fault slip, both of which are assumed to occur on the fault geometry estimated by \citet{Wei2011} with some modifications.
+We estimate coseismic and time-dependent postseismic fault slip, both of which are assumed to occur on a fault geometry modified from \citet{Wei2011}.
 Field studies \citep{Fletcher2014} and LIDAR observations \citep{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \citet{Wei2011}, especially within the Sierra Cucapah.
 However, we find that a relatively simple coseismic fault geometry based on \citep{Wei2011} is adequate because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \citet{Fletcher2014} and \citet{Oskin2012}.
-The fault geometry used in this study (figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \citet{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
+The fault geometry used in this study (Figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \citet{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
 Both segments extend from the surface to 15 km depth.
-We extend the northern segment by 40 km to the northwest, motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
+We extend the northern segment by 40 km to the north-west, motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
 This extended fault segment was also found to be necessary by \citet{Rollins2015} and \citet{Pollitz2012} in order to describe the postseismic deformation.
@@
 \subsection{elastic inversion}\label{sec:ElasticInversion}    
-We consider a variety of rheologic models for the lithosphere and asthenosphere.
-The simplest rheologic model is to consider the lithospere and asthenosphere to be effectively elastic and isotropic.
-In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the values listed in table \ref{tab:MaterialProperties} throughout this paper.
-The values for $\lambda$ and $\mu$ are consistent with the properties used in the coseismic model by \citet{Wei2011} and the 1D SCEC velocity model.
-The only unknown is the distribution of fault slip, which can be easily estimated due to the linearity of the forward problem.
+We consider a variety of rheologic models for the lower crust and upper mantle.
+The simplest rheologic model is to consider them to be effectively elastic and isotropic.
+In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the values listed in Table \ref{tab:MaterialProperties} throughout this paper.
+The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.
 Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane and they did not require any viscoelastic relaxation to describe the observations.
-We also perform an elastic slip inversion but we use GPS stations within a larger radius about the El Mayor-Cucapah epicenter (400 km instead of $\sim$200 km).
-Our forward problem describing predicted postseismic deformation $u_\mathrm{pred}$ in terms of time dependent fault slip $s$ is
+We also perform an elastic slip inversion but we use GPS stations within a larger radius about the El Mayor-Cucapah epicentre (400 km instead of $\sim$200 km).
+Our forward problem describing predicted postseismic deformation, $u_\mathrm{pred}$, in terms of time dependent fault slip, $s$, is
 \begin{equation}\label{eq:ElasticForward}
@@
 \end{equation}           
-where $g(x,\xi)$ is an elastic Green's function describing the displacement at surface position $x$ resulting from a unit of slip at $\xi$ on the fault, denoted by $F$.
-We estimate coseismic slip, as well as the rate of afterslip over time intervals spanning 0.0-0.125 years, 0.125-0.25 years, 0.5-1.0 years, and at 1.0 year intervals for the remaining five years.
+where $g(x,\xi)$ is elastic Green's function describing displacement at surface position $x$ resulting from a unit of slip at $\xi$ on the fault, which is denoted by $F$.
+We estimate coseismic slip and the rate of afterslip at the discrete time intervals, 0.0-0.125, 0.125-0.25, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
 Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
-We impose that direction slip and slip rate are within 45$^\circ$ of right-lateral.
+We impose that the direction of slip and slip rate are within 45$^\circ$ of right-lateral.
 We also add zeroth order Tikhonov regularization so that our solution for $s$ satisfies
@@
 
-Our coseismic and afterslip solutions are shown in figure \ref{fig:ElasticSlip}.
+Our coseismic slip and afterslip solutions are shown in Figure \ref{fig:ElasticSlip}.
 As with \citet{Rollins2015}, we find that a large amount of afterslip on the southern fault segment is required to explain the observations.
-The potency of our inferred coseismic slip is $3.2\times10^9 \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPS.
-The potency of our inferred cumulative five years of afterslip is $6.1\times10^9 \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to the result of relaxation of coseismicly induced stresses.
-Our slip model accurately describes near field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicenter (figure \ref{fig:RecordSectionElastic}).
+The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPa.
+The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to the result of relaxation of coseismicly induced stresses.
+Our slip model accurately describes near field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
-Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next section.
+Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next Section.
 
@@
 
-For any linear viscoelastic rheology of the lithosphere and asthenosphere, postseismic displacement resulting from time dependent fault slip can be described as  
+For any linear viscoelastic rheology of the crust and mantle, postseismic displacements resulting from time dependent fault slip can be described as  
 \begin{equation}\label{GeneralForward}
@@
 $f$ is a function of $\lambda$, $\mu$, and any additional rheologic parameters controlling the viscoelastic response, which are generally not well known.
-Schematic representations of the viscoelastic rheologic models considered in this study for the lower crust and upper mantle are shown in figure \ref{fig:Rheology}.
-We consider Maxwell viscoelasticity, where the steady state viscosity $\eta_M$ is unknown, Zener viscoelasticty, where the transient viscosity $\eta_K$ and transient shear modulus $\mu_K$ are unknown, and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all unknown.
+Schematic representations of the viscoelastic rheologic models considered in this study are shown in Figure \ref{fig:Rheology}.
+We consider Maxwell viscoelasticity, where the steady-state viscosity, $\eta_M$, is unknown, Zener viscoelasticty, where the transient viscosity, $\eta_K$, and transient shear modulus, $\mu_K$, are unknown, and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all unknown.
 We further discuss these rheologic models and their use in geophysical studies in the discussion.
@@
 In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2015} to constrain an initial effective lithospheric viscosity structure from the early postseismic deformation.
-The method relies upon the fact that immediately after an earthquake, stresses throughout the lithosphere and asthenosphere are only controlled by the relatively well known instantaneous elastic properties.
-This means that the rate of deformation in each parcel of the lithosphere will deform at a rate that is inversely proportional to its effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$, and independent of $\eta_{\mathrm{eff}}$ elsewhere.
-Then, through linear superposition, we can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's viscosity.
+The method relies upon the fact that immediately after an earthquake, stresses throughout the crust and mantle are only controlled by the relatively well known instantaneous elastic properties and each parcel will have a strain rate, $\dot\epsilon$, that is proportional to stress, $\sigma$, and inversely proportional to the parcel's effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$.
+Through linear superposition, we can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's effective viscosity.
 That is to say
@@
 \end{equation}
-where $h(x,\xi,\zeta)$ describes the initial rate of deformation resultion from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and $L$ denotes the lithosphere and asthenosphere.
+where $h(x,\xi,\zeta)$ describes the initial rate of deformation resulting from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and $L$ denotes the crust and mantle.
 We can combine eq.
-\ref{InitialRate} with \ref{GeneralForward} to get a first order approximation for early postseismic deformation,
+(\ref{InitialRate}) with eq.
+(\ref{GeneralForward}) to get a first order approximation for early postseismic deformation,
 \begin{equation}\label{ApproxForward}
@@
 We perform an initial inversion of postseismic displacements using the approximation in eq.
-\ref{ApproxForward}.
-We estimate coseismic slip and afterslip with the same spatial and temporal discretization as in section \ref{sec:ElasticInversion}.
-Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and 150 km to the bottom of our numerical model domain at 800 km.
+(\ref{ApproxForward}).
+We estimate coseismic slip and afterslip with the same spatial and temporal discretization as in Section \ref{sec:ElasticInversion}.
+Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, as well as from 150 km to the bottom of our numerical model domain at 800 km.
 We again restrict fault slip to occur between 0 and 15 km depth and we made this choice to help eliminate inevitable non uniqueness.
-It has long been recognized that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional models \citep{Savage1990}.
+It has long been recognized that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional earthquake models \citep{Savage1990}.
 Since we are trying to simultaneously model these two processes, it is necessary to put sensible constraints on the depth of fault slip.
 Additionally, we note that when simultaneously estimating afterslip in the lower crust and a lower crustal viscosity, the inverse problem becomes particularly ill-posed.
-This ill-posedness is illustrated in figure (\ref{fig:LowerCrust}), which shows the displacement resulting from a meter of slip on a fault extending from 15 to 30 km depth as well as the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
-The horizontal displacement from fault slip is in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
+This ill-posedness is illustrated in Figure (\ref{fig:LowerCrust}), which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+The horizontal displacements from fault slip are in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
 This means that surface displacements resulting from afterslip at lower crustal depths can be cancelled out, at least partially, by a low viscosity lower crust.
 We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
-This is not to say that we do not believe deep afterslip to be a possibility, rather we restrict slip to seismogenic depths as a modeling necessity.
-Although, it has been noted that the pattern of vertical postseismic deformation following the El Mayor-Cucpah earthquake indicates that a significant amount of afterslip must be shallow \cite{Rollins2015}.
+This is not to say that we do not believe deep afterslip to be a possibility, rather we restrict slip to seismogenic depths as a modelling necessity.
+Although, it has been noted that the pattern of vertical postseismic deformation following the El Mayor-Cucpah earthquake indicates that a significant amount of afterslip must be shallow \citep{Rollins2015}.
 
@@
 
-Further details of how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2015}.
-We note that a nonlinear Kalman filter based inverse method can be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parameterization of $s$.
+Further details on how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2015}.
+A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
 We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity.
-Moreover, we believe the piecewise continuous respresentation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
+Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
 
-The first step in our inverse method is to determine at which point the early postseismic approximation, eq.
-\ref{ApproxForward} breaks down, which we will denote as $t_{\mathrm{bd}}$.
+The first step in our inverse method is to determine at which point the early postseismic approximation breaks down, which we will denote as $t_{\mathrm{bd}}$.
 As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
-We can almost certainly assume that deformation at the most far-field stations, which are $\sim400$ km away from the El Mayor-Cucapah epicenter, is the result of viscoelastic relaxation.
+We can almost certainly assume that deformation at the most far-field stations, which are $\sim400$ km away from the El Mayor-Cucapah epicentre, is the result of viscoelastic relaxation.
 The approximation should then be valid for as long as a linear trend adequately approximates the far-field deformation.
@@
 Another way to determine $t_{\mathrm{bd}}$ is to find the best fitting prediction of eq.
-\ref{ApproxForward} to observed deformation using increasing durations of the postseismic timeseries.
+(\ref{ApproxForward}) to observed deformation using increasing durations of the postseismic time series.
 $t_\mathrm{bd}$ should be the point when eq.
-\ref{ApproxForward} is no longer capable of describing the observed deformation without incurring systematic misfits.
-This is illustrated in figure \ref{fig:RecordSection1}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
+(\ref{ApproxForward}) is no longer capable of describing the observed deformation without incurring systematic misfits.
+This is illustrated in Figure \ref{fig:RecordSection1}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
 When using eq.
-\ref{ApproxForward} to fit the entire five years of postseismic displacement we see that the near-field displacements, eg.
-station P501, are accurately predicted but when looking at displacement in the far-field, eg.
+(\ref{ApproxForward}) to fit the entire 5 years of postseismic displacement we see that the near-field displacements, e.g.
+station P501, are accurately predicted but when looking at displacement in the far-field, e.g.
 station P621, we see that eq.
-\ref{ApproxForward} overestimates the rate of deformation in the later postseismic and underestimates the rate of deformation in the early period.
+(\ref{ApproxForward}) overestimates the rate of deformation in the later postseismic period and underestimates the rate of deformation in the early period.
 Due to the low signal-to-noise ratios for far-field stations, it is difficult to determine at what point eq.
-\ref{ApproxForward} is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{bd}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
-As noted in \cite{Hines2015}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$; although the uncertainties would be larger.
-We can then consider our subsequent inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the lithospheric strength needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
+(\ref{ApproxForward}) is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{bd}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
+As noted in \citet{Hines2015}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$, although the uncertainties would be larger.
+We can then consider our subsequent inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the viscosity needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
 
@@
 \centering 
-\caption{record section}
+\caption{record Section}
 \label{fig:RecordSection1}
@@
 where $u_\mathrm{obs}$ consists of the first 0.8 years of postseismic deformation and $u_\mathrm{pred}$ are the predicted displacements from eq.
-\ref{ApproxForward}.
-Due to inherent nonuniqueness, we have added zeroth order Tikhonov regularization to estimates of $s$, and second order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^-1$.
-The degree to which we impose the regularization on slip and viscosity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$.
+(\ref{ApproxForward}).
+Due to inherent non uniqueness, we have added zeroth order Tikhonov regularization to estimates of $s$, and second order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^{-1}$.
+The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$.
 The penalty parameters are chosen with two trade-off curves.
-We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then $\lambda_\eta$ is determined while fixing $\lambda_s$ at the chosen value.
-We note that our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in section \ref{sec:FullInversion}.
-Estimates of $s$ made here will not be used in section \ref{sec:FullInversion}, and so the motivation behind even adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
-\ref{ApproxForward} is sensible.
+We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then we determine $\lambda_\eta$ with $\lambda_s$ fixed at the chosen value.
+Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full 5 years, which we do in Section \ref{sec:FullInversion}.
+Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind even adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
+(\ref{ApproxForward}) is sensible.
 
-Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were inferred through bootstrapping.
+Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in Figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were estimated through bootstrapping.
 Although fluidity is rarely used in geophysical literature, eq.
-\ref{InitialRate} is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each discretized layer of the lithosphere and asthenosphere.
+(\ref{InitialRate}) is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each layer.
 We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_\eta$.
-Our choice our $\lambda_\eta$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
-It is therefore difficult to interpret the magnitude of uncertainties on viscosities shown in figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
+Our choice of $\lambda_\eta$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
+It is therefore difficult to interpret the magnitude of uncertainties on viscosities shown in Figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
 A robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
-The viscosity below $\sim60$ km depth needs to be $~1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
+This transitional depth is also consistent with the the viscosity structure required to explain far field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
+We find that the viscosity below 60 km depth needs to be $\sim1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
 The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
-Our inference of a mantle viscosity on the order of $10^{18}$ Pa s and a relatively stronger lower crust is consistent with the inferred steady-state viscosities from \citet{Pollitz2000}, \citet{Pollitz2003}, \citet{Johnson2007}, \citet{Spinler2015}, and \citet{Rollins2015}.
 
@@
 
-Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in figure \ref{fig:InitialSlip}.
-Similar to our elastic slip model from section \ref{sec:ElasticInversion}, coseismic slip is inferred to be in the Sierra Cucapah and it is right lateral with a significant normal component.
-This is consistent with field studies \cite{Fletcher2014}, as well as the coseismic slip from \cite{Wei2011}.
-The potency of inferred coseismic slip is $3.3\times 10^{9} \mathrm{m}^3$, which is also about the same as that inferred from section \ref{sec:ElasticInversion}.
-The present inference of afterslip on the Indiviso fault is significantly less than what was found in the section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
-When fault slip is simultaneously estimated with a lithospheric and asthenospheric viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9 \mathrm{m}^3$, compared to $3.46\times10^{9} \mathrm{m}^3$ when we assume the lithosphere and asthenosphere are elastic.
-The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
+Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in Figure \ref{fig:InitialSlip}.
+Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, coseismic slip is inferred to be in the Sierra Cucapah and it is right lateral with a significant normal component.
+This is consistent with field studies \citep{Fletcher2014}, as well as the coseismic slip from \citet{Wei2011}.
+The potency of inferred coseismic slip is $3.3\times 10^{9}\ \mathrm{m}^3$, which is also about the same as that inferred from Section \ref{sec:ElasticInversion}.
+The present inference of afterslip on the Indiviso fault is significantly less than what was found in the Section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
+When fault slip is simultaneously estimated with a lithospheric and asthenospheric viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.46\times10^{9}\ \mathrm{m}^3$ when we assume the lithosphere and asthenosphere are elastic.
+The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodelled viscoelastic relaxation at depths greater than $60$ km.
 The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
@@
 
-In the previous section, we used the efficient inverse method described by \citet{Hines2015} to constrain the effective lithospheric viscosity required to explain the first 0.8 years of postseismic deformation.
-In this section, we use the effective lithospheric viscosities inferred above as a prior constraint when searching for rheologic models of the lithosphere which are capable of describing the available five years of postseismic data.
-Figure \ref{fig:Rheology} describes how the inferred effective viscosities from section \ref{sec:InitialInversion} constrain the rheologic parameters for various assumed rheologic models.
-We perform a series of inversions where we estimate the coseismic slip and afterslip assuming a variety of lithospheric rheologies which are consistent with our findings from section \ref{sec:InitialInversion}.
-Our forward problem is now eq.
+In the previous section, we used the inverse method from \citet{Hines2015} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
+In this section, we use the effective viscosities inferred above as a prior constraint when searching for models which are capable of describing the available 5 years of postseismic data, where our forward problem is now eq.
 (\ref{GeneralForward}) rather than the approximation given by eq.
 (\ref{ApproxForward}).
-
-%As a reference, we compare the best fit solution for each assumed lithospheric model to a the best fit solution assuming an entirely elastic lithosphere.
-One intuitive criterion for a viscoelastic lithospheric model to be plausible is that it should be able to predict observable deformation better than a lithospheric model which is elastic.
-
-We first assume that the crust and mantle can be described with a Maxwell rheology, and we use $\eta_{\mathrm{eff}}$ from section \ref{sec:InitialInversion} for our assumed value of $\eta_{\mathrm{M}}$.
-We compute $f$ and $g$ from eq.
-(\ref{GeneralForward}) using the finite element software, Pylith \citep{Aagaard2009}, and assume the same spatial and temporal discretization of $s$ as in sections \ref{sec:ElasticInversion} and \ref{sec:InitialInversion}.
-We estimate $s$ using linear least squares and we find the mean chi squared value,
+We perform a series of coseismic slip and afterslip inversion assuming a variety of rheologies for the lower crust and upper mantle which are consistent with our findings from Section \ref{sec:InitialInversion}.
+We appraise each model using the mean chi squared value,
 \begin{equation}\label{eq:Misfit}
@@
 \end{equation}
-is 37.4.
-For comparison, $\bar\chi^2=35.3$ for the elastic model from section \ref{sec:ElasticInversion}.
-The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years.
-As noted, our estimates of $\eta_\mathrm{eff}$ can be thought of as an upper limit, and we have tried using Maxwell viscoelastic Green's functions with lower viscosities; however, that only increases the misfit.
+where $N$ is the number of observations.
+
+We first assume that the crust and mantle can be described with a Maxwell rheology, and we set $\eta_\mathrm{M}$ equal to our inference of $\eta_{\mathrm{eff}}$.
+We compute $f$ and $g$ from eq.
+(\ref{GeneralForward}) using the finite element software, Pylith \citep{Aagaard2009}, and assume the same spatial and temporal discretization of $s$ as in Sections \ref{sec:ElasticInversion} and \ref{sec:InitialInversion}.
+We estimate $s$ using linear least squares and we find $\bar\chi^2=37.4$.
+For comparison, $\bar\chi^2=35.3$ for the elastic model from Section \ref{sec:ElasticInversion}.
+The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years \ref{fig:RecordSection2}.
+Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle.
+However, decreasing the viscosity only increases the misfit.
 Although, the viscosities used here are consistent with the successful Maxwell viscoelastic models found by \citet{Rollins2015} and \citet{Spinler2015}, which had mantle viscosities on the order of $10^{18}$ Pa s, we find that such a model is incapable of describing the entire postseismic time series.
@@
 We assume that the lower crust still has a Maxwell rheology.
-The steady state viscosity, $\eta_{M}$, in the crust and the transient viscosity, $\eta_\mathrm{K}$, in the mantle are set equal to the inferred effective viscosities.
+The steady-state viscosity, $\eta_{M}$, in the crust and the transient viscosity, $\eta_\mathrm{K}$, in the mantle are set equal to the inferred effective viscosities.
 We then estimate the ratio of shear moduli, $\frac{\mu_K}{\mu}$.
 We compute nine different sets of Green's functions, $f$ and $g$, using Pylith, where we assume values of $\frac{\mu_K}{\mu}$ ranging from 0 to 1.
-The former being a degenerate case when the Zener model becomes the Maxwell model.
+The former being a degenerate case where the Zener model reduces to the above Maxwell model.
 We estimate coseismic slip and afterslip for each realization of $\frac{\mu_K}{\mu}$.
-The optimal shear moduli ratio is found to be $0.375$ which has a misfit of $\bar\chi^2=31.2$ (figure \ref{fig:ShearModulusRatio}).
-The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (figure \ref{fig:RecordSection2}).
+The shear moduli ratio that yields to best prediction to the observed postseismic displacements is found to be $0.375$ with a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
+The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSection2}).
 The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the 5 years.
@@
 
-Because we are able to adequately describe the available five years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in section \ref{sec:InitialInversion} and a steady state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
+Because we are able to adequately describe the available 5 years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
+However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-0state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
 
-The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in figure \ref{fig:FinalSlip} and the predicted postiseismic displacements are shown figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
+The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip} and the predicted postseismic displacements are shown Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
 Overall, the trends in the near-field and far-field transient deformation are accurately described by our preferred model.
-In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (figure \ref{fig:RecordSection2}).
+In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (Figure \ref{fig:RecordSection2}).
 There are a few areas where we have notable misfit.
-Most of our misfit is for the near-field stations in the Imperial Valley, and we attribute this misfit to our relatively simple fault geometry, which does not account for fault slip in the Imperial Valley triggered by the El Mayor earthquake \citep{Wei2011a,Wei2015}.
+Most of our misfit is for the near-field stations in the Imperial Valley, and we attribute this misfit to our relatively simple fault geometry, which does not account for potential fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
 In particular, we are unable to model the sustained rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
-Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
+Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodelled postseismic deformation resulting from those earthquakes.
 Lastly, there are clear discrepancies between the observed and predicted vertical deformation following the first year after the El Mayor Cucapah earthquake.
-We observe a general uplift throughout Southern California, which is inconsistent with any postseismic model, which would produce a quadrant pattern of deformation.
+We observe a broad uplift throughout Southern California, which is inconsistent with any postseismic model.
 
@@
 
-The cumulative potency of slip over time is shown in figure (TBD).
-The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of five years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
+The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of 5 years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
 Most of the afterslip in our preferred model occurs within the first year after the earthquake with a significant amount inferred to be shallow and in the Sierra Cucapah.
 The afterslip within the first year is accounting for the most rapid near-field transient deformation.
-After one year, afterslip is inferred to be deeper and under the Sierra Cucapah, which is describing much of the sustained near-field postseismic deformation.
+After 1 year, afterslip is inferred to be deeper and under the Sierra Cucapah, which is describing much of the sustained near-field postseismic deformation.
 We emphasize, that the GPS station closest to our inferred afterslip, P496, is still about 30 km away, which is too far away for us to conclusively argue for sustained brittle deformation rather shallow ductile deformation.
-The deep afterslip inferred after one year could potentially be describing deformation resulting from lower crustal flow.
-Indeed, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from section \ref{sec:InitialInversion}, and we find that such a model adequately describes the observations without any afterslip after one year.
-Our model with a weaker lower crust still requires about the same amount of afterslip over the first year.
+The deep afterslip inferred after 1 year could potentially be describing deformation resulting from lower crustal flow.
+To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}.
+After performing another slip inversion, we find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after 1 year, while still requiring about the same amount of afterslip over the first year.
 We do believe that the early shallow afterslip is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
@@
 Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}, which is the simplest viscoelastic rheologic model.
-In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucuapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities ranging from $10^{17}$ to $10^{18}$ Pa s, with a relatively stronger lower crust.
-Our inference that the the crust and uppermost mantle are relatively strong compared to the underlying mantle is also consistent with that found by \citet{Freed2007a}.
-While these studies found viscosities that are consistent with our effective viscosities from section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
-Studies on the earthquake cycle \citep{Lundgren2009} and lake loading \citep{Luttrell2007} in Southern California, which are both processes that occur on the time scale of $~10^2$ years, infer a Maxwell viscoelastic upper mantle with a viscosity on the order of $10^{19}$ Pa s.
+In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities of $\gtrsim 10^{19}$ Pa s.
+These postseismic studies are corroborated by \citet{Kaufmann2000} who found that a lower crust and upper mantle with viscosities on the order of $10^{20}$ and $10^{18}$ Pa s, respectively, are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal time scales as postseismic deformation.
+While these studies found viscosities that are consistent with our effective viscosities from Section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
+For example, \citet{Lundgren2009} found that lower crust and upper mantle viscosities on the order of $10^{21}$ and $10^{19}$ Pa s, respectively, are needed to describe interseismic deformation along the Southern San Andreas and San Jacinto fault.
+An even higher mantle viscosity on the order of $10^{20}$ Pa s is required to describe deflection resulting from Lake Bonneville, which occurs on the time scales of $10^{4}$ years \citep{Crittenden1967,Bills1987}.
 
-An additional deficiency in the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate of postseismic deformation.
+An additional deficiency with the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate of postseismic deformation.
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
-However, postseismic deformation at distances greater than $\sim200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep{Freed2007a} but we have demonstrated that it cannot be explained with a Maxwell rheology (figure \ref{fig:RecordSection2}).
+However, postseismic deformation at distances greater than $\sim200$ km from the El Mayor-Cucapah epicentre can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSection2}).
 
 We found that a Zener rheology in the upper mantle with a transient viscosity of $\sim10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
-A generalization of the Zener viscoelastic model, consisting of several Kelvin elements connected in series, is commonly used to describe seismic attenuation \citep{Liu1976}.
-The highest viscosity needed to describe attenuation of Earth's lowest frequency normal modes is on the order of $10^{16}$ Pa s \citep{Yuen1982} and the largest characteristic relaxation time would be on the order of days.
+A generalization of the Zener viscoelastic model, schematically represented as several Kelvin elements connected in series, is commonly used to describe seismic attenuation \citep{Liu1976}.
+The highest viscosity needed to describe seismic attenuation is on the order of $10^{16}$ Pa s \citep{Yuen1982} which has a characteristic relaxation time on the order of days.
 Even though our inferred transient viscosity is orders of magnitude larger than that required for seismic attenuation models, the two models are not incompatible.
@@
 
-Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid behaviour required for mantle dynamics on geologic time scales.
-\citet{Yuen1982} proposed a Burgers rheology with a low transient viscosity ($\mu_K\approx10^{16}$ Pa s) and high steady-state viscosity ($\eta_M\approx10^{21}$ Pa s) to describe both seismic attenuation and the fluid-like behaviour required for glacial isostatic rebound and mantle convection.
+Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid-like behaviour required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
+\citet{Yuen1982} proposed a Burgers rheology with a low transient viscosity ($\eta_K\approx10^{16}$ Pa s) and high steady-state viscosity ($\eta_M\approx10^{21}$ Pa s) to describe both seismic attenuation and long term geologic processes.
 The justification of a Burger's rheology mantle is further supported by laboratory experiments on olivine \citep{Chopra1997}.
-\citet{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady state viscosity of $4.6\times10^{18}$ Pa s.
-While the Burgers rheology was introduced as a means of bridging the gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from \citet{Lundgren2009} and \citet{Luttrell2007}.
-Additionally, the transient viscosity inferred by \citet{Pollitz2003} is needed to describe the earliest phase of postseismic deformation following the Hector Mine earthquake, which may be the result of shallow afterslip.
+\citet{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady-state viscosity of $4.6\times10^{18}$ Pa s.
+While the Burgers rheology was introduced as a means of bridging the gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from earthquake cycle and lake loading studies.
+The transient viscosity inferred by \citet{Pollitz2003} is constrained by the earliest phase of postseismic deformation following the Hector Mine earthquake.
 While \citet{Pollitz2003} ruled out deep afterslip as an alternative mechanism based on inconsistent vertical deformation, it is still possible to successfully describe all components of early postseismic deformation following the Hector Mine earthquake with afterslip at seismogenic depths \citep{Jacobs2002}.
@@
 This is in contrast to the present study, where we have inferred a lithospheric viscosity structure simultaneously with afterslip.
-While we also argue that a transient rheology is necessary to explain postseismic deformation, our preferred transient viscosity of $10^{18}$ Pa s is an order of magnitude larger than the transient viscosity found by \cite{Pollitz2003}.
-Since we found that a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over five years, would also be able to describe the postseismic deformation.
+We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of $\sim10^{18}$ Pa s in the mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
+Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over 5 years, would also be able to describe the postseismic deformation.
 Such a Burgers model might then be consistent with the steady state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.

### 2016-04-09 RoughDraft/ElMayor.tex
commit before push

@@
-\documentclass[1p]{elsarticle}
+\documentclass[review]{elsarticle}
 
@@
 \section{Introduction}
-Ground deformation in the years following a large ($gtrsim$Mw7) earthquake provides insight into the mechanical behaviour of the crust and upper mantle.
+Ground deformation in the years following a large ($\gtrsim$Mw7) earthquake provides insight into the mechanical behaviour of the crust and upper mantle.
 It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
@@
 As noted in \citet{Hines2015}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$, although the uncertainties would be larger.
-We can then consider our subsequent inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the viscosity needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
+We can then consider inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the viscosity needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
 
@@
 In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities of $\gtrsim 10^{19}$ Pa s.
-These postseismic studies are corroborated by \citet{Kaufmann2000} who found that a lower crust and upper mantle with viscosities on the order of $10^{20}$ and $10^{18}$ Pa s, respectively, are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal time scales as postseismic deformation.
+These postseismic studies are corroborated by \citet{Kaufmann2000} who found that a lower crust and upper mantle with viscosities on the order of $10^{20}$ and $10^{18}$ Pa s, respectively, are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal scales as postseismic deformation.
 While these studies found viscosities that are consistent with our effective viscosities from Section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
@@
 
+\section{Conclusion}
+Postseismic deformation following the El Mayor-Cucapah earthquake displays far-field ($\gtrsim 200$ km from the epicentre) transient postseismic deformation that is largely undetectable after about 3 years, while near-field deformation exhibits transience that decays to a sustained, elevated rate after about 1 to 2 year.
+We find that the near-field transient deformation can be explained with shallow afterslip and the sustained rate of near field deformation can either be explained with continued afterslip or a lower crustal viscosity of $\sim10^{19}$ Pa s.
+Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than $\sim60$ km.
+Beneath that depth, a transient viscosity of $\sim10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the 5 years considered in this study.
+By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.
+
 \section*{Acknowledgements}

### 2016-04-10 RoughDraft/ElMayor.tex
commit before push

@@
 \begin{abstract}
+Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its preseismic trend after about 3 years at epicentral distances greater than $\sim200$ km.
+In the near-field, we observe rapid transience that decays to a sustained rate which exceeds its preseismic trend.
+We attempt to determine the mechanisms driving this observed deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
+We find that early, rapid, near-field deformation can be explained with afterslip on the portion of the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip or a stead-state viscosity of $\sim10^{19}$ Pa s in the lower crust.
+The trend in far-field deformation is best explained with a transient viscosity of $\sim10^{18}$ Pa s in the upper mantle.
+We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the observable postseismic deformation and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies on geophysical processes occurring over longer time scales.
+
 \end{abstract}
@@
 Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the postseismic deformation with afterslip in an elastic half-space.
-\citet{Gonzalez-ortega2014} described five months of postseismic deformation observed by near-field ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR with afterslip and contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} described five months of postseismic deformation, observed by near-field ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR, with afterslip and contraction on the coseismically ruptured fault.
 \citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodelled viscoelastic relaxation.
 Using continuous GPS stations, which are mostly north of rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of slip inferred on the least constrained, southern-most fault segment.
-Here, we suggest the afterslip inferred by \cite{Rollins2015} may have been acting as a proxy for distributed relaxation in the upper mantle.
+Here, we suggest the afterslip inferred by \citet{Rollins2015} may have been acting as a proxy for distributed relaxation in the upper mantle.
 
@@
 Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
-For example, it is commonly assumed that the lithosphere consists of only three homogeneous, Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep[e.g.][]{Riva2009,Hines2013}.
+For example, it is commonly assumed that the lithosphere consists of only three homogeneous, Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep{Riva2009,Hines2013}.
 To further reduce the model space dimensions being search, it is also necessary to make simplifying assumptions about the nature of afterslip.
@@
 \includegraphics[scale=0.7]{Figures/ContextMap} 
-\caption{Map of the area where postseismic deformation following the El Mayor-Cucapah earthquake can be observed geodetically.
-The large focal mechanism is for the El Mayor Cucapah earthquake and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
+\caption{Map of the region considered in this study.
+The large focal mechanism is for the El Mayor-Cucapah earthquake and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
 The black dots indicate the locations of GPS stations used in this study.
 The fault geometry used in this study is shown in cyan where dashed lines indicate buried edges of the fault segments.
-The green and red boxes denote the extent of the near and far-field displacement maps.
-The blue sector highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis and stations within this sector are used in the record Sections in Figures \ref{fig:RecordSection1} and \ref{fig:RecordSection2}}
+The green and red boxes demarcate the extent of the near-field and far-field maps (figures \ref{fig:NearField} and \ref{fig:FarField}).
+Stations within the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in the record sections in Figures \ref{fig:RecordSectionElastic}, \ref{fig:RecordSection1}, and \ref{fig:RecordSection2}}.
 \label{fig:ContextMap}
@@
 \centering
-\caption{}
+\caption{Left panels show GPS time series from UNAVCO (black) and the predicted displacement (blue) from eq.
+(\ref{TimeSeriesModel}) for a near-field station.
+Red lines indicate the times of the El Mayor-Cucapah and Ocotillo earthquake.
+The right panels show estimated coseismic and postseismic displacements, $u_\mathrm{post}$, which are extracted from the predicted displacements.
+The 68\% confidence interval is shown in light blue.}
 \label{fig:P496}
@@
 \centering
-\caption{} 
+\caption{same as Figure \ref{fig:P496} but for a far-field station.} 
 \label{fig:P619}
@@
 We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as the coseismic displacements.
-In the far-field to the north, we can see south trending displacements for the first 3.0 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicentre.
+In the far-field to the north, we can see south trending displacements for the first 3 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicentre.
 These displacements are most pronounced along the direction of the El Mayor-Cucapah P axis.
@@
 \centering 
-\caption{}
+\caption{Near-field coseismic and postseismic displacements (black) as well as predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
+Observed vertical deformation is shown as an interpolant and predicted vertical displacements are shown within the circles at the base of each vector.
+Note that the interpolant is not well constrained in Mexico where there is no data available.}
 \label{fig:NearField}
@@
 \centering 
-\caption{}
+\caption{Same as Figure \ref{fig:NearField} but for far-field stations.}
 \label{fig:FarField}
@@
 \caption{Assumed and estimated material properties.
-$\lambda$, $\mu$, and $\rho$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in Section \ref{sec:InitialInversion} and $\mu_k/\mu$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology.}
+$\lambda$ and $\mu$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in Section \ref{sec:InitialInversion} and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.}
 
@@
 The penalty parameters, $\lambda_s$, is chosen with a trade-off curve.
+We use Pylith \citep{Aagaard2009} to compute the Green's functions for this inversion and for the remaining inversions in this paper.
 
@@
 The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPa.
-The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to the result of relaxation of coseismicly induced stresses.
-Our slip model accurately describes near field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
+The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
+Our elastic slip model accurately describes near-field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
-Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next Section.
+Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next section.
 
@@
 \includegraphics[scale=0.7]{Figures/ElasticSlip}
-\caption{}
+\caption{Coseismic slip and cumulative afterslip over the indicated intervals for the elastic model from Section \ref{sec:ElasticInversion}.
+Color indicates the magnitude of slip while arrows indicate the motion of the hanging wall.}
 \label{fig:ElasticSlip}
@@
 \includegraphics[scale=0.7]{Figures/RecordSectionElastic}
-\caption{}
+\caption{Scaled record section for the radial component of observed postseismic displacements, $u_\mathrm{obs}$ (black) and displacements predicted by an elastic model, $u_\mathrm{pred}$ (blue).
+Downward motion indicates that the station is moving toward the El Mayor-Cucapah epicentre.
+Displacement time series are scaled so that the minimum and maximum observed values lie on the grid lines.
+The standard deviation of observed displacements are shown in gray.}
 \label{fig:RecordSectionElastic}
@@
 We consider Maxwell viscoelasticity, where the steady-state viscosity, $\eta_M$, is unknown, Zener viscoelasticty, where the transient viscosity, $\eta_K$, and transient shear modulus, $\mu_K$, are unknown, and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all unknown.
-We further discuss these rheologic models and their use in geophysical studies in the discussion.
+We further discuss these rheologic models and their use in geophysical studies in Section \ref{Discussion}.
 
@@
 \centering 
-\caption{}
+\caption{Schematic illustration of rheologic models considered in this paper as well as their initial effection viscosities, $\eta_\mathrm{eff}=\frac{\sigma}{\dot\epsilon}|_{t=0}$.}
 \label{fig:Rheology}
@@
 \includegraphics[scale=0.5]{Figures/Cancellation}
-\caption{afterslip and viscoelastic relaxation in lower crust}
+\caption{Displacements resulting from fault slip at lower crustal depths (left), and initial velocity resulting from subsequent relaxation of a viscoelastic lower crust (right).
+The fault segment dips $75^\circ$ to the north east and its surface projection is outlined in green.
+The highlighted area on the fault extends from 15 to 30 km depth and indicates where 1 meter of right-lateral slip was imposed.
+The elastic properties of the crust and mantle are the same as in Table \ref{tab:MaterialProperties} and $\eta_\mathrm{eff}=10^{18}$ Pa s in the lower crust.
+Vertical dispalcements are interpolated between station locations.}
 \label{fig:LowerCrust}
@@
 \centering 
-\caption{record Section}
+\caption{Illustration of how $t_\mathrm{bd}$ is chosen.
+Observed postseismic displacements are shown in black.
+Blue, green and yellow lines are the best fitting predictions to 5.0, 3.0, and 0.8 years of the postseismic data, respectively, from eq.
+\ref{ApproxForward}.}
 \label{fig:RecordSection1}
@@
 The penalty parameters are chosen with two trade-off curves.
-We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then we determine $\lambda_\eta$ with $\lambda_s$ fixed at the chosen value.
+We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then we determine $\lambda_\eta$ with $\lambda_s$ fixed at its chosen value.
 Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full 5 years, which we do in Section \ref{sec:FullInversion}.
@@
 \centering 
-\caption{effective viscosity}
+\caption{Effective viscosity and associated fludities inferred by fitting eq.
+(\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.
+95\% confidence intervals, estimated from bootstrapping, are also shown.}
 \label{fig:EffectiveViscosity}
@@
 \includegraphics[scale=0.7]{Figures/InitialSlip}
-\caption{}
+\caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
 \label{fig:InitialSlip}
@@
 \centering 
-\caption{misfit with different shear modulus ratios}
+\caption{Misfit as a function of the transient shear modulus in a Zener rheology upper mantle.}
 \label{fig:ShearModulusRatio}
@@
 \centering 
-\caption{}
+\caption{Observed postseismic displacements (black) and predicted postseismic displacements for the best fitting slip models when using a Maxwell (blue) and Zener (green) rheology in the upper mantle.
+The effective viscosities are the same for both models and are shown in Figure \ref{fig:EffectiveViscosity}.}
 \label{fig:RecordSection2}
@@
 \centering 
-\caption{}
+\caption{Inferred coseismic slip and afterslip when assuming a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.
+$\eta_K$ in the mantle and $\eta_M$ in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}.
+We use $\frac{\mu_K}{\mu}=0.375$ in the upper mantle.}
 \label{fig:FinalSlip}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+\section{Discussion}\label{Discussion}
 

### 2016-04-20 JGRSubmission/ElMayor.tex
commit before push

--- 2016-04-10 RoughDraft/ElMayor.tex
@@
-\documentclass[review]{elsarticle}
-
+\documentclass[draft,linenumbers]{AGUJournal}
+\draftfalse
 \usepackage{amssymb,amsmath,amsthm,amsfonts}
-%\usepackage[margin=1.0in]{geometry}
-%\usepackage{fancyhdr} % required for custom header
-%\usepackage{graphicx}
-%\usepackage{listings}
-%\usepackage{courier}
-%\usepackage[usenames,dvipsnames]{color}
-\usepackage[maxfloats=40]{morefloats}
-%\usepackage{caption}
-%\usepackage{subcaption}
-%\usepackage{natbib}
-%\usepackage{setspace}
-%\doublespacing
+\journalname{JGR-Solid Earth}
 
@@
 
+\begin{Document}
 %% Title
 %%------------------------------------------------------------------------------
+
 \title{	
@@
 
-\begin{document}
 \begin{abstract}
-Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its preseismic trend after about 3 years at epicentral distances greater than $\sim200$ km.
-In the near-field, we observe rapid transience that decays to a sustained rate which exceeds its preseismic trend.
+Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about 3 years at epicentral distances greater than $\sim200$ km.
+In the near-field, we observe rapid transience that decays to a sustained rate which exceeds its pre-earthquake trend.
 We attempt to determine the mechanisms driving this observed deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
-We find that early, rapid, near-field deformation can be explained with afterslip on the portion of the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip or a stead-state viscosity of $\sim10^{19}$ Pa s in the lower crust.
+We find that early, rapid, near-field deformation can be explained with afterslip on the portion of the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of $\sim10^{19}$ Pa s.
 The trend in far-field deformation is best explained with a transient viscosity of $\sim10^{18}$ Pa s in the upper mantle.
-We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the observable postseismic deformation and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies on geophysical processes occurring over longer time scales.
-
+We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay of the postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
 \end{abstract}
@@
 Modelling both of these mechanisms creates a high dimensional model space that must be searched with non-linear optimization methods.
-We first develop an initial postseismic model using the method described in \citet{Hines2015}.
+We first develop an initial postseismic model using the method described in \citet{Hines2016}.
 This method simultaneously estimate the afterslip and effective lithospheric viscosity structure necessary to describe the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
@@
 
-In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2015} to constrain an initial effective lithospheric viscosity structure from the early postseismic deformation.
+In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2016} to constrain an initial effective lithospheric viscosity structure from the early postseismic deformation.
 The method relies upon the fact that immediately after an earthquake, stresses throughout the crust and mantle are only controlled by the relatively well known instantaneous elastic properties and each parcel will have a strain rate, $\dot\epsilon$, that is proportional to stress, $\sigma$, and inversely proportional to the parcel's effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$.
@@
 
-Further details on how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2015}.
+Further details on how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2016}.
 A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
-We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity.
+We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2016} because of its relative simplicity.
 Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
@@
 (\ref{ApproxForward}) is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{bd}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
-As noted in \citet{Hines2015}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$, although the uncertainties would be larger.
+As noted in \citet{Hines2016}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$, although the uncertainties would be larger.
 We can then consider inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the viscosity needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
@@
 
-In the previous section, we used the inverse method from \citet{Hines2015} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
+In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
 In this section, we use the effective viscosities inferred above as a prior constraint when searching for models which are capable of describing the available 5 years of postseismic data, where our forward problem is now eq.
@@
 
+It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001,Hearn2003,Feigl2006}.
+The similarity of the horizontal postseismic deformation results in a non-uniqueness in inferences of afterslip or viscoelastic relaxation.
+In contrast, the spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}.
+It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981, Hetland2014}.
+The similarity between deformation resulting from deep afterslip and viscoelastic relaxation of coseismic stresses is different from the ill-posedness described in Section \ref{sec:InitialInversion}.
+In our method, any inferred afterslip will also mechanically drive additional viscoelastic relaxation.
+The horizontal deformation resulting from deep afterslip will generally be in the opposite direction as horizontal deformation resulting from viscoelastic relaxation of subsequent stresses in the lower crust (Figure \ref{fig:LowerCrust}).
+As a result, there is a trade-off between inferences of deep afterslip and lower crustal viscosity.
+In our synthetic tests in \citet{Hines2016}, we have found that inverting surface deformation for afterslip and viscosity within the same depth interval tends to result in overestimated afterslip and an underestimated viscosity at that depth.
+
 Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}, which is the simplest viscoelastic rheologic model.
@@
 \section{Conclusion}
-Postseismic deformation following the El Mayor-Cucapah earthquake displays far-field ($\gtrsim 200$ km from the epicentre) transient postseismic deformation that is largely undetectable after about 3 years, while near-field deformation exhibits transience that decays to a sustained, elevated rate after about 1 to 2 year.
-We find that the near-field transient deformation can be explained with shallow afterslip and the sustained rate of near field deformation can either be explained with continued afterslip or a lower crustal viscosity of $\sim10^{19}$ Pa s.
+
+We have extracted a filtered and smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacements time series.
+We have treated postseismic deformation as a stochastic process where we did not presume any characteristic shape of the postseismic time series.
+We can observe transient postseismic deformation at distances of $\sim400$ km from the El Mayor-Cucapah epicenter which is largely undetectable after about 3 years.
+Near-field deformation exhibits transience that decays to a sustained, elevated rate after about 1 to 2 year.
+We found that the near-field transient deformation can be explained with shallow afterslip and the sustained rate of near field deformation can either be explained with continued afterslip or relaxation in a lower crustal with a viscosity of $\sim10^{19}$ Pa s.
 Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than $\sim60$ km.

### 2016-04-20 JGRSubmission/agujournalsample.tex
commit before push

%% 2/18/2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalSample.tex: this sample file is for articles formatted with LaTeX
%
% This sample file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \renewcommand, or \def.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
% DO NOT USE \psfrag or \subfigure commands.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to latex@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format:
%
% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
% 
% 2) numberline will give you line numbers.

% Tip:
%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

%% To submit your paper:
\documentclass[linenumbers,draft]{AGUJournal}

% Now, type in the journal name: \journalname{<Journal Name>}
% ie,
\journalname{JGR-Atmospheres}

%% Choose from this list of Journals:
%
% JGR-Atmospheres
% JGR-Biogeosciences
% JGR-Earth Surface
% JGR-Oceans
% JGR-Planets
% JGR-Solid Earth
% JGR-Space Physics
% Global Biochemical Cycles
% Geophysical Research Letters
% Paleoceanography
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resource Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science

%% ------------------------------------------------------------------------ %%
%
%  ENTER Title Page commands:
%
%% ------------------------------------------------------------------------ %%

% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general terms then specific results are optimized in
% searches)

% Example: \title{This is a test title}

% (List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.  
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

%% Keypoints, final entry on title page.
% Example: 
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special
% characters or punctuation 
% \end{keypoints}

%% \begin{abstract} begins second page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Track Changes:
% To add words, \added{<word added>}
% To delete words, \deleted{<word deleted>}
% To replace words, \replace{<word to be replaced>}{<replacement word>}
% To explain why change was made: \explain{<explanation>}

% At the end of the document, use \listofchanges, which will list the
% changes and the page and line number where the change was made.

% When final version, \listofchanges will not produce anything,
% \added{} word will be printed, \deleted{} will take away the word,
% \replaced{}{} will print only the 2nd argument.
% \explain will not print anything.

% Optional argument:
% You can also add additional information to be printed with the list
% of changes, to indicate the initials of the person changing the text,
% and the time and/or date of the change, or any other comment by using
% the optional [] argument:
% \added[AH, 3:30pm, Feb 18, 2016]{added term}
% will yield 
% [AH, 3:30pm, Feb 18, 2016] added term on page...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

\title{Trends in the predictive performance of raw ensemble weather forecasts}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

 \authors{A. B. Smith\affil{1}\thanks{Current address, McMurdo Station,
 Antartica},
 Eric Brown\affil{1,2}, Rick Williams\affil{3},
 John B. McDougall\affil{4}, and S. Visconti\affil{5}\thanks{Also
 funded by Monsanto.}}

\affiliation{1}{Department of Hydrology and Water Resources,
University of Arizona, Tucson, Arizona, USA.}
\affiliation{2}{Department of Geography, Ohio State University,
Columbus, Ohio, USA.}
\affiliation{3}{Department of Space Sciences, University of
Michigan, Ann Arbor, Michigan, USA.}
\affiliation{4}{Division of Hydrologic Sciences, Desert Research
Institute, Reno, Nevada, USA.}
\affiliation{5}{Dipartimento di Idraulica, Trasporti ed
Infrastrutture Civili, Politecnico di Torino, Turin, Italy.}

%% Corresponding Author
%(include name and email addresses of the corresponding author.  More
%than one corresponding author is allowed in this Word file and for
%publication; but only one corresponding author is allowed in our
%editorial system.)

\correspondingauthor{A. B. Smith}{email@address.edu}

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation

\begin{keypoints}
\item Evolution of raw ensemble forecast \replaced{skill}{skills}
\item Future benefits from statistical post-processing
\item Global distribution of forecast skill development
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

\begin{abstract}
This study applies statistical post-processing to ensemble
forecasts of near-surface temperature, 24-hour 
%% below are examples of track changes:
\deleted[date/time, etc.]{precipitation},
\added{all} totals,
and near-surface wind speed from the global model of the European
Centre for Medium-Range Weather Forecasts (ECMWF). The main objective
is to evaluate the evolution of the difference in skill between the
raw ensemble and the post-processed forecasts. Reliability and
sharpness, and 
%% another example of track changes.
\replaced{hence}{therefore} skill,
 of the former is expected to improve over
time. Thus, the gain by post-processing is expected to decrease. Based
on ECMWF forecasts from January 2002 to March 2014 and corresponding
observations from globally distributed stations we generate
post-processed forecasts by ensemble model output statistics
%% another example of track changes.
\added{abbreviated as} (EMOS)
for each station and variable. Given the higher average skill of the
post-processed forecasts, we analyse the evolution of the difference
in skill between raw ensemble and EMOS. This skill gap remains almost
constant over time indicating that post-processing will keep adding
skill in the foreseeable future.
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

%%% Suggested section heads:
% \section{Introduction}
% 
% The main text should start with an introduction. Except for short
% manuscripts (such as comments and replies), the text should be divided
% into sections, each with its own heading.

% Headings should be sentence fragments and do not begin with a
% lowercase letter or number. Examples of good headings are:

% \section{Materials and Methods}
% Here is text on Materials and Methods.

% \subsection{A descriptive heading about methods}
% More about Methods.
% 
% \section{Data} (Or section title might be a descriptive heading about data)
% 
% \section{Results} (Or section title might be a descriptive heading about the
% results)
% 
% \section{Conclusions}

\section{Introduction}
\label{sec:intro}
Over the last two decades the paradigm in weather forecasting has
shifted from being deterministic to probabilistic \citep[see
e.g.][]{Palm00,Hami00}. Accordingly, numerical weather prediction
(NWP) models have been run increasingly as ensemble forecasting
systems. The goal of such ensemble forecasts is to approximate the
forecast probability distribution by a finite sample of scenarios
\citet{Leit74}\footnote{See \citet{Leit74} for a more in-depth
description of these issues and their complex implications.}
Global ensemble forecast systems, like the European
Centre for Medium-Range Weather Forecasts (ECMWF) ensemble, are prone
to probabilistic biases, and are therefore not reliable. They
particularly tend to be underdispersive for surface weather parameters
\citet{Boug10, Park08}. In order to correct for forecast
underdispersion and bias in NWP ensembles different
statistical
post-processing methods have been developed, of which ensemble model
output statistics (EMOS) \citep{Gneit05} is among the most widely
applied. EMOS yields a parametric forecast distribution by linking its
parameters to ensemble statistics. Due to its simplicity and low
computational cost, we focus on EMOS for this study.

The ECMWF ensemble is under continuous development, and hence its
forecast skill improves over time \citep{Buiz98,Buiz07,Rich13,Haid14}.
Parts of these improvements may be due to a reduction of probabilistic
biases. From this we deduce the following hypothesis: As the raw
forecasts continuously improve, it is hypothesized that the gap in
skill between raw ensemble and post-processed forecasts narrows,
because systematic errors typically captured by post-processing are
reduced 
by those improvements. 
%%
%% Use \explain{} before change, so that it ends up on the right line.
\explain[Jon, 2/16/16]{Redundant sentence, better without it} 
\deleted{In other words, probabilistic biases,
which can be reduced by statistical post-processing methods, decrease
over time.}
Assuming that the raw ensemble forecasts continue to
improve in the future, the gap in skill may eventually be closed when
the raw ensemble forecasts become reliable and unbiased.  In this work
we analyse the evolution of the global performance of the operational
ECMWF raw ensemble and the corresponding post-processed EMOS forecasts
for 2 metre temperature (T2M), 24-hour precipitation (PPT24), and 10-m
wind speed (V10). We verify the forecasts against globally distributed
surface synoptic observations (SYNOP) data over a period of about 10
years. We firstly evaluate the monthly average skill in terms of CRPS
for both the raw and the EMOS forecasts. In order to assess the extent
to which the results depend on the choice of the post-processing
method, Bayesian model averaging (BMA), \citet{Raft05,Fra10} is
additionally applied to the T2M raw ensemble forecasts. We will use
the negatively oriented (i.e. the lower the value the higher the
skill) continuous ranked probability score (CRPS) \citep{Math76} as a
measure of skill. As the CRPS assesses both reliability and sharpness
and is a proper score \citep{Gneit07b}, we rely on it for model fitting
and verification throughout this study. Note that skill and
reliability are linked in that given constant sharpness an improvement
in reliability leads to an improvement in skill and vice versa. We
finally analyse the evolution of the gap in CRPS between raw ensemble
and post-processed forecasts.

After presenting the dataset in section~\ref{sec:intro} we summarize
the methods for post-processing and for the assessment of the global
skill evolution in section~\ref{sec:meth}. In section~\ref{sec:res}
the results are shown.  This is followed by a discussion in
section~\ref{sec:disc} along with some concluding
remarks. These
analyses have been performed using the statistical software \texttt{R}
\citep{R2013}.

%% Enter Figures and Tables near as possible to where they are first mentioned:
%
% DO NOT USE \psfrag or \subfigure commands.
%
% Figure captions go below the figure.
% Table titles go above tables;  other caption information
%  should be placed in last line of the table, using
% \multicolumn2l{$^a$ This is a table note.}
%
%----------------
% EXAMPLE FIGURE
%
% \begin{figure}
% \end{figure}

\begin{figure}[h]
% \centering
% when using pdflatex, use pdf file:
% \includegraphics[width=20pc]{figsamp.pdf}
%
% when using dvips, use .eps file:
% \includegraphics[width=20pc]{figsamp.eps}
%
% If you don't specify the file extension, 
% \includegraphics will insert the right file:
\centerline{\includegraphics[height=1.5in]{figsamp}}
\caption{Short caption}
\label{figone}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=45,height=2in]{figsamp}}
\caption{The figure caption should begin with an overall descriptive
statement of the figure followed by additional text. They should be
immediately after each figure.  Figure parts are indicated with
lower-case letters ({\bf a, b, c}\ldots).  For initial submission, please place
both the figures and captions in the text near where they are cited.}
\label{fig:mean_and_slope}
\end{figure}

\begin{table}
\caption{Start this caption with a short description of your
table.
Large tables
especially presenting rich data should be presented as separate excel
or .cvs files, not as part of the main text.}
== Table Here ==
\end{table}

%
% ---------------
% EXAMPLE TABLE
%
\begin{table}
\caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
\centering
\begin{tabular}{l c}
\hline
 Run  & Time (min)  \\
\hline
  $l1$  & 260   \\
  $l2$  & 300   \\
  $l3$  & 340   \\
  $h1$  & 270   \\
  $h2$  & 250   \\
  $h3$  & 380   \\
  $r1$  & 370   \\
  $r2$  & 390   \\
\hline
\multicolumn{2}{l}{$^{a}$Table note text here.}
\end{tabular}
\end{table}

% See below for how to make sideways figures or tables.

% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
 \begin{sidewaysfigure}
 \includegraphics[width=20pc]{figsamp}
 \caption{Caption here}
 \label{newfig}
 \end{sidewaysfigure}
%
 \begin{sidewaystable}
 \caption{Caption here}
\label{tab:signif_gap_clos}
 \begin{tabular}{ccc}
one&two&three\\
four&five&six
 \end{tabular}
 \end{sidewaystable}

\clearpage

\section{Methods}
\label{sec:meth}

\subsection{Post-processing Using EMOS}
Post-processing using EMOS converts a raw ensemble of discrete
forecasts into a probability distribution. Let $y$ be the variable to
be forecast (here: T2M, PPT24 or V10) and let ${f}=(f_{1}, f_{2},
\dots, f_{K})^{T}$ be the vector of the $K$ member raw ensemble
forecasts (here: HRES, ENS, and CTRL). Then the EMOS
\added{predictive}
density can be written as:
\begin{linenomath*}
\begin{equation}
y|{f} \sim g(m, \sigma),
\end{equation}
\end{linenomath*}
where $g(\cdot)$ is a parametric density function with location and
scale parameters $m$ and $\sigma$, respectively, which depend on the
raw ensemble.

\subsubsection{Temperature}
For T2M forecasts $g(\cdot)$ is a normal density distribution with
mean $m$ and variance $\sigma^{2}$. Here, we use a variant of the
original EMOS approach similar to the one proposed by
\citet{ScheueBue13} where the departures of observed temperatures from
their climatological means are related to those of the forecasts.
Specifically, let $T=\{t_{1},\ldots,t_{n}\}$ be a training period of
$n$ days preceding the forecast initialization and denote by $f_{tk}$
the forecast of the k-th ensemble member and by $y_{t}$ the
observation on day $t\in T$. As a first step, we fit a regression
model
%%% \begin{linenomath*} ...\end{linenomath*} puts a line number in equation:
\begin{linenomath*}
\begin{equation}
y_{t_{j}} = c_{0} + c_{1}\sin\left(\frac{2\pi j}{365}\right) +
c_{2}\cos\left(\frac{2\pi j}{365}\right) + \varepsilon_{t_{j}}, \quad
j=1,\ldots,n
\end{equation}
\end{linenomath*}
which captures the seasonal variation of T2M. The residual terms
$\varepsilon_{t_{j}}$ are likely correlated over time, but for
simplicity an ordinary least squares fit is performed. We denote by
$\tilde{y}_{t}$ the fitted value of this periodic regression model on
day $t$ and interpret it as the climatological mean temperature on
this day. This model can easily be extrapolated to future days
$t_{d+1}, t_{d+2}, \ldots$ The above regression includes both a sine
and a cosine term which is equivalent to a cosine model with variable
phase and amplitude. Since $j=1,\ldots,n$ is just a numbering of the
days in $T$, different training periods have different phase
parameters and hence $c_{1}$ and $c_{2}$ evolve over the calendar
year. We fit the same type of model also to the ensemble mean,
control, and high resolution run and obtain climatological means
$\tilde{f}_{\overline{\mathrm{ENS}},t}, \tilde{f}_{\mathrm{CTRL},t}$,
and $\tilde{f}_{\mathrm{HRES},t}$. The mean of the forecast
distribution is then:
\begin{linenomath*}
\begin{equation}
m = \tilde{y} + a_{1}(f_{\mathrm{HRES}} - \tilde{f}_{\mathrm{HRES}}) +
a_{2}(f_{\mathrm{CTRL}} - \tilde{f}_{\mathrm{CTRL}}) +
a_{3}(f_{\overline{\mathrm{ENS}}} -
\tilde{f}_{\overline{\mathrm{ENS}}}).
\end{equation}
\end{linenomath*}
The variance of the forecast distribution is linked to the raw
ensemble by: 
\begin{linenomath*}
\begin{equation}
\sigma^{2} = b_{0} + b_{1}s^{2},
\end{equation}
\end{linenomath*}
where $s^{2} = \frac{1}{K}\sum_{k=1}^{K}(f_{k} -
\frac{1}{K}\sum_{k=1}^{K}f_{k})^{2}$. The parameters
${\theta}_{T2M}=(a_{1}, a_{2}, a_{3}, b_{0}, b_{1})^{T}$ are
constrained to be non-negative, and hence $a_{k}/\sum_{k=1}^{K} a_{k}$
can be understood as the weight of model $k$.

\subsubsection{Precipitation}
For PPT24 we use the EMOS approach proposed by \citet{Scheu14}, where
$g(\cdot)$ is a left-censored (at zero) generalized extreme value
(GEV) distribution. While the shape parameter $\xi$ of the GEV is kept
constant ($\xi=0.2$), the location and the scale parameters $m$ and
$\sigma$ are linked to the raw ensemble via:
\begin{linenomath*}
\begin{eqnarray}
m &=& a_{0} + a_{1} f_{\mathrm{HRES}} + a_{2} f_{\mathrm{CTRL}} +
a_{3} f_{\overline{\mathrm{ENS}}} + a_{4} \pi_{0},\nonumber\\
\sigma &=& b_{0} + b_{1} \mathrm{MD}_{f},
\end{eqnarray}
\end{linenomath*}
where $\pi_{0}$ is the fraction of ensemble members predicting zero
precipitation and $\mathrm{MD}_{f}:= K^{-2}$\break
$\sum_{k, k' = 1}^{K} |
f_{k} - f_{k'} |$ is the ensemble mean difference. Again, the
parameters are denoted by $\theta_{PPT24}=(a_{0}, \dots, a_{4}, b_{0},
b_{1})^{T}$. The parameters $a_{1}, a_{2}, a_{3}, b_{0}, b_{1}$ are
constrained to be non-negative, and hence the normalized parameters
$a_{1}$ to $a_{3}$ can be understood as weights.

\subsection{Global CRPS Analysis}
 \label{sec:meth_glob_crps}

As stated in the introduction, the main objective of this study is to
analyse whether the gap in CRPS between the raw ensemble and the
post-processed forecast narrows over time. This is assessed
station-wise using both a parametric and a non-parametric approach.
For the former, we fit the following regression model to the monthly
time series of CRPS differences ($\Delta \mathrm{CRPS}_{t} =
\mathrm{CRPS}_{\mathrm{raw},t} - \mathrm{CRPS}_{\mathrm{EMOS}, t}$):
\begin{linenomath*}
\begin{equation}
\Delta \mathrm{CRPS}_{t} = \beta_{0} + \beta_{1} t + \beta_{2} \sin\left(\frac{2\pi t}{12}\right) + \beta_{3} \cos\left(\frac{2\pi t}{12} \right) + \epsilon, \phantom{bla} \epsilon \sim \mathcal{N}(0, \sigma^{2}) \label{eq:linseas}
\end{equation}
\end{linenomath*}
where $\Delta \mathrm{CRPS}_{t}$ is the predictand, $t$ is now the
time in months, and $\sigma^{2}$ denotes the error variance. For the
latter, we use Kendall's $\tau$ correlation coefficient and the
associated test statistics \citep{Mann45} as implemented in the
\texttt{R} package \texttt{Kendall} \citep{Kendall}. In order to
correct for seasonal effects, we calculate the $\tau$ statistics using
the residuals of the following model:
\begin{linenomath*}
\begin{equation}
\Delta \mathrm{CRPS}_{t} = \gamma_{0} + \gamma_{1} \sin\left(\frac{2\pi t}{12}\right) + \gamma_{2} \cos\left(\frac{2\pi t}{12} \right) + \epsilon, \phantom{bla} \epsilon \sim \mathcal{N}(0, \sigma^{2})
\label{eq:tauseas}
\end{equation}
\end{linenomath*}
Note that negative $\tau$ values indicate a negative trend and
positive values a positive one. Figure~\ref{figone} a) and b)
show the regression lines estimated by model (\ref{eq:linseas}) for
monthly averages of $\Delta \mathrm{CRPS}$ and the corresponding
Kendall's $\tau$ test statistics for an example with decreasing and
increasing gap.

\section{Results}
\label{sec:res}

\subsection{Are There Any Significant Temporal Trends?}

The above results indicate a tendency of a decrease in $\Delta$CRPS
over time at least for T2M and PPT24. In the following we check the
percentages of stations with decreasing, an absence of, or increasing
trend in $\Delta$CRPS over time at a significance level of 0.05. In
order to be more confident about the results this analysis is
performed using both the parametric regression model and the
non-parametric Kendall's $\tau$ correlation coefficient test. As
already mentioned both approaches correct for seasonal effects.
Furthermore, in case of T2M the same analysis has been performed
additionally using BMA instead of EMOS in order to relax the
dependence on one particular post-processing method. As shown in
Table~\ref{tab:signif_gap_clos} the stations with no significant trend
outnumber the stations with either negative or positive trend for all
three variables and lead times considered. Note that the percentage of
stations without any significant trend increases with increasing lead
time. In line with the results shown in
Figure~\ref{fig:mean_and_slope}, significantly negative trends are
more common than positive ones for T2M and PPT24. The difference
between the number of stations with negative and those with positive
trend reduces with increasing lead time, but is still greater than
zero for a 10 day forecast. Note that the high number of
non-significant stations in case of PPT24 is likely to be due to the
high variability of precipitation amounts, and hence variability of
CRPS values, which leads to a large residual standard error in case of
the parametric regression model and to a lot of pairs (a pair denotes
here a value of $\Delta$CRPS and its associated time stamp) opposite
to the estimated direction in case of the $\tau$ test statistics. In
case of V10 the stations with a negative trend and those with a
positive trend are almost equally frequent regardless of the lead
time. Figures of the global distributions of stations with no,
significantly negative, and significantly positive trend in
$\Delta$CRPS are available as supplemental material to this paper.

\section{Discussion and Conclusions}
\label{sec:disc}

According to the above analyses the gap in CRPS between the raw
ensemble and the EMOS forecasts remains almost constant over time. For
T2M and PPT24 $\Delta$CRPS shows a slightly decreasing tendency. The
higher the lead time the less accentuated is this tendency. For V10
such a tendency cannot be detected. The parametric regression model
and the non-parametric $\tau$ test yield similar results. Hence, a
linear model that is overlaid by seasonal fluctuations seems to be
reasonable. Note that the skill of the raw ensemble and the EMOS
forecasts may sometimes be negatively affected by upgrades to the
atmospheric model. Model upgrades may deteriorate raw ensemble skill
at some individual stations. For instance, a resolution increase may
introduce new issues with statistical downscaling of the forecasts to
some specific observation sites. But more importantly, the skill of
the post-pro\-cessed forecasts can be lowered dramatically if a model
update happens between the training and the verification period. These
issues may result in positive trends in $\Delta$CRPS. Ideally,
post-processing would be based on a cascade of reforecasts. That is,
for each atmospheric model version, training of the post-processing
model would be done using a corresponding time series of reforecasts
made with that same model version. Furthermore, the observations may
be affected by measurement errors. If these errors change over time,
they may also influence the estimates of the trends in $\Delta$CRPS.
As the problems introduced by statistical downscaling may be mitigated
by verifying against model analysis, a similar study that replaces
observations by model analysis, as proposed by \citet{Ghel00} and
\citet{Papp09}, may give further insights.

From the above we conclude that the probabilistic skill of both the
raw ensembles and the EMOS forecasts improves over time. The fact that
the gap in skill has remained almost \textbf{constant}, especially for
V10, suggests that improvements to the atmospheric model have an
effect quite different from what calibration by statistical
post-processing is doing. That is, they are increasing potential
skill. Thus this study indicates that (a) further model development is
important even if one is just interested in point forecasts, and (b)
statistical post-processing is important because it will keep adding
skill in the foreseeable future.

%% ------------------------------------------------------------------------ %%
\section*{Citations}

% Please use ONLY \citet and \citep for reference citations.
% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).

\subsection*{Cites made with \tt\string\citet\string{\string}}
...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
\citet{Ghel00}, and \citet{Leit74}.

\subsection*{Cites made with \tt\string\citep\string{\string}}
...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
\citep{Ghel00, Leit74}.

...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.

%%% End of body of article

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% A: Here Is Appendix Title
%
\appendix
\section{Here is a sample appendix}
This is an Appendix section.

\subsection{subsection}
This is an Appendix subsection.

\subsubsection{subsubsection}
This is an Appendix subsubsection.
\begin{linenomath*}
\begin{equation}asdf\end{equation}
\end{linenomath*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary, Notation or Acronym section goes here:
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
\begin{glossary}
\term{Term}
 Term Definition here
\term{Term}
 Term Definition here
\term{Term}
 Term Definition here
\end{glossary}

%
%%%%%%%%%%%%%%
% Acronyms
 \begin{acronyms}
 \acro{Acronym}
 Definition here
 \acro{EMOS}
 Ensemble model output statistics 
 \acro{ECMWF}
 Centre for Medium-Range Weather Forecasts
 \end{acronyms}

%
%%%%%%%%%%%%%%
% Notation 
 \begin{notation}
 \notation{$a+b$} Notation Definition here
 \notation{$e=mc^2$} 
 Equation in German-born physicist Albert Einstein's theory of special
relativity that showed that the increased relativistic mass ($m$) of a
body comes from the energy of motion of the body—that is, its kinetic
energy ($E$)—divided by the speed of light squared ($c^2$).
 \end{notation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS

\acknowledgments
The forecast data used in this study can be made available subject to
a handling charge. SYNOP observations are not available through ECMWF.
We are grateful to F. Rabier, D. S. Richardson, D. Lavers, and other
colleagues at ECMWF for helpful discussions and inputs. We thank David
M\"{o}ller of the University of Heidelberg for his contribution.
Furthermore, we like to thank T. Gneiting of the Heidelberg Institute
for Theoretical Studies and of the Institute for Stochastics at
Karlsruhe Institute of Technology for valuable comments, and the
colleagues at the Heidelberg Institute for Theoretical Studies.
Additionally, we are grateful to two anonymous reviewers for their
helpful comments. We are indebted to the ECMWF for granting access to
their products.

The Editor thanks Pierre Pinson and an anonymous reviewer for their assistance in evaluating this paper.

%%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
%
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% Or, to use BibTeX:
%
% Follow these steps
%
% 1. Type in \bibliography{<name of your .bib file>} 
%    Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Run LaTeX on your new file which will produce the citations.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

\begin{thebibliography}{}

\bibitem[{\textit{Bell and Munoz}}(2008)]{Boug10} Bell, A.~H., and
Munoz, D.~P.  (2008). Activity in the superior colliculus reflects
dynamic interactions between voluntary and involuntary influences on
orienting behaviour. \textit{Eur. J. Neurosci.} 28, 1654--1660.

\bibitem[{\textit{Corbetta et~al.}}(1991)]{Buiz07} Corbetta, M.,
Miezin, F.~M., Dobmeyer, S., Shulman, G.~L., and Petersen, S.~E.
(1991). Selective and divided attention during visual discriminations
of shape, color, and speed: functional anatomy by positron emission
tomography. \textit{J.~Neurosci.} 11, 2383--2402.

\bibitem[{\textit{Borra et~al.}}(2014)]{Buiz98} Borra, E., Gerbella,
M., Rozzi, S., Tonelli, S., and Luppino, G.  (2014). Projections to
the superior colliculus from inferior parietal, ventral premotor, and
ventrolateral prefrontal areas involved in controlling goal-directed
hand actions in the macaque. \textit{Cereb. Cortex} 24, 1054--1065.

\bibitem[{\textit{Dorris et~al.}}(1997)]{Fra10}
 Dorris, M.~C.,
Par\'{e}, M., and Munoz, D.~P.  (1997). Neuronal activity in monkey
superior colliculus related to the initiation of saccadic eye
movements. \textit{J.~Neurosci.} 17, 8566--8579.

\bibitem[{\textit{Elsabbagh et~al.}}(2009)]{Ghel00} 
Elsabbagh, M.,
Volein, A., Holmboe, K., Tucker, L., Csibra, G., Baron-Cohen, S.,
et~al.  (2009). Visual orienting in the early broader autism
phenotype: disengagement. \textit{J.~Child Psychol. Psychiatry} 50,
637--642.

\bibitem[{\textit{Fortin et~al.}}(1999)]{Gneit05} Fortin, S., Chabli,
A., Dumont, I., Shumikhina, S., Itaya, S.~K., and Molotchnikoff, S.
(1999). Maturation of visual receptive field properties in the rat
superior colliculus. \textit{bibain Res. Dev. Brain Res.} 1112,
55--64.

\bibitem[{\textit{Felsen and Mainen}}(2008)]{Gneit07b} Felsen, G., and
Mainen, Z.~F.  (2008). Neural substrates of sensory-guided locomotor
decisions in the rat superior colliculus. \textit{Neuron} 60,
137--148.

\bibitem[{\textit{Gattass and Desimone}}(1996)]{Haid14} Gattass, R.,
and Desimone, R.  (1996). Responses of cells in the superior
colliculus during performance of a spatial attention task in the
macaque. \textit{Rev. Bras. Biol.} 56, 257--279.

\bibitem[{\textit{Goldberg and Wurtz}}(1972)]{Hami00} Goldberg, M.~E.,
and Wurtz, R.~H.  (1972). Activity of superior colliculus in behaving
monkey. II. Effect of attention on neuronal responses.
\textit{J.~Neurophysiol.} 35, \hbox{560--574}.

\bibitem[{\textit{Krauzlis}}(2003)]{Kendall} Krauzlis, R.~J.  (2003).
Neuronal activity in the rostral superior colliculus related to the
initiation of pursuit and saccadic eye movements.
\textit{J.~Neurosci.} 23, 4333--4344.

\bibitem[{\textit{Heesy}}(2009)]{Leit74} 
Heesy, C.~P.  (2009). Seeing
in stereo: the ecology and evolution of primate binocular vision and
stereopsis. \textit{Evol. Anthropol.} 18, 21--35.

\bibitem[{\textit{Hilbig et~al.}}(2000)]{Mann45} Hilbig, H., Bidmon,
H.~J., Ettrich, P., and M\"{u}ller, A.  (2000). Projection neurons in
the superficial layers of the superior colliculus in the rat: a
topographic and quantitative morphometric analysis.
\textit{Neuroscience} 96, 109--119.

\bibitem[{\textit{Ignashchenkova et~al.}}(2004)]{Math76}
Ignashchenkova, A., Dicke, P.~W., Haarmeier, T., and Their, P.
(2004). Neuron-specific contribution of the superior colliculus to
overt and covert shifts of attention. \textit{Nat. Neurosci.} 7,
56--64.

\bibitem[{\textit{Krauzlis et~al.}}(2013)]{Palm00} Krauzlis, R.~J.,
Lovejoy, L.~P., and Z\'{e}non, A.  (2013). Superior colliculus and
visual spatial attention. \textit{Annu. Rev. Neurosci.} 36, 165--182.

\bibitem[{\textit{Kustov and Robinson}}(1996)]{Papp09} Kustov, A.~A.,
and Robinson, D.~L.  (1996). Shared neural control of attentional
shifts and eye movements. \textit{Nature} 384, 74--77.

\bibitem[{\textit{Landry and Bryson}}(2004)]{Park08} Landry, R., and
Bryson, S.~E.  (2004). Impaired disengagement of attention in young
children with autism. \textit{J.~Child Psychol. Psychiatry} 45,
1115--1122.

\bibitem[{\textit{Kobayashi et~al.}}(2003)]{R2013} Kobayashi, T.,
Tran, A.~H., Nishijo, H., Ono, T., and Matsumoto, G.  (2003).
Contribution of hippocampal place cell activity to learning and
formation of goal-directed navigation in rats. \textit{Neuroscience}
117, 1025--1035.

\bibitem[{\textit{McHaffie et~al.}}(2005)]{Raft05} McHaffie, J.~G.,
Stanford, T.~R., Stein, B.~E., Coizet, V., and Redgrave, P.  (2005).
Subcortical loops through the basal ganglia. \textit{Trends Neurosci.}
28, 401--407.

\bibitem[{\textit{McPeek and Keller}}(2004)]{Rich13} McPeek, R.~M.,
and Keller, E.~L.  (2004). Deficits in saccade target selection after
inactivation of superior colliculus. \textit{Nat. Neurosci.} 7,
757--763.

\bibitem[{\textit{M\"{u}ller et~al.}}(2005)]{Scheu14} M\"{u}ller,
J.~R., Philiastides, M.~G., and Newsome, W.~T.  (2005).
Microstimulation of the superior colliculus focuses attention without
moving the eyes. \textit{Proc. Natl. Acad. Sci. U.S.A.} 102, 524--529.

\bibitem[{\textit{Munoz and Istvan}}(1998)]{ScheueBue13} Munoz, D.~P.,
and Istvan, P.~J.  (1998). Lateral inhibitory interactions in
the intermediate layers of the monkey superior colliculus.
\textit{J.~Neurophysiol.} 79, 1193--1209.

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Track Changes:
% To add words, \added{<word added>}
% To delete words, \deleted{<word deleted>}
% To replace words, \replace{<word to be replaced>}{<replacement word>}

% At the end of the document, use \listofchanges, which will list the
% changes and the page and line number where the change was made.

% When final version, \listofchanges will not produce anything,
% \added{} word will be printed, \deleted{} will take away the word,
% \replaced{}{} will print only the 2nd argument.

%%%
\listofchanges
%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supporting Information
%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
%% for Supporting Information.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

### 2016-04-20 JGRSubmission/agujournaltemplate.tex
commit before push

--- 2016-04-20 JGRSubmission/ElMayor.tex
@@
+%% 11/23/2015
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
+%
+% This file includes commands and instructions
+% given in the order necessary to produce a final output that will
+% satisfy AGU requirements. 
+%
+% You may copy this file and give it your
+% article name, and enter your text.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PLEASE DO NOT USE YOUR OWN MACROS
+% DO NOT USE \newcommand, \renewcommand, or \def, etc.
+%
+% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
+% DO NOT USE \psfrag or \subfigure commands.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% All questions should be e-mailed to latex@agu.org.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Step 1: Set the \documentclass
+%
+% There are two options for article format:
+%
+% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
+% The draft option produces double spaced output.
+% 
+% 2) numberline will give you line numbers.
+
+%% To submit your paper:
 \documentclass[draft,linenumbers]{AGUJournal}
@@
 \usepackage{amssymb,amsmath,amsthm,amsfonts}
+%% For final version.
+% \documentclass{AGUJournal}
+
 \journalname{JGR-Solid Earth}
 
-%set up the header
-%\pagestyle{fancy}
-%\lhead{Trever Hines}
-%\chead{El Mayor Postseismic}
-%\rhead{\today}
+\begin{document}
 
-%\setlength{\headheight}{15pt}
-%\renewcommand\headrulewidth{1.0pt} % Size of the header rule
+\title{Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
 
-\begin{Document}
-%% Title
-%%------------------------------------------------------------------------------
+\authors{T. T. Hines\affil{1}, E. A. Hetland\affil{1}}
 
-\title{	
-Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
-\author{T. T. Hines\fnref{fn}}
-\author{E. A. Hetland\fnref{fn}}
-\fntext[fn]{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, MI, USA}
+\affiliation{1}{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, Michigan, USA.}
+
+\correspondingauthor{T. T. Hines}{hinest@umich.edu}
+
+%% Keypoints, final entry on title page.
+
+% Example: 
+% \begin{keypoints}
+% \item	List up to three key points (at least one is required)
+% \item	Key Points summarize the main points and conclusions of the article
+% \item	Each must be 100 characters or less with no special characters or punctuation 
+% \end{keypoints}
+
+%  List up to three key points (at least one is required)
+%  Key Points summarize the main points and conclusions of the article
+%  Each must be 100 characters or less with no special characters or punctuation
+
+\begin{keypoints}
+\item = enter point 1 here = 
+\item = enter point 2 here = 
+\item = enter point 3 here = 
+\end{keypoints}
 
 \begin{abstract}
-Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about 3 years at epicentral distances greater than $\sim200$ km.
-In the near-field, we observe rapid transience that decays to a sustained rate which exceeds its pre-earthquake trend.
-We attempt to determine the mechanisms driving this observed deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
-We find that early, rapid, near-field deformation can be explained with afterslip on the portion of the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of $\sim10^{19}$ Pa s.
-The trend in far-field deformation is best explained with a transient viscosity of $\sim10^{18}$ Pa s in the upper mantle.
-We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay of the postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
+Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after ${\sim}3$ years at epicentral distances greater than ${\sim}200$ km.
+At closer distances, the rapid transience decays to a sustained rate which exceeds its pre-earthquake trend.
+We attempt to determine the mechanisms driving this deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
+We find that early, rapid, near-field deformation can be explained with afterslip on the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of ${\sim}10^{19}$ Pa s.
+The trend in far-field deformation is best explained with a transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle.
+We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay in postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
 \end{abstract}
-\maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
-Thanks to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California produced observable postseismic deformation at more GPS stations than any other earthquake in California to date.
+Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date.
 With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake, where we consider both afterslip and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
@@
 Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the postseismic deformation with afterslip in an elastic half-space.
-\citet{Gonzalez-ortega2014} described five months of postseismic deformation, observed by near-field ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR, with afterslip and contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} described five months of postseismic deformation, observed by InSAR and GPS within ${\sim}50$ km rupture, with afterslip and contraction on the coseismically ruptured fault.
 \citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodelled viscoelastic relaxation.
-Using continuous GPS stations, which are mostly north of rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of slip inferred on the least constrained, southern-most fault segment.
+Using only continuous GPS stations, which are mostly north of the rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of slip inferred on the least constrained, southern-most fault segment.
 Here, we suggest the afterslip inferred by \citet{Rollins2015} may have been acting as a proxy for distributed relaxation in the upper mantle.
@@
 The inference of these rheologic parameters is a computationally expensive non-linear inverse problem which is typically approached with a forward modelling grid search method.
-Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
+Consequently, a simplified structure for the lithosphere must be assumed in order to minimize the number of rheologic parameters that need to be estimated.
 For example, it is commonly assumed that the lithosphere consists of only three homogeneous, Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep{Riva2009,Hines2013}.
-To further reduce the model space dimensions being search, it is also necessary to make simplifying assumptions about the nature of afterslip.
+To further reduce the dimensions of the model space, it is also necessary to make simplifying assumptions about the nature of afterslip.
 For example, one can assume a frictional model for afterslip and parametrize afterslip in terms of the unknown rheologic properties of the fault \citep[e.g.][]{Johnson2009,Johnson2004}.
@@
 However, postseismic afterslip in similar tectonic settings has been observed to persist for decades following earthquakes \citep{Cakir2012,Cetin2014}.
-Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to a biased inference of lithospheric viscosity.
-Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near-field deformation, which could be indicative of unmodelled continued afterslip.
+Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates deformation in the Imperial Valley, which could be indicative of unmodelled continued afterslip.
+Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to biased inferences of lithospheric viscosities.
 
@@
 We first develop an initial postseismic model using the method described in \citet{Hines2016}.
-This method simultaneously estimate the afterslip and effective lithospheric viscosity structure necessary to describe the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We then use the inferred effective viscosity structure to create a suite of postseismic models which are tested against the available 5 years of postseismic data.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip beneath the Sierra Cucapah, a Zener rheology upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
+This method simultaneously estimates the afterslip and effective lithospheric viscosity structure necessary to describe early postseismic deformation.
+Our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
+We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the 5 years of postseismic data available to date.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on a fault segment running through the Sierra Cucapah, a Zener rheology in the upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
 
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/ContextMap} 
+\includegraphics[scale=0.8]{Figures/ContextMap} 
 \caption{Map of the region considered in this study.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data Processing}\label{sec:Data}
@@
 The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.3 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
-We treat the displacements resulting from the Brawley swarm as a single event because the time series are provided by UNAVCO as daily solutions.
-Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation and we model displacements resulting from these events with a Heaviside function, $H(t)$.
+We treat the displacements resulting from the Brawley swarm as a single event because the daily solutions provided by UNAVCO cannot resolve the separate events.
+Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation, and we model displacements resulting from these events with only a Heaviside function, $H(t)$, describing the coseismic offsets.
 We then model $u_\mathrm{obs}(t)$ as
 \begin{equation}
-  u_\mathrm{obs}(t) = u_\mathrm{pred}(t) + \epsilon
+  u_\mathrm{obs}(t) = u_\mathrm{pred}(t) + \epsilon,
 \end{equation}
@@
 Stations which recorded displacements that clearly cannot be described by the aforementioned processes are not included in our analysis.
-This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Bawden2001,Argus2005} .
+This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Bawden2001,Argus2005}.
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it is possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
-However, we use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
-We use displacements because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertainties depending on exactly how the estimation is done.
-This modelling choice prevents us from using the newly installed stations in Baja California for our analysis.
+Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015}.
+Although it would be possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities, we do not do so here.
+We use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
+We use displacements because estimating velocities from an already noisy displacement time series can introduce significant uncertainties depending on exactly how the estimation is done.
+This choice prevents us from using the newly installed stations in Baja California for our analysis.
 
-The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred about 270 km north of the El Mayor-Cucapah epicentre, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
+The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred ${\sim}270$ km north of the El Mayor-Cucapah epicentre, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
 We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicentre are approximately constant \citep{Savage2009}.
@@
 The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ over fitting the data.
-While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we instead take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/FilterP496}
+\includegraphics[scale=0.8]{Figures/FilterP496}
 \centering
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/FilterP619}
+\includegraphics[scale=0.8]{Figures/FilterP619}
 \centering
@@
 (\ref{TimeSeriesModel}) as stochastic variables \citep{Murray2005}.
-By using constant seasonal amplitudes our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodelled annual and semi-annual oscillations (e.g.
+By using constant seasonal amplitudes, our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodelled annual and semi-annual oscillations (e.g.
 Figure \ref{fig:P619}).
 
-We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as the coseismic displacements.
-In the far-field to the north, we can see south trending displacements for the first 3 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicentre.
-These displacements are most pronounced along the direction of the El Mayor-Cucapah P axis.
-A similar eastward trend can be seen in the few far-field stations along the T axis in Arizona.
+We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the time intervals 0-1 years, 1-3 years, and 3-5 years, as well as the coseismic displacements.
+Stations at epicentral distances ranging from ${\sim}200$ km to as far as ${\sim}400$ km have an elevated rate of deformation for the first 3 years following the earthquake.
+This far-field deformation has a southward trend along the direction of the El Mayor-Cucapah P axis and a similar eastward trend can be seen in the few far-field stations in Arizona, located along the T axis.
 After 3 years, the trend in far-field postseismic deformation is barely perceptible.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/MapViewNearField}
+\includegraphics[scale=0.8]{Figures/MapViewNearField}
 \centering 
-\caption{Near-field coseismic and postseismic displacements (black) as well as predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
-Observed vertical deformation is shown as an interpolant and predicted vertical displacements are shown within the circles at the base of each vector.
+\caption{Near-field coseismic and cumulative postseismic displacements over the indicated time periods (black) as well as predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
+Observed vertical deformation is shown as an interpolated field and predicted vertical displacements are shown within the circles at the base of each vector.
 Note that the interpolant is not well constrained in Mexico where there is no data available.}
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/MapViewFarField}
+\includegraphics[scale=0.8]{Figures/MapViewFarField}
 \centering 
@@
 The near-field postseismic deformation is notably sustained when compared to the far-field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicentre, P496, has been moving at a steady rate of $\sim1.5$ cm/yr to the south since $\sim1$ year after the El Mayor-Cucapah earthquake.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicentre, P496, has been moving at a steady rate of ${\sim}1.5$ cm/yr to the south since ${\sim}1$ year after the El Mayor-Cucapah earthquake.
 Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from tectonic processes.
 However, the vertical postseismic signal is only apparent for the first year after the earthquake (Figure \ref{fig:NearField}).
-As with the far-field deformation, there is a general trend of uplift in the near-field after $\sim1$ year, which we do not consider to be related to postseismic processes.
+As with the far-field deformation, there is a general trend of uplift in the near-field after ${\sim}1$ year, which we do not consider to be related to postseismic processes.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Postseismic Modeling}\label{sec:Model}
@@
 depth (km) &$\lambda$ (GPa)&$\mu$ (GPa)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
-0-5 & 24.0 & 24.3 & - & -\\
-5-15 & 35.2 & 35.4 & - & -\\
-15-30 & 41.8 & 41.9 & 44.3 & 0.0\\
-30-60 & 61.0 & 60.8 & 5.91 & 0.375\\
-60-90 & 61.0 & 60.8 & 1.99 & 0.375\\
-90-120 & 61.0 & 60.8 & 1.31 & 0.375\\
-120-150 & 61.0 & 60.8 & 1.10 & 0.375\\
-150-$\infty$ & 61.0 & 60.8 & 1.07 & 0.375\\
+0-5 & 24.0 & 24.0 & - & -\\
+5-15 & 35.0 & 35.0 & - & -\\
+15-30 & 42.0 & 42.0 & 44.3 & 0.0\\
+30-60 & 61.0 & 61.0 & 5.91 & 0.375\\
+60-90 & 61.0 & 61.0 & 1.99 & 0.375\\
+90-120 & 61.0 & 61.0 & 1.31 & 0.375\\
+120-150 & 61.0 & 61.0 & 1.10 & 0.375\\
+150-$\infty$ & 61.0 & 61.0 & 1.07 & 0.375\\
 \end{tabular}
 \caption{Assumed and estimated material properties.
-$\lambda$ and $\mu$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in Section \ref{sec:InitialInversion} and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.}
+$\lambda$ and $\mu$ are assumed known \textit{a priori} and are based on the values used for the coseismic model by \citet{Wei2011}.
+The values for $\eta_\mathrm{eff}$ are estimated in Section \ref{sec:InitialInversion} and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.}
 
@@
 We consider afterslip and viscoelastic relaxation in the lithosphere and asthenosphere as candidate mechanisms.
-Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
+Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} found that poroelastic rebound is unlikely to be a significant contributor to postseismic deformation following the El Mayor-Cucapah earthquake.
 Furthermore, we consider stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
@@
 The simplest rheologic model is to consider them to be effectively elastic and isotropic.
-In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the values listed in Table \ref{tab:MaterialProperties} throughout this paper.
+In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011}, which are listed in Table \ref{tab:MaterialProperties}, throughout this paper.
 The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.
-Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane and they did not require any viscoelastic relaxation to describe the observations.
-We also perform an elastic slip inversion but we use GPS stations within a larger radius about the El Mayor-Cucapah epicentre (400 km instead of $\sim$200 km).
+Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that 3 years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
+We also perform an elastic slip inversion, but we use GPS stations within a larger radius about the El Mayor-Cucapah epicentre (400 km instead of ${\sim}200$ km).
 Our forward problem describing predicted postseismic deformation, $u_\mathrm{pred}$, in terms of time dependent fault slip, $s$, is
@@
 The penalty parameters, $\lambda_s$, is chosen with a trade-off curve.
-We use Pylith \citep{Aagaard2009} to compute the Green's functions for this inversion and for the remaining inversions in this paper.
+We use Pylith \citep{Aagaard2009} to compute the Green's functions for this inversion, as well as for the remaining inversions in this paper.
 
@@
 The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
-Our elastic slip model accurately describes near-field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
+Our elastic slip model accurately describes near-field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than ${\sim}150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/ElasticSlip}
+\includegraphics[scale=0.8]{Figures/ElasticSlip}
 \caption{Coseismic slip and cumulative afterslip over the indicated intervals for the elastic model from Section \ref{sec:ElasticInversion}.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/RecordSectionElastic}
+\includegraphics[scale=0.8]{Figures/RecordSectionElastic}
 \caption{Scaled record section for the radial component of observed postseismic displacements, $u_\mathrm{obs}$ (black) and displacements predicted by an elastic model, $u_\mathrm{pred}$ (blue).
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/rheology}
+\includegraphics[scale=0.8]{Figures/rheology}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.5]{Figures/Cancellation}
+\includegraphics[scale=0.8]{Figures/Cancellation}
 \caption{Displacements resulting from fault slip at lower crustal depths (left), and initial velocity resulting from subsequent relaxation of a viscoelastic lower crust (right).
@@
 As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
-We can almost certainly assume that deformation at the most far-field stations, which are $\sim400$ km away from the El Mayor-Cucapah epicentre, is the result of viscoelastic relaxation.
+We can almost certainly assume that deformation at the most far-field stations, which are ${\sim}400$ km away from the El Mayor-Cucapah epicentre, is the result of viscoelastic relaxation.
 The approximation should then be valid for as long as a linear trend adequately approximates the far-field deformation.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/RecordSectionDuration}
+\includegraphics[scale=0.8]{Figures/RecordSectionDuration}
 \centering 
@@
 This transitional depth is also consistent with the the viscosity structure required to explain far field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
-We find that the viscosity below 60 km depth needs to be $\sim1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
+We find that the viscosity below 60 km depth needs to be ${\sim}1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
 The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/EffectiveViscosity}
+\includegraphics[scale=0.8]{Figures/EffectiveViscosity}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/InitialSlip}
+\includegraphics[scale=0.8]{Figures/InitialSlip}
 \caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[scale=0.8]{Figures/FinalSlip}
@@
 
-It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001,Hearn2003,Feigl2006}.
+It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001, Hearn2003, Feigl2006}.
 The similarity of the horizontal postseismic deformation results in a non-uniqueness in inferences of afterslip or viscoelastic relaxation.
 In contrast, the spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}.
-It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981, Hetland2014}.
+It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981,Hetland2014}.
 The similarity between deformation resulting from deep afterslip and viscoelastic relaxation of coseismic stresses is different from the ill-posedness described in Section \ref{sec:InitialInversion}.
@@
 As a result, there is a trade-off between inferences of deep afterslip and lower crustal viscosity.
-In our synthetic tests in \citet{Hines2016}, we have found that inverting surface deformation for afterslip and viscosity within the same depth interval tends to result in overestimated afterslip and an underestimated viscosity at that depth.
+In our synthetic tests in \citet{HinesHetland2015}, we have found that inverting surface deformation for afterslip and viscosity within the same depth interval tends to result in overestimated afterslip and an underestimated viscosity at that depth.
 
@@
 In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities of $\gtrsim 10^{19}$ Pa s.
-These postseismic studies are corroborated by \citet{Kaufmann2000} who found that a lower crust and upper mantle with viscosities on the order of $10^{20}$ and $10^{18}$ Pa s, respectively, are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal scales as postseismic deformation.
+These postseismic studies are consistent with \citet{Kaufmann2000,Cavalie2007} who found that an upper mantle viscosity of $10^{18}$ Pa s and a crustal viscosity $\gtrsim10^{20}$ Pa s are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal scales as postseismic deformation.
 While these studies found viscosities that are consistent with our effective viscosities from Section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
@@
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
-However, postseismic deformation at distances greater than $\sim200$ km from the El Mayor-Cucapah epicentre can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSection2}).
+However, postseismic deformation at distances greater than ${\sim}200$ km from the El Mayor-Cucapah epicentre can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSection2}).
 
-We found that a Zener rheology in the upper mantle with a transient viscosity of $\sim10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
+We found that a Zener rheology in the upper mantle with a transient viscosity of ${\sim}10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
 A generalization of the Zener viscoelastic model, schematically represented as several Kelvin elements connected in series, is commonly used to describe seismic attenuation \citep{Liu1976}.
@@
 This is in contrast to the present study, where we have inferred a lithospheric viscosity structure simultaneously with afterslip.
-We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of $\sim10^{18}$ Pa s in the mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
+We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of ${\sim}10^{18}$ Pa s in the mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
 Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over 5 years, would also be able to describe the postseismic deformation.
@@
 We have treated postseismic deformation as a stochastic process where we did not presume any characteristic shape of the postseismic time series.
-We can observe transient postseismic deformation at distances of $\sim400$ km from the El Mayor-Cucapah epicenter which is largely undetectable after about 3 years.
+We can observe transient postseismic deformation at distances of ${\sim}400$ km from the El Mayor-Cucapah epicenter which is largely undetectable after about 3 years.
 Near-field deformation exhibits transience that decays to a sustained, elevated rate after about 1 to 2 year.
-We found that the near-field transient deformation can be explained with shallow afterslip and the sustained rate of near field deformation can either be explained with continued afterslip or relaxation in a lower crustal with a viscosity of $\sim10^{19}$ Pa s.
-Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than $\sim60$ km.
-Beneath that depth, a transient viscosity of $\sim10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the 5 years considered in this study.
+We found that the near-field transient deformation can be explained with shallow afterslip and the sustained rate of near field deformation can either be explained with continued afterslip or relaxation in a lower crustal with a viscosity of ${\sim}10^{19}$ Pa s.
+Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km.
+Beneath that depth, a transient viscosity of ${\sim}10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the 5 years considered in this study.
 By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.
@@
 
-\bibliographystyle{apalike}
-\bibliography{mybib}
+%----------------
+% EXAMPLE FIGURE
+%
+% \begin{figure}[h]
+% \centering
+% when using pdflatex, use pdf file:
+% \includegraphics[width=20pc]{figsamp.pdf}
+%
+% when using dvips, use .eps file:
+% \includegraphics[width=20pc]{figsamp.eps}
+%
+% \caption{Short caption}
+% \label{figone}
+%  \end{figure}
+%
+% ---------------
+% EXAMPLE TABLE
+%
+% \begin{table}
+% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
+% \centering
+% \begin{tabular}{l c}
+% \hline
+%  Run  & Time (min)  \\
+% \hline
+%   $l1$  & 260   \\
+%   $l2$  & 300   \\
+%   $l3$  & 340   \\
+%   $h1$  & 270   \\
+%   $h2$  & 250   \\
+%   $h3$  & 380   \\
+%   $r1$  & 370   \\
+%   $r2$  & 390   \\
+% \hline
+% \multicolumn{2}{l}{$^{a}$Footnote text here.}
+% \end{tabular}
+% \end{table}
+
+%% SIDEWAYS FIGURE and TABLE 
+% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
+%
+% \begin{sidewaysfigure}
+% \includegraphics[width=20pc]{figsamp}
+% \caption{caption here}
+% \label{newfig}
+% \end{sidewaysfigure}
+% 
+%  \begin{sidewaystable}
+%  \caption{Caption here}
+% \label{tab:signif_gap_clos}
+%  \begin{tabular}{ccc}
+% one&two&three\\
+% four&five&six
+%  \end{tabular}
+%  \end{sidewaystable}
+
+%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
+%\begin{linenomath*}
+%\begin{equation}
+%y|{f} {\sim} g(m, \sigma),
+%\end{equation}
+%\end{linenomath*}
+
+%%% End of body of article
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional Appendix goes here
+%
+% The \appendix command resets counters and redefines section heads
+%
+% After typing \appendix
+%
+%\section{Here Is Appendix Title}
+% will show
+% A: Here Is Appendix Title
+%
+%\appendix
+%\section{Here is a sample appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Optional Glossary, Notation or Acronym section goes here:
+%
+%%%%%%%%%%%%%%  
+% Glossary is only allowed in Reviews of Geophysics
+%  \begin{glossary}
+%  \term{Term}
+%   Term Definition here
+%  \term{Term}
+%   Term Definition here
+%  \term{Term}
+%   Term Definition here
+%  \end{glossary}
+
+%
+%%%%%%%%%%%%%%
+% Acronyms
+%   \begin{acronyms}
+%   \acro{Acronym}
+%   Definition here
+%   \acro{EMOS}
+%   Ensemble model output statistics 
+%   \acro{ECMWF}
+%   Centre for Medium-Range Weather Forecasts
+%   \end{acronyms}
+
+%
+%%%%%%%%%%%%%%
+% Notation 
+%   \begin{notation}
+%   \notation{$a+b$} Notation Definition here
+%   \notation{$e=mc^2$} 
+%   Equation in German-born physicist Albert Einstein's theory of special
+%  relativity that showed that the increased relativistic mass ($m$) of a
+%  body comes from the energy of motion of the body—that is, its kinetic
+%  energy ($E$)—divided by the speed of light squared ($c^2$).
+%   \end{notation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  ACKNOWLEDGMENTS
+%
+% The acknowledgments must list:
+%
+% •	All funding sources related to this work from all authors
+%
+% •	Any real or perceived financial conflicts of interests for any
+%	author
+%
+% •	Other affiliations for any author that may be perceived as
+% 	having a conflict of interest with respect to the results of this
+% 	paper.
+%
+% •	A statement that indicates to the reader where the data
+% 	supporting the conclusions can be obtained (for example, in the
+% 	references, tables, supporting information, and other databases).
+%
+% It is also the appropriate place to thank colleagues and other contributors. 
+% AGU does not normally allow dedications.
+
+\acknowledgments
+ = enter acknowledgments here =
+
+%% ------------------------------------------------------------------------ %%
+%% Citations
+
+% Please use ONLY \citet and \citep for reference citations.
+% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).
+
+%% Example \citet and \citep:
+%  ...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
+%  \citet{Ghel00}, and \citet{Leit74}.
+
+%  ...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
+%  \citep{Ghel00, Leit74}.
+
+%  ...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.
+
+%%  REFERENCE LIST AND TEXT CITATIONS
+%
+% Either type in your references using
+%
+% \begin{thebibliography}{}
+% \bibitem[{\textit{Kobayashi et~al.}}(2003)]{R2013} Kobayashi, T.,
+% Tran, A.~H., Nishijo, H., Ono, T., and Matsumoto, G.  (2003).
+% Contribution of hippocampal place cell activity to learning and
+% formation of goal-directed navigation in rats. \textit{Neuroscience}
+% 117, 1025--1035.
+%
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Or, to use BibTeX:
+%
+% Follow these steps
+%
+% 1. Type in \bibliography{<name of your .bib file>} 
+%    Run LaTeX on your LaTeX file.
+%
+% 2. Run BiBTeX on your LaTeX file.
+%
+% 3. Open the new .bbl file containing the reference list and
+%   copy all the contents into your LaTeX file here.
+%
+% 4. Run LaTeX on your new file which will produce the citations.
+%
+% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.
+
+%% After you run BibTeX, Copy in the contents of the .bbl file here:
+%\bibliography{mybib.bib}
+\begin{thebibliography}{52}
+\providecommand{\natexlab}[1]{#1}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+
+\bibitem[{\textit{Aagaard et~al.}(2009)\textit{Aagaard, Williams, Knepley,
+  Kientz, and Strand}}]{Aagaard2009}
+Aagaard, B., C.~Williams, M.~Knepley, S.~Kientz, and L.~Strand (2009),
+  {PyLith}.
+
+\bibitem[{\textit{Argus et~al.}(2005)\textit{Argus, Heflin, Peltzer,
+  Cramp{\'{e}}, and Webb}}]{Argus2005}
+Argus, D.~F., M.~B. Heflin, G.~Peltzer, F.~Cramp{\'{e}}, and F.~H. Webb (2005),
+  {Interseismic strain accumulation and anthropogenic motion in metropolitan
+  Los Angeles}, \textit{Journal of Geophysical Research B: Solid Earth},
+  \textit{110}(4), 1--26, \doi{10.1029/2003JB002934}.
+
+\bibitem[{\textit{Bawden et~al.}(2001)\textit{Bawden, Thatcher, Stein, Hudnut,
+  and Peltzer}}]{Bawden2001}
+Bawden, G.~W., W.~Thatcher, R.~S. Stein, K.~W. Hudnut, and G.~Peltzer (2001),
+  {Tectonic contraction across Los Angeles after removal of groundwater pumping
+  effects.}, \textit{Nature}, \textit{412}(August), 812--815,
+  \doi{10.1038/35090558}.
+
+\bibitem[{\textit{Bills and May}(1987)}]{Bills1987}
+Bills, B.~G., and G.~M. May (1987), {Lake Bonneville: Constraints on
+  Lithospheric Thickness and Upper Mantle Viscosity From Isostatic Warping of
+  Bonneville, Provo, and Gilbert Stage Shorelines}, \textit{Journal of
+  Geophysical Research-Solid Earth and Planets}, \textit{92}(B11),
+  11,493--11,508, \doi{10.1029/JB092iB11p11493}.
+
+\bibitem[{\textit{{\c{C}}akir et~al.}(2012)\textit{{\c{C}}akir, Ergintav,
+  {\"{O}}zener, Dogan, Akoglu, Meghraoui, and Reilinger}}]{Cakir2012}
+{\c{C}}akir, Z., S.~Ergintav, H.~{\"{O}}zener, U.~Dogan, A.~M. Akoglu,
+  M.~Meghraoui, and R.~Reilinger (2012), {Onset of aseismic creep on major
+  strike-slip faults}, \textit{Geology}, \textit{40}(12), 1115--1118,
+  \doi{10.1130/G33522.1}.
+
+\bibitem[{\textit{Cetin et~al.}(2014)\textit{Cetin, Cakir, Meghraoui, Ergintav,
+  and Akoglu}}]{Cetin2014}
+Cetin, E., Z.~Cakir, M.~Meghraoui, S.~Ergintav, and A.~M. Akoglu (2014),
+  {Extent and distribution of aseismic slip on the Ismetpasa segment of the
+  North Anatolian Fault (Turkey) from Persistent Scatterer InSAR},
+  \textit{Geochemistry, Geophysics, Geosystems}, \textit{15},
+  \doi{10.1002/2014GC005307.Received}.
+
+\bibitem[{\textit{Chopra}(1997)}]{Chopra1997}
+Chopra, P.~N. (1997), {High-temperature transient creep in olivine rocks},
+  \textit{Tectonophysics}, \textit{279}, 93--111,
+  \doi{10.1016/S0040-1951(97)00134-0}.
+
+\bibitem[{\textit{Crittenden}(1967)}]{Crittenden1967}
+Crittenden, M. (1967), {Viscosity and Finite Strength of the Mantle as
+  Determined from Water and Ice Loads*}, \textit{Geophysical Journal of the
+  Royal Astronomical {\ldots}}, pp. 261--279,
+  \doi{10.1111/j.1365-246X.1967.tb06243.x}.
+
+\bibitem[{\textit{Davis et~al.}(2012)\textit{Davis, Wernicke, and
+  Tamisiea}}]{Davis2012}
+Davis, J.~L., B.~P. Wernicke, and M.~E. Tamisiea (2012), {On seasonal signals
+  in geodetic time series}, \textit{Journal of Geophysical Research: Solid
+  Earth}, \textit{117}(1), 1--10, \doi{10.1029/2011JB008690}.
+
+\bibitem[{\textit{Feigl and Thatcher}(2006)}]{Feigl2006}
+Feigl, K.~L., and W.~Thatcher (2006), {Geodetic observations of post-seismic
+  transients in the context of the earthquake deformation cycle},
+  \textit{Comptes Rendus - Geoscience}, \textit{338}, 1012--1028,
+  \doi{10.1016/j.crte.2006.06.006}.
+
+\bibitem[{\textit{Fletcher et~al.}(2014)\textit{Fletcher, Teran, Rockwell,
+  Oskin, Hudnut, Mueller, Spelz, Akciz, Masana, Faneros, Fielding, Leprince,
+  Morelan, Stock, Lynch, Elliott, Gold, Liu-Zeng, Gonz{\'{a}}lez-Ortega,
+  Hinojosa-Corona, and Gonz{\'{a}}lez-Garc{\'{i}}a}}]{Fletcher2014}
+Fletcher, J.~M., O.~J. Teran, T.~K. Rockwell, M.~E. Oskin, K.~W. Hudnut, K.~J.
+  Mueller, R.~M. Spelz, S.~O. Akciz, E.~Masana, G.~Faneros, E.~J. Fielding,
+  S.~Leprince, A.~E. Morelan, J.~Stock, D.~K. Lynch, A.~J. Elliott, P.~Gold,
+  J.~Liu-Zeng, A.~Gonz{\'{a}}lez-Ortega, A.~Hinojosa-Corona, and
+  J.~Gonz{\'{a}}lez-Garc{\'{i}}a (2014), {Assembly of a large earthquake from a
+  complex fault system: Surface rupture kinematics of the 4 April 2010 El
+  Mayor-Cucapah (Mexico) Mw 7.2 earthquake}, \textit{Geosphere},
+  \textit{10}(4), 797--827, \doi{10.1130/GES00933.1}.
+
+\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais,
+  Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
+Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and
+  S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002
+  Denali, Alaska, earthquake for postseismic relaxation processes and
+  lithospheric rheology}, \textit{Journal of Geophysical Research: Solid
+  Earth}, \textit{111}, 1--23, \doi{10.1029/2005JB003894}.
+
+\bibitem[{\textit{Freed et~al.}(2007)\textit{Freed, B{\"{u}}rgmann, and
+  Herring}}]{Freed2007a}
+Freed, A.~M., R.~B{\"{u}}rgmann, and T.~Herring (2007), {Far-reaching transient
+  motions after Mojave earthquakes require broad mantle flow beneath a strong
+  crust}, \textit{Geophysical Research Letters}, \textit{34}, 1--5,
+  \doi{10.1029/2007GL030959}.
+
+\bibitem[{\textit{Gonzalez-Ortega et~al.}(2014)\textit{Gonzalez-Ortega, Fialko,
+  Sandwell, Nava-pichardo, Fletcher, Gonzalez-garcia, Lipovsky, Floyd, and
+  Funning}}]{Gonzalez-ortega2014}
+Gonzalez-Ortega, A., Y.~Fialko, D.~Sandwell, F.~A. Nava-pichardo, J.~Fletcher,
+  J.~Gonzalez-garcia, B.~Lipovsky, M.~Floyd, and G.~Funning (2014), {El
+  Mayor-Cucapah (Mw7.2) earthquake: early near-field postseismic deformation
+  from InSar and GPS observations}, \textit{Journal of Geophysical Research},
+  \textit{119}, 1482--1497, \doi{10.1002/2013JB010193.Received}.
+
+\bibitem[{\textit{Hauksson et~al.}(2011)\textit{Hauksson, Stock, Hutton, Yang,
+  Vidal-Villegas, and Kanamori}}]{Hauksson2011}
+Hauksson, E., J.~Stock, K.~Hutton, W.~Yang, J.~A. Vidal-Villegas, and
+  H.~Kanamori (2011), {The 2010 Mw 7.2 El mayor-cucapah earthquake sequence,
+  Baja California, Mexico and Southernmost California, USA: Active
+  seismotectonics along the Mexican pacific margin}, \textit{Pure and Applied
+  Geophysics}, \textit{168}(3918), 1255--1277, \doi{10.1007/s00024-010-0209-7}.
+
+\bibitem[{\textit{Hearn}(2003)}]{Hearn2003}
+Hearn, E.~H. (2003), {What can GPS data tell us about the dynamics of
+  post-seismic deformation ?}, (2003), 753--777.
+
+\bibitem[{\textit{Hearn et~al.}(2009)\textit{Hearn, McClusky, Ergintav, and
+  Reilinger}}]{Hearn2009}
+Hearn, E.~H., S.~McClusky, S.~Ergintav, and R.~E. Reilinger (2009), {Izmit
+  earthquake postseismic deformation and dynamics of the North Anatolian Fault
+  Zone}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{114}(August 2008), 1--21, \doi{10.1029/2008JB006026}.
+
+\bibitem[{\textit{Hetland}(2003)}]{Hetland2003}
+Hetland, E.~A. (2003), {Postseismic relaxation across the Central Nevada
+  Seismic Belt}, \textit{Journal of Geophysical Research}, \textit{108}(Figure
+  2), 1--13, \doi{10.1029/2002JB002257}.
+
+\bibitem[{\textit{Hetland and Zhang}(2014)}]{Hetland2014}
+Hetland, E.~A., and G.~Zhang (2014), {Effect of shear zones on post-seismic
+  deformation with application to the 1997 Mw 7.6 manyi earthquake},
+  \textit{Geophysical Journal International}, \textit{198}, 259--269,
+  \doi{10.1093/gji/ggu127}.
+
+\bibitem[{\textit{Hines and Hetland}(2013)}]{Hines2013}
+Hines, T.~T., and E.~A. Hetland (2013), {Bias in estimates of lithosphere
+  viscosity from interseismic deformation}, \textit{Geophysical Research
+  Letters}, \textit{40}(16), 4260--4265, \doi{10.1002/grl.50839}.
+
+\bibitem[{\textit{Hines and Hetland}(2016)}]{Hines2016}
+Hines, T.~T., and E.~A. Hetland (2016), {Rapid and simultaneous estimation of
+  fault slip and heterogeneous lithospheric viscosity from post-seismic
+  deformation}, \textit{Geophysical Journal International}, \textit{204}(1),
+  569--582, \doi{10.1093/gji/ggv477}.
+
+\bibitem[{\textit{Jacobs et~al.}(2002)\textit{Jacobs, Sandwell, Fialko, and
+  Sichoix}}]{Jacobs2002}
+Jacobs, A., D.~Sandwell, Y.~Fialko, and L.~Sichoix (2002), {The 1999 (Mw7.1)
+  Hector Mine, California, Earthquake: Near-Field Postseismic Deformation from
+  ERS Interferometry}, \textit{Bulletin of the Seismological Society of
+  America}, \textit{92}(May), 1433--1442.
+
+\bibitem[{\textit{Johnson and Segall}(2004)}]{Johnson2004}
+Johnson, K.~M., and P.~Segall (2004), {Viscoelastic earthquake cycle models
+  with deep stress-driven creep along the San Andreas fault system},
+  \textit{Journal of Geophysical Research B: Solid Earth}, \textit{109}, 1--19,
+  \doi{10.1029/2004JB003096}.
+
+\bibitem[{\textit{Johnson et~al.}(2009)\textit{Johnson, B{\"{u}}rgmann, and
+  Freymueller}}]{Johnson2009}
+Johnson, K.~M., R.~B{\"{u}}rgmann, and J.~T. Freymueller (2009), {Coupled
+  afterslip and viscoelastic flow following the 2002 Denali Fault, Alaska
+  earthquake}, \textit{Geophysical Journal International}, \textit{176}(3),
+  670--682, \doi{10.1111/j.1365-246X.2008.04029.x}.
+
+\bibitem[{\textit{J{\'{o}}nsson et~al.}(2003)\textit{J{\'{o}}nsson, Segall,
+  Pedersen, and Bjornsson}}]{Jonsson2003}
+J{\'{o}}nsson, S., P.~Segall, R.~Pedersen, and G.~Bjornsson (2003),
+  {Post-earthquake ground movements correlated to pore-pressure transients},
+  \textit{Nature}, \textit{424}(July), 179--183, \doi{10.1038/nature01758.1.}
+
+\bibitem[{\textit{Kaufmann and Amelung}(2000)}]{Kaufmann2000}
+Kaufmann, G., and F.~Amelung (2000), {Reservoir-induced deformation and
+  continental rheology in vicinity of Lake Mead, Nevada}, \textit{Journal of
+  Geophysical Research}, \textit{105}(B7), 16,341, \doi{10.1029/2000JB900079}.
+
+\bibitem[{\textit{Kroll et~al.}(2013)\textit{Kroll, Cochran, Richards-Dinger,
+  and Sumy}}]{Kroll2013}
+Kroll, K.~A., E.~S. Cochran, K.~B. Richards-Dinger, and D.~F. Sumy (2013),
+  {Aftershocks of the 2010 Mw 7.2 El Mayor-Cucapah earthquake reveal complex
+  faulting in the Yuha Desert, California}, \textit{Journal of Geophysical
+  Research: Solid Earth}, \textit{118}(October), 6146--6164,
+  \doi{10.1002/2013JB010529}.
+
+\bibitem[{\textit{Lekic et~al.}(2011)\textit{Lekic, French, and
+  Fischer}}]{Lekic2011}
+Lekic, V., S.~W. French, and K.~M. Fischer (2011), {Lithospheric Thinning
+  Beneath Rifted Regions of Southern California}, \textit{Science},
+  \textit{334}(November), 783--787.
+
+\bibitem[{\textit{Liu et~al.}(1976)\textit{Liu, Anderson, and
+  Kanamori}}]{Liu1976}
+Liu, H.-P., D.~L. Anderson, and H.~Kanamori (1976), {Velocity dispersion due to
+  anelasticity; implications for seismology and mantle composition},
+  \textit{Geophysical Journal International}, \textit{47}(1), 41--58,
+  \doi{10.1111/j.1365-246X.1976.tb01261.x}.
+
+\bibitem[{\textit{Lundgren et~al.}(2009)\textit{Lundgren, Hetland, Liu, and
+  Fielding}}]{Lundgren2009}
+Lundgren, P., E.~A. Hetland, Z.~Liu, and E.~J. Fielding (2009), {Southern San
+  Andreas-San Jacinto fault system slip rates estimated from earthquake cycle
+  models constrained by GPS and interferometric synthetic aperture radar
+  observations}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{114}(2), 1--18, \doi{10.1029/2008JB005996}.
+
+\bibitem[{\textit{McGuire and Segall}(2003)}]{McGuire2003}
+McGuire, J.~J., and P.~Segall (2003), {Imaging of aseismic fault slip
+  transients recorded by dense geodetic networks}, \textit{Geophysical Journal
+  International}, \textit{155}(3), 778--788,
+  \doi{10.1111/j.1365-246X.2003.02022.x}.
+
+\bibitem[{\textit{Meade and Hager}(2005)}]{Meade2005}
+Meade, B.~J., and B.~H. Hager (2005), {Block models of crustal motion in
+  southern California constrained by GPS measurements}, \textit{Journal of
+  Geophysical Research B: Solid Earth}, \textit{110}, 1--19,
+  \doi{10.1029/2004JB003209}.
+
+\bibitem[{\textit{Murray and Segall}(2005)}]{Murray2005}
+Murray, J.~R., and P.~Segall (2005), {Spatiotemporal evolution of a transient
+  slip event on the San Andreas fault near Parkfield, California},
+  \textit{Journal of Geophysical Research : Solid Earth}, \textit{110}(9),
+  1--12, \doi{10.1029/2005JB003651}.
+
+\bibitem[{\textit{Nur and Mavko}(1974)}]{Nur1974}
+Nur, A., and G.~Mavko (1974), {Postseismic viscoelastic rebound},
+  \textit{Science}, \textit{183}(4121), 204--206, \doi{10.1038/098448b0}.
+
+\bibitem[{\textit{O'Connell}(1971)}]{OConnell1971}
+O'Connell, R.~J. (1971), {Rheology of the Mantle}, \textit{EOS, Transactions,
+  American Geophysical Union}, \textit{52}, 140--142.
+
+\bibitem[{\textit{Oskin et~al.}(2012)\textit{Oskin, Arrowsmith, {Hinojosa
+  Corona}, Elliott, Fletcher, Fielding, Gold, {Gonzalez Garcia}, Hudnut,
+  Liu-Zeng, and Teran}}]{Oskin2012}
+Oskin, M.~E., J.~R. Arrowsmith, A.~{Hinojosa Corona}, A.~J. Elliott, J.~M.
+  Fletcher, E.~J. Fielding, P.~O. Gold, J.~J. {Gonzalez Garcia}, K.~W. Hudnut,
+  J.~Liu-Zeng, and O.~J. Teran (2012), {Near-field deformation from the El
+  Mayor-Cucapah earthquake revealed by differential LIDAR}, \textit{Science},
+  \textit{335}(6069), 702--705, \doi{10.1126/science.1213778}.
+
+\bibitem[{\textit{Pollitz et~al.}(2001)\textit{Pollitz, Wicks, and
+  Thatcher}}]{Pollitz2001}
+Pollitz, F., C.~Wicks, and W.~Thatcher (2001), {Mantle Flow Beneath a
+  Continental Strike-Slip Fault : Postseismic Deformation After the 1999 Hector
+  Mine Earthquake}, \textit{Science}, \textit{1814}(2001), 1814--1818,
+  \doi{10.1126/science.1061361}.
+
+\bibitem[{\textit{Pollitz}(2003)}]{Pollitz2003}
+Pollitz, F.~F. (2003), {Transient rheology of the uppermost mantle beneath the
+  Mojave Desert, California}, \textit{Earth and Planetary Science Letters},
+  \textit{215}, 89--104, \doi{10.1016/S0012-821X(03)00432-1}.
+
+\bibitem[{\textit{Pollitz et~al.}(2000)\textit{Pollitz, Peltzer, and
+  B{\"{u}}rgmann}}]{Pollitz2000}
+Pollitz, F.~F., G.~Peltzer, and R.~B{\"{u}}rgmann (2000), {Mobility of
+  continental mantle: Evidence from postseismic geodetic observations following
+  the 1992 Landers earthquake}, \textit{Journal of Geophysical Research},
+  \textit{105}(1999), 8035, \doi{10.1029/1999JB900380}.
+
+\bibitem[{\textit{Pollitz et~al.}(2012)\textit{Pollitz, B{\"{u}}rgmann, and
+  Thatcher}}]{Pollitz2012}
+Pollitz, F.~F., R.~B{\"{u}}rgmann, and W.~Thatcher (2012), {Illumination of
+  rheological mantle heterogeneity by the M7.2 2010 El Mayor-Cucapah
+  earthquake}, \textit{Geochemistry, Geophysics, Geosystems}, \textit{13}(6),
+  1--17, \doi{10.1029/2012GC004139}.
+
+\bibitem[{\textit{Rauch et~al.}(1965)\textit{Rauch, Tung, and
+  Striebel}}]{Rauch1965}
+Rauch, H.~E., F.~Tung, and C.~T. Striebel (1965), {Maximum likelihood estimates
+  of linear dynamic systems}, \textit{AIAA Journal}, \textit{3}(8), 1445--1450.
+
+\bibitem[{\textit{Riva and Govers}(2009)}]{Riva2009}
+Riva, R. E.~M., and R.~Govers (2009), {Relating viscosities from postseismic
+  relaxation to a realistic viscosity structure for the lithosphere},
+  \textit{Geophysical Journal International}, \textit{176}, 614--624,
+  \doi{10.1111/j.1365-246X.2008.04004.x}.
+
+\bibitem[{\textit{Rollins et~al.}(2015)\textit{Rollins, Barbot, and
+  Avouac}}]{Rollins2015}
+Rollins, C., S.~Barbot, and J.-P. Avouac (2015), {Postseismic Deformation
+  Following the 2010 M7.2 El Mayor-Cucapah Earthquake : Observations ,
+  Kinematic Inversions , and Dynamic Models}, \textit{Pure and Applied
+  Geophysics}, \doi{10.1007/s00024-014-1005-6}.
+
+\bibitem[{\textit{Savage}(1990)}]{Savage1990}
+Savage, J.~C. (1990), {Equivalent strike-slip earthquake cycles in half-space
+  and lithosphere-asthenosphere earth models}, \textit{Journal of Geophysical
+  Research}, \textit{95}, 4873, \doi{10.1029/JB095iB04p04873}.
+
+\bibitem[{\textit{Savage and Svarc}(2009)}]{Savage2009}
+Savage, J.~C., and J.~L. Svarc (2009), {Postseismic relaxation following the
+  1992 M 7.3 Landers and 1999 M 7.1 Hector Mine earthquakes , southern
+  California}, \textit{Journal of Geophysical Research}, \textit{114}(B01401),
+  \doi{10.1029/2008JB005938}.
+
+\bibitem[{\textit{Savage et~al.}(2005)\textit{Savage, Svarc, and
+  Yu}}]{Savage2005a}
+Savage, J.~C., J.~L. Svarc, and S.~B. Yu (2005), {Postseismic relaxation and
+  transient creep}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{110}, 1--14, \doi{10.1029/2005JB003687}.
+
+\bibitem[{\textit{Segall and Mathews}(1997)}]{Segall1997}
+Segall, P., and M.~Mathews (1997), {Time dependent inversion of geodetic data},
+  \textit{Journal of Geophysical Research}, \textit{102}.
+
+\bibitem[{\textit{Spinler et~al.}(2015)\textit{Spinler, Bennett, Walls, Shawn,
+  and Garcia}}]{Spinler2015}
+Spinler, J.~C., R.~A. Bennett, C.~Walls, L.~Shawn, and J.~J.~G. Garcia (2015),
+  {Assessing long-term postseismic deformation following the M7.2 4 April 2010,
+  El Mayor-Cucapah earthquake with implications for lithospheric rheology in
+  the Salton Trough}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{120}, 3664--3679, \doi{10.1002/2014JB011613.Received}.
+
+\bibitem[{\textit{Wei et~al.}(2011{\natexlab{a}})\textit{Wei, Sandwell, Fialko,
+  and Bilham}}]{Wei2011a}
+Wei, M., D.~Sandwell, Y.~Fialko, and R.~Bilham (2011{\natexlab{a}}), {Slip on
+  faults in the Imperial Valley triggered by the 4 April 2010 Mw 7.2 El
+  Mayor-Cucapah earthquake revealed by InSAR}, \textit{Geophysical Research
+  Letters}, \textit{38}(January), 1--6, \doi{10.1029/2010GL045235}.
+
+\bibitem[{\textit{Wei et~al.}(2015)\textit{Wei, Liu, Kaneko, Mcguire, and
+  Bilham}}]{Wei2015}
+Wei, M., Y.~Liu, Y.~Kaneko, J.~J. Mcguire, and R.~Bilham (2015), {Dynamic
+  triggering of creep events in the Salton Trough, Southern California by
+  regional M≥5.4 earthquakes constrained by geodetic observations and
+  numerical simulations}, \textit{Earth and Planetary Science Letters},
+  \textit{427}, 1--10, \doi{10.1016/j.epsl.2015.06.044}.
+
+\bibitem[{\textit{Wei et~al.}(2011{\natexlab{b}})\textit{Wei, Fielding,
+  Leprince, Sladen, Avouac, Helmberger, Hauksson, Chu, Simons, Hudnut, Herring,
+  and Briggs}}]{Wei2011}
+Wei, S., E.~Fielding, S.~Leprince, A.~Sladen, J.-P. Avouac, D.~Helmberger,
+  E.~Hauksson, R.~Chu, M.~Simons, K.~Hudnut, T.~Herring, and R.~Briggs
+  (2011{\natexlab{b}}), {Superficial simplicity of the 2010 El Mayor–Cucapah
+  earthquake of Baja California in Mexico}, \textit{Nature Geoscience},
+  \textit{4}(9), 615--618, \doi{10.1038/ngeo1213}.
+
+\bibitem[{\textit{Yuen and Peltier}(1982)}]{Yuen1982}
+Yuen, D.~A., and W.~R. Peltier (1982), {Normal modes of the viscoelastic
+  earth}, \textit{Geophysical Journal of the Royal Astronomical Society},
+  \textit{69}, 495--526, \doi{10.1111/j.1365-246X.1982.tb04962.x}.
+
+\end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Track Changes:
+% To add words, \added{<word added>}
+% To delete words, \deleted{<word deleted>}
+% To replace words, \replace{<word to be replaced>}{<replacement word>}
+% To explain why change was made: \explain{<explanation>} This will put
+% a comment into the right margin.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% At the end of the document, use \listofchanges, which will list the
+% changes and the page and line number where the change was made.
+
+% When final version, \listofchanges will not produce anything,
+% \added{<word or words>} word will be printed, \deleted{<word or words} will take away the word,
+% \replaced{<delete this word>}{<replace with this word>} will print only the replacement word.
+%  In the final version, \explain will not print anything.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%
+\listofchanges
+%%%
 
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Supporting Information
+%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
+%% for Supporting Information.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+More Information and Advice:
+
+%% ------------------------------------------------------------------------ %%
+%
+%  SECTION HEADS
+%
+%% ------------------------------------------------------------------------ %%
+
+% Capitalize the first letter of each word (except for
+% prepositions, conjunctions, and articles that are
+% three or fewer letters).
+
+% AGU follows standard outline style; therefore, there cannot be a section 1 without
+% a section 2, or a section 2.3.1 without a section 2.3.2.
+% Please make sure your section numbers are balanced.
+% ---------------
+% Level 1 head
+%
+% Use the \section{} command to identify level 1 heads;
+% type the appropriate head wording between the curly
+% brackets, as shown below.
+%
+%An example:
+%\section{Level 1 Head: Introduction}
+%
+% ---------------
+% Level 2 head
+%
+% Use the \subsection{} command to identify level 2 heads.
+%An example:
+%\subsection{Level 2 Head}
+%
+% ---------------
+% Level 3 head
+%
+% Use the \subsubsection{} command to identify level 3 heads
+%An example:
+%\subsubsection{Level 3 Head}
+%
+%---------------
+% Level 4 head
+%
+% Use the \subsubsubsection{} command to identify level 3 heads
+% An example:
+%\subsubsubsection{Level 4 Head} An example.
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  IN-TEXT LISTS
+%
+%% ------------------------------------------------------------------------ %%
+%
+% Do not use bulleted lists; enumerated lists are okay.
+% \begin{enumerate}
+% \item
+% \item
+% \item
+% \end{enumerate}
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  EQUATIONS
+%
+%% ------------------------------------------------------------------------ %%
+
+% Single-line equations are centered.
+% Equation arrays will appear left-aligned.
+
+Math coded inside display math mode \[ ...\]
+ will not be numbered, e.g.,:
+ \[ x^2=y^2 + z^2\]
+
+ Math coded inside \begin{equation} and \end{equation} will
+ be automatically numbered, e.g.,:
+ \begin{equation}
+ x^2=y^2 + z^2
+ \end{equation}
+
+% To create multiline equations, use the
+% \begin{eqnarray} and \end{eqnarray} environment
+% as demonstrated below.
+\begin{eqnarray}
+  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
+        && + (y - y_{0}) \sin \Theta  \nonumber \\
+  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
+        && + (y - y_{0}) \cos \Theta.
+\end{eqnarray}
+
+%If you don't want an equation number, use the star form:
+%\begin{eqnarray*}...\end{eqnarray*}
+
+% Break each line at a sign of operation
+% (+, -, etc.) if possible, with the sign of operation
+% on the new line.
+
+% Indent second and subsequent lines to align with
+% the first character following the equal sign on the
+% first line.
+
+% Use an \hspace{} command to insert horizontal space
+% into your equation if necessary. Place an appropriate
+% unit of measure between the curly braces, e.g.
+% \hspace{1in}; you may have to experiment to achieve
+% the correct amount of space.
+
+%% ------------------------------------------------------------------------ %%
+%
+%  EQUATION NUMBERING: COUNTER
+%
+%% ------------------------------------------------------------------------ %%
+
+% You may change equation numbering by resetting
+% the equation counter or by explicitly numbering
+% an equation.
+
+% To explicitly number an equation, type \eqnum{}
+% (with the desired number between the brackets)
+% after the \begin{equation} or \begin{eqnarray}
+% command.  The \eqnum{} command will affect only
+% the equation it appears with; LaTeX will number
+% any equations appearing later in the manuscript
+% according to the equation counter.
+%
+
+% If you have a multiline equation that needs only
+% one equation number, use a \nonumber command in
+% front of the double backslashes (\\) as shown in
+% the multiline equation above.
+
+% If you are using line numbers, remember to surround
+% equations with \begin{linenomath*}...\end{linenomath*}
+
+%  To add line numbers to lines in equations:
+%  \begin{linenomath*}
+%  \begin{equation}
+%  \end{equation}
+%  \end{linenomath*}

### 2016-04-20 JGRSubmission/agusuppinfosample.tex
commit before push

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supporting Information
%% (Optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OVERVIEW
%
% Please note that all supporting information will be peer reviewed with your manuscript.
% In general, the purpose of the supporting information is to enable
% authors to provide and archive auxiliary information such as data
% tables, method information, figures, video, or computer software,
% in digital formats so that other scientists can use it.

% The key criteria are that the data:
% 1. supplement the main scientific conclusions of the paper but are not essential to the conclusions (with the exception of
%    including data so the experiment can be reproducible);
% 2. are likely to be usable or used by other scientists working in the field;
% 3. are described with sufficient precision that other scientists can understand them, and
% 4. are not exe files.
%

% All Supporting text and figures should be included in this document.

% Data sets, large tables, movie files,
% and audio files should be uploaded separately, following AGU naming
% conventions. Include their captions in this document and list the
% file name with the caption. You will be prompted to upload these
% files on the Upload Files tab during the submission process, using
% file type “Supporting Information (SI)”

\documentclass[draft]{agujournal}

% Please type in the journal name: \journalname{<Journal Name>}
% ie,
\journalname{Journal of Geophysical Research}

%% Choose from this list of Journals:
%
% Journal of Geophysical Research
% JGR-Biogeosciences
% JGR-Earth Surface
% JGR-Planets
% JGR-Solid Earth
% JGR-Space Physics
% Global Biochemical Cycles
% Geophysical Research Letters
% Paleoceanography
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resource Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science

\begin{document}

%% This command needs article title as argument to \supportinginfo{}:
\supportinginfo{Trends in the predictive performance of raw ensemble weather forecasts}

 \authors{A. B. Smith\affil{1}\thanks{Current address, McMurdo Station,
 Antartica},
 Eric Brown\affil{1,2}, Rick Williams\affil{3},
 John B. McDougall\affil{4}, and S. Visconti\affil{5}\thanks{Also
 funded by Monsanto.}}

\affiliation{1}{Department of Hydrology and Water Resources,
University of Arizona, Tucson, Arizona, USA.}
\affiliation{2}{Department of Geography, Ohio State University,
Columbus, Ohio, USA.}
\affiliation{3}{Department of Space Sciences, University of
Michigan, Ann Arbor, Michigan, USA.}
\affiliation{4}{Division of Hydrologic Sciences, Desert Research
Institute, Reno, Nevada, USA.}
\affiliation{5}{Dipartimento di Idraulica, Trasporti ed
Infrastrutture Civili, Politecnico di Torino, Turin, Italy.}

%% Corresponding Author
%(include name and email addresses of the corresponding author.  More
%than one corresponding author is allowed in this Word file and for
%publication; but only one corresponding author is allowed in our
%editorial system.)

\correspondingauthor{A. B. Smith}{email@address.edu}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

\section*{Contents}
%%%Remove or add items as needed%%%
\begin{enumerate}
\item Text S1 to Sx
\item Figures S1 to Sx
\item Tables S1 to Sx
\end{enumerate}

\section*{Additional Supporting Information (Files uploaded separately)}

\begin{enumerate}
\item Captions for Datasets S1 to Sx
\item Captions for large Tables S1 to Sx (if larger than 1 page, upload as separate excel file)
\item Captions for Movies S1 to Sx
\item Captions for Audio S1 to Sx
\end{enumerate}

\section*{Introduction}

%Delete all unused file types below. 
%Copy/paste for multiples of each file type as needed.

\section*{Text S1.}

Type or paste text here. This should be additional explanatory text,
such as: extended descriptions of results, full details of models,
extended lists of acknowledgements etc.  It should not be
additional discussion, analysis, interpretation or critique. It
should not be an additional scientific experiment or paper.

Repeat for any additional Supporting Text

%%Enter Data Set, Movie, and Audio captions here
%%EXAMPLE CAPTIONS

\section*{Data Set S1.} %Type or paste caption here.

Upload your dataset(s) to AGU's journal submission site and select
"Supporting Information (SI)" as the file type. Following naming
convention: ds01.

Repeat for any additional Supporting data sets

\section*{Movie S1.}

Type or paste caption here.

Upload your movie(s) to AGU's journal submission site and select,
"Supporting Information (SI)" as the file type. Following naming convention: ms01.

Repeat any additional Supporting movies

\section*{Audio S1.}

Type or paste caption here.

Upload your audio file(s) to AGU's journal submission site and select
Supporting Information ``(SI)" as the file type. Following naming
convention: auds01.

Repeat for any additional Supporting audio files

\end{document}

### 2016-04-20 RoughDraft/ElMayor.tex
commit before push

@@
 \begin{abstract}
-Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its preseismic trend after about 3 years at epicentral distances greater than $\sim200$ km.
-In the near-field, we observe rapid transience that decays to a sustained rate which exceeds its preseismic trend.
+Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about 3 years at epicentral distances greater than $\sim200$ km.
+In the near-field, we observe rapid transience that decays to a sustained rate which exceeds its pre-earthquake trend.
 We attempt to determine the mechanisms driving this observed deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
-We find that early, rapid, near-field deformation can be explained with afterslip on the portion of the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip or a stead-state viscosity of $\sim10^{19}$ Pa s in the lower crust.
+We find that early, rapid, near-field deformation can be explained with afterslip on the portion of the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of $\sim10^{19}$ Pa s.
 The trend in far-field deformation is best explained with a transient viscosity of $\sim10^{18}$ Pa s in the upper mantle.
-We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the observable postseismic deformation and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies on geophysical processes occurring over longer time scales.
-
+We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay of the postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
 \end{abstract}

### 2016-04-20 JGRSubmission/Supplementary/effective_viscosity.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python
+import numpy as np
+import sympy as sp
+import matplotlib.pyplot as plt
+
+
+def ivt(uhat,s,n):
+  ''' 
+  Extension of the initial value theorem which computes the n'th
+  derivative of u(t) evaluated at t=0 from the Laplace transform of
+  u(t), uhat(s).
+
+  This is eq. (A.5) in Appendix A
+
+  PARAMETERS
+  ----------
+    uhat: Laplace transform of u. This is a symbolic expression
+      containing s
+    s: Laplace domain variable
+    n: the derivative order
+
+  RETURNS
+  -------
+    u_n: symbolic expression for the nth derivative of u evaluated at
+      t=0
+  '''
+  if n == 0:
+    expr = s*uhat
+    u_0 = expr.limit(s,np.inf)
+    return u_0
+
+  elif n > 0:
+    expr = s**(n+1)*uhat - sum(s**m*ivt(uhat,s,n-m) for m in range(1,n+1))
+    u_n = expr.limit(s,np.inf)
+    return u_n
+
+def ilt(uhat,s,t,N):
+  ''' 
+  Evaluates the inverse Laplace transform of uhat(s) through a Taylor
+  series expansion
+
+  This is a combination of eqs. (A.7) and (A.5) in Appendix A
+
+  PARAMETERS
+  ----------
+    uhat: Laplace transform of u. This is a symbolic expression
+      containing s
+    s: Laplace domain variable
+    t: time domain variable
+    N: order of the Taylor series expansion
+
+  RETURNS
+  -------
+    series: symbolic expression for the series expansion of the u(x)
+     about x=0
+  '''
+  series = sum((ivt(uhat,s,n)*t**n)/sp.factorial(n) for n in range(N+1))
+  return series
+
+s = sp.symbols('s')
+t = sp.symbols('t')
+mu = sp.symbols('mu')
+muk = sp.symbols('mu_K')
+muk1 = sp.symbols('mu_K1')
+muk2 = sp.symbols('mu_K2')
+etam = sp.symbols('eta_M')
+etak = sp.symbols('eta_K')
[…]

### 2016-04-20 JGRSubmission/agujournaltemplate.tex
commit before push;

@@
-%% 11/23/2015
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
-%
-% This file includes commands and instructions
-% given in the order necessary to produce a final output that will
-% satisfy AGU requirements. 
-%
-% You may copy this file and give it your
-% article name, and enter your text.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PLEASE DO NOT USE YOUR OWN MACROS
-% DO NOT USE \newcommand, \renewcommand, or \def, etc.
-%
-% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
-% DO NOT USE \psfrag or \subfigure commands.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% All questions should be e-mailed to latex@agu.org.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Step 1: Set the \documentclass
-%
-% There are two options for article format:
-%
-% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
-% The draft option produces double spaced output.
-% 
-% 2) numberline will give you line numbers.
-
-%% To submit your paper:
 \documentclass[draft,linenumbers]{AGUJournal}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{elastic inversion}\label{sec:ElasticInversion}    
@@
 The penalty parameters, $\lambda_s$, is chosen with a trade-off curve.
-We use Pylith \citep{Aagaard2009} to compute the Green's functions for this inversion, as well as for the remaining inversions in this paper.
+We use Pylith \citep{Aagaard2013} to compute the Green's functions for this inversion, as well as for the remaining inversions in this paper.
 
@@
 The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
-Our elastic slip model accurately describes near-field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than ${\sim}150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
+Figure \ref{fig:RecordSectionElastic} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P axis.
+We show the radial component of displacements with respect to the El Mayor-Cucapah epicentre and we also rescale the displacements so that the difference between the minimum and maximum observed displacements are the same for each station.
+Our elastic slip model accurately describes near-field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than ${\sim}150$ km from the El Mayor-Cucapah epicentre.
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{constraints on effective viscosity}\label{sec:InitialInversion}
@@
 In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2016} to constrain an initial effective lithospheric viscosity structure from the early postseismic deformation.
-The method relies upon the fact that immediately after an earthquake, stresses throughout the crust and mantle are only controlled by the relatively well known instantaneous elastic properties and each parcel will have a strain rate, $\dot\epsilon$, that is proportional to stress, $\sigma$, and inversely proportional to the parcel's effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$.
-Through linear superposition, we can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's effective viscosity.
+Our method utilizes the fact that coseismic stresses throughout the crust and upper mantle depend on the instantaneous elastic parameters and are independent of the viscoelastic parameters which we wish to estimate.
+Immediately following an earthquake, each parcel will have a strain rate that is proportional to the coseismic stress and inversely proportional to the parcel's effective viscosity,
+$\eta_\mathrm{eff}$.  Using one-dimensional viscoelastic models, we define the effective viscosity as
+\begin{equation}
+  \eta_\mathrm{eff} = \left.\frac{\sigma}{\dot{\varepsilon}}\right|_{t=0}
+\end{equation}
+where $\sigma$ is an applied stress at $t=0$ and $\dot\epsilon$ is the resulting strain rate.
+Figure \ref{fig:Rheology} shows how $\eta_\mathrm{eff}$ relates to the parameters for various linear viscoelastic rheologies.
+We can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from relaxation in each parcel, scaled by the reciprocal of the parcel's effective viscosity.
 That is to say
@@
 \end{equation}
-where $h(x,\xi,\zeta)$ describes the initial rate of deformation resulting from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$ and $L$ denotes the crust and mantle.
+where $L$ denotes the crust and mantle and $h(x,\xi,\zeta)$ describes the initial rate of deformation resulting from viscoelastic relaxation at $\zeta$ induced by slip at $\xi$.
 We can combine eq.
@@
 which is valid for as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
+
+Details on how eq.
+(\ref{ApproxForward}) is used to estimate $s$ and $\eta_\mathrm{eff}$ from postseismic deformation can be found in \citet{Hines2016}.
+A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
+We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2016} because of its relative simplicity.
+Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
+
 Although eq.
-(\ref{ApproxForward}) may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are only functions of the fault geometry and instantaneous elastic properties, $\lambda$ and $\mu$, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem in eq.
+(\ref{ApproxForward}) may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are only functions of the fault geometry and instantaneous elastic properties, $\lambda$ and $\mu$, and thus $g$ and $h$ can be computed numerically as a preprocessing step.
+The forward problem in eq.
 (\ref{ApproxForward}) can be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
@@
 (\ref{GeneralForward}), numerically for each realization of $s$ and unknown rheologic properties.
-Figure \ref{fig:Rheology} shows how estimates of $\eta_\mathrm{eff}$ can then be used as a constraint on the unknown parameters for various linear viscoelastic rheologies.
 
@@
 Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, as well as from 150 km to the bottom of our numerical model domain at 800 km.
-We again restrict fault slip to occur between 0 and 15 km depth and we made this choice to help eliminate inevitable non uniqueness.
+We again restrict fault slip to occur between 0 and 15 km depth, which is done in order to help eliminate inevitable non-uniqueness in the inversion.
 It has long been recognized that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional earthquake models \citep{Savage1990}.
-Since we are trying to simultaneously model these two processes, it is necessary to put sensible constraints on the depth of fault slip.
-Additionally, we note that when simultaneously estimating afterslip in the lower crust and a lower crustal viscosity, the inverse problem becomes particularly ill-posed.
-This ill-posedness is illustrated in Figure (\ref{fig:LowerCrust}), which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
-The horizontal displacements from fault slip are in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
+Additionally, we note that when simultaneously estimating both afterslip and viscosity in the lower crust, the inverse problem becomes particularly ill-posed.
+This ill-posedness is illustrated in Figure (\ref{fig:LowerCrust}), which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from subsequent viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+In this demonstration, the viscoelastic relaxation is entirely driven by the fault slip in the lower crust.
+The horizontal displacements from fault slip are in the opposite direction as the displacements resulting from viscoelastic relaxation.
 This means that surface displacements resulting from afterslip at lower crustal depths can be cancelled out, at least partially, by a low viscosity lower crust.
@@
 \includegraphics[scale=0.8]{Figures/Cancellation}
-\caption{Displacements resulting from fault slip at lower crustal depths (left), and initial velocity resulting from subsequent relaxation of a viscoelastic lower crust (right).
+\caption{Displacements resulting from fault slip at lower crustal depths (left), and initial velocities resulting from subsequent relaxation of a viscoelastic lower crust (right).
 The fault segment dips $75^\circ$ to the north east and its surface projection is outlined in green.
@@
 \end{figure}
-
-Further details on how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2016}.
-A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
-We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2016} because of its relative simplicity.
-Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
 
@@
 (\ref{ApproxForward}) is no longer capable of describing the observed deformation without incurring systematic misfits.
-This is illustrated in Figure \ref{fig:RecordSection1}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
 When using eq.
-(\ref{ApproxForward}) to fit the entire 5 years of postseismic displacement we see that the near-field displacements, e.g.
-station P501, are accurately predicted but when looking at displacement in the far-field, e.g.
-station P621, we see that eq.
-(\ref{ApproxForward}) overestimates the rate of deformation in the later postseismic period and underestimates the rate of deformation in the early period.
+(\ref{ApproxForward}) to fit the entire 5 years of postseismic displacements, we see that the near-field displacements (e.g., station P501) are accurately predicted but when looking at displacement in the far-field (e.g., station P621) we see that eq.
+(\ref{ApproxForward}) overestimates the rate of deformation in the later postseismic period and underestimates the rate of deformation in the early period (Figure \ref{fig:RecordSection1}).
 Due to the low signal-to-noise ratios for far-field stations, it is difficult to determine at what point eq.
@@
 \centering 
-\caption{Illustration of how $t_\mathrm{bd}$ is chosen.
-Observed postseismic displacements are shown in black.
-Blue, green and yellow lines are the best fitting predictions to 5.0, 3.0, and 0.8 years of the postseismic data, respectively, from eq.
-\ref{ApproxForward}.}
+\caption{Observed postseismic displacements (black) and best fitting predictions of eq. (\ref{ApproxForward}) to 5.0 (blue), 3.0 (green), and 0.8 (yellow) years of the postseismic data.} 
 \label{fig:RecordSection1}
@@
 (\ref{ApproxForward}).
-Due to inherent non uniqueness, we have added zeroth order Tikhonov regularization to estimates of $s$, and second order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^{-1}$.
+Due to inherent non uniqueness, we have added zeroth-order Tikhonov regularization to estimates of $s$, and second-order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^{-1}$.
 The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$.
@@
 Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full 5 years, which we do in Section \ref{sec:FullInversion}.
-Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind even adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
+Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
 (\ref{ApproxForward}) is sensible.
 
-Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in Figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were estimated through bootstrapping.
+Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in Figure \ref{fig:EffectiveViscosity}.
 Although fluidity is rarely used in geophysical literature, eq.
 (\ref{InitialRate}) is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each layer.
-We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_\eta$.
-Our choice of $\lambda_\eta$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
-It is therefore difficult to interpret the magnitude of uncertainties on viscosities shown in Figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
+We also show 95\% confidence intervals for estimated viscosities and fluidities but we note that the uncertainties tend to be underestimated due to the added regularization \citep{Aster2011}.
+Although, we do believe that the relative uncertainty between layers is accurately depicted.
 A robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
@@
 \centering 
-\caption{Effective viscosity and associated fludities inferred by fitting eq.
+\caption{Effective viscosities and associated fludities inferred by fitting eq.
 (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.
-95\% confidence intervals, estimated from bootstrapping, are also shown.}
+95\% confidence intervals, estimated from bootstrapping, are indicated by color fields.}
 \label{fig:EffectiveViscosity}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Full Inversion}\label{sec:FullInversion}
@@
 In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
-In this section, we use the effective viscosities inferred above as a prior constraint when searching for models which are capable of describing the available 5 years of postseismic data, where our forward problem is now eq.
+In this section, we use these effective viscosities as a prior constraint when searching for models which are capable of describing the available 5 years of postseismic data, where our forward problem is now eq.
 (\ref{GeneralForward}) rather than the approximation given by eq.
@@
 We perform a series of coseismic slip and afterslip inversion assuming a variety of rheologies for the lower crust and upper mantle which are consistent with our findings from Section \ref{sec:InitialInversion}.
-We appraise each model using the mean chi squared value,
+We appraise each model using the mean chi-squared value,
 \begin{equation}\label{eq:Misfit}
@@
 For comparison, $\bar\chi^2=35.3$ for the elastic model from Section \ref{sec:ElasticInversion}.
-The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years \ref{fig:RecordSection2}.
+The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years (Figure \ref{fig:RecordSection2}).
 Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle.
@@
 
-Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces the unknown parameter $\mu_{K}$.
+Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces one additional unknown parameter, $\mu_{K}$.
 We assume that the lower crust still has a Maxwell rheology.
@@
 \centering 
-\caption{Misfit as a function of the transient shear modulus in a Zener rheology upper mantle.}
+\caption{Mean chi-squared value for the best fitting slip model as a function of the transient shear modulus relative to the elastic shear modulus in a Zenner upper mantle.
+Large dot indicates our preferred ratio.}
 \label{fig:ShearModulusRatio}
@@
 Because we are able to adequately describe the available 5 years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-0state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
-
-The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip} and the predicted postseismic displacements are shown Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
+However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
+
+The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip}, and the predicted postseismic displacements are shown Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
 Overall, the trends in the near-field and far-field transient deformation are accurately described by our preferred model.
@@
 Most of our misfit is for the near-field stations in the Imperial Valley, and we attribute this misfit to our relatively simple fault geometry, which does not account for potential fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
-In particular, we are unable to model the sustained rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
-Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodelled postseismic deformation resulting from those earthquakes.
+In particular, we are unable to model the sustained, rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
+Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodelled postseismic deformation resulting from those earthquakes.
 Lastly, there are clear discrepancies between the observed and predicted vertical deformation following the first year after the El Mayor Cucapah earthquake.
@@
 The afterslip within the first year is accounting for the most rapid near-field transient deformation.
-After 1 year, afterslip is inferred to be deeper and under the Sierra Cucapah, which is describing much of the sustained near-field postseismic deformation.
-We emphasize, that the GPS station closest to our inferred afterslip, P496, is still about 30 km away, which is too far away for us to conclusively argue for sustained brittle deformation rather shallow ductile deformation.
+After 1 year, afterslip is inferred to be deeper down on the Sierra Cucapah segment, which is describing much of the sustained near-field postseismic deformation.
+We emphasize, that the GPS station closest to our inferred afterslip, P496, is still about 30 km away, which is too far away for us to conclusively argue for sustained localized deformation rather shallow distributed deformation.
 The deep afterslip inferred after 1 year could potentially be describing deformation resulting from lower crustal flow.
-To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}.
-After performing another slip inversion, we find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after 1 year, while still requiring about the same amount of afterslip over the first year.
-We do believe that the early shallow afterslip is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}, and inverted for fault slip.
+We find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after 1 year, while still requiring about the same amount of afterslip over the first year.
+We do believe that the early shallow afterslip on the Sierra Cucapah segment is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
+
 \section{Discussion}\label{Discussion}
@@
 Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}, which is the simplest viscoelastic rheologic model.
-In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities of $\gtrsim 10^{19}$ Pa s.
-These postseismic studies are consistent with \citet{Kaufmann2000,Cavalie2007} who found that an upper mantle viscosity of $10^{18}$ Pa s and a crustal viscosity $\gtrsim10^{20}$ Pa s are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal scales as postseismic deformation.
+In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities $\gtrsim 10^{19}$ Pa s.
+These postseismic studies are consistent with \citet{Kaufmann2000} and \citet{Cavalie2007}, who found that an upper mantle viscosity of $10^{18}$ Pa s and a crustal viscosity $\gtrsim10^{20}$ Pa s are necessary to describe subsidence resulting from changes in loading from Lake Mead.
+This isostatic adjustment is a process with similar spatial and temporal scales as postseismic deformation, and thus the inferred viscosities of these two types of studies would likely agree.
 While these studies found viscosities that are consistent with our effective viscosities from Section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
-For example, \citet{Lundgren2009} found that lower crust and upper mantle viscosities on the order of $10^{21}$ and $10^{19}$ Pa s, respectively, are needed to describe interseismic deformation along the Southern San Andreas and San Jacinto fault.
-An even higher mantle viscosity on the order of $10^{20}$ Pa s is required to describe deflection resulting from Lake Bonneville, which occurs on the time scales of $10^{4}$ years \citep{Crittenden1967,Bills1987}.
-
-An additional deficiency with the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate of postseismic deformation.
+For example, \citet{Lundgren2009} found that lower crust and upper mantle viscosities on the order of $10^{21}$ and $10^{19}$ Pa s, respectively, are needed to describe interseismic deformation along the Southern San Andreas fault zone in the Salton Sea region.
+An even higher mantle viscosity, on the order of $10^{20}$ Pa s, is required to describe isostatic adjustment resulting from the draining of Lake Bonneville, which occurs on the time scales of $10^{4}$ years \citep{Crittenden1967,Bills1987}.
+
+An additional deficiency with the Maxwell rheology is that it predicts a steady decay in the rate of postseismic deformation over time, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate of postseismic deformation.
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
@@
 \section*{Acknowledgements}
-We are grateful to Andy Freed for an illuminating discussion on the material in this manuscript.
-
+We thank Andy Freed for an illuminating discussion on the data used in this study.
 This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.
 EAR-1261833.
-
 This material is based upon work supported by the National Science
@@
 
-%----------------
-% EXAMPLE FIGURE
-%
-% \begin{figure}[h]
-% \centering
-% when using pdflatex, use pdf file:
-% \includegraphics[width=20pc]{figsamp.pdf}
-%
-% when using dvips, use .eps file:
-% \includegraphics[width=20pc]{figsamp.eps}
-%
-% \caption{Short caption}
-% \label{figone}
-%  \end{figure}
-%
-% ---------------
-% EXAMPLE TABLE
-%
-% \begin{table}
-% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
-% \centering
-% \begin{tabular}{l c}
-% \hline
-%  Run  & Time (min)  \\
-% \hline
-%   $l1$  & 260   \\
-%   $l2$  & 300   \\
-%   $l3$  & 340   \\
-%   $h1$  & 270   \\
-%   $h2$  & 250   \\
-%   $h3$  & 380   \\
-%   $r1$  & 370   \\
-%   $r2$  & 390   \\
-% \hline
-% \multicolumn{2}{l}{$^{a}$Footnote text here.}
-% \end{tabular}
-% \end{table}
-
-%% SIDEWAYS FIGURE and TABLE 
-% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
-%
-% \begin{sidewaysfigure}
-% \includegraphics[width=20pc]{figsamp}
-% \caption{caption here}
-% \label{newfig}
-% \end{sidewaysfigure}
-% 
-%  \begin{sidewaystable}
-%  \caption{Caption here}
-% \label{tab:signif_gap_clos}
-%  \begin{tabular}{ccc}
-% one&two&three\\
-% four&five&six
-%  \end{tabular}
-%  \end{sidewaystable}
-
-%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
-%\begin{linenomath*}
-%\begin{equation}
-%y|{f} {\sim} g(m, \sigma),
-%\end{equation}
-%\end{linenomath*}
-
-%%% End of body of article
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional Appendix goes here
-%
-% The \appendix command resets counters and redefines section heads
-%
-% After typing \appendix
-%
-%\section{Here Is Appendix Title}
-% will show
-% A: Here Is Appendix Title
-%
-%\appendix
-%\section{Here is a sample appendix}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Optional Glossary, Notation or Acronym section goes here:
-%
-%%%%%%%%%%%%%%  
-% Glossary is only allowed in Reviews of Geophysics
-%  \begin{glossary}
-%  \term{Term}
-%   Term Definition here
-%  \term{Term}
-%   Term Definition here
-%  \term{Term}
-%   Term Definition here
-%  \end{glossary}
-
-%
-%%%%%%%%%%%%%%
-% Acronyms
-%   \begin{acronyms}
-%   \acro{Acronym}
-%   Definition here
-%   \acro{EMOS}
-%   Ensemble model output statistics 
-%   \acro{ECMWF}
-%   Centre for Medium-Range Weather Forecasts
-%   \end{acronyms}
-
-%
-%%%%%%%%%%%%%%
-% Notation 
-%   \begin{notation}
-%   \notation{$a+b$} Notation Definition here
-%   \notation{$e=mc^2$} 
-%   Equation in German-born physicist Albert Einstein's theory of special
-%  relativity that showed that the increased relativistic mass ($m$) of a
-%  body comes from the energy of motion of the body—that is, its kinetic
-%  energy ($E$)—divided by the speed of light squared ($c^2$).
-%   \end{notation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  ACKNOWLEDGMENTS
-%
-% The acknowledgments must list:
-%
-% •	All funding sources related to this work from all authors
-%
-% •	Any real or perceived financial conflicts of interests for any
-%	author
-%
-% •	Other affiliations for any author that may be perceived as
-% 	having a conflict of interest with respect to the results of this
-% 	paper.
-%
-% •	A statement that indicates to the reader where the data
-% 	supporting the conclusions can be obtained (for example, in the
-% 	references, tables, supporting information, and other databases).
-%
-% It is also the appropriate place to thank colleagues and other contributors. 
-% AGU does not normally allow dedications.
-
-\acknowledgments
- = enter acknowledgments here =
-
-%% ------------------------------------------------------------------------ %%
-%% Citations
-
-% Please use ONLY \citet and \citep for reference citations.
-% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).
-
-%% Example \citet and \citep:
-%  ...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
-%  \citet{Ghel00}, and \citet{Leit74}.
-
-%  ...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
-%  \citep{Ghel00, Leit74}.
-
-%  ...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.
-
-%%  REFERENCE LIST AND TEXT CITATIONS
-%
-% Either type in your references using
-%
-% \begin{thebibliography}{}
-% \bibitem[{\textit{Kobayashi et~al.}}(2003)]{R2013} Kobayashi, T.,
-% Tran, A.~H., Nishijo, H., Ono, T., and Matsumoto, G.  (2003).
-% Contribution of hippocampal place cell activity to learning and
-% formation of goal-directed navigation in rats. \textit{Neuroscience}
-% 117, 1025--1035.
-%
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\bibitem[{\textit{Aagaard et~al.}(2009)\textit{Aagaard, Williams, Knepley,
-  Kientz, and Strand}}]{Aagaard2009}
-Aagaard, B., C.~Williams, M.~Knepley, S.~Kientz, and L.~Strand (2009),
-  {PyLith}.
+\bibitem[{\textit{Aagaard et~al.}(2013)\textit{Aagaard, Knepley, Williams}}]{Aagaard2013}
+Aagaard, B.~T., M.~G. Knepley, and C.~A. Williams (2013). {A domain decomposition approach to implementing
+fault slip in finite-element models of quasi-static and dynamic crustal deformation}, \textit{Journal of Geophysical
+Research: Solid Earth}, \textit{118}, \doi{10.1002/jgrb.50217}.
 
@@
   {Interseismic strain accumulation and anthropogenic motion in metropolitan
-  Los Angeles}, \textit{Journal of Geophysical Research B: Solid Earth},
+  Los Angeles}, \textit{Journal of Geophysical Research: Solid Earth},
   \textit{110}(4), 1--26, \doi{10.1029/2003JB002934}.
+
+\bibitem[{\textit{Aster et~al.}(2011)\textit{Aster, Borchers, and
+  Thurber}}]{Aster2011}
+Aster, R.~C., B.~Borchers, and C.~H. Thurber (2011), {Parameter
+  Estimation and Inverse Problems}, vol. 90, Academic Press.
 
@@
   \doi{10.1130/G33522.1}.
+
+\bibitem[{\textit{Cavali{\'{e}} et~al.}(2007)\textit{Cavali{\'{e}}, Doin,
+  Lasserre, and Briole}}]{Cavalie2007}
+Cavali{\'{e}}, O., M.~P. Doin, C.~Lasserre, and P.~Briole (2007), {Ground
+  motion measurement in the Lake Mead area, Nevada, by differential synthetic
+  aperture radar interferometry time series analysis: Probing the lithosphere
+  rheological structure}, \textit{Journal of Geophysical Research: Solid
+  Earth}, \textit{112}(3), 1--18, \doi{10.1029/2006JB004344}.
 

### 2016-04-21 JGRSubmission/agujournaltemplate.tex
commit before push

@@
 \begin{abstract}
-Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after ${\sim}3$ years at epicentral distances greater than ${\sim}200$ km.
+Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about three years at epicentral distances greater than ${\sim}200$ km.
 At closer distances, the rapid transience decays to a sustained rate which exceeds its pre-earthquake trend.
@@
 The inference of these rheologic parameters is a computationally expensive non-linear inverse problem which is typically approached with a forward modelling grid search method.
-Consequently, a simplified structure for the lithosphere must be assumed in order to minimize the number of rheologic parameters that need to be estimated.
-For example, it is commonly assumed that the lithosphere consists of only three homogeneous, Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep{Riva2009,Hines2013}.
+Consequently, a simplified structure for the Earth must be assumed in order to minimize the number of rheologic parameters that need to be estimated.
+For example, it is commonly assumed that the lower crust and upper mantle are homogeneous, Maxwell viscoelastic layers, which may be too simplistic for postseismic studies  \citep{Riva2009,Hines2013}.
 To further reduce the dimensions of the model space, it is also necessary to make simplifying assumptions about the nature of afterslip.
@@
 
-In this study, we assume that both afterslip and viscoelastic relaxation can contribute to postseismic deformation.
-Modelling both of these mechanisms creates a high dimensional model space that must be searched with non-linear optimization methods.
-We first develop an initial postseismic model using the method described in \citet{Hines2016}.
-This method simultaneously estimates the afterslip and effective lithospheric viscosity structure necessary to describe early postseismic deformation.
+In this study, we perform a kinematic inversion for fault slip, allowing it to persist throughout the postseismic period, while simultaneously estimating the viscosity of the lower crust and upper mantle.
+we use the method described in \citet{Hines2016} to create an initial model of the fault slip and effective viscosity necessary to describe the early postseismic deformation.
 Our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the 5 years of postseismic data available to date.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on a fault segment running through the Sierra Cucapah, a Zener rheology in the upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
+We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah, a Zener rheology in the upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
 
@@
 The fault geometry used in this study is shown in cyan where dashed lines indicate buried edges of the fault segments.
-The green and red boxes demarcate the extent of the near-field and far-field maps (figures \ref{fig:NearField} and \ref{fig:FarField}).
-Stations within the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in the record sections in Figures \ref{fig:RecordSectionElastic}, \ref{fig:RecordSection1}, and \ref{fig:RecordSection2}}.
+The green and red boxes demarcate the extent of the near-field and far-field maps (Figures \ref{fig:NearField} and \ref{fig:FarField}).
+Stations within the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in Figures \ref{fig:RecordSectionElastic}, \ref{fig:RecordSection1}, and \ref{fig:RecordSection2}}.
 \label{fig:ContextMap}
@@
 We collectively describe the coseismic and postseismic displacements resulting from the El Mayor-Cucapah earthquake as $u_\mathrm{post}(t)$.
-We consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.3 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
+We consider the GPS position time series $u_\mathrm{obs}(t)$ to be the combination of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
+The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.4 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
 We treat the displacements resulting from the Brawley swarm as a single event because the daily solutions provided by UNAVCO cannot resolve the separate events.
-Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation, and we model displacements resulting from these events with only a Heaviside function, $H(t)$, describing the coseismic offsets.
+Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation.
+We model displacements resulting from these events with only a Heaviside function, $H(t)$, describing the coseismic offsets.
 We then model $u_\mathrm{obs}(t)$ as
@@
 We initiate the Kalman filter by assuming a prior estimate of $\mathbf{X}(t)$ at the first time epoch, denoted $\mathbf{X}_{1|0}$, which has a sufficiently large covariance, denoted $\mathbf{\Sigma}_{1|0}$, to effectively make our prior uninformed.
-For each time epoch, $t_i$, Bayesian linear regression is used to incorporate GPS derived estimates of displacement with our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a posterior estimate of the state, $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
-
+For each time epoch $t_i$, Bayesian linear regression is used to incorporate GPS derived estimates of displacement with our prior estimate of the state $\mathbf{X}_{i|i-1}$ to form a posterior estimate of the state $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
 We then use the posterior estimate of the state at time $t_i$ to form a prior estimate of the state at time $t_{i+1}$ through the transition function
 \begin{equation}\label{predict}
-  \mathbf{X}_{i+1|i} = \mathbf{F}_{i+1}\mathbf{X}_{i|i} + \mathbf{\delta}_{i+1} 
+  \mathbf{X}_{i+1|i} = \mathbf{F}_{i+1}\mathbf{X}_{i|i} + \mathbf{\delta}_{i+1}, 
 \end{equation}
@@
 \end{equation}
-
 The covariance of the new prior state, $\mathbf{X}_{i+1|i}$, is then described by
@@
 \end{equation}
-
 This process is repeated for each of the $N$ time epochs at which point we use Rauch-Tung-Striebel smoothing \citep{Rauch1965} to find $\mathbf{X}_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates GPS observation for all $N$ time epochs.
@@
 We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (Figure \ref{fig:P496}).
-By down sampling, we implicitly assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
+We assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
 \citet{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicentre, we also clearly see far reaching postseismic transient deformation (Figure \ref{fig:P619}).
@@
 We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the time intervals 0-1 years, 1-3 years, and 3-5 years, as well as the coseismic displacements.
-Stations at epicentral distances ranging from ${\sim}200$ km to as far as ${\sim}400$ km have an elevated rate of deformation for the first 3 years following the earthquake.
+Stations at epicentral distances beyond ${\sim}200$ km have an elevated rate of deformation for the first three years following the earthquake.
 This far-field deformation has a southward trend along the direction of the El Mayor-Cucapah P axis and a similar eastward trend can be seen in the few far-field stations in Arizona, located along the T axis.
-After 3 years, the trend in far-field postseismic deformation is barely perceptible.
-The vertical deformation in the far-field is difficult to attribute to postseismic processes.
+After three years, the trend in far-field postseismic deformation is barely perceptible.
 Most far-field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
@@
 The near-field postseismic deformation is notably sustained when compared to the far-field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicentre, P496, has been moving at a steady rate of ${\sim}1.5$ cm/yr to the south since ${\sim}1$ year after the El Mayor-Cucapah earthquake.
-Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from tectonic processes.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicentre, P496, has been moving at a steady rate of ${\sim}1.5$ cm/yr to the south since about one year after the El Mayor-Cucapah earthquake.
+Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from postseismic processes.
 However, the vertical postseismic signal is only apparent for the first year after the earthquake (Figure \ref{fig:NearField}).
-As with the far-field deformation, there is a general trend of uplift in the near-field after ${\sim}1$ year, which we do not consider to be related to postseismic processes.
+As with the far-field deformation, there is a general trend of uplift in the near-field after about one year.
 
@@
 \end{table}
-In this paper, we seek to find the mechanisms driving 5 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We consider afterslip and viscoelastic relaxation in the lithosphere and asthenosphere as candidate mechanisms.
+We seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake and we consider afterslip and viscoelastic relaxation as candidate mechanisms.
 Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} found that poroelastic rebound is unlikely to be a significant contributor to postseismic deformation following the El Mayor-Cucapah earthquake.
@@
 The simplest rheologic model is to consider them to be effectively elastic and isotropic.
-In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011}, which are listed in Table \ref{tab:MaterialProperties}, throughout this paper.
+In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011} throughout this paper (Table \ref{tab:MaterialProperties}).
 The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.
-Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that 3 years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
+Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that three years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
 We also perform an elastic slip inversion, but we use GPS stations within a larger radius about the El Mayor-Cucapah epicentre (400 km instead of ${\sim}200$ km).
-Our forward problem describing predicted postseismic deformation, $u_\mathrm{pred}$, in terms of time dependent fault slip, $s$, is
+Our forward problem describing predicted postseismic deformation $u_\mathrm{pred}$ in terms of time dependent fault slip, $s$, is
 \begin{equation}\label{eq:ElasticForward}
-  u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi 
-\end{equation}           
-where $g(x,\xi)$ is elastic Green's function describing displacement at surface position $x$ resulting from a unit of slip at $\xi$ on the fault, which is denoted by $F$.
+  u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi, 
+\end{equation}           
+where $F$ denotes the fault and $g(x,\xi)$ is the elastic Green's function describing displacement at surface position $x$ resulting from slip at $\xi$ on the fault.
 We estimate coseismic slip and the rate of afterslip at the discrete time intervals, 0.0-0.125, 0.125-0.25, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
@@
 We impose that the direction of slip and slip rate are within 45$^\circ$ of right-lateral.
-We also add zeroth order Tikhonov regularization so that our solution for $s$ satisfies
+We also add zeroth-order Tikhonov regularization so that our solution for $s$ satisfies
 \begin{equation}\label{eq:ElasticObjective}
   \min_s \left(\left|\left|\frac{u_\mathrm{pred}(s) - u_\mathrm{post}}                
-                                {\sigma_\mathrm{obs}}\right|\right|_2^2 + 
-                                \lambda_s||s||_2^2\right). 
-\end{equation}
-The penalty parameters, $\lambda_s$, is chosen with a trade-off curve.
-We use Pylith \citep{Aagaard2013} to compute the Green's functions for this inversion, as well as for the remaining inversions in this paper.
+                                {\sigma_\mathrm{post}}\right|\right|_2^2 + 
+                                \lambda_s||s||_2^2\right),
+\end{equation}
+where $\sigma_\mathrm{post}$ is the uncertainty on postseismic displacements and $\lambda_s$ is a penalty parameter which is chosen with a trade-off curve.
+We use Pylith \citep{Aagaard2013} to compute the Green's functions for this inversion as well as for the remaining inversions in this paper.
 
@@
 The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPa.
-The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
+The potency of our inferred cumulative five years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
 Figure \ref{fig:RecordSectionElastic} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P axis.
 We show the radial component of displacements with respect to the El Mayor-Cucapah epicentre and we also rescale the displacements so that the difference between the minimum and maximum observed displacements are the same for each station.
-Our elastic slip model accurately describes near-field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than ${\sim}150$ km from the El Mayor-Cucapah epicentre.
+Our elastic slip model accurately describes near-field postseismic deformation and systematically underestimates postseismic deformation at epicentral distances ${\gtrsim}150$ km.
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
-Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next section.
+Because an elastic model requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next section.
 
@@
 \includegraphics[scale=0.8]{Figures/RecordSectionElastic}
-\caption{Scaled record section for the radial component of observed postseismic displacements, $u_\mathrm{obs}$ (black) and displacements predicted by an elastic model, $u_\mathrm{pred}$ (blue).
+\caption{Scaled radial component of observed postseismic displacements $u_\mathrm{obs}$ (black) and displacements predicted by the best fitting elastic model $u_\mathrm{pred}$ (blue).
 Downward motion indicates that the station is moving toward the El Mayor-Cucapah epicentre.
 Displacement time series are scaled so that the minimum and maximum observed values lie on the grid lines.
-The standard deviation of observed displacements are shown in gray.}
+The 68\% confidence interval for the observed displacements are shown in gray.}
 \label{fig:RecordSectionElastic}
@@
 Schematic representations of the viscoelastic rheologic models considered in this study are shown in Figure \ref{fig:Rheology}.
-We consider Maxwell viscoelasticity, where the steady-state viscosity, $\eta_M$, is unknown, Zener viscoelasticty, where the transient viscosity, $\eta_K$, and transient shear modulus, $\mu_K$, are unknown, and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all unknown.
-We further discuss these rheologic models and their use in geophysical studies in Section \ref{Discussion}.
+We discuss these rheologic models and their use in geophysical studies in Section \ref{Discussion}.
 
@@
 \centering 
-\caption{Schematic illustration of rheologic models considered in this paper as well as their initial effection viscosities, $\eta_\mathrm{eff}=\frac{\sigma}{\dot\epsilon}|_{t=0}$.}
+\caption{Schematic illustration of rheologic models considered in this paper as well as their effective viscosities.}
 \label{fig:Rheology}
@@
 \end{equation}
-where $\sigma$ is an applied stress at $t=0$ and $\dot\epsilon$ is the resulting strain rate.
+where $\sigma$ is an applied stress at $t=0$ and $\dot\varepsilon$ is the resulting strain rate.
 Figure \ref{fig:Rheology} shows how $\eta_\mathrm{eff}$ relates to the parameters for various linear viscoelastic rheologies.
@@
 Additionally, we note that when simultaneously estimating both afterslip and viscosity in the lower crust, the inverse problem becomes particularly ill-posed.
-This ill-posedness is illustrated in Figure (\ref{fig:LowerCrust}), which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from subsequent viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+This ill-posedness is illustrated in Figure \ref{fig:LowerCrust}, which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from subsequent viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
 In this demonstration, the viscoelastic relaxation is entirely driven by the fault slip in the lower crust.
@@
 We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
-This is not to say that we do not believe deep afterslip to be a possibility, rather we restrict slip to seismogenic depths as a modelling necessity.
+This is not to say that we do not believe deep afterslip to be a possibility; rather, we restrict slip to seismogenic depths as a modelling necessity.
 Although, it has been noted that the pattern of vertical postseismic deformation following the El Mayor-Cucpah earthquake indicates that a significant amount of afterslip must be shallow \citep{Rollins2015}.
@@
 \includegraphics[scale=0.8]{Figures/Cancellation}
-\caption{Displacements resulting from fault slip at lower crustal depths (left), and initial velocities resulting from subsequent relaxation of a viscoelastic lower crust (right).
-The fault segment dips $75^\circ$ to the north east and its surface projection is outlined in green.
+\caption{Displacements resulting from fault slip at lower crustal depths (a), and initial velocities resulting from subsequent relaxation of a viscoelastic lower crust (b).
+The fault segment dips $75^\circ$ to the north-east and its surface projection is outlined in magenta.
 The highlighted area on the fault extends from 15 to 30 km depth and indicates where 1 meter of right-lateral slip was imposed.
@@
 
-The first step in our inverse method is to determine at which point the early postseismic approximation breaks down, which we will denote as $t_{\mathrm{bd}}$.
-As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
+We must determine at which point the early postseismic approximation breaks down, which we will denote as $t_{\mathrm{bd}}$.
+As noted, eq.
+(\ref{ApproxForward}) is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
 We can almost certainly assume that deformation at the most far-field stations, which are ${\sim}400$ km away from the El Mayor-Cucapah epicentre, is the result of viscoelastic relaxation.
 The approximation should then be valid for as long as a linear trend adequately approximates the far-field deformation.
-Using this logic, it would appear that $t_{\mathrm{bd}}\approx1$ year after the El Mayor-Cucapah earthquake.
+Using this logic, it would appear that $t_{\mathrm{bd}}$ is about one year after the El Mayor-Cucapah earthquake.
 Another way to determine $t_{\mathrm{bd}}$ is to find the best fitting prediction of eq.
@@
 When using eq.
-(\ref{ApproxForward}) to fit the entire 5 years of postseismic displacements, we see that the near-field displacements (e.g., station P501) are accurately predicted but when looking at displacement in the far-field (e.g., station P621) we see that eq.
+(\ref{ApproxForward}) to fit the entire five years of postseismic displacements, we see that the near-field displacements (e.g., station P501) are accurately predicted but when looking at displacement in the far-field (e.g., station P621) we see that eq.
 (\ref{ApproxForward}) overestimates the rate of deformation in the later postseismic period and underestimates the rate of deformation in the early period (Figure \ref{fig:RecordSection1}).
@@
  \mathrm{min}_{s,\eta_\mathrm{eff}} \left(\left|\left|
- \frac{u_\mathrm{pred}(s,\eta_\mathrm{eff}) - u_\mathrm{obs}}
- {\mathbf{\sigma_\mathrm{obs}}}\right|\right|_2^2 + 
+ \frac{u_\mathrm{pred}(s,\eta_\mathrm{eff}) - u_\mathrm{post}}
+ {\mathbf{\sigma_\mathrm{post}}}\right|\right|_2^2 + 
  \lambda_s||s||_2^2 + 
- \lambda_\eta||\nabla \eta_{\mathrm{eff}}^{-1}||_2^2\right)
-\end{equation} 
-where $u_\mathrm{obs}$ consists of the first 0.8 years of postseismic deformation and $u_\mathrm{pred}$ are the predicted displacements from eq.
+ \lambda_\eta||\nabla \eta_{\mathrm{eff}}^{-1}||_2^2\right),
+\end{equation} 
+where $u_\mathrm{post}$ consists of the first 0.8 years of postseismic deformation and $u_\mathrm{pred}$ are the predicted displacements from eq.
 (\ref{ApproxForward}).
-Due to inherent non uniqueness, we have added zeroth-order Tikhonov regularization to estimates of $s$, and second-order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^{-1}$.
-The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$.
-The penalty parameters are chosen with two trade-off curves.
-We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then we determine $\lambda_\eta$ with $\lambda_s$ fixed at its chosen value.
-Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full 5 years, which we do in Section \ref{sec:FullInversion}.
+Due to inherent non-uniqueness, we have added zeroth-order Tikhonov regularization to estimates of $s$, and second-order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^{-1}$.
+The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$, which are chosen with trade-off curves.
+Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in Section \ref{sec:FullInversion}.
 Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
@@
 (\ref{InitialRate}) is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each layer.
-We also show 95\% confidence intervals for estimated viscosities and fluidities but we note that the uncertainties tend to be underestimated due to the added regularization \citep{Aster2011}.
-Although, we do believe that the relative uncertainty between layers is accurately depicted.
+We also show the 95\% confidence intervals for estimated viscosities and fluidities but we note that the uncertainties tend to be underestimated due to the added regularization \citep{Aster2011}.
 A robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
-This transitional depth is also consistent with the the viscosity structure required to explain far field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
+This transitional depth is also consistent with the the viscosity structure required to explain far-field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
 We find that the viscosity below 60 km depth needs to be ${\sim}1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
@@
 Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in Figure \ref{fig:InitialSlip}.
-Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, coseismic slip is inferred to be in the Sierra Cucapah and it is right lateral with a significant normal component.
-This is consistent with field studies \citep{Fletcher2014}, as well as the coseismic slip from \citet{Wei2011}.
+Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, a significant amount of right-lateral and normal coseismic slip is inferred to be on the Sierra Cucapah fault segment and in a region that is consistent with field studies \citep{Fletcher2014} and the coseismic slip from \citet{Wei2011}.
 The potency of inferred coseismic slip is $3.3\times 10^{9}\ \mathrm{m}^3$, which is also about the same as that inferred from Section \ref{sec:ElasticInversion}.
 The present inference of afterslip on the Indiviso fault is significantly less than what was found in the Section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
-When fault slip is simultaneously estimated with a lithospheric and asthenospheric viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.46\times10^{9}\ \mathrm{m}^3$ when we assume the lithosphere and asthenosphere are elastic.
+When fault slip is simultaneously estimated with a lithospheric and asthenospheric viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.46\times10^{9}\ \mathrm{m}^3$ when we assume crust and upper mantle are elastic.
 The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodelled viscoelastic relaxation at depths greater than $60$ km.
@@
 In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
-In this section, we use these effective viscosities as a prior constraint when searching for models which are capable of describing the available 5 years of postseismic data, where our forward problem is now eq.
+In this section, we use these effective viscosities as a prior constraint when searching for models which are capable of describing the available five years of postseismic data, where our forward problem is now eq.
 (\ref{GeneralForward}) rather than the approximation given by eq.
@@
 For comparison, $\bar\chi^2=35.3$ for the elastic model from Section \ref{sec:ElasticInversion}.
-The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years (Figure \ref{fig:RecordSection2}).
+The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about three years (Figure \ref{fig:RecordSection2}).
 Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle.
@@
 The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSection2}).
-The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the 5 years.
+The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the five years.
 
@@
 
-Because we are able to adequately describe the available 5 years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
+Because we are able to adequately describe the available five years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
+However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of five years, would also be able to satisfactorily describe the observable postseismic deformation.
 
@@
 
-The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of 5 years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
+The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of five years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
 Most of the afterslip in our preferred model occurs within the first year after the earthquake with a significant amount inferred to be shallow and in the Sierra Cucapah.
@@
 Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}, which is the simplest viscoelastic rheologic model.
-In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities $\gtrsim 10^{19}$ Pa s.
+In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lower crust and upper mantle and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities $\gtrsim 10^{19}$ Pa s.
 These postseismic studies are consistent with \citet{Kaufmann2000} and \citet{Cavalie2007}, who found that an upper mantle viscosity of $10^{18}$ Pa s and a crustal viscosity $\gtrsim10^{20}$ Pa s are necessary to describe subsidence resulting from changes in loading from Lake Mead.
@@
 We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of ${\sim}10^{18}$ Pa s in the mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
-Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over 5 years, would also be able to describe the postseismic deformation.
+Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over five years, would also be able to describe the postseismic deformation.
 Such a Burgers model might then be consistent with the steady state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.
@@
 We have treated postseismic deformation as a stochastic process where we did not presume any characteristic shape of the postseismic time series.
-We can observe transient postseismic deformation at distances of ${\sim}400$ km from the El Mayor-Cucapah epicenter which is largely undetectable after about 3 years.
+We can observe transient postseismic deformation at distances of ${\sim}400$ km from the El Mayor-Cucapah epicenter which is largely undetectable after about three years.
 Near-field deformation exhibits transience that decays to a sustained, elevated rate after about 1 to 2 year.
@@
 Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km.
-Beneath that depth, a transient viscosity of ${\sim}10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the 5 years considered in this study.
+Beneath that depth, a transient viscosity of ${\sim}10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the five years considered in this study.
 By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.

### 2016-04-22 JGRSubmission/ElMayor.tex
commit before push;

--- 2016-04-09 RoughDraft/ElMayor.tex
@@
-\documentclass[review]{elsarticle}
+\documentclass[draft,linenumbers]{AGUJournal}
+\draftfalse
+\usepackage{amssymb,amsmath,amsthm,amsfonts}
+%% For final version.
+% \documentclass{AGUJournal}
 
-\usepackage{amssymb,amsmath,amsthm,amsfonts}
-%\usepackage[margin=1.0in]{geometry}
-%\usepackage{fancyhdr} % required for custom header
-%\usepackage{graphicx}
-%\usepackage{listings}
-%\usepackage{courier}
-%\usepackage[usenames,dvipsnames]{color}
-\usepackage[maxfloats=40]{morefloats}
-%\usepackage{caption}
-%\usepackage{subcaption}
-%\usepackage{natbib}
-%\usepackage{setspace}
-%\doublespacing
-
-%set up the header
-%\pagestyle{fancy}
-%\lhead{Trever Hines}
-%\chead{El Mayor Postseismic}
-%\rhead{\today}
-
-%\setlength{\headheight}{15pt}
-%\renewcommand\headrulewidth{1.0pt} % Size of the header rule
-
-%% Title
-%%------------------------------------------------------------------------------
-\title{	
-Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
-\author{T. T. Hines\fnref{fn}}
-\author{E. A. Hetland\fnref{fn}}
-\fntext[fn]{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, MI, USA}
+\journalname{JGR-Solid Earth}
 
 \begin{document}
+
+\title{Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
+
+\authors{T. T. Hines\affil{1}, E. A. Hetland\affil{1}}
+
+\affiliation{1}{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, Michigan, USA.}
+
+\correspondingauthor{T. T. Hines}{hinest@umich.edu}
+
+%% Keypoints, final entry on title page.
+
+% Example: 
+% \begin{keypoints}
+% \item	List up to three key points (at least one is required)
+% \item	Key Points summarize the main points and conclusions of the article
+% \item	Each must be 100 characters or less with no special characters or punctuation 
+% \end{keypoints}
+
+%  List up to three key points (at least one is required)
+%  Key Points summarize the main points and conclusions of the article
+%  Each must be 100 characters or less with no special characters or punctuation
+
+\begin{keypoints}
+\item = enter point 1 here = 
+\item = enter point 2 here = 
+\item = enter point 3 here = 
+\end{keypoints}
+
 \begin{abstract}
+Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about three years at epicentral distances greater than ${\sim}200$ km.
+At closer distances, the rapid transience decays to a sustained rate which exceeds its pre-earthquake trend.
+We attempt to determine the mechanisms driving this deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
+We find that early, rapid, near-field deformation can be explained with afterslip on the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of ${\sim}10^{19}$ Pa s.
+The trend in far-field deformation is best explained with a transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle.
+We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay in postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
 \end{abstract}
-\maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Ground deformation in the years following a large ($\gtrsim$Mw7) earthquake provides insight into the mechanical behaviour of the crust and upper mantle.
+Ground deformation in the years following a large ($\gtrsim$Mw7) earthquake provides insight into the mechanical behavior of the crust and upper mantle.
 It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
-Thanks to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California produced observable postseismic deformation at more GPS stations than any other earthquake in California to date.
+Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date.
 With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake, where we consider both afterslip and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
 
-Previous studies which have modelled postseismic deformation following the El Mayor-Cucapah earthquake include \citet{Pollitz2012}, \citet{Gonzalez-ortega2014}, \citet{Spinler2015}, and \citet{Rollins2015}.
+Previous studies which have modeled postseismic deformation following the El Mayor-Cucapah earthquake include \citet{Pollitz2012}, \citet{Gonzalez-ortega2014}, \citet{Spinler2015}, and \citet{Rollins2015}.
 Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the postseismic deformation with afterslip in an elastic half-space.
-\citet{Gonzalez-ortega2014} described five months of postseismic deformation observed by near-field ($\lesssim$ 50 km from the rupture) campaign GPS and InSAR with afterslip and contraction on the coseismically ruptured fault.
-\citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodelled viscoelastic relaxation.
-Using continuous GPS stations, which are mostly north of rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of slip inferred on the least constrained, southern-most fault segment.
-Here, we suggest the afterslip inferred by \cite{Rollins2015} may have been acting as a proxy for distributed relaxation in the upper mantle.
+\citet{Gonzalez-ortega2014} described five months of postseismic deformation, observed by InSAR and GPS within ${\sim}50$ km of the rupture, with afterslip and contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
+Using only continuous GPS stations, which are mostly north of the rupture zone, \citet{Rollins2015} found that three years of postseismic deformation can be adequately explained by afterslip, albeit with an implausibly large amount of slip inferred on the least constrained, southern-most fault segment.
+Here, we suggest the afterslip inferred by \citet{Rollins2015} may have been acting as a proxy for distributed relaxation in the upper mantle.
 
 \citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential postseismic deformation mechanism.
-The rheology of the crust and mantle is largely unknown and so modelling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and then find the best fitting rheologic parameters.
-The inference of these rheologic parameters is a computationally expensive non-linear inverse problem which is typically approached with a forward modelling grid search method.
-Consequently, a simplified structure for the lithosphere must be made to minimize the number of rheologic parameters that need to be estimated.
-For example, it is commonly assumed that the lithosphere consists of only three homogeneous, Maxwell viscoelastic layers, which may be an inadequate representation of the lithosphere \citep[e.g.][]{Riva2009,Hines2013}.
-To further reduce the model space dimensions being search, it is also necessary to make simplifying assumptions about the nature of afterslip.
+The rheology of the crust and mantle is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and then find the best fitting rheologic parameters.
+The inference of these rheologic parameters is a computationally expensive non-linear inverse problem which is typically approached with a forward modeling grid search method.
+Consequently, a simplified structure for the Earth must be assumed in order to minimize the number of rheologic parameters that need to be estimated.
+For example, it is commonly assumed that the lower crust and upper mantle are homogeneous, Maxwell viscoelastic layers, which may be too simplistic for postseismic studies  \citep{Riva2009,Hines2013}.
+To further reduce the dimensions of the model space, it is also necessary to make simplifying assumptions about the nature of afterslip.
 For example, one can assume a frictional model for afterslip and parametrize afterslip in terms of the unknown rheologic properties of the fault \citep[e.g.][]{Johnson2009,Johnson2004}.
@@
 However, postseismic afterslip in similar tectonic settings has been observed to persist for decades following earthquakes \citep{Cakir2012,Cetin2014}.
-Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to a biased inference of lithospheric viscosity.
-Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates near-field deformation, which could be indicative of unmodelled continued afterslip.
+Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates deformation in the Imperial Valley, which could be indicative of unmodeled continued afterslip.
+Neglecting to allow for sustained afterslip as a postseismic mechanism could then lead to biased inferences of viscosities.
 
-In this study, we assume that both afterslip and viscoelastic relaxation can contribute to postseismic deformation.
-Modelling both of these mechanisms creates a high dimensional model space that must be searched with non-linear optimization methods.
-We first develop an initial postseismic model using the method described in \citet{Hines2015}.
-This method simultaneously estimate the afterslip and effective lithospheric viscosity structure necessary to describe the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We then use the inferred effective viscosity structure to create a suite of postseismic models which are tested against the available 5 years of postseismic data.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip beneath the Sierra Cucapah, a Zener rheology upper mantle with a transient viscosity that decays from $5\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
+In this study, we perform a kinematic inversion for fault slip, allowing it to persist throughout the postseismic period, while simultaneously estimating the viscosity of the lower crust and upper mantle.
+we use the method described in \citet{Hines2016} to create an initial model of the fault slip and effective viscosity necessary to describe early postseismic deformation, which has the richest signature of the underlying deformation mechanisms.
+Our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
+We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah, a Zener rheology in the upper mantle with a transient viscosity that decays from $6\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
 
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/ContextMap} 
-\caption{Map of the area where postseismic deformation following the El Mayor-Cucapah earthquake can be observed geodetically.
-The large focal mechanism is for the El Mayor Cucapah earthquake and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
+\includegraphics[scale=0.8]{Figures/ContextMap} 
+\caption{Map of the region considered in this study.
+The large focal mechanism is for the El Mayor-Cucapah earthquake, and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
 The black dots indicate the locations of GPS stations used in this study.
 The fault geometry used in this study is shown in cyan where dashed lines indicate buried edges of the fault segments.
-The green and red boxes denote the extent of the near and far-field displacement maps.
-The blue sector highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis and stations within this sector are used in the record Sections in Figures \ref{fig:RecordSection1} and \ref{fig:RecordSection2}}
+The green and red boxes demarcate the extent of the near-field and far-field maps (Figures \ref{fig:NearField} and \ref{fig:FarField}).
+Stations inside the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in Figures \ref{fig:RecordSectionElastic}, \ref{fig:RecordSection1}, and \ref{fig:RecordSection2}}.
 \label{fig:ContextMap}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data Processing}\label{sec:Data}
 
-We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicentre.
+We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicenter.
 We collectively describe the coseismic and postseismic displacements resulting from the El Mayor-Cucapah earthquake as $u_\mathrm{post}(t)$.
-We consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the superposition of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.3 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
-We treat the displacements resulting from the Brawley swarm as a single event because the time series are provided by UNAVCO as daily solutions.
-Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation and we model displacements resulting from these events with a Heaviside function, $H(t)$.
+We consider the GPS position time series $u_\mathrm{obs}(t)$ to be the combination of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
+The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.4 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
+We treat the displacements resulting from the Brawley swarm as a single event because the daily solutions provided by UNAVCO cannot resolve the separate events.
+Although the Ocotillo earthquake had its own series of aftershocks \citep{Hauksson2011}, neither the Ocotillo earthquake nor the Brawley swarm produced detectable postseismic deformation.
+We model displacements resulting from these events with only a Heaviside function, $H(t)$, describing the coseismic offsets.
 We then model $u_\mathrm{obs}(t)$ as
 \begin{equation}
-  u_\mathrm{obs}(t) = u_\mathrm{pred}(t) + \epsilon
+  u_\mathrm{obs}(t) = u_\mathrm{pred}(t) + \epsilon,
 \end{equation}
@@
 In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthquake, Ocotillo earthquake, and the Brawley swarm, respectively, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
-We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicentres.
+We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicenters.
 
 Stations which recorded displacements that clearly cannot be described by the aforementioned processes are not included in our analysis.
-This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Bawden2001,Argus2005} .
+This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Bawden2001,Argus2005}.
 In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015} and it is possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities.
-However, we use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
-We use displacements because estimating velocities from an already noisy displacement time series can introduce significant aleatoric and epistemic uncertainties depending on exactly how the estimation is done.
-This modelling choice prevents us from using the newly installed stations in Baja California for our analysis.
+Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015}.
+Although it would be possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities, we do not do so here.
+We use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
+We use displacements because estimating velocities from an already noisy displacement time series can introduce significant uncertainties depending on exactly how the estimation is done.
+This choice prevents us from using the newly installed stations in Baja California for our analysis.
 
-The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred about 270 km north of the El Mayor-Cucapah epicentre, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
-We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicentre are approximately constant \citep{Savage2009}.
-When appraising our model fit in Section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine epicentre, which may be the result of errors in the assumption that the trend in Hector Mine postseismic deformation is linear after six years.
+The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred ${\sim}270$ km north of the El Mayor-Cucapah epicenter, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
+When appraising our model fit in Section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine epicenter, which may be the result of errors in the assumption that the trend in Hector Mine postseismic deformation is linear after six years.
 
@@
 The smoothness of $u_\mathrm{post}(t)$ is controlled by the chosen value of $\sigma^2$, which describes how rapidly we expect postseismic displacements to vary over time.
-Setting $\sigma^2$ equal to zero will effectively result in modelling $u_\mathrm{post}(t)$ as a straight line which is insufficient to describe the expected transient behaviour in postseismic deformation.
+Setting $\sigma^2$ equal to zero will effectively result in modeling $u_\mathrm{post}(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation.
 The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ over fitting the data.
-While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we rather take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we instead take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
 We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (Figure \ref{fig:P496}).
-By down sampling, we implicitly assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
-\citet{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicentre, we also clearly see far reaching postseismic transient deformation (Figure \ref{fig:P619}).
+We assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
+\citet{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we also clearly see far reaching postseismic transient deformation (Figure \ref{fig:P619}).
 
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/FilterP496}
+\includegraphics[scale=0.8]{Figures/FilterP496}
 \centering
-\caption{}
+\caption{Left panels show GPS time series from UNAVCO (black) and the predicted displacement (blue) from eq.
+(\ref{TimeSeriesModel}) for a near-field station.
+Red lines indicate the times of the El Mayor-Cucapah and Ocotillo earthquake.
+The right panels show estimated coseismic and postseismic displacements $u_\mathrm{post}$ which are extracted from the predicted displacements.
+The 68\% confidence interval is shown in light blue.}
 \label{fig:P496}
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/FilterP619}
+\includegraphics[scale=0.8]{Figures/FilterP619}
 \centering
-\caption{} 
+\caption{same as Figure \ref{fig:P496} but for a far-field station.} 
 \label{fig:P619}
@@
 (\ref{TimeSeriesModel}).
-For example, we assume a constant rate of secular deformation, which appears to be an appropriate approximation for all but perhaps the stations closest to the Hector Mine epicentre, as noted above.
+For example, we assume a constant rate of secular deformation, which appears to be an appropriate approximation for all but perhaps the stations closest to the Hector Mine epicenter, as noted above.
 Also, our model for seasonal deformation in eq.
@@
 (\ref{TimeSeriesModel}) as stochastic variables \citep{Murray2005}.
-By using constant seasonal amplitudes our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodelled annual and semi-annual oscillations (e.g.
+By using constant seasonal amplitudes, our estimate of $u_\mathrm{post}(t)$ seems to describe some of the unmodeled annual and semi-annual oscillations (e.g.
 Figure \ref{fig:P619}).
 
-We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the intervals  0-0.8 years, 0.8-3.0 years, and 3.0-5.0 years, as well as the coseismic displacements.
-In the far-field to the north, we can see south trending displacements for the first 3.0 years following the earthquake at stations as far as $\sim$400 km from of the El Mayor Cucapah epicentre.
-These displacements are most pronounced along the direction of the El Mayor-Cucapah P axis.
-A similar eastward trend can be seen in the few far-field stations along the T axis in Arizona.
-After 3 years, the trend in far-field postseismic deformation is barely perceptible.
-The vertical deformation in the far-field is difficult to attribute to postseismic processes.
+We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the time intervals 0-1 years, 1-3 years, and 3-5 years, as well as the coseismic displacements.
+Stations at epicentral distances beyond ${\sim}200$ km have an elevated rate of deformation for the first three years following the earthquake.
+This far-field deformation has a southward trend along the direction of the El Mayor-Cucapah P axis and a similar eastward trend can be seen in the few far-field stations in Arizona, located along the T axis.
+After three years, the trend in far-field postseismic deformation is barely perceptible.
 Most far-field stations display an initial subsidence for the first year after the El Mayor-Cucapah earthquake followed by continued uplift.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/MapViewNearField}
+\includegraphics[scale=0.8]{Figures/MapViewNearField}
 \centering 
-\caption{}
+\caption{Near-field coseismic and cumulative postseismic displacements over the indicated time periods (black) as well as predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
+Observed vertical deformation is shown as an interpolated field and predicted vertical displacements are shown within the circles at the base of each vector.
+Note that the interpolant is not well constrained in Mexico where there is no data available.}
 \label{fig:NearField}
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/MapViewFarField}
+\includegraphics[scale=0.8]{Figures/MapViewFarField}
 \centering 
-\caption{}
+\caption{Same as Figure \ref{fig:NearField} but for far-field stations.}
 \label{fig:FarField}
@@
 The near-field postseismic deformation is notably sustained when compared to the far-field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicentre, P496, has been moving at a steady rate of $\sim1.5$ cm/yr to the south since $\sim1$ year after the El Mayor-Cucapah earthquake.
-Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from tectonic processes.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, has been moving at a steady rate of ${\sim}1.5$ cm/yr to the south since about one year after the El Mayor-Cucapah earthquake.
+Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from postseismic processes.
 However, the vertical postseismic signal is only apparent for the first year after the earthquake (Figure \ref{fig:NearField}).
-As with the far-field deformation, there is a general trend of uplift in the near-field after $\sim1$ year, which we do not consider to be related to postseismic processes.
+As with the far-field deformation, there is a general trend of uplift in the near-field after about one year.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Postseismic Modeling}\label{sec:Model}
@@
 depth (km) &$\lambda$ (GPa)&$\mu$ (GPa)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
-0-5 & 24.0 & 24.3 & - & -\\
-5-15 & 35.2 & 35.4 & - & -\\
-15-30 & 41.8 & 41.9 & 44.3 & 0.0\\
-30-60 & 61.0 & 60.8 & 5.91 & 0.375\\
-60-90 & 61.0 & 60.8 & 1.99 & 0.375\\
-90-120 & 61.0 & 60.8 & 1.31 & 0.375\\
-120-150 & 61.0 & 60.8 & 1.10 & 0.375\\
-150-$\infty$ & 61.0 & 60.8 & 1.07 & 0.375\\
+0-5 & 24.0 & 24.0 & - & -\\
+5-15 & 35.0 & 35.0 & - & -\\
+15-30 & 42.0 & 42.0 & 44.3 & 0.0\\
+30-60 & 61.0 & 61.0 & 5.91 & 0.375\\
+60-90 & 61.0 & 61.0 & 1.99 & 0.375\\
+90-120 & 61.0 & 61.0 & 1.31 & 0.375\\
+120-150 & 61.0 & 61.0 & 1.10 & 0.375\\
+150-$\infty$ & 61.0 & 61.0 & 1.07 & 0.375\\
 \end{tabular}
 \caption{Assumed and estimated material properties.
-$\lambda$, $\mu$, and $\rho$ are assumed known \textit{a priori}, $\eta_\mathrm{eff}$ is estimated in Section \ref{sec:InitialInversion} and $\mu_k/\mu$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology.}
+$\lambda$ and $\mu$ are assumed known \textit{a priori} and are based on the values used for the coseismic model by \citet{Wei2011}.
+The values for $\eta_\mathrm{eff}$ are estimated in Section \ref{sec:InitialInversion}, and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.}
 
 \end{table}
-In this paper, we seek to find the mechanisms driving 5 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We consider afterslip and viscoelastic relaxation in the lithosphere and asthenosphere as candidate mechanisms.
-Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} suggest that any contribution to postseismic deformation from poroelastic rebound would be negligible.
+We seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake and we consider afterslip and viscoelastic relaxation as candidate mechanisms.
+Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} found that poroelastic rebound is unlikely to be a significant contributor to postseismic deformation following the El Mayor-Cucapah earthquake.
 Furthermore, we consider stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{elastic inversion}\label{sec:ElasticInversion}    
+\subsection{Elastic Postseismic Inversion}\label{sec:ElasticInversion}    
 We consider a variety of rheologic models for the lower crust and upper mantle.
 The simplest rheologic model is to consider them to be effectively elastic and isotropic.
-In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the values listed in Table \ref{tab:MaterialProperties} throughout this paper.
+In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011} throughout this paper (Table \ref{tab:MaterialProperties}).
 The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.
-Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane and they did not require any viscoelastic relaxation to describe the observations.
-We also perform an elastic slip inversion but we use GPS stations within a larger radius about the El Mayor-Cucapah epicentre (400 km instead of $\sim$200 km).
-Our forward problem describing predicted postseismic deformation, $u_\mathrm{pred}$, in terms of time dependent fault slip, $s$, is
+Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that three years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
+We also perform an elastic slip inversion, but we use GPS stations within a larger radius about the El Mayor-Cucapah epicenter (400 km instead of ${\sim}200$ km).
+Our forward problem describing predicted postseismic deformation $u_\mathrm{pred}$ in terms of time dependent fault slip, $s$, is
 \begin{equation}\label{eq:ElasticForward}
-  u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi 
+  u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi, 
 \end{equation}           
-where $g(x,\xi)$ is elastic Green's function describing displacement at surface position $x$ resulting from a unit of slip at $\xi$ on the fault, which is denoted by $F$.
+where $F$ denotes the fault and $g(x,\xi)$ is the elastic Green's function describing displacement at surface position $x$ resulting from slip at $\xi$ on the fault.
 We estimate coseismic slip and the rate of afterslip at the discrete time intervals, 0.0-0.125, 0.125-0.25, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
@@
 We impose that the direction of slip and slip rate are within 45$^\circ$ of right-lateral.
-We also add zeroth order Tikhonov regularization so that our solution for $s$ satisfies
+We also add zeroth-order Tikhonov regularization so that our solution for $s$ satisfies
 \begin{equation}\label{eq:ElasticObjective}
   \min_s \left(\left|\left|\frac{u_\mathrm{pred}(s) - u_\mathrm{post}}                
-                                {\sigma_\mathrm{obs}}\right|\right|_2^2 + 
-                                \lambda_s||s||_2^2\right). 
+                                {\sigma_\mathrm{post}}\right|\right|_2^2 + 
+                                \lambda_s||s||_2^2\right),
 \end{equation}
-The penalty parameters, $\lambda_s$, is chosen with a trade-off curve.
+where $\sigma_\mathrm{post}$ is the uncertainty on postseismic displacements and $\lambda_s$ is a penalty parameter which is chosen with a trade-off curve.
+We use Pylith \citep{Aagaard2013} to compute the Green's functions for this inversion as well as for the remaining inversions in this paper.
 
@@
 The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPa.
-The potency of our inferred cumulative 5 years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to the result of relaxation of coseismicly induced stresses.
-Our slip model accurately describes near field postseismic deformation, while it systematically underestimates postseismic deformation for stations further than $\sim150$ km from the El Mayor-Cucapah epicentre (Figure \ref{fig:RecordSectionElastic}).
+The potency of our inferred cumulative five years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
+Figure \ref{fig:RecordSectionElastic} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P axis.
+We show the radial component of displacements with respect to the El Mayor-Cucapah epicenter and we also rescale the displacements so that the difference between the minimum and maximum observed displacements are the same for each station.
+Our elastic slip model accurately describes near-field postseismic deformation and systematically underestimates postseismic deformation at epicentral distances ${\gtrsim}150$ km.
 When the fault segments used in the inversion are extended down to 30 km depth, rather than 15 km, the systematic far-field residuals are smaller but remain apparent.
-Because an elastic model for the lithosphere requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next Section.
+Because an elastic model requires an unrealistic amount of afterslip and is unable to predict far-field deformation, we move on to consider viscoelastic models in the next section.
 
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/ElasticSlip}
-\caption{}
+\includegraphics[scale=0.8]{Figures/ElasticSlip}
+\caption{Coseismic slip and cumulative afterslip over the indicated intervals for the elastic model from Section \ref{sec:ElasticInversion}.
+Color indicates the magnitude of slip while arrows indicate the motion of the hanging wall.}
 \label{fig:ElasticSlip}
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/RecordSectionElastic}
-\caption{}
+\includegraphics[scale=0.8]{Figures/RecordSectionElastic}
+\caption{Scaled radial component of observed postseismic displacements $u_\mathrm{obs}$ (black) and displacements predicted by the best fitting elastic model $u_\mathrm{pred}$ (blue).
+Downward motion indicates that the station is moving toward the El Mayor-Cucapah epicenter.
+Displacement time series are scaled so that the minimum and maximum observed values lie on the grid lines.
+The 68\% confidence interval for the observed displacements are shown in gray.}
 \label{fig:RecordSectionElastic}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{constraints on effective viscosity}\label{sec:InitialInversion}
+\subsection{Early Postseismic Inversion}\label{sec:InitialInversion}
 
@@
   u_\mathrm{pred}(x,t) = \int_F s(\xi,t)g(x,\xi)d\xi + 
-           \int_0^t\int_F s(\xi,\tau) f(t-\tau,x,\xi) d\xi d\tau
+           \int_0^t\int_F s(\xi,\tau) f(t-\tau,x,\xi) d\xi d\tau,
 \end{equation}
@@
 Schematic representations of the viscoelastic rheologic models considered in this study are shown in Figure \ref{fig:Rheology}.
-We consider Maxwell viscoelasticity, where the steady-state viscosity, $\eta_M$, is unknown, Zener viscoelasticty, where the transient viscosity, $\eta_K$, and transient shear modulus, $\mu_K$, are unknown, and Burgers viscoelasticity, where $\eta_M$, $\eta_K$, and $\mu_K$, are all unknown.
-We further discuss these rheologic models and their use in geophysical studies in the discussion.
+We discuss these rheologic models and their use in geophysical studies in Section \ref{Discussion}.
 
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/rheology}
+\includegraphics[scale=0.8]{Figures/rheology}
 \centering 
-\caption{}
+\caption{Schematic illustration of the rheologic models considered in this paper as well as their effective viscosities.}
 \label{fig:Rheology}
@@
 
-In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2015} to constrain an initial effective lithospheric viscosity structure from the early postseismic deformation.
-The method relies upon the fact that immediately after an earthquake, stresses throughout the crust and mantle are only controlled by the relatively well known instantaneous elastic properties and each parcel will have a strain rate, $\dot\epsilon$, that is proportional to stress, $\sigma$, and inversely proportional to the parcel's effective viscosity, $\eta_{\mathrm{eff}}=\frac{\sigma}{\dot{\epsilon}}|_{t=0}$.
-Through linear superposition, we can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from each parcel, scaled by the reciprocal of the parcel's effective viscosity.
+In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2016} to constrain an initial effective viscosity structure from the early postseismic deformation.
+Our method utilizes the fact that coseismic stresses throughout the crust and upper mantle depend on the instantaneous elastic parameters and are independent of the viscoelastic parameters which we wish to estimate.
+Immediately following an earthquake, each parcel will have a strain rate that is proportional to the coseismic stress and inversely proportional to the parcel's effective viscosity,
+$\eta_\mathrm{eff}$.  Using one-dimensional viscoelastic models, we define the effective viscosity as
+\begin{equation}
+  \eta_\mathrm{eff} = \left.\frac{\sigma}{\dot{\varepsilon}}\right|_{t=0},
+\end{equation}
+where $\sigma$ is an applied stress at $t=0$ and $\dot\varepsilon$ is the resulting strain rate.
+Figure \ref{fig:Rheology} shows how $\eta_\mathrm{eff}$ relates to the parameters for various linear viscoelastic rheologies.
+We can deduce that the initial rate of surface deformation resulting from viscoelastic relaxation is a summation of the surface deformation resulting from relaxation in each parcel, scaled by the reciprocal of the parcel's effective viscosity.
 That is to say
@@
 Although eq.
-(\ref{ApproxForward}) may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are only functions of the fault geometry and instantaneous elastic properties, $\lambda$ and $\mu$, and so $g$ and $h$ can be computed numerically as a preprocessing step and the forward problem in eq.
-(\ref{ApproxForward}) can be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
+(\ref{ApproxForward}) may only be valid for a short portion of the postseismic period, its utility becomes apparent when noting that $g$ and $h$ are only functions of the fault geometry and instantaneous elastic properties, $\lambda$ and $\mu$, and thus $g$ and $h$ can be computed numerically as a preprocessing step.
+The forward problem in eq.
+(\ref{ApproxForward}) can then be rapidly evaluated for any realization of $s$ and $\eta_{\mathrm{eff}}$.
 This is in contrast to evaluating the full forward problem, eq.
-(\ref{GeneralForward}), numerically for each realization of $s$ and unknown rheologic properties.
-Figure \ref{fig:Rheology} shows how estimates of $\eta_\mathrm{eff}$ can then be used as a constraint on the unknown parameters for various linear viscoelastic rheologies.
+(\ref{GeneralForward}), numerically for each realization of $s$ and the unknown rheologic properties.
 
-We perform an initial inversion of postseismic displacements using the approximation in eq.
-(\ref{ApproxForward}).
+Details on how eq.
+(\ref{ApproxForward}) is used to estimate $s$ and $\eta_\mathrm{eff}$ from postseismic deformation can be found in \citet{Hines2016}.
+A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
+We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2016} because of its relative simplicity.
+Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
+
 We estimate coseismic slip and afterslip with the same spatial and temporal discretization as in Section \ref{sec:ElasticInversion}.
 Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, as well as from 150 km to the bottom of our numerical model domain at 800 km.
-We again restrict fault slip to occur between 0 and 15 km depth and we made this choice to help eliminate inevitable non uniqueness.
+We again restrict fault slip to occur between 0 and 15 km depth, which is done in order to help eliminate inevitable non-uniqueness in the inversion.
 It has long been recognized that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional earthquake models \citep{Savage1990}.
-Since we are trying to simultaneously model these two processes, it is necessary to put sensible constraints on the depth of fault slip.
-Additionally, we note that when simultaneously estimating afterslip in the lower crust and a lower crustal viscosity, the inverse problem becomes particularly ill-posed.
-This ill-posedness is illustrated in Figure (\ref{fig:LowerCrust}), which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
-The horizontal displacements from fault slip are in the opposite direction as the displacements resulting from subsequent viscoelastic relaxation.
+Additionally, we note that when simultaneously estimating both afterslip and viscosity in the lower crust, the inverse problem becomes particularly ill-posed.
+This ill-posedness is illustrated in Figure \ref{fig:LowerCrust}, which shows the displacements resulting from a meter of slip on a fault extending from 15 to 30 km depth and the initial velocity resulting from subsequent viscoelastic relaxation in the lower crust, which is given a viscosity of $10^{18}$ Pa s.
+In this demonstration, the viscoelastic relaxation is entirely driven by the fault slip in the lower crust.
+The horizontal displacements from fault slip are in the opposite direction as the displacements resulting from viscoelastic relaxation.
 This means that surface displacements resulting from afterslip at lower crustal depths can be cancelled out, at least partially, by a low viscosity lower crust.
 We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
-This is not to say that we do not believe deep afterslip to be a possibility, rather we restrict slip to seismogenic depths as a modelling necessity.
+This is not to say that we do not believe deep afterslip to be a possibility; rather, we restrict slip to seismogenic depths as a modeling necessity.
 Although, it has been noted that the pattern of vertical postseismic deformation following the El Mayor-Cucpah earthquake indicates that a significant amount of afterslip must be shallow \citep{Rollins2015}.
@@
 \begin{figure}
-\includegraphics[scale=0.5]{Figures/Cancellation}
-\caption{afterslip and viscoelastic relaxation in lower crust}
+\includegraphics[scale=0.8]{Figures/Cancellation}
+\caption{Displacements resulting from fault slip at lower crustal depths (a), and initial velocities resulting from subsequent relaxation of a viscoelastic lower crust (b).
+The fault segment dips $75^\circ$ to the north-east and its surface projection is outlined in magenta.
+The highlighted area on the fault extends from 15 to 30 km depth and indicates where 1 meter of right-lateral slip was imposed.
+The elastic properties of the crust and mantle are the same as in Table \ref{tab:MaterialProperties}, and $\eta_\mathrm{eff}$  is $10^{18}$ Pa s in the lower crust.
+Vertical displacements are interpolated between station locations.}
 \label{fig:LowerCrust}
@@
 
-Further details on how $s$ and $\eta_\mathrm{eff}$ are estimated from postseismic deformation can be found in \citet{Hines2015}.
-A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
-We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2015} because of its relative simplicity.
-Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
-
-The first step in our inverse method is to determine at which point the early postseismic approximation breaks down, which we will denote as $t_{\mathrm{bd}}$.
-As noted, it is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
-We can almost certainly assume that deformation at the most far-field stations, which are $\sim400$ km away from the El Mayor-Cucapah epicentre, is the result of viscoelastic relaxation.
+We must determine at which point the early postseismic approximation breaks down, which we will denote as $t_{\mathrm{bd}}$.
+As noted, eq.
+(\ref{ApproxForward}) is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
+We can almost certainly assume that deformation at the most far-field stations, which are ${\sim}400$ km away from the El Mayor-Cucapah epicenter, is the result of viscoelastic relaxation.
 The approximation should then be valid for as long as a linear trend adequately approximates the far-field deformation.
-Using this logic, it would appear that $t_{\mathrm{bd}}\approx1$ year after the El Mayor-Cucapah earthquake.
+Using this logic, it would appear that $t_{\mathrm{bd}}$ is about one year after the El Mayor-Cucapah earthquake.
 Another way to determine $t_{\mathrm{bd}}$ is to find the best fitting prediction of eq.
@@
 (\ref{ApproxForward}) is no longer capable of describing the observed deformation without incurring systematic misfits.
-This is illustrated in Figure \ref{fig:RecordSection1}, which show the scaled radial components of displacement for stations along the El Mayor-Cucapah P axis.
 When using eq.
-(\ref{ApproxForward}) to fit the entire 5 years of postseismic displacement we see that the near-field displacements, e.g.
-station P501, are accurately predicted but when looking at displacement in the far-field, e.g.
-station P621, we see that eq.
-(\ref{ApproxForward}) overestimates the rate of deformation in the later postseismic period and underestimates the rate of deformation in the early period.
+(\ref{ApproxForward}) to fit the entire five years of postseismic displacements, we see that the near-field displacements (e.g., station P501) are accurately predicted.
+When looking at displacements in the far-field (e.g., station P621), we see that eq.
+(\ref{ApproxForward}) overestimates the rate of deformation in the later postseismic period and underestimates the rate of deformation in the early period (Figure \ref{fig:RecordSection1}).
 Due to the low signal-to-noise ratios for far-field stations, it is difficult to determine at what point eq.
-(\ref{ApproxForward}) is no longer able to predict the observed displacements without incurring any significant systematic misfit; however, we settle on $t_{\mathrm{bd}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
-As noted in \citet{Hines2015}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$, although the uncertainties would be larger.
+(\ref{ApproxForward}) is no longer able to predict the observed displacements; however, we settle on $t_{\mathrm{bd}}=0.8$ years after the earthquake, while acknowledging that the choice is subjective.
+As noted in \citet{Hines2016}, overestimating $t_{\mathrm{bd}}$ will result in a bias towards overestimating $\eta_{\mathrm{eff}}$, while picking a $t_\mathrm{bd}$ which is too low will not necessarily result in a biased estimate of $\eta_\mathrm{eff}$, although the uncertainties would be larger.
 We can then consider inferences of $\eta_{\mathrm{eff}}$ to be an upper bound on the viscosity needed to describe the far-field rate of deformation during the first 0.8 years of postseismic deformation.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/RecordSectionDuration}
+\includegraphics[scale=0.8]{Figures/RecordSectionDuration}
 \centering 
-\caption{record Section}
+\caption{Observed postseismic displacements (black) and best fitting predictions of eq. (\ref{ApproxForward}) to 5.0 (blue), 3.0 (green), and 0.8 (yellow) years of the postseismic data.} 
 \label{fig:RecordSection1}
@@
 
-We estimate coseismic slip, afterslip, and effective viscosity by solving 
+We estimate coseismic slip, afterslip, and effective viscosities by solving 
 \begin{equation}\label{ObjectiveFunction}
  \mathrm{min}_{s,\eta_\mathrm{eff}} \left(\left|\left|
- \frac{u_\mathrm{pred}(s,\eta_\mathrm{eff}) - u_\mathrm{obs}}
- {\mathbf{\sigma_\mathrm{obs}}}\right|\right|_2^2 + 
+ \frac{u_\mathrm{pred}(s,\eta_\mathrm{eff}) - u_\mathrm{post}}
+ {\mathbf{\sigma_\mathrm{post}}}\right|\right|_2^2 + 
  \lambda_s||s||_2^2 + 
- \lambda_\eta||\nabla \eta_{\mathrm{eff}}^{-1}||_2^2\right)
+ \lambda_\eta||\nabla \eta_{\mathrm{eff}}^{-1}||_2^2\right),
 \end{equation} 
-where $u_\mathrm{obs}$ consists of the first 0.8 years of postseismic deformation and $u_\mathrm{pred}$ are the predicted displacements from eq.
+where $u_\mathrm{post}$ consists of the first 0.8 years of postseismic deformation and $u_\mathrm{pred}$ are the predicted displacements from eq.
 (\ref{ApproxForward}).
-Due to inherent non uniqueness, we have added zeroth order Tikhonov regularization to estimates of $s$, and second order Tikhonov regularization to estimates of effective fluidity, $\eta_\mathrm{eff}^{-1}$.
-The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$.
-The penalty parameters are chosen with two trade-off curves.
-We first choose $\lambda_s$ while fixing $\lambda_\eta$ at 0 and then we determine $\lambda_\eta$ with $\lambda_s$ fixed at the chosen value.
-Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full 5 years, which we do in Section \ref{sec:FullInversion}.
-Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind even adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
+Due to inherent non-uniqueness, we have added zeroth-order Tikhonov regularization to estimates of $s$ and second-order Tikhonov regularization to estimates of effective fluidity $\eta_\mathrm{eff}^{-1}$.
+The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$, which are chosen with trade-off curves.
+Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in Section \ref{sec:FullInversion}.
+Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
 (\ref{ApproxForward}) is sensible.
 
-Our inferred estimates of effective viscosities, and corresponding fluidities, are shown in Figure \ref{fig:EffectiveViscosity} with their 95\% confidence intervals indicated, which were estimated through bootstrapping.
+Our estimated effective viscosities, and corresponding fluidities, are shown in Figure \ref{fig:EffectiveViscosity}.
 Although fluidity is rarely used in geophysical literature, eq.
 (\ref{InitialRate}) is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each layer.
-We note that the magnitude of the uncertainties on viscosity tend to decrease as we increase $\lambda_\eta$.
-Our choice of $\lambda_\eta$ was based on a standard technique used in geophysical inverse problems which has no statistical backing.
-It is therefore difficult to interpret the magnitude of uncertainties on viscosities shown in Figure \ref{fig:EffectiveViscosity}; although, we do believe that the relative uncertainty between layers is accurately depicted.
+We also show the 95\% confidence intervals for estimated viscosities and fluidities but we note that the uncertainties tend to be underestimated due to the added regularization \citep{Aster2011}.
 A robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
-This transitional depth is also consistent with the the viscosity structure required to explain far field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
-We find that the viscosity below 60 km depth needs to be $\sim1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
+This transitional depth is also consistent with the the viscosity structure required to explain far-field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
+We find that the viscosity below 60 km depth needs to be ${\sim}10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
 The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
@@
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/EffectiveViscosity}
+\includegraphics[scale=0.8]{Figures/EffectiveViscosity}
 \centering 
-\caption{effective viscosity}
+\caption{Effective viscosities and associated fluidities inferred by fitting eq.
+(\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.
+95\% confidence intervals, estimated from bootstrapping, are indicated by color fields.}
 \label{fig:EffectiveViscosity}
@@
 Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in Figure \ref{fig:InitialSlip}.
-Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, coseismic slip is inferred to be in the Sierra Cucapah and it is right lateral with a significant normal component.
-This is consistent with field studies \citep{Fletcher2014}, as well as the coseismic slip from \citet{Wei2011}.
+Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, a significant amount of right-lateral and normal coseismic slip is inferred to be on the Sierra Cucapah fault segment.
+Our coseismic slip solution is consistent with field studies \citep{Fletcher2014} and the model from \citet{Wei2011}.
 The potency of inferred coseismic slip is $3.3\times 10^{9}\ \mathrm{m}^3$, which is also about the same as that inferred from Section \ref{sec:ElasticInversion}.
 The present inference of afterslip on the Indiviso fault is significantly less than what was found in the Section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
-When fault slip is simultaneously estimated with a lithospheric and asthenospheric viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.46\times10^{9}\ \mathrm{m}^3$ when we assume the lithosphere and asthenosphere are elastic.
-The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodelled viscoelastic relaxation at depths greater than $60$ km.
-The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault even when allowing for viscoelastic relaxation in the lower crust and upper mantle raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
+When fault slip is simultaneously estimated with viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.5\times10^{9}\ \mathrm{m}^3$ when we assume the crust and upper mantle are elastic.
+The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
+The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
 
 \begin{figure}
-\includegraphics[scale=0.7]{Figures/InitialSlip}
-\caption{}
+\includegraphics[scale=0.8]{Figures/InitialSlip}
+\caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
 \label{fig:InitialSlip}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Full Inversion}\label{sec:FullInversion}
+\subsection{Full Postseismic Inversion}\label{sec:FullInversion}
 
-In the previous section, we used the inverse method from \citet{Hines2015} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
-In this section, we use the effective viscosities inferred above as a prior constraint when searching for models which are capable of describing the available 5 years of postseismic data, where our forward problem is now eq.
+In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
+In this section, we use these effective viscosities as a prior constraint when searching for models which are capable of describing the available five years of postseismic data, where our forward problem is now eq.
 (\ref{GeneralForward}) rather than the approximation given by eq.
 (\ref{ApproxForward}).
-We perform a series of coseismic slip and afterslip inversion assuming a variety of rheologies for the lower crust and upper mantle which are consistent with our findings from Section \ref{sec:InitialInversion}.
-We appraise each model using the mean chi squared value,
+We perform a series of fault slip inversions assuming a variety of rheologies for the lower crust and upper mantle which are consistent with our findings from Section \ref{sec:InitialInversion}.
+We appraise each model using the mean chi-squared value,
 \begin{equation}\label{eq:Misfit}
@@
 
-We first assume that the crust and mantle can be described with a Maxwell rheology, and we set $\eta_\mathrm{M}$ equal to our inference of $\eta_{\mathrm{eff}}$.
+We first assume that the crust and mantle can be described with a Maxwell rheology, and we set the steady-state viscosity $\eta_\mathrm{M}$ equal to our inference of $\eta_{\mathrm{eff}}$.
 We compute $f$ and $g$ from eq.
-(\ref{GeneralForward}) using the finite element software, Pylith \citep{Aagaard2009}, and assume the same spatial and temporal discretization of $s$ as in Sections \ref{sec:ElasticInversion} and \ref{sec:InitialInversion}.
-We estimate $s$ using linear least squares and we find $\bar\chi^2=37.4$.
+(\ref{GeneralForward}) using Pylith, and we use the same spatial and temporal discretization of $s$ as in Sections \ref{sec:ElasticInversion} and \ref{sec:InitialInversion}.
+We estimate $s$ using linear least squares and find a misfit of $\bar\chi^2=37.4$.
 For comparison, $\bar\chi^2=35.3$ for the elastic model from Section \ref{sec:ElasticInversion}.
-The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about 3 years \ref{fig:RecordSection2}.
+The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about three years (Figure \ref{fig:RecordSection2}).
 Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle.
 However, decreasing the viscosity only increases the misfit.
-Although, the viscosities used here are consistent with the successful Maxwell viscoelastic models found by \citet{Rollins2015} and \citet{Spinler2015}, which had mantle viscosities on the order of $10^{18}$ Pa s, we find that such a model is incapable of describing the entire postseismic time series.
+Although, the viscosities used here are consistent with the successful Maxwell viscoelastic models found by \citet{Rollins2015} and \citet{Spinler2015}, which had mantle viscosities on the order of $10^{18}$ Pa s and relatively higher lower crustal viscosities, we find that such a model is incapable of describing the entire postseismic time series.
 \citet{Pollitz2001} similarly recognized this deficiency in a Maxwell rheology, which then motivated their exploration of a Burgers rheology upper mantle \citep{Pollitz2003}.
 
-Rather than exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, $\eta_{K}$ and $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces the unknown parameter $\mu_{K}$.
+Instead of exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, the transient viscosity $\eta_{K}$ and transient shear modulus $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces one additional unknown parameter, $\mu_{K}$.
 We assume that the lower crust still has a Maxwell rheology.
-The steady-state viscosity, $\eta_{M}$, in the crust and the transient viscosity, $\eta_\mathrm{K}$, in the mantle are set equal to the inferred effective viscosities.
-We then estimate the ratio of shear moduli, $\frac{\mu_K}{\mu}$.
-We compute nine different sets of Green's functions, $f$ and $g$, using Pylith, where we assume values of $\frac{\mu_K}{\mu}$ ranging from 0 to 1.
+The steady-state viscosity in the crust and the transient viscosity in the mantle are set equal to the inferred effective viscosities.
+We then estimate the ratio of shear moduli $\frac{\mu_K}{\mu}$.
+We compute nine different sets of Green's functions, $f$ and $g$, where we assume values of $\frac{\mu_K}{\mu}$ ranging from 0 to 1.
 The former being a degenerate case where the Zener model reduces to the above Maxwell model.
 We estimate coseismic slip and afterslip for each realization of $\frac{\mu_K}{\mu}$.
-The shear moduli ratio that yields to best prediction to the observed postseismic displacements is found to be $0.375$ with a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
+The shear moduli ratio that yields the best prediction to the observed postseismic displacements is found to be $0.375$ which produces a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
 The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSection2}).
-The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the 5 years.
+The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the five years.
 
@@
 \centering 
-\caption{misfit with different shear modulus ratios}
+\caption{Mean chi-squared value for the best fitting slip model as a function of the transient shear modulus relative to the elastic shear modulus in a Zener upper mantle.
+Large dot indicates our preferred ratio.}
 \label{fig:ShearModulusRatio}
@@
 \centering 
-\caption{}
+\caption{Observed postseismic displacements (black).
+Predicted postseismic displacements for the best fitting slip model when assuming a Maxwell viscoelastic lower crust and upper mantle (blue).
+Predicted postseismic displacements for the best fitting slip model when assuming a Maxwell viscoelastic lower crust and a Zener viscoelastic upper mantle (green).
+The effective viscosities are the same for both models and are shown in Figure \ref{fig:EffectiveViscosity}.}
 \label{fig:RecordSection2}
@@
 
-Because we are able to adequately describe the available 5 years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
-However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-0state viscosity of $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of 5 years, would also be able to satisfactorily describe the observable postseismic deformation.
+Because we are able to adequately describe the available five years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
+However, since the Zener model is a Burgers model with an infinite steady-state viscosity, we can conclude that any Burgers rheology that has a transient viscosity consistent with that found in Section \ref{sec:InitialInversion} and a steady-state viscosity $\gtrsim10^{20}$ Pa s, which is effectively infinite on the time scale of five years, would also be able to satisfactorily describe the observable postseismic deformation.
 
-The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip} and the predicted postseismic displacements are shown Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
-Overall, the trends in the near-field and far-field transient deformation are accurately described by our preferred model.
+The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip}.
+The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and most of the slip is shallow and on the Sierra Cucapah fault segment.
+The potency of five years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
+Most of the afterslip in our preferred model occurs within the first year after the earthquake and coincides with the location of our inferred coseismic slip.
+Inferred afterslip within the first year is accounting for the most rapid near-field transient deformation.
+After one year, afterslip is inferred to be deeper down on the Sierra Cucapah segment, which is describing much of the sustained near-field postseismic deformation.
+We emphasize, that the GPS station closest to where we infer afterslip, P496, is still about 30 km away, which is too far for us to conclusively argue for sustained localized deformation rather than shallow distributed deformation.
+The deep afterslip inferred after one year could potentially be describing deformation resulting from lower crustal flow.
+To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}, and inverted for fault slip.
+We find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after one year, while still requiring about the same amount of afterslip over the first year.
+We do believe that the early shallow afterslip on the Sierra Cucapah segment is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
+
+the postseismic displacements predicted by our preferred model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
+Overall, the trends in the near-field and far-field transient deformation are accurately described.
 In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (Figure \ref{fig:RecordSection2}).
@@
 Most of our misfit is for the near-field stations in the Imperial Valley, and we attribute this misfit to our relatively simple fault geometry, which does not account for potential fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
-In particular, we are unable to model the sustained rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
-Additionally, we see systematic misfit in the later postseismic period west of the location of the Landers and Hector Mine earthquakes, which may be the result of unmodelled postseismic deformation resulting from those earthquakes.
+In particular, we are unable to model the sustained, rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
+Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
 Lastly, there are clear discrepancies between the observed and predicted vertical deformation following the first year after the El Mayor Cucapah earthquake.
@@
 
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[scale=0.8]{Figures/FinalSlip}
 \centering 
-\caption{}
+\caption{Inferred coseismic slip and afterslip when assuming a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.
+The transient viscosity $\eta_K$ in the mantle and steady-state viscosity $\eta_M$ in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}.
+We set $\frac{\mu_K}{\mu}=0.375$ in the upper mantle.}
 \label{fig:FinalSlip}
@@
 
-The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and the potency of 5 years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
-Most of the afterslip in our preferred model occurs within the first year after the earthquake with a significant amount inferred to be shallow and in the Sierra Cucapah.
-The afterslip within the first year is accounting for the most rapid near-field transient deformation.
-After 1 year, afterslip is inferred to be deeper and under the Sierra Cucapah, which is describing much of the sustained near-field postseismic deformation.
-We emphasize, that the GPS station closest to our inferred afterslip, P496, is still about 30 km away, which is too far away for us to conclusively argue for sustained brittle deformation rather shallow ductile deformation.
-The deep afterslip inferred after 1 year could potentially be describing deformation resulting from lower crustal flow.
-To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}.
-After performing another slip inversion, we find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after 1 year, while still requiring about the same amount of afterslip over the first year.
-We do believe that the early shallow afterslip is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
+\section{Discussion}\label{Discussion}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001, Hearn2003, Feigl2006}.
+The similarity of the horizontal postseismic deformation results in a non-uniqueness in inferences of afterslip or viscoelastic relaxation.
+In contrast, the spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}.
+It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981,Hetland2014}.
+The similarity between deformation resulting from deep afterslip and viscoelastic relaxation of coseismic stresses is different from the ill-posedness described in Section \ref{sec:InitialInversion}.
+In our method, any inferred afterslip will also mechanically drive additional viscoelastic relaxation.
+The horizontal deformation resulting from deep afterslip will generally be in the opposite direction as horizontal deformation resulting from viscoelastic relaxation of subsequent stresses in the lower crust (Figure \ref{fig:LowerCrust}).
+As a result, there is a trade-off between inferences of deep afterslip and lower crustal viscosity.
+In our synthetic tests in \citet{Hines2016}, we have found that inverting surface deformation for afterslip and viscosity within the same depth interval tends to result in overestimated afterslip and an underestimated viscosity.
 
 Most postseismic studies assume Maxwell viscoelasticity in the lower crust and upper mantle \citep[e.g.][]{Nur1974,Pollitz2000,Hetland2003,Freed2006a,Johnson2009,Hearn2009}, which is the simplest viscoelastic rheologic model.
-In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lithosphere and asthenosphere and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities of $\gtrsim 10^{19}$ Pa s.
-These postseismic studies are corroborated by \citet{Kaufmann2000} who found that a lower crust and upper mantle with viscosities on the order of $10^{20}$ and $10^{18}$ Pa s, respectively, are necessary to describe subsidence resulting from Lake Mead, which is a process with similar spatial and temporal scales as postseismic deformation.
+In Southern California, postseismic studies following the Landers \citep{Pollitz2000}, Hector Mine \citep{Pollitz2001}, and El Mayor-Cucapah earthquake \citep{Spinler2015,Rollins2015}, have assumed Maxwell viscoelasticity in the lower crust and upper mantle and have inferred upper mantle viscosities on the order of $10^{17}$ to $10^{18}$ Pa s and lower crust viscosities $\gtrsim 10^{19}$ Pa s.
+These postseismic studies are consistent with \citet{Kaufmann2000} and \citet{Cavalie2007}, who found that an upper mantle viscosity of $10^{18}$ Pa s and a crustal viscosity $\gtrsim10^{20}$ Pa s are necessary to describe subsidence resulting from changes in loading from Lake Mead.
+This isostatic adjustment is a process with similar spatial and temporal scales as postseismic deformation, and thus the inferred viscosities of these two types of studies would likely agree.
 While these studies found viscosities that are consistent with our effective viscosities from Section \ref{sec:InitialInversion}, they are inconsistent with viscosity estimates made from geophysical processes that occur over longer time scales.
-For example, \citet{Lundgren2009} found that lower crust and upper mantle viscosities on the order of $10^{21}$ and $10^{19}$ Pa s, respectively, are needed to describe interseismic deformation along the Southern San Andreas and San Jacinto fault.
-An even higher mantle viscosity on the order of $10^{20}$ Pa s is required to describe deflection resulting from Lake Bonneville, which occurs on the time scales of $10^{4}$ years \citep{Crittenden1967,Bills1987}.
+For example, \citet{Lundgren2009} found that lower crust and upper mantle viscosities on the order of $10^{21}$ and $10^{19}$ Pa s, respectively, are needed to describe interseismic deformation along the Southern San Andreas fault zone in the Salton Sea region.
+An even higher mantle viscosity, on the order of $10^{20}$ Pa s, is required to describe isostatic adjustment resulting from the draining of Lake Bonneville, which occurs on the time scales of $10^{4}$ years \citep{Crittenden1967,Bills1987}.
 
-An additional deficiency with the Maxwell rheology is that it predicts a steady decay over time in the rate of postseismic deformation, which fails to describe the commonly observed rapid early transience followed by a relatively steady rate of postseismic deformation.
+An additional deficiency with the Maxwell rheology is that it predicts a steady decay in the rate of postseismic deformation over time, which fails to describe the commonly observed rapid, early transience followed by a relatively steady rate of postseismic deformation.
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
-However, postseismic deformation at distances greater than $\sim200$ km from the El Mayor-Cucapah epicentre can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSection2}).
+However, postseismic deformation at distances greater than ${\sim}200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSection2}).
 
-We found that a Zener rheology in the upper mantle with a transient viscosity of $\sim10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
+We found that a Zener rheology in the upper mantle with a transient viscosity of ${\sim}10^{18}$ Pa s does a noticeably better job at predicting far-field postseismic deformation.
 A generalization of the Zener viscoelastic model, schematically represented as several Kelvin elements connected in series, is commonly used to describe seismic attenuation \citep{Liu1976}.
@@
 
-Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid-like behaviour required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
+Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid-like behavior required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
 \citet{Yuen1982} proposed a Burgers rheology with a low transient viscosity ($\eta_K\approx10^{16}$ Pa s) and high steady-state viscosity ($\eta_M\approx10^{21}$ Pa s) to describe both seismic attenuation and long term geologic processes.
@@
 \citet{Pollitz2003} sought to describe postseismic deformation following Hector Mine with a Burgers rheology mantle and they found a best fitting transient viscosity of $1.6\times10^{17}$ Pa s and steady-state viscosity of $4.6\times10^{18}$ Pa s.
-While the Burgers rheology was introduced as a means of bridging the gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from earthquake cycle and lake loading studies.
+While the Burgers rheology was introduced as a means of bridging the gap between relaxation observed in long and short term geophysical processes, the inferred steady state viscosity from \citet{Pollitz2003} is still inconsistent with the Maxwell viscosities inferred from studies on the earthquake cycle and Lake Bonneville.
 The transient viscosity inferred by \citet{Pollitz2003} is constrained by the earliest phase of postseismic deformation following the Hector Mine earthquake.
@@
 It is then possible that the preferred rheologic model from \citet{Pollitz2003} was biased towards inferring a particularly low transient viscosity by neglecting to account for afterslip.
-This is in contrast to the present study, where we have inferred a lithospheric viscosity structure simultaneously with afterslip.
-We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of $\sim10^{18}$ Pa s in the mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
-Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over 5 years, would also be able to describe the postseismic deformation.
-Such a Burgers model might then be consistent with the steady state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.
+This is in contrast to the present study, where we have inferred a viscosity structure simultaneously with afterslip.
+We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
+Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over five years, would also be able to describe the postseismic deformation.
+Such a Burgers model might then be consistent with the steady-state viscosities necessary for lake loading, interseismic deformation, and mantle dynamics.
 
 \section{Conclusion}
-Postseismic deformation following the El Mayor-Cucapah earthquake displays far-field ($\gtrsim 200$ km from the epicentre) transient postseismic deformation that is largely undetectable after about 3 years, while near-field deformation exhibits transience that decays to a sustained, elevated rate after about 1 to 2 year.
-We find that the near-field transient deformation can be explained with shallow afterslip and the sustained rate of near field deformation can either be explained with continued afterslip or a lower crustal viscosity of $\sim10^{19}$ Pa s.
-Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than $\sim60$ km.
-Beneath that depth, a transient viscosity of $\sim10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the 5 years considered in this study.
+
+We have extracted a filtered and smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.
+We treated postseismic deformation as a stochastic process where we did not presume any characteristic shape of the postseismic time series.
+Our estimated postseismic deformation reveals far-field (epicentral distances beyond ${\sim}200$ km) transient deformation which is largely undetectable after about three years.
+Near-field deformation exhibits transience that decays to a sustained, elevated rate after about one or two years.
+We found that near-field transient deformation can be explained with shallow afterslip, and the sustained rate of near-field deformation can either be explained with continued afterslip or relaxation in a lower crustal with a viscosity of ${\sim}10^{19}$ Pa s.
+Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km.
+Beneath that depth, a transient viscosity of ${\sim}10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the five years considered in this study.
 By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.
@@
 \section*{Acknowledgements}
-We are grateful to Andy Freed for an illuminating discussion on the material in this manuscript.
-
+We thank Andy Freed for an illuminating discussion on the data used in this study.
 This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.
 EAR-1261833.
+This material is based upon work supported by the National Science Foundation under Grant Numbers EAR 1045372 and EAR 1245263.
 
-This material is based upon work supported by the National Science
-Foundation under Grant Numbers EAR 1045372 and EAR 1245263.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Or, to use BibTeX:
+%
+% Follow these steps
+%
+% 1. Type in \bibliography{<name of your .bib file>} 
+%    Run LaTeX on your LaTeX file.
+%
+% 2. Run BiBTeX on your LaTeX file.
+%
+% 3. Open the new .bbl file containing the reference list and
+%   copy all the contents into your LaTeX file here.
+%
+% 4. Run LaTeX on your new file which will produce the citations.
+%
+% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.
 
-\bibliographystyle{apalike}
-\bibliography{mybib}
+%% After you run BibTeX, Copy in the contents of the .bbl file here:
+%\bibliography{mybib.bib}
+\begin{thebibliography}{52}
+\providecommand{\natexlab}[1]{#1}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+
+\bibitem[{\textit{Aagaard et~al.}(2013)\textit{Aagaard, Knepley, Williams}}]{Aagaard2013}
+Aagaard, B.~T., M.~G. Knepley, and C.~A. Williams (2013). {A domain decomposition approach to implementing
+fault slip in finite-element models of quasi-static and dynamic crustal deformation}, \textit{Journal of Geophysical
+Research: Solid Earth}, \textit{118}, \doi{10.1002/jgrb.50217}.
+
+\bibitem[{\textit{Argus et~al.}(2005)\textit{Argus, Heflin, Peltzer,
+  Cramp{\'{e}}, and Webb}}]{Argus2005}
+Argus, D.~F., M.~B. Heflin, G.~Peltzer, F.~Cramp{\'{e}}, and F.~H. Webb (2005),
+  {Interseismic strain accumulation and anthropogenic motion in metropolitan
+  Los Angeles}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{110}(4), 1--26, \doi{10.1029/2003JB002934}.
+
+\bibitem[{\textit{Aster et~al.}(2011)\textit{Aster, Borchers, and
+  Thurber}}]{Aster2011}
+Aster, R.~C., B.~Borchers, and C.~H. Thurber (2011), {Parameter
+  Estimation and Inverse Problems}, vol. 90, Academic Press.
+
+\bibitem[{\textit{Bawden et~al.}(2001)\textit{Bawden, Thatcher, Stein, Hudnut,
+  and Peltzer}}]{Bawden2001}
+Bawden, G.~W., W.~Thatcher, R.~S. Stein, K.~W. Hudnut, and G.~Peltzer (2001),
+  {Tectonic contraction across Los Angeles after removal of groundwater pumping
+  effects.}, \textit{Nature}, \textit{412}(August), 812--815,
+  \doi{10.1038/35090558}.
+
+\bibitem[{\textit{Bills and May}(1987)}]{Bills1987}
+Bills, B.~G., and G.~M. May (1987), {Lake Bonneville: Constraints on
+  Lithospheric Thickness and Upper Mantle Viscosity From Isostatic Warping of
+  Bonneville, Provo, and Gilbert Stage Shorelines}, \textit{Journal of
+  Geophysical Research-Solid Earth and Planets}, \textit{92}(B11),
+  11,493--11,508, \doi{10.1029/JB092iB11p11493}.
+
+\bibitem[{\textit{{\c{C}}akir et~al.}(2012)\textit{{\c{C}}akir, Ergintav,
+  {\"{O}}zener, Dogan, Akoglu, Meghraoui, and Reilinger}}]{Cakir2012}
+{\c{C}}akir, Z., S.~Ergintav, H.~{\"{O}}zener, U.~Dogan, A.~M. Akoglu,
+  M.~Meghraoui, and R.~Reilinger (2012), {Onset of aseismic creep on major
+  strike-slip faults}, \textit{Geology}, \textit{40}(12), 1115--1118,
+  \doi{10.1130/G33522.1}.
+
+\bibitem[{\textit{Cavali{\'{e}} et~al.}(2007)\textit{Cavali{\'{e}}, Doin,
+  Lasserre, and Briole}}]{Cavalie2007}
+Cavali{\'{e}}, O., M.~P. Doin, C.~Lasserre, and P.~Briole (2007), {Ground
+  motion measurement in the Lake Mead area, Nevada, by differential synthetic
+  aperture radar interferometry time series analysis: Probing the lithosphere
+  rheological structure}, \textit{Journal of Geophysical Research: Solid
+  Earth}, \textit{112}(3), 1--18, \doi{10.1029/2006JB004344}.
+
+\bibitem[{\textit{Cetin et~al.}(2014)\textit{Cetin, Cakir, Meghraoui, Ergintav,
+  and Akoglu}}]{Cetin2014}
+Cetin, E., Z.~Cakir, M.~Meghraoui, S.~Ergintav, and A.~M. Akoglu (2014),
+  {Extent and distribution of aseismic slip on the Ismetpasa segment of the
+  North Anatolian Fault (Turkey) from Persistent Scatterer InSAR},
+  \textit{Geochemistry, Geophysics, Geosystems}, \textit{15},
+  \doi{10.1002/2014GC005307.Received}.
+
+\bibitem[{\textit{Chopra}(1997)}]{Chopra1997}
+Chopra, P.~N. (1997), {High-temperature transient creep in olivine rocks},
+  \textit{Tectonophysics}, \textit{279}, 93--111,
+  \doi{10.1016/S0040-1951(97)00134-0}.
+
+\bibitem[{\textit{Crittenden}(1967)}]{Crittenden1967}
+Crittenden, M. (1967), {Viscosity and Finite Strength of the Mantle as
+  Determined from Water and Ice Loads*}, \textit{Geophysical Journal of the
+  Royal Astronomical {\ldots}}, pp. 261--279,
+  \doi{10.1111/j.1365-246X.1967.tb06243.x}.
+
+\bibitem[{\textit{Davis et~al.}(2012)\textit{Davis, Wernicke, and
+  Tamisiea}}]{Davis2012}
+Davis, J.~L., B.~P. Wernicke, and M.~E. Tamisiea (2012), {On seasonal signals
+  in geodetic time series}, \textit{Journal of Geophysical Research: Solid
+  Earth}, \textit{117}(1), 1--10, \doi{10.1029/2011JB008690}.
+
+\bibitem[{\textit{Feigl and Thatcher}(2006)}]{Feigl2006}
+Feigl, K.~L., and W.~Thatcher (2006), {Geodetic observations of post-seismic
+  transients in the context of the earthquake deformation cycle},
+  \textit{Comptes Rendus - Geoscience}, \textit{338}, 1012--1028,
+  \doi{10.1016/j.crte.2006.06.006}.
+
+\bibitem[{\textit{Fletcher et~al.}(2014)\textit{Fletcher, Teran, Rockwell,
+  Oskin, Hudnut, Mueller, Spelz, Akciz, Masana, Faneros, Fielding, Leprince,
+  Morelan, Stock, Lynch, Elliott, Gold, Liu-Zeng, Gonz{\'{a}}lez-Ortega,
+  Hinojosa-Corona, and Gonz{\'{a}}lez-Garc{\'{i}}a}}]{Fletcher2014}
+Fletcher, J.~M., O.~J. Teran, T.~K. Rockwell, M.~E. Oskin, K.~W. Hudnut, K.~J.
+  Mueller, R.~M. Spelz, S.~O. Akciz, E.~Masana, G.~Faneros, E.~J. Fielding,
+  S.~Leprince, A.~E. Morelan, J.~Stock, D.~K. Lynch, A.~J. Elliott, P.~Gold,
+  J.~Liu-Zeng, A.~Gonz{\'{a}}lez-Ortega, A.~Hinojosa-Corona, and
+  J.~Gonz{\'{a}}lez-Garc{\'{i}}a (2014), {Assembly of a large earthquake from a
+  complex fault system: Surface rupture kinematics of the 4 April 2010 El
+  Mayor-Cucapah (Mexico) Mw 7.2 earthquake}, \textit{Geosphere},
+  \textit{10}(4), 797--827, \doi{10.1130/GES00933.1}.
+
+\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais,
+  Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
+Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and
+  S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002
+  Denali, Alaska, earthquake for postseismic relaxation processes and
+  lithospheric rheology}, \textit{Journal of Geophysical Research: Solid
+  Earth}, \textit{111}, 1--23, \doi{10.1029/2005JB003894}.
+
+\bibitem[{\textit{Freed et~al.}(2007)\textit{Freed, B{\"{u}}rgmann, and
+  Herring}}]{Freed2007a}
+Freed, A.~M., R.~B{\"{u}}rgmann, and T.~Herring (2007), {Far-reaching transient
+  motions after Mojave earthquakes require broad mantle flow beneath a strong
+  crust}, \textit{Geophysical Research Letters}, \textit{34}, 1--5,
+  \doi{10.1029/2007GL030959}.
+
+\bibitem[{\textit{Gonzalez-Ortega et~al.}(2014)\textit{Gonzalez-Ortega, Fialko,
+  Sandwell, Nava-pichardo, Fletcher, Gonzalez-garcia, Lipovsky, Floyd, and
+  Funning}}]{Gonzalez-ortega2014}
+Gonzalez-Ortega, A., Y.~Fialko, D.~Sandwell, F.~A. Nava-pichardo, J.~Fletcher,
+  J.~Gonzalez-garcia, B.~Lipovsky, M.~Floyd, and G.~Funning (2014), {El
+  Mayor-Cucapah (Mw7.2) earthquake: early near-field postseismic deformation
+  from InSar and GPS observations}, \textit{Journal of Geophysical Research},
+  \textit{119}, 1482--1497, \doi{10.1002/2013JB010193.Received}.
+
+\bibitem[{\textit{Hauksson et~al.}(2011)\textit{Hauksson, Stock, Hutton, Yang,
+  Vidal-Villegas, and Kanamori}}]{Hauksson2011}
+Hauksson, E., J.~Stock, K.~Hutton, W.~Yang, J.~A. Vidal-Villegas, and
+  H.~Kanamori (2011), {The 2010 Mw 7.2 El mayor-cucapah earthquake sequence,
+  Baja California, Mexico and Southernmost California, USA: Active
+  seismotectonics along the Mexican pacific margin}, \textit{Pure and Applied
+  Geophysics}, \textit{168}(3918), 1255--1277, \doi{10.1007/s00024-010-0209-7}.
+
+\bibitem[{\textit{Hearn}(2003)}]{Hearn2003}
+Hearn, E.~H. (2003), {What can GPS data tell us about the dynamics of
+  post-seismic deformation ?}, (2003), 753--777.
+
+\bibitem[{\textit{Hearn et~al.}(2009)\textit{Hearn, McClusky, Ergintav, and
+  Reilinger}}]{Hearn2009}
+Hearn, E.~H., S.~McClusky, S.~Ergintav, and R.~E. Reilinger (2009), {Izmit
+  earthquake postseismic deformation and dynamics of the North Anatolian Fault
+  Zone}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{114}(August 2008), 1--21, \doi{10.1029/2008JB006026}.
+
+\bibitem[{\textit{Hetland}(2003)}]{Hetland2003}
+Hetland, E.~A. (2003), {Postseismic relaxation across the Central Nevada
+  Seismic Belt}, \textit{Journal of Geophysical Research}, \textit{108}(Figure
+  2), 1--13, \doi{10.1029/2002JB002257}.
+
+\bibitem[{\textit{Hetland and Zhang}(2014)}]{Hetland2014}
+Hetland, E.~A., and G.~Zhang (2014), {Effect of shear zones on post-seismic
+  deformation with application to the 1997 Mw 7.6 manyi earthquake},
+  \textit{Geophysical Journal International}, \textit{198}, 259--269,
+  \doi{10.1093/gji/ggu127}.
+
+\bibitem[{\textit{Hines and Hetland}(2013)}]{Hines2013}
+Hines, T.~T., and E.~A. Hetland (2013), {Bias in estimates of lithosphere
+  viscosity from interseismic deformation}, \textit{Geophysical Research
+  Letters}, \textit{40}(16), 4260--4265, \doi{10.1002/grl.50839}.
+
+\bibitem[{\textit{Hines and Hetland}(2016)}]{Hines2016}
+Hines, T.~T., and E.~A. Hetland (2016), {Rapid and simultaneous estimation of
+  fault slip and heterogeneous lithospheric viscosity from post-seismic
+  deformation}, \textit{Geophysical Journal International}, \textit{204}(1),
+  569--582, \doi{10.1093/gji/ggv477}.
+
+\bibitem[{\textit{Jacobs et~al.}(2002)\textit{Jacobs, Sandwell, Fialko, and
+  Sichoix}}]{Jacobs2002}
+Jacobs, A., D.~Sandwell, Y.~Fialko, and L.~Sichoix (2002), {The 1999 (Mw7.1)
+  Hector Mine, California, Earthquake: Near-Field Postseismic Deformation from
+  ERS Interferometry}, \textit{Bulletin of the Seismological Society of
+  America}, \textit{92}(May), 1433--1442.
+
+\bibitem[{\textit{Johnson and Segall}(2004)}]{Johnson2004}
+Johnson, K.~M., and P.~Segall (2004), {Viscoelastic earthquake cycle models
+  with deep stress-driven creep along the San Andreas fault system},
+  \textit{Journal of Geophysical Research B: Solid Earth}, \textit{109}, 1--19,
+  \doi{10.1029/2004JB003096}.
+
+\bibitem[{\textit{Johnson et~al.}(2009)\textit{Johnson, B{\"{u}}rgmann, and
+  Freymueller}}]{Johnson2009}
+Johnson, K.~M., R.~B{\"{u}}rgmann, and J.~T. Freymueller (2009), {Coupled
+  afterslip and viscoelastic flow following the 2002 Denali Fault, Alaska
+  earthquake}, \textit{Geophysical Journal International}, \textit{176}(3),
+  670--682, \doi{10.1111/j.1365-246X.2008.04029.x}.
+
+\bibitem[{\textit{J{\'{o}}nsson et~al.}(2003)\textit{J{\'{o}}nsson, Segall,
+  Pedersen, and Bjornsson}}]{Jonsson2003}
+J{\'{o}}nsson, S., P.~Segall, R.~Pedersen, and G.~Bjornsson (2003),
+  {Post-earthquake ground movements correlated to pore-pressure transients},
+  \textit{Nature}, \textit{424}(July), 179--183, \doi{10.1038/nature01758.1.}
+
+\bibitem[{\textit{Kaufmann and Amelung}(2000)}]{Kaufmann2000}
+Kaufmann, G., and F.~Amelung (2000), {Reservoir-induced deformation and
+  continental rheology in vicinity of Lake Mead, Nevada}, \textit{Journal of
+  Geophysical Research}, \textit{105}(B7), 16,341, \doi{10.1029/2000JB900079}.
+
+\bibitem[{\textit{Kroll et~al.}(2013)\textit{Kroll, Cochran, Richards-Dinger,
+  and Sumy}}]{Kroll2013}
+Kroll, K.~A., E.~S. Cochran, K.~B. Richards-Dinger, and D.~F. Sumy (2013),
+  {Aftershocks of the 2010 Mw 7.2 El Mayor-Cucapah earthquake reveal complex
+  faulting in the Yuha Desert, California}, \textit{Journal of Geophysical
+  Research: Solid Earth}, \textit{118}(October), 6146--6164,
+  \doi{10.1002/2013JB010529}.
+
+\bibitem[{\textit{Lekic et~al.}(2011)\textit{Lekic, French, and
+  Fischer}}]{Lekic2011}
+Lekic, V., S.~W. French, and K.~M. Fischer (2011), {Lithospheric Thinning
+  Beneath Rifted Regions of Southern California}, \textit{Science},
+  \textit{334}(November), 783--787.
+
+\bibitem[{\textit{Liu et~al.}(1976)\textit{Liu, Anderson, and
+  Kanamori}}]{Liu1976}
+Liu, H.-P., D.~L. Anderson, and H.~Kanamori (1976), {Velocity dispersion due to
+  anelasticity; implications for seismology and mantle composition},
+  \textit{Geophysical Journal International}, \textit{47}(1), 41--58,
+  \doi{10.1111/j.1365-246X.1976.tb01261.x}.
+
+\bibitem[{\textit{Lundgren et~al.}(2009)\textit{Lundgren, Hetland, Liu, and
+  Fielding}}]{Lundgren2009}
+Lundgren, P., E.~A. Hetland, Z.~Liu, and E.~J. Fielding (2009), {Southern San
+  Andreas-San Jacinto fault system slip rates estimated from earthquake cycle
+  models constrained by GPS and interferometric synthetic aperture radar
+  observations}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{114}(2), 1--18, \doi{10.1029/2008JB005996}.
+
+\bibitem[{\textit{McGuire and Segall}(2003)}]{McGuire2003}
+McGuire, J.~J., and P.~Segall (2003), {Imaging of aseismic fault slip
+  transients recorded by dense geodetic networks}, \textit{Geophysical Journal
+  International}, \textit{155}(3), 778--788,
+  \doi{10.1111/j.1365-246X.2003.02022.x}.
+
+\bibitem[{\textit{Meade and Hager}(2005)}]{Meade2005}
+Meade, B.~J., and B.~H. Hager (2005), {Block models of crustal motion in
+  southern California constrained by GPS measurements}, \textit{Journal of
+  Geophysical Research B: Solid Earth}, \textit{110}, 1--19,
+  \doi{10.1029/2004JB003209}.
+
+\bibitem[{\textit{Murray and Segall}(2005)}]{Murray2005}
+Murray, J.~R., and P.~Segall (2005), {Spatiotemporal evolution of a transient
+  slip event on the San Andreas fault near Parkfield, California},
+  \textit{Journal of Geophysical Research : Solid Earth}, \textit{110}(9),
+  1--12, \doi{10.1029/2005JB003651}.
+
+\bibitem[{\textit{Nur and Mavko}(1974)}]{Nur1974}
+Nur, A., and G.~Mavko (1974), {Postseismic viscoelastic rebound},
+  \textit{Science}, \textit{183}(4121), 204--206, \doi{10.1038/098448b0}.
+
+\bibitem[{\textit{O'Connell}(1971)}]{OConnell1971}
+O'Connell, R.~J. (1971), {Rheology of the Mantle}, \textit{EOS, Transactions,
+  American Geophysical Union}, \textit{52}, 140--142.
+
+\bibitem[{\textit{Oskin et~al.}(2012)\textit{Oskin, Arrowsmith, {Hinojosa
+  Corona}, Elliott, Fletcher, Fielding, Gold, {Gonzalez Garcia}, Hudnut,
+  Liu-Zeng, and Teran}}]{Oskin2012}
+Oskin, M.~E., J.~R. Arrowsmith, A.~{Hinojosa Corona}, A.~J. Elliott, J.~M.
+  Fletcher, E.~J. Fielding, P.~O. Gold, J.~J. {Gonzalez Garcia}, K.~W. Hudnut,
+  J.~Liu-Zeng, and O.~J. Teran (2012), {Near-field deformation from the El
+  Mayor-Cucapah earthquake revealed by differential LIDAR}, \textit{Science},
+  \textit{335}(6069), 702--705, \doi{10.1126/science.1213778}.
+
+\bibitem[{\textit{Pollitz et~al.}(2001)\textit{Pollitz, Wicks, and
+  Thatcher}}]{Pollitz2001}
+Pollitz, F., C.~Wicks, and W.~Thatcher (2001), {Mantle Flow Beneath a
+  Continental Strike-Slip Fault : Postseismic Deformation After the 1999 Hector
+  Mine Earthquake}, \textit{Science}, \textit{1814}(2001), 1814--1818,
+  \doi{10.1126/science.1061361}.
+
+\bibitem[{\textit{Pollitz}(2003)}]{Pollitz2003}
+Pollitz, F.~F. (2003), {Transient rheology of the uppermost mantle beneath the
+  Mojave Desert, California}, \textit{Earth and Planetary Science Letters},
+  \textit{215}, 89--104, \doi{10.1016/S0012-821X(03)00432-1}.
+
+\bibitem[{\textit{Pollitz et~al.}(2000)\textit{Pollitz, Peltzer, and
+  B{\"{u}}rgmann}}]{Pollitz2000}
+Pollitz, F.~F., G.~Peltzer, and R.~B{\"{u}}rgmann (2000), {Mobility of
+  continental mantle: Evidence from postseismic geodetic observations following
+  the 1992 Landers earthquake}, \textit{Journal of Geophysical Research},
+  \textit{105}(1999), 8035, \doi{10.1029/1999JB900380}.
+
+\bibitem[{\textit{Pollitz et~al.}(2012)\textit{Pollitz, B{\"{u}}rgmann, and
+  Thatcher}}]{Pollitz2012}
+Pollitz, F.~F., R.~B{\"{u}}rgmann, and W.~Thatcher (2012), {Illumination of
+  rheological mantle heterogeneity by the M7.2 2010 El Mayor-Cucapah
+  earthquake}, \textit{Geochemistry, Geophysics, Geosystems}, \textit{13}(6),
+  1--17, \doi{10.1029/2012GC004139}.
+
+\bibitem[{\textit{Rauch et~al.}(1965)\textit{Rauch, Tung, and
+  Striebel}}]{Rauch1965}
+Rauch, H.~E., F.~Tung, and C.~T. Striebel (1965), {Maximum likelihood estimates
+  of linear dynamic systems}, \textit{AIAA Journal}, \textit{3}(8), 1445--1450.
+
+\bibitem[{\textit{Riva and Govers}(2009)}]{Riva2009}
+Riva, R. E.~M., and R.~Govers (2009), {Relating viscosities from postseismic
+  relaxation to a realistic viscosity structure for the lithosphere},
+  \textit{Geophysical Journal International}, \textit{176}, 614--624,
+  \doi{10.1111/j.1365-246X.2008.04004.x}.
+
+\bibitem[{\textit{Rollins et~al.}(2015)\textit{Rollins, Barbot, and
+  Avouac}}]{Rollins2015}
+Rollins, C., S.~Barbot, and J.-P. Avouac (2015), {Postseismic Deformation
+  Following the 2010 M7.2 El Mayor-Cucapah Earthquake : Observations ,
+  Kinematic Inversions , and Dynamic Models}, \textit{Pure and Applied
+  Geophysics}, \doi{10.1007/s00024-014-1005-6}.
+
+\bibitem[{\textit{Savage}(1990)}]{Savage1990}
+Savage, J.~C. (1990), {Equivalent strike-slip earthquake cycles in half-space
+  and lithosphere-asthenosphere earth models}, \textit{Journal of Geophysical
+  Research}, \textit{95}, 4873, \doi{10.1029/JB095iB04p04873}.
+
+\bibitem[{\textit{Savage and Svarc}(2009)}]{Savage2009}
+Savage, J.~C., and J.~L. Svarc (2009), {Postseismic relaxation following the
+  1992 M 7.3 Landers and 1999 M 7.1 Hector Mine earthquakes , southern
+  California}, \textit{Journal of Geophysical Research}, \textit{114}(B01401),
+  \doi{10.1029/2008JB005938}.
+
+\bibitem[{\textit{Savage et~al.}(2005)\textit{Savage, Svarc, and
+  Yu}}]{Savage2005a}
+Savage, J.~C., J.~L. Svarc, and S.~B. Yu (2005), {Postseismic relaxation and
+  transient creep}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{110}, 1--14, \doi{10.1029/2005JB003687}.
+
+\bibitem[{\textit{Segall and Mathews}(1997)}]{Segall1997}
+Segall, P., and M.~Mathews (1997), {Time dependent inversion of geodetic data},
+  \textit{Journal of Geophysical Research}, \textit{102}.
+
+\bibitem[{\textit{Spinler et~al.}(2015)\textit{Spinler, Bennett, Walls, Shawn,
+  and Garcia}}]{Spinler2015}
+Spinler, J.~C., R.~A. Bennett, C.~Walls, L.~Shawn, and J.~J.~G. Garcia (2015),
+  {Assessing long-term postseismic deformation following the M7.2 4 April 2010,
+  El Mayor-Cucapah earthquake with implications for lithospheric rheology in
+  the Salton Trough}, \textit{Journal of Geophysical Research: Solid Earth},
+  \textit{120}, 3664--3679, \doi{10.1002/2014JB011613.Received}.
+
+\bibitem[{\textit{Wei et~al.}(2011{\natexlab{a}})\textit{Wei, Sandwell, Fialko,
+  and Bilham}}]{Wei2011a}
+Wei, M., D.~Sandwell, Y.~Fialko, and R.~Bilham (2011{\natexlab{a}}), {Slip on
+  faults in the Imperial Valley triggered by the 4 April 2010 Mw 7.2 El
+  Mayor-Cucapah earthquake revealed by InSAR}, \textit{Geophysical Research
+  Letters}, \textit{38}(January), 1--6, \doi{10.1029/2010GL045235}.
+
+\bibitem[{\textit{Wei et~al.}(2015)\textit{Wei, Liu, Kaneko, Mcguire, and
+  Bilham}}]{Wei2015}
+Wei, M., Y.~Liu, Y.~Kaneko, J.~J. Mcguire, and R.~Bilham (2015), {Dynamic
+  triggering of creep events in the Salton Trough, Southern California by
+  regional M≥5.4 earthquakes constrained by geodetic observations and
+  numerical simulations}, \textit{Earth and Planetary Science Letters},
+  \textit{427}, 1--10, \doi{10.1016/j.epsl.2015.06.044}.
+
+\bibitem[{\textit{Wei et~al.}(2011{\natexlab{b}})\textit{Wei, Fielding,
+  Leprince, Sladen, Avouac, Helmberger, Hauksson, Chu, Simons, Hudnut, Herring,
+  and Briggs}}]{Wei2011}
+Wei, S., E.~Fielding, S.~Leprince, A.~Sladen, J.-P. Avouac, D.~Helmberger,
+  E.~Hauksson, R.~Chu, M.~Simons, K.~Hudnut, T.~Herring, and R.~Briggs
+  (2011{\natexlab{b}}), {Superficial simplicity of the 2010 El Mayor–Cucapah
+  earthquake of Baja California in Mexico}, \textit{Nature Geoscience},
+  \textit{4}(9), 615--618, \doi{10.1038/ngeo1213}.
+
+\bibitem[{\textit{Yang and Toks\"oz}(1981)}]{Yang1981}
+Yang M., and M.~N. Toks\"oz (1981), {Time-dependent deformation and stress relaxation after strike-slip earthquakes}, \textit{Journal of Geophysical Research}, \textit{86}, 2889--2901.
+
+\bibitem[{\textit{Yuen and Peltier}(1982)}]{Yuen1982}
+Yuen, D.~A., and W.~R. Peltier (1982), {Normal modes of the viscoelastic
+  earth}, \textit{Geophysical Journal of the Royal Astronomical Society},
+  \textit{69}, 495--526, \doi{10.1111/j.1365-246X.1982.tb04962.x}.
+
+\end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Track Changes:
+% To add words, \added{<word added>}
+% To delete words, \deleted{<word deleted>}
+% To replace words, \replace{<word to be replaced>}{<replacement word>}
+% To explain why change was made: \explain{<explanation>} This will put
+% a comment into the right margin.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% At the end of the document, use \listofchanges, which will list the
+% changes and the page and line number where the change was made.
+
+% When final version, \listofchanges will not produce anything,
+% \added{<word or words>} word will be printed, \deleted{<word or words} will take away the word,
+% \replaced{<delete this word>}{<replace with this word>} will print only the replacement word.
+%  In the final version, \explain will not print anything.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%
+\listofchanges
+%%%
 
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Supporting Information
+%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
+%% for Supporting Information.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+More Information and Advice:
+
+%% ------------------------------------------------------------------------ %%
+%
+%  SECTION HEADS
+%
+%% ------------------------------------------------------------------------ %%
+
+% Capitalize the first letter of each word (except for
+% prepositions, conjunctions, and articles that are
+% three or fewer letters).
+
+% AGU follows standard outline style; therefore, there cannot be a section 1 without
+% a section 2, or a section 2.3.1 without a section 2.3.2.
+% Please make sure your section numbers are balanced.
+% ---------------
+% Level 1 head
+%
+% Use the \section{} command to identify level 1 heads;
+% type the appropriate head wording between the curly
+% brackets, as shown below.
+%
+%An example:
+%\section{Level 1 Head: Introduction}
+%
+% ---------------
+% Level 2 head
+%
+% Use the \subsection{} command to identify level 2 heads.
+%An example:
+%\subsection{Level 2 Head}
+%
+% ---------------
+% Level 3 head
+%
+% Use the \subsubsection{} command to identify level 3 heads
+%An example:
+%\subsubsection{Level 3 Head}
+%
+%---------------
+% Level 4 head
+%
+% Use the \subsubsubsection{} command to identify level 3 heads
+% An example:
+%\subsubsubsection{Level 4 Head} An example.
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  IN-TEXT LISTS
+%
+%% ------------------------------------------------------------------------ %%
+%
+% Do not use bulleted lists; enumerated lists are okay.
+% \begin{enumerate}
+% \item
+% \item
+% \item
+% \end{enumerate}
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  EQUATIONS
+%
+%% ------------------------------------------------------------------------ %%
+
+% Single-line equations are centered.
+% Equation arrays will appear left-aligned.
+
+Math coded inside display math mode \[ ...\]
+ will not be numbered, e.g.,:
+ \[ x^2=y^2 + z^2\]
+
+ Math coded inside \begin{equation} and \end{equation} will
+ be automatically numbered, e.g.,:
+ \begin{equation}
+ x^2=y^2 + z^2
+ \end{equation}
+
+% To create multiline equations, use the
+% \begin{eqnarray} and \end{eqnarray} environment
+% as demonstrated below.
+\begin{eqnarray}
+  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
+        && + (y - y_{0}) \sin \Theta  \nonumber \\
+  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
+        && + (y - y_{0}) \cos \Theta.
+\end{eqnarray}
+
+%If you don't want an equation number, use the star form:
+%\begin{eqnarray*}...\end{eqnarray*}
+
+% Break each line at a sign of operation
+% (+, -, etc.) if possible, with the sign of operation
+% on the new line.
+
+% Indent second and subsequent lines to align with
+% the first character following the equal sign on the
+% first line.
+
+% Use an \hspace{} command to insert horizontal space
+% into your equation if necessary. Place an appropriate
+% unit of measure between the curly braces, e.g.
+% \hspace{1in}; you may have to experiment to achieve
+% the correct amount of space.
+
+%% ------------------------------------------------------------------------ %%
+%
+%  EQUATION NUMBERING: COUNTER
+%
+%% ------------------------------------------------------------------------ %%
+
+% You may change equation numbering by resetting
+% the equation counter or by explicitly numbering
+% an equation.
+
+% To explicitly number an equation, type \eqnum{}
+% (with the desired number between the brackets)
+% after the \begin{equation} or \begin{eqnarray}
+% command.  The \eqnum{} command will affect only
+% the equation it appears with; LaTeX will number
+% any equations appearing later in the manuscript
+% according to the equation counter.
+%
+
+% If you have a multiline equation that needs only
+% one equation number, use a \nonumber command in
+% front of the double backslashes (\\) as shown in
+% the multiline equation above.
+
+% If you are using line numbers, remember to surround
+% equations with \begin{linenomath*}...\end{linenomath*}
+
+%  To add line numbers to lines in equations:
+%  \begin{linenomath*}
+%  \begin{equation}
+%  \end{equation}
+%  \end{linenomath*}

### 2016-04-22 JGRSubmission/ElMayor.tex
commit before push;

@@
 \begin{keypoints}
-\item = enter point 1 here = 
-\item = enter point 2 here = 
-\item = enter point 3 here = 
+\item Transient postseismic deformation can be observed following the El Mayor-Cucapah earthquake at epicentral distances of up to 400 km
+
+\item Near-field postseismic deformation exhibits early transience that decays to a sustained rate which is elevated above the preseismic trend
+
+\item A Zener or Burgers upper mantle can explain far-field deformation while near-field transience can be described with afterslip
 \end{keypoints}
@@
 In this study, we perform a kinematic inversion for fault slip, allowing it to persist throughout the postseismic period, while simultaneously estimating the viscosity of the lower crust and upper mantle.
-we use the method described in \citet{Hines2016} to create an initial model of the fault slip and effective viscosity necessary to describe early postseismic deformation, which has the richest signature of the underlying deformation mechanisms.
-Our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
+We create an initial model of the fault slip and effective viscosity necessary to describe early postseismic deformation using the method described in \citet{Hines2016}.
+This method utilizes a first-order approximation of surface deformation resulting from viscoelastic relaxation which is only applicable to the early postseismic period.
+In this case, our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
 We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah, a Zener rheology in the upper mantle with a transient viscosity that decays from $6\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and a Zener rheology in the upper mantle with a transient viscosity that decays from $6\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth.
 
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[scale=0.8]{Figures/FinalSlip}

### 2016-04-22 JGRSubmission/ElMayor.tex
commit before push

@@
 
-\begin{figure}
-\includegraphics[scale=0.8]{Figures/ContextMap} 
-\caption{Map of the region considered in this study.
+%\begin{figure}
+%\includegraphics[scale=0.8]{Figures/ContextMap} 
+%\caption{Map of the region considered in this study.
 The large focal mechanism is for the El Mayor-Cucapah earthquake, and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
@@
 Stations inside the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in Figures \ref{fig:RecordSectionElastic}, \ref{fig:RecordSection1}, and \ref{fig:RecordSection2}}.
-\label{fig:ContextMap}
-\end{figure}
+%\label{fig:ContextMap}
+%\end{figure}
 
 \section{Data Processing}\label{sec:Data}
-
 We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicenter.
@@
 We then model $u_\mathrm{obs}(t)$ as
+
 \begin{equation}
@@
 where
+
 \begin{equation}\label{TimeSeriesModel}
@@
 We therefore do not assume any parametric form for $u_\mathrm{post}(t)$ and rather treat it as integrated Brownian motion, so that
+
 \begin{equation}
@@
 In the context of Kalman filtering, our time varying state vector is
+
 \begin{equation}
@@
 We then use the posterior estimate of the state at time $t_i$ to form a prior estimate of the state at time $t_{i+1}$ through the transition function
+
 \begin{equation}\label{predict}
@@
 where
+
 \begin{equation}
@@
 and $\mathbf{\delta}_{i+1}$ is the process noise, which has zero mean and covariance described by
+
 \begin{equation}
@@
 The covariance of the new prior state, $\mathbf{X}_{i+1|i}$, is then described by
+
 \begin{equation}
@@
 Our forward problem describing predicted postseismic deformation $u_\mathrm{pred}$ in terms of time dependent fault slip, $s$, is
+
 \begin{equation}\label{eq:ElasticForward}
@@
 We also add zeroth-order Tikhonov regularization so that our solution for $s$ satisfies
+
 \begin{equation}\label{eq:ElasticObjective}
@@
 For any linear viscoelastic rheology of the crust and mantle, postseismic displacements resulting from time dependent fault slip can be described as
+
 \begin{equation}\label{GeneralForward}
@@
 $\eta_\mathrm{eff}$.  Using one-dimensional viscoelastic models, we define the effective viscosity as
+
 \begin{equation}
@@
 That is to say
+
 \begin{equation}\label{InitialRate}
@@
 (\ref{GeneralForward}) to get a first order approximation for early postseismic deformation,
+
 \begin{equation}\label{ApproxForward}
@@
 We estimate coseismic slip, afterslip, and effective viscosities by solving
+
 \begin{equation}\label{ObjectiveFunction}
@@
 We appraise each model using the mean chi-squared value,
+
 \begin{equation}\label{eq:Misfit}
@@
 EAR-1261833.
+The data used in this study can be found at www.unavco.org.
 This material is based upon work supported by the National Science Foundation under Grant Numbers EAR 1045372 and EAR 1245263.

### 2016-05-02 JGRSubmission/ElMayor.tex
cleaned up directory

--- 2016-04-22 JGRSubmission/ElMayor.tex
@@
 \section{Data Processing}\label{sec:Data}
-
 We use continuous GPS position time series provided by University Navstar Consortium (UNAVCO) for stations within a 400 km radius about the El Mayor-Cucapah epicenter.
@@
 We find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after one year, while still requiring about the same amount of afterslip over the first year.
-We do believe that the early shallow afterslip on the Sierra Cucapah segment is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
+We do believe that the early, shallow afterslip on the Sierra Cucapah segment is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
 
@@
 We have extracted a filtered and smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.
-We treated postseismic deformation as a stochastic process where we did not presume any characteristic shape of the postseismic time series.
 Our estimated postseismic deformation reveals far-field (epicentral distances beyond ${\sim}200$ km) transient deformation which is largely undetectable after about three years.
 Near-field deformation exhibits transience that decays to a sustained, elevated rate after about one or two years.
-We found that near-field transient deformation can be explained with shallow afterslip, and the sustained rate of near-field deformation can either be explained with continued afterslip or relaxation in a lower crustal with a viscosity of ${\sim}10^{19}$ Pa s.
+We found that near-field transient deformation can be explained with shallow afterslip, and the sustained rate of near-field deformation can either be explained with continued afterslip or viscoelastic relaxation in the lower crust.
 Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km.

### 2016-06-27 JGRRevision/CoverLetter.tex
started working on revisions

\documentclass[12pt,letterpaper]{letter}

\oddsidemargin -0.3in
\evensidemargin -0.3in
\textwidth 7.1in
\topmargin -0.5in
\textheight 9in

\begin{document}

\address{Department of Earth and Environmental Sciences\\
  University of Michigan\\
  1100 North University Ave.\\
  Ann Arbor, MI 48109\\}

\signature{Trever T. Hines}

\begin{letter}{Journal of Geophysical Research: Solid Earth}
\opening{Dear Editor,}

We are submitting this manuscript, ``Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake'', for consideration for publication in
Journal of Geophysical Research: Solid Earth.  The first author is a PhD student in his fourth year and this manuscript will be the third chapter of his dissertation.  In this manuscript, we analyze displacement time series for GPS stations within 400 km of the 2010 El Mayor-Cucapah earthquake. After estimating postseismic displacements at each station, we observe transient deformation over a much broader region than has been recognized in previous studies on this earthquake.  We attempt to describe the mechanisms causing this deformation using our recently published technique.  We find that a transient viscoelastic rheology, rather than a fluid-like rheology (e.g. Maxwell viscoelasticity), is needed to describe the far-field postseismic deformation.  We are particularly excited by this result because our preferred model does not conflict with the steady-state viscosities inferred from geophysical processes occurring over longer time scales, which is a problem with most postseismic studies.

\closing{Thank you for your consideration,}

\end{letter}
\end{document}

### 2016-06-27 JGRRevision/ElMayor.tex
started working on revisions

--- 2016-05-02 JGRSubmission/ElMayor.tex
@@
 \begin{abstract}
-Five years of postseismic deformation following the  Mw7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about three years at epicentral distances greater than ${\sim}200$ km.
-At closer distances, the rapid transience decays to a sustained rate which exceeds its pre-earthquake trend.
+Five years of postseismic deformation following the  Mw=7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about three years at epicentral distances greater than ${\sim}200$ km.
+At shorter distances, the rapid transience decays to a sustained rate which exceeds its pre-earthquake trend.
 We attempt to determine the mechanisms driving this deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
@@
 \section{Introduction}
-Ground deformation in the years following a large ($\gtrsim$Mw7) earthquake provides insight into the mechanical behavior of the crust and upper mantle.
-It has long been recognized that interpretations of postseismic deformation can be ambiguous because multiple postseismic deformation mechanisms can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
+Ground deformation in the years following a large ($\gtrsim$Mw7) earthquake can be used to gain insight into the mechanical behavior of the crust and upper mantle.
+The interpretations of postseismic deformation are not always conclusive because multiple postseismic deformation mechanisms, such as afterslip or viscoelastic relaxation in the lower crust and upper mantle, can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
+This complication can potentially be remedied by having a sufficient number of well positioned observations of the postseismic displacement field \citep{Hearn2003}.
 Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date.
-With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake, where we consider both afterslip and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
+With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake.
+
+Here is some background on the El Mayor Earthquake
 
@@
 For example, it is commonly assumed that the lower crust and upper mantle are homogeneous, Maxwell viscoelastic layers, which may be too simplistic for postseismic studies  \citep{Riva2009,Hines2013}.
-To further reduce the dimensions of the model space, it is also necessary to make simplifying assumptions about the nature of afterslip.
+To further reduce the dimensions of the model space, it is also necessary to make simplifying assumptions about the behavior of afterslip.
 For example, one can assume a frictional model for afterslip and parametrize afterslip in terms of the unknown rheologic properties of the fault \citep[e.g.][]{Johnson2009,Johnson2004}.
@@
 The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ over fitting the data.
-While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we instead take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most pronounced rapid changes in velocity.
+While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we instead take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most rapid changes in velocity.
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
@@
 The near-field postseismic deformation is notably sustained when compared to the far-field deformation.
-Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, has been moving at a steady rate of ${\sim}1.5$ cm/yr to the south since about one year after the El Mayor-Cucapah earthquake.
+Namely, the station in this study which is closest to the El Mayor-Cucapah epicenter, P496, has a steady postseismic trend of ${\sim}1.5$ cm/yr to the south after about one year.
 Vertical postseismic deformation in the near-field does display a quadrant pattern which is consistent with the coseismic vertical deformation, suggesting that it is resulting from postseismic processes.
@@
 where $F$ denotes the fault and $g(x,\xi)$ is the elastic Green's function describing displacement at surface position $x$ resulting from slip at $\xi$ on the fault.
-We estimate coseismic slip and the rate of afterslip at the discrete time intervals, 0.0-0.125, 0.125-0.25, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
-Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and thrust component of slip for each patch.
+We estimate coseismic slip and the rate of afterslip over the time intervals 0.0-0.125, 0.125-0.25, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
+Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and dip component of slip for each patch.
 We impose that the direction of slip and slip rate are within 45$^\circ$ of right-lateral.

### 2016-06-29 JGRRevision/ElMayor.tex
made checkerboard figures

@@
 The simplest rheologic model is to consider them to be effectively elastic and isotropic.
-In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011} throughout this paper (Table \ref{tab:MaterialProperties}).
+In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011} throughout this paper (Table 1).
 The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.

### 2016-06-29 JGRRevision/ElMayor.tex
added supplementary material

@@
 \begin{abstract}
+
 Five years of postseismic deformation following the  Mw=7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about three years at epicentral distances greater than ${\sim}200$ km.
@@
 \section{Introduction}
-Ground deformation in the years following a large ($\gtrsim$Mw7) earthquake can be used to gain insight into the mechanical behavior of the crust and upper mantle.
+Ground deformation in the years following a large (Mw$\gtrsim$7) earthquake can be used to gain insight into the mechanical behavior of the crust and upper mantle.
 The interpretations of postseismic deformation are not always conclusive because multiple postseismic deformation mechanisms, such as afterslip or viscoelastic relaxation in the lower crust and upper mantle, can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
 This complication can potentially be remedied by having a sufficient number of well positioned observations of the postseismic displacement field \citep{Hearn2003}.
-Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date.
+Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw=7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date.
 With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake.
@@
 The green and red boxes demarcate the extent of the near-field and far-field maps (Figures \ref{fig:NearField} and \ref{fig:FarField}).
-Stations inside the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in Figures \ref{fig:RecordSectionElastic}, \ref{fig:RecordSection1}, and \ref{fig:RecordSection2}}.
+Stations inside the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in Figures \ref{fig:RecordSectionMain} and \ref{fig:RecordSection1}.}
 \label{fig:ContextMap}
@@
 We consider the GPS position time series $u_\mathrm{obs}(t)$ to be the combination of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010, Mw5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw5.5 and an Mw5.4 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
+The June 14, 2010, Mw=5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw=5.5 and an Mw=5.4 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
 We treat the displacements resulting from the Brawley swarm as a single event because the daily solutions provided by UNAVCO cannot resolve the separate events.
@@
 
-The October 16, 1999, Mw7.1 Hector Mine earthquake, which occurred ${\sim}270$ km north of the El Mayor-Cucapah epicenter, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
+The October 16, 1999, Mw=7.1 Hector Mine earthquake, which occurred ${\sim}270$ km north of the El Mayor-Cucapah epicenter, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
 We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/FilterP496}
+\includegraphics[scale=0.9]{Figures/FilterP496}
 \centering
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/FilterP619}
+\noindent\includegraphics[scale=0.9]{Figures/FilterP619}
 \centering
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/MapViewNearField}
+\includegraphics[scale=0.9]{Figures/MapViewNearField}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/MapViewFarField}
+\includegraphics[scale=0.9]{Figures/MapViewFarField}
 \centering 
@@
 As with \citet{Rollins2015}, we find that a large amount of afterslip on the southern fault segment is required to explain the observations.
-The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.28 earthquake when assuming a shear modulus of 32 GPa.
-The potency of our inferred cumulative five years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
-Figure \ref{fig:RecordSectionElastic} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P axis.
+The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw=7.28 earthquake when assuming a shear modulus of 32 GPa.
+The potency of our inferred cumulative five years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw=7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
+Figure \ref{fig:RecordSectionMain} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P axis.
 We show the radial component of displacements with respect to the El Mayor-Cucapah epicenter and we also rescale the displacements so that the difference between the minimum and maximum observed displacements are the same for each station.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/ElasticSlip}
+\includegraphics[scale=0.9]{Figures/ElasticSlip}
 \caption{Coseismic slip and cumulative afterslip over the indicated intervals for the elastic model from Section \ref{sec:ElasticInversion}.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/RecordSectionElastic}
-\caption{Scaled radial component of observed postseismic displacements $u_\mathrm{obs}$ (black) and displacements predicted by the best fitting elastic model $u_\mathrm{pred}$ (blue).
+\includegraphics[scale=0.9]{Figures/RecordSectionFinal}
+\caption{Scaled radial component of postseismic displacements.
 Downward motion indicates that the station is moving toward the El Mayor-Cucapah epicenter.
 Displacement time series are scaled so that the minimum and maximum observed values lie on the grid lines.
-The 68\% confidence interval for the observed displacements are shown in gray.}
-\label{fig:RecordSectionElastic}
+The observed postseismic displacements, $u_\mathrm{obs}$ are shown in black with gray indicating the 68\% confidence interval.
+The displacements predicted by the best fitting elastic model $u_\mathrm{pred}$ are shown in red.
+The blue and green lines are the predicted postseismic displacements for the models discussed in Section 3.3.
+The blue lines show the predicted displacements for the model with a Maxwell viscoelastic lower crust and upper mantle.
+The green line shows the predicted displacements for the model with a Maxwell viscoelastic lower crust and a Zener viscoelastic upper mantle.
+The effective viscosities are the same for both models and are shown in Figure \ref{fig:EffectiveViscosity}.}
+\label{fig:RecordSectionMain}
 \end{figure}
@@
 \subsection{Early Postseismic Inversion}\label{sec:InitialInversion}
-
 For any linear viscoelastic rheology of the crust and mantle, postseismic displacements resulting from time dependent fault slip can be described as
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/rheology}
+\includegraphics[scale=0.9]{Figures/rheology}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/Cancellation}
+\includegraphics[scale=0.9]{Figures/Cancellation}
 \caption{Displacements resulting from fault slip at lower crustal depths (a), and initial velocities resulting from subsequent relaxation of a viscoelastic lower crust (b).
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/RecordSectionDuration}
+\includegraphics[scale=0.9]{Figures/RecordSectionDuration}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/EffectiveViscosity}
+\includegraphics[scale=0.9]{Figures/EffectiveViscosity}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/InitialSlip}
+\includegraphics[scale=0.9]{Figures/InitialSlip}
 \caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
@@
 For comparison, $\bar\chi^2=35.3$ for the elastic model from Section \ref{sec:ElasticInversion}.
-The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about three years (Figure \ref{fig:RecordSection2}).
+The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about three years (Figure \ref{fig:RecordSectionMain}).
 Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle.
@@
 The shear moduli ratio that yields the best prediction to the observed postseismic displacements is found to be $0.375$ which produces a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
-The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSection2}).
+The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSectionMain}).
 The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the five years.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/RatioMisfit}
+\includegraphics[scale=0.9]{Figures/RatioMisfit}
 \centering 
@@
 
-\begin{figure}
-\includegraphics[scale=0.8]{Figures/RecordSectionFinal}
-\centering 
-\caption{Observed postseismic displacements (black).
-Predicted postseismic displacements for the best fitting slip model when assuming a Maxwell viscoelastic lower crust and upper mantle (blue).
-Predicted postseismic displacements for the best fitting slip model when assuming a Maxwell viscoelastic lower crust and a Zener viscoelastic upper mantle (green).
-The effective viscosities are the same for both models and are shown in Figure \ref{fig:EffectiveViscosity}.}
-\label{fig:RecordSection2}
-\end{figure}
-
 Because we are able to adequately describe the available five years of postseismic deformation with a Zener model, we do not find it necessary to explore the parameter space for a more complicated Burgers rheology.
@@
 The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip}.
-The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw7.26 earthquake, and most of the slip is shallow and on the Sierra Cucapah fault segment.
+The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw=7.26 earthquake, and most of the slip is shallow and on the Sierra Cucapah fault segment.
 The potency of five years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
@@
 
-the postseismic displacements predicted by our preferred model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSection2}.
+the postseismic displacements predicted by our preferred model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
 Overall, the trends in the near-field and far-field transient deformation are accurately described.
-In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (Figure \ref{fig:RecordSection2}).
+In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (Figure \ref{fig:RecordSectionMain}).
 There are a few areas where we have notable misfit.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/FinalSlip}
+\includegraphics[scale=0.9]{Figures/FinalSlip}
 \centering 
@@
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
-However, postseismic deformation at distances greater than ${\sim}200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSection2}).
+However, postseismic deformation at distances greater than ${\sim}200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSectionMain}).
 

### 2016-06-29 JGRRevision/Supplementary/effective_viscosity.py

@@ -1,102 +1,0 @@
-#!/usr/bin/env python
-import numpy as np
-import sympy as sp
-import matplotlib.pyplot as plt
-
-
-def ivt(uhat,s,n):
-  ''' 
-  Extension of the initial value theorem which computes the n'th
-  derivative of u(t) evaluated at t=0 from the Laplace transform of
-  u(t), uhat(s).
-
-  This is eq. (A.5) in Appendix A
-
-  PARAMETERS
-  ----------
-    uhat: Laplace transform of u. This is a symbolic expression
-      containing s
-    s: Laplace domain variable
-    n: the derivative order
-
-  RETURNS
-  -------
-    u_n: symbolic expression for the nth derivative of u evaluated at
-      t=0
-  '''
-  if n == 0:
-    expr = s*uhat
-    u_0 = expr.limit(s,np.inf)
-    return u_0
-
-  elif n > 0:
-    expr = s**(n+1)*uhat - sum(s**m*ivt(uhat,s,n-m) for m in range(1,n+1))
-    u_n = expr.limit(s,np.inf)
-    return u_n
-
-def ilt(uhat,s,t,N):
-  ''' 
-  Evaluates the inverse Laplace transform of uhat(s) through a Taylor
-  series expansion
-
-  This is a combination of eqs. (A.7) and (A.5) in Appendix A
-
-  PARAMETERS
-  ----------
-    uhat: Laplace transform of u. This is a symbolic expression
-      containing s
-    s: Laplace domain variable
-    t: time domain variable
-    N: order of the Taylor series expansion
-
-  RETURNS
-  -------
-    series: symbolic expression for the series expansion of the u(x)
-     about x=0
-  '''
-  series = sum((ivt(uhat,s,n)*t**n)/sp.factorial(n) for n in range(N+1))
-  return series
-
-s = sp.symbols('s')
-t = sp.symbols('t')
-mu = sp.symbols('mu')
-muk = sp.symbols('mu_K')
-muk1 = sp.symbols('mu_K1')
-muk2 = sp.symbols('mu_K2')
-etam = sp.symbols('eta_M')
-etak = sp.symbols('eta_K')
[…]

### 2016-06-30 JGRRevision/ElMayor.tex
made some revisions

@@
 
-\item A Zener or Burgers upper mantle can explain far-field deformation while near-field transience can be described with afterslip
+\item Far-field postseismic deformation can be explained with a Zener or Burgers rheology upper mantle
+
 \end{keypoints}
@@
 
-Five years of postseismic deformation following the  Mw=7.2 El Mayor-Cucapah earthquake reveals transient deformation that decays back to its pre-earthquake trend after about three years at epicentral distances greater than ${\sim}200$ km.
-At shorter distances, the rapid transience decays to a sustained rate which exceeds its pre-earthquake trend.
+We analyze five years of Southern California GPS data following the Mw=7.2 El Mayor-Cucapah earthquake.
+We observed transient postseismic deformation which persists for three years at epicentral distances greater than ${\sim}200$ km.
+In the near-field, rapid postseismic transience decays to a sustained rate which exceeds its pre-earthquake trend.
 We attempt to determine the mechanisms driving this deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
@@
 Of these studies, \citet{Gonzalez-ortega2014} and \citet{Rollins2015} have attempted to describe the postseismic deformation with afterslip in an elastic half-space.
-\citet{Gonzalez-ortega2014} described five months of postseismic deformation, observed by InSAR and GPS within ${\sim}50$ km of the rupture, with afterslip and contraction on the coseismically ruptured fault.
+\citet{Gonzalez-ortega2014} described five months of postseismic deformation, observed by InSAR and GPS stations within ${\sim}50$ km of the rupture, with afterslip and contraction on the coseismically ruptured fault.
 \citet{Gonzalez-ortega2014} noted that their preferred model underestimated the GPS displacements for stations $\gtrsim 25$ km from the rupture and suggested that it could be the result of unmodeled viscoelastic relaxation.
@@
 We create an initial model of the fault slip and effective viscosity necessary to describe early postseismic deformation using the method described in \citet{Hines2016}.
-This method utilizes a first-order approximation of surface deformation resulting from viscoelastic relaxation which is only applicable to the early postseismic period.
+This method uses a first-order approximation of surface deformation resulting from viscoelastic relaxation which is only applicable to the early postseismic period.
 In this case, our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
 We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and a Zener rheology in the upper mantle with a transient viscosity that decays from $6\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and a Zener rheology in the upper mantle with a transient viscosity on the order of $10^{18}$ Pa s.
 
@@
 We collectively describe the coseismic and postseismic displacements resulting from the El Mayor-Cucapah earthquake as $u_\mathrm{post}(t)$.
-We consider the GPS position time series $u_\mathrm{obs}(t)$ to be the combination of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
+We consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the combination of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
 The June 14, 2010, Mw=5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw=5.5 and an Mw=5.4 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
@@
 In the above equations, $t_\mathrm{emc}$, $t_\mathrm{oc}$ and $t_\mathrm{bs}$ are the times of the El Mayor-Cucapah earthquake, Ocotillo earthquake, and the Brawley swarm, respectively, $c_0$ through $c_7$ are unknown coefficients, and $\epsilon$ is the observation noise.
+We are using years as our unit of time which makes $c_2$ through $c_5$ the coefficients for annual and semi-annual oscillations.
 We only estimate jumps associated with the Ocotillo earthquake and Brawley swarm for stations within 40 km of their epicenters.
@@
 This includes stations in the Los Angeles basin, where anthropogenic deformation can be larger than the postseismic signal that we are trying to estimate \citep{Bawden2001,Argus2005}.
-In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake.
-Several GPS stations were installed after the El Mayor-Cucapah earthquake to improve the spatial resolution of postseismic deformation \citep{Spinler2015}.
-Although it would be possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities, we do not do so here.
-We use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
-We use displacements because estimating velocities from an already noisy displacement time series can introduce significant uncertainties depending on exactly how the estimation is done.
-This choice prevents us from using the newly installed stations in Baja California for our analysis.
+In order to ensure an accurate estimation of the secular deformation, we only use stations that were installed at least six months prior to El Mayor-Cucapah earthquake even though several GPS stations were installed after the earthquake to get better coverage of the postseismic deformation field \citep{Spinler2015}.
+It would be possible to subtract secular velocities derived from elastic block models \citep[e.g.][]{Meade2005} from velocities recorded at the newly installed stations to get an estimate of postseismic velocities at those stations.
+However, estimating velocities from an already noisy displacement time series can introduce significant uncertainties depending on exactly how the estimation is done.
+We therefore use coseismic and postseismic displacements, rather than velocities, in our inverse method described in Section \ref{sec:Model}.
+This choice prevents us from using the newly installed stations for our analysis.
 
 The October 16, 1999, Mw=7.1 Hector Mine earthquake, which occurred ${\sim}270$ km north of the El Mayor-Cucapah epicenter, produced transient postseismic deformation which we do not wish to model, either mechanically or through empirical line fitting.
-We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites proximal to the Hector Mine epicenter are approximately constant \citep{Savage2009}.
+We thus restrict our analysis to deformation observed six years after the Hector Mine earthquake, which is when postseismic velocities at sites near the Hector Mine epicenter are approximately constant \citep{Savage2009}.
 When appraising our model fit in Section \ref{sec:Model}, we see some systematic residuals in the vicinity of the Hector Mine epicenter, which may be the result of errors in the assumption that the trend in Hector Mine postseismic deformation is linear after six years.
@@
 We initiate the Kalman filter by assuming a prior estimate of $\mathbf{X}(t)$ at the first time epoch, denoted $\mathbf{X}_{1|0}$, which has a sufficiently large covariance, denoted $\mathbf{\Sigma}_{1|0}$, to effectively make our prior uninformed.
-For each time epoch $t_i$, Bayesian linear regression is used to incorporate GPS derived estimates of displacement with our prior estimate of the state $\mathbf{X}_{i|i-1}$ to form a posterior estimate of the state $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
+For each time epoch, $t_i$, Bayesian linear regression is used to incorporate GPS derived estimates of displacement with our prior estimate of the state, $\mathbf{X}_{i|i-1}$, to form a posterior estimate of the state, $\mathbf{X}_{i|i}$, which has covariance $\mathbf{\Sigma}_{i|i}$.
 We then use the posterior estimate of the state at time $t_i$ to form a prior estimate of the state at time $t_{i+1}$ through the transition function
@@
 We assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
-\citet{Freed2007a} noted that postseismic deformation can be observed at distances greater than 200 km from the Hector Mine earthquake and, after filtering the time series for stations up to 400 km from the El Mayor-Cucapah epicenter, we also clearly see far reaching postseismic transient deformation (Figure \ref{fig:P619}).
+We include an example of estimating $u_\mathrm{post}(t)$ for a far-field station, P619, which is about 359 km from the El Mayor-Cucapah epicenter (Figure \ref{fig:P619}).
+At station P619, along with all the other stations in the Mojave region, there is a south-trending postseismic transience that persists for the first three years after the El Mayor-Cucapah earthquake.
+Postseismic deformation that extends to these epicentral distances has also been observed after the Hector Mine earthquake \citep{Freed2007a}.
 
@@
 Stations at epicentral distances beyond ${\sim}200$ km have an elevated rate of deformation for the first three years following the earthquake.
-This far-field deformation has a southward trend along the direction of the El Mayor-Cucapah P axis and a similar eastward trend can be seen in the few far-field stations in Arizona, located along the T axis.
+This far-field deformation is trending southward at a rate of a few millimeters per year along the direction of the El Mayor-Cucapah P axis.
+A similar eastward trend can be seen in the few far-field stations in Arizona, located along the T axis.
 After three years, the trend in far-field postseismic deformation is barely perceptible.
@@
 \caption{Near-field coseismic and cumulative postseismic displacements over the indicated time periods (black) as well as predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
-Observed vertical deformation is shown as an interpolated field and predicted vertical displacements are shown within the circles at the base of each vector.
+Observed vertical deformation is shown as an interpolated field and predicted vertical displacements are shown within the green circles.
 Note that the interpolant is not well constrained in Mexico where there is no data available.}
@@
 where $F$ denotes the fault and $g(x,\xi)$ is the elastic Green's function describing displacement at surface position $x$ resulting from slip at $\xi$ on the fault.
-We estimate coseismic slip and the rate of afterslip over the time intervals 0.0-0.125, 0.125-0.25, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
+We estimate coseismic slip and the rate of afterslip over the time intervals 0.0-0.125, 0.125-0.25, 0.25-0.5, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
 Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and dip component of slip for each patch.
@@
 Our coseismic slip and afterslip solutions are shown in Figure \ref{fig:ElasticSlip}.
-As with \citet{Rollins2015}, we find that a large amount of afterslip on the southern fault segment is required to explain the observations.
+As with \citet{Rollins2015}, we find that a large amount of afterslip on the Indiviso fault segment is required to explain the observations.
 The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw=7.28 earthquake when assuming a shear modulus of 32 GPa.
@@
 Displacement time series are scaled so that the minimum and maximum observed values lie on the grid lines.
-The observed postseismic displacements, $u_\mathrm{obs}$ are shown in black with gray indicating the 68\% confidence interval.
+The observed postseismic displacements, $u_\mathrm{post}$ are shown in black with gray indicating the 68\% confidence interval.
 The displacements predicted by the best fitting elastic model $u_\mathrm{pred}$ are shown in red.
@@
 In order to greatly simplify the inverse problem, we use the method described in \citet{Hines2016} to constrain an initial effective viscosity structure from the early postseismic deformation.
-Our method utilizes the fact that coseismic stresses throughout the crust and upper mantle depend on the instantaneous elastic parameters and are independent of the viscoelastic parameters which we wish to estimate.
-Immediately following an earthquake, each parcel will have a strain rate that is proportional to the coseismic stress and inversely proportional to the parcel's effective viscosity,
-$\eta_\mathrm{eff}$.  Using one-dimensional viscoelastic models, we define the effective viscosity as
+Our method uses the fact that coseismic stresses throughout the crust and upper mantle depend on the instantaneous elastic parameters and are independent of the viscoelastic parameters which we wish to estimate.
+Immediately following an earthquake, each parcel will have a strain rate that is proportional to the coseismic stress and inversely proportional to the parcel's effective viscosity, $\eta_\mathrm{eff}$.
+Using one-dimensional rheologic models, we define the effective viscosity as
 
@@
 Due to inherent non-uniqueness, we have added zeroth-order Tikhonov regularization to estimates of $s$ and second-order Tikhonov regularization to estimates of effective fluidity $\eta_\mathrm{eff}^{-1}$.
-The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$, which are chosen with trade-off curves.
+The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$, which are chosen with trade-off curves (Figure S1).
 Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in Section \ref{sec:FullInversion}.
@@
 
+Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in Figure \ref{fig:InitialSlip}.
+Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, a significant amount of right-lateral and normal coseismic slip is inferred to be on the Sierra Cucapah segment.
+Our coseismic slip solution on the Sierra Cucapah segment is consistent with field studies \citep{Fletcher2014} and the model from \citet{Wei2011}.
+Our inferred slip on the Indiviso fault segment differs from \citet{Wei2011} because the GPS data used in this study is not capable of resolving the spatial distribution of fault slip on that segment (Figure S2).
+The potency of inferred coseismic slip is $3.3\times 10^{9}\ \mathrm{m}^3$, which is also about the same as that inferred from Section \ref{sec:ElasticInversion}.
+The present inference of afterslip on the Indiviso fault is significantly less than what was found in the Section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
+When fault slip is simultaneously estimated with viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.5\times10^{9}\ \mathrm{m}^3$ when we assume the crust and upper mantle are elastic.
+The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
+The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
+
 Our estimated effective viscosities, and corresponding fluidities, are shown in Figure \ref{fig:EffectiveViscosity}.
@@
 (\ref{InitialRate}) is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each layer.
-We also show the 95\% confidence intervals for estimated viscosities and fluidities but we note that the uncertainties tend to be underestimated due to the added regularization \citep{Aster2011}.
-A robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
+We use bootstrapping to find the 95\% confidence intervals for our estimated effective viscosities which are shown in Figure \ref{fig:EffectiveViscosity}.
+It is important to remember that the presented effective viscosities were estimated with a smoothing regularization constraint and so the uncertainties are almost certainly underestimated \citep{Aster2011}.
+The uncertainties are shown to give the reader a sense of the relative confidence between layers.
+Indeed, many viscosity profiles which are outside of the shown confidence intervals can just as adequately described the first 0.8 years of postseismic deformation.
+The solution in (Figure \ref{fig:EffectiveViscosity}) should be interpreted as the smoothest effective viscosity profile which is capable of describing the data.
+This means that any  sharp viscosity transitions will be tapered out, which we demonstrate with a synthetic test in Figure S2.
+Nonetheless, a robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
 This transitional depth is also consistent with the the viscosity structure required to explain far-field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
 We find that the viscosity below 60 km depth needs to be ${\sim}10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
-The viscosity of the lower crust is the least well constrained as there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
+The viscosity of the lower crust is the least well constrained because there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
+
+\begin{figure}
+\includegraphics[scale=0.9]{Figures/InitialSlip}
+\caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
+\label{fig:InitialSlip}
+\end{figure}
 
@@
 
-Our initial estimate for coseismic slip and cumulative afterslip over the first 0.8 years after the El Mayor-Cucapah earthquake are shown in Figure \ref{fig:InitialSlip}.
-Similar to our elastic slip model from Section \ref{sec:ElasticInversion}, a significant amount of right-lateral and normal coseismic slip is inferred to be on the Sierra Cucapah fault segment.
-Our coseismic slip solution is consistent with field studies \citep{Fletcher2014} and the model from \citet{Wei2011}.
-The potency of inferred coseismic slip is $3.3\times 10^{9}\ \mathrm{m}^3$, which is also about the same as that inferred from Section \ref{sec:ElasticInversion}.
-The present inference of afterslip on the Indiviso fault is significantly less than what was found in the Section \ref{sec:ElasticInversion} where we did not account for viscoelasticity.
-When fault slip is simultaneously estimated with viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.5\times10^{9}\ \mathrm{m}^3$ when we assume the crust and upper mantle are elastic.
-The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
-The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
-
-\begin{figure}
-\includegraphics[scale=0.9]{Figures/InitialSlip}
-\caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
-\label{fig:InitialSlip}
-\end{figure}
-
 \subsection{Full Postseismic Inversion}\label{sec:FullInversion}
@@
 \begin{equation}\label{eq:Misfit}
-  \bar\chi^2 = \frac{1}{N}\left|\left|\frac{u_\mathrm{pred} - u_\mathrm{obs}}{\sigma_\mathrm{obs}}\right|\right|_2^2,
+  \bar\chi^2 = \frac{1}{N}\left|\left|\frac{u_\mathrm{pred} - u_\mathrm{post}}{\sigma_\mathrm{post}}\right|\right|_2^2,
 \end{equation}
@@
 
-We first assume that the crust and mantle can be described with a Maxwell rheology, and we set the steady-state viscosity $\eta_\mathrm{M}$ equal to our inference of $\eta_{\mathrm{eff}}$.
+We first assume that the crust and mantle can be described with a Maxwell rheology, and we set the steady-state viscosity, $\eta_\mathrm{M}$, equal to our inference of $\eta_{\mathrm{eff}}$.
 We compute $f$ and $g$ from eq.
@@
 
-Instead of exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, the transient viscosity $\eta_{K}$ and transient shear modulus $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces one additional unknown parameter, $\mu_{K}$.
+Instead of exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, the transient viscosity, $\eta_{K}$, and transient shear modulus, $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces one additional unknown parameter, $\mu_{K}$.
 We assume that the lower crust still has a Maxwell rheology.
 The steady-state viscosity in the crust and the transient viscosity in the mantle are set equal to the inferred effective viscosities.
-We then estimate the ratio of shear moduli $\frac{\mu_K}{\mu}$.
+We then estimate the ratio of shear moduli, $\frac{\mu_K}{\mu}$.
 We compute nine different sets of Green's functions, $f$ and $g$, where we assume values of $\frac{\mu_K}{\mu}$ ranging from 0 to 1.
@@
 We estimate coseismic slip and afterslip for each realization of $\frac{\mu_K}{\mu}$.
-The shear moduli ratio that yields the best prediction to the observed postseismic displacements is found to be $0.375$ which produces a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
-The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSectionMain}).
-The Zener model does a significantly better job at explaining the transient rate of far-field deformation throughout the five years.
+We find that a shear moduli ratio of 0.375 yields the best prediction to the observed postseismic displacements with a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
+The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSectionMain}) where the Zener model does a significantly better job at explaining the transient rate of deformation throughout the five years considered in this study.
 
@@
 The deep afterslip inferred after one year could potentially be describing deformation resulting from lower crustal flow.
-To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}, and inverted for fault slip.
+To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}, and we inverted for fault slip.
 We find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after one year, while still requiring about the same amount of afterslip over the first year.
@@
 
-the postseismic displacements predicted by our preferred model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
+The postseismic displacements predicted by our preferred model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
 Overall, the trends in the near-field and far-field transient deformation are accurately described.
@@
 
-Of course, it has long been recognized that a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid-like behavior required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
+Of course, a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid-like behavior required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
 \citet{Yuen1982} proposed a Burgers rheology with a low transient viscosity ($\eta_K\approx10^{16}$ Pa s) and high steady-state viscosity ($\eta_M\approx10^{21}$ Pa s) to describe both seismic attenuation and long term geologic processes.
@@
 
-We have extracted a filtered and smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.
-Our estimated postseismic deformation reveals far-field (epicentral distances beyond ${\sim}200$ km) transient deformation which is largely undetectable after about three years.
+We have extracted a smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.
+Our estimated postseismic deformation reveals far-field (epicentral distances ${\gtrsim}200$ km) transient deformation which is undetectable after about three years.
 Near-field deformation exhibits transience that decays to a sustained, elevated rate after about one or two years.

### 2016-07-01 JGRRevision/2016JB013114.tex
change name to 2016JB013114

--- 2016-06-30 JGRRevision/ElMayor.tex
@@
 We also argue that a transient rheology is necessary to explain postseismic deformation; however, our preferred transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle is an order of magnitude larger than the transient viscosity found by \citet{Pollitz2003}.
+The transient viscosity inferred here is consistent with the results of \citet{Pollitz2015}, who reanalyzed postseismic data following the Landers and Hector Mine earthquake allowing the first few months of transient deformation to be described by afterslip.
 Since a Zener model is able to describe the available postseismic deformation following the El Mayor-Cucapah earthquake, any Burgers rheology with a steady-state viscosity that is $\gtrsim10^{20}$ Pa s, effectively infinite over five years, would also be able to describe the postseismic deformation.
@@
   with deep stress-driven creep along the San Andreas fault system},
-  \textit{Journal of Geophysical Research B: Solid Earth}, \textit{109}, 1--19,
+  \textit{Journal of Geophysical Research: Solid Earth}, \textit{109}, 1--19,
   \doi{10.1029/2004JB003096}.
@@
   1--17, \doi{10.1029/2012GC004139}.
+
+\bibitem[{\textit{Pollitz}(2015)}]{Pollitz2015}
+Pollitz, F.~F.
+(2015).
+{Postearthquake relaxation evidence for laterally variable viscoelastic structure and water content in the Southern California mantle}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{120},2672--2696, \doi{10.1002/2014JB011603}.
 

### 2016-07-01 JGRRevision/2016JB013114.tex
commit before going home to work on this

@@
 This complication can potentially be remedied by having a sufficient number of well positioned observations of the postseismic displacement field \citep{Hearn2003}.
-Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw=7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date.
+Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw=7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date (see \citet{Hauksson2011} and \citet{Fletcher2014} for a detailed description of this earthquake and its seismotectonic context).
 With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake.
-
-Here is some background on the El Mayor Earthquake
 
@@
 We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.
-Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and a Zener rheology in the upper mantle with a transient viscosity on the order of $10^{18}$ Pa s.
+Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and viscoelastic relaxation in a Zener rheology upper mantle with a transient viscosity on the order of $10^{18}$ Pa s.
 
@@
 \caption{Map of the region considered in this study.
-The large focal mechanism is for the El Mayor-Cucapah earthquake, and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
+The large focal mechanism is the GCMT solution for the El Mayor-Cucapah earthquake, and the three small focal mechanisms are for the Ocotillo earthquake and the two main shocks during the Brawley swarm.
 The black dots indicate the locations of GPS stations used in this study.
-The fault geometry used in this study is shown in cyan where dashed lines indicate buried edges of the fault segments.
+The fault geometry used in this study is shown in magenta where dashed lines indicate buried edges of the fault segments.
 The green and red boxes demarcate the extent of the near-field and far-field maps (Figures \ref{fig:NearField} and \ref{fig:FarField}).
-Stations inside the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P axis, are used in Figures \ref{fig:RecordSectionMain} and \ref{fig:RecordSection1}.}
+Stations inside the blue sector, which highlights the area within 10$^\circ$ of the El Mayor-Cucapah P-axis, are used in Figures \ref{fig:RecordSectionMain} and \ref{fig:RecordSection1}.}
 \label{fig:ContextMap}
@@
 This ensures that $\sigma^2$ will be sufficiently large so that our estimate of $u_\mathrm{post}(t)$ does not smooth out potentially valuable postseismic signal at the remaining stations.
-We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which gets incorporated into our estimate of coseismic displacements (Figure \ref{fig:P496}).
-We assume that the first week of deformation is overwhelmingly the result of afterslip and this afterslip is lumped into our estimates of coseismic slip.
-We include an example of estimating $u_\mathrm{post}(t)$ for a far-field station, P619, which is about 359 km from the El Mayor-Cucapah epicenter (Figure \ref{fig:P619}).
+We find that using $\sigma^2 = 0.05 \mathrm{m}^2 / \mathrm{yr}^3$ adequately describe all but the first week of postseismic deformation at station P496, which slightly increases our estimate of coseismic displacements (Figure \ref{fig:P496}).
+We include an example of estimating $u_\mathrm{post}(t)$ for a far-field station, P619, which is about 359 km north of the El Mayor-Cucapah epicenter (Figure \ref{fig:P619}).
 At station P619, along with all the other stations in the Mojave region, there is a south-trending postseismic transience that persists for the first three years after the El Mayor-Cucapah earthquake.
@@
 Stations at epicentral distances beyond ${\sim}200$ km have an elevated rate of deformation for the first three years following the earthquake.
-This far-field deformation is trending southward at a rate of a few millimeters per year along the direction of the El Mayor-Cucapah P axis.
-A similar eastward trend can be seen in the few far-field stations in Arizona, located along the T axis.
+This far-field deformation is trending southward at a rate of a few millimeters per year along the direction of the El Mayor-Cucapah P-axis.
+A similar eastward trend can be seen in the few far-field stations in Arizona, located along the T-axis.
 After three years, the trend in far-field postseismic deformation is barely perceptible.
@@
 This trend in vertical deformation can be observed in all three of the quadrants where postseismic data is available, which means that the vertical deformation does not exhibit an anti-symmetric quadrant pattern, as would be expected for postseismic processes.
-Although we use vertical deformation in our analysis in Section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation as it likely does not have postseismic origins.
+Although we use vertical deformation in our analysis in Section \ref{sec:Model},  we do not put an emphasis on trying to describe the vertical deformation because it likely does not have postseismic origins.
 
@@
 \centering 
-\caption{Near-field coseismic and cumulative postseismic displacements over the indicated time periods (black) as well as predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
-Observed vertical deformation is shown as an interpolated field and predicted vertical displacements are shown within the green circles.
+\caption{Near-field coseismic and cumulative postseismic displacements over the indicated time periods (black) and predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
+Observed vertical displacements are shown as an interpolated field and predicted vertical displacements are shown within the green circles.
 Note that the interpolant is not well constrained in Mexico where there is no data available.}
@@
 Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} found that poroelastic rebound is unlikely to be a significant contributor to postseismic deformation following the El Mayor-Cucapah earthquake.
-Furthermore, we consider stations which are sufficiently far away from the main rupture that poroelastic rebound should be insignificant.
+Furthermore, we consider stations which are sufficiently far away from the rupture that poroelastic rebound should be insignificant.
 
@@
 Both segments extend from the surface to 15 km depth.
-We extend the northern segment by 40 km to the north-west, motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
+We extend the northern segment by 40 km to the northwest, motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
 This extended fault segment was also found to be necessary by \citet{Rollins2015} and \citet{Pollitz2012} in order to describe the postseismic deformation.
@@
 We also perform an elastic slip inversion, but we use GPS stations within a larger radius about the El Mayor-Cucapah epicenter (400 km instead of ${\sim}200$ km).
-Our forward problem describing predicted postseismic deformation $u_\mathrm{pred}$ in terms of time dependent fault slip, $s$, is
+Our forward problem describing predicted postseismic deformation, $u_\mathrm{pred}$, in terms of time dependent fault slip, $s$, is
 
@@
 where $F$ denotes the fault and $g(x,\xi)$ is the elastic Green's function describing displacement at surface position $x$ resulting from slip at $\xi$ on the fault.
-We estimate coseismic slip and the rate of afterslip over the time intervals 0.0-0.125, 0.125-0.25, 0.25-0.5, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years after the earthquake.
-Each fault segment is discretized into roughly 4 km by 4 km patches and we estimate a strike-slip and dip component of slip for each patch.
-We impose that the direction of slip and slip rate are within 45$^\circ$ of right-lateral.
+We estimate coseismic slip and the rate of afterslip over the postseismic time intervals 0.0-0.125, 0.125-0.25, 0.25-0.5, 0.5-1.0, 1.0-2.0, 2.0-3.0, 3.0-4.0, and 4.0-5.0 years.
+Each fault segment is discretized into roughly 4 km by 4 km patches an we impose that the direction of slip and slip rate are within 45$^\circ$ of right-lateral.
 We also add zeroth-order Tikhonov regularization so that our solution for $s$ satisfies
@@
 The potency of our inferred cumulative five years of afterslip is $6.1\times10^9\ \mathrm{m}^3$, equivalent to a Mw=7.46 earthquake, which is unrealistically large if we consider afterslip to be driven by coseismically induced stresses.
-Figure \ref{fig:RecordSectionMain} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P axis.
+Figure \ref{fig:RecordSectionMain} shows the time series for the observed and predicted postseismic displacements at stations along the El Mayor-Cucapah P-axis.
 We show the radial component of displacements with respect to the El Mayor-Cucapah epicenter and we also rescale the displacements so that the difference between the minimum and maximum observed displacements are the same for each station.
@@
 We again restrict fault slip to occur between 0 and 15 km depth, which is done in order to help eliminate inevitable non-uniqueness in the inversion.
-It has long been recognized that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional earthquake models \citep{Savage1990}.
+It is well understood that fault slip at sufficiently great depths can produce surface deformation that is indistinguishable from viscoelastic relaxation, at least in two-dimensional earthquake models \citep{Savage1990}.
 Additionally, we note that when simultaneously estimating both afterslip and viscosity in the lower crust, the inverse problem becomes particularly ill-posed.
@@
 As noted, eq.
-(\ref{ApproxForward}) is valid for approximately as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
+(\ref{ApproxForward}) is valid for as long as the rate of deformation resulting from viscoelastic relaxation is approximately constant.
 We can almost certainly assume that deformation at the most far-field stations, which are ${\sim}400$ km away from the El Mayor-Cucapah epicenter, is the result of viscoelastic relaxation.
@@
 The degree to which we impose the regularization on slip and fluidity is controlled by the penalty parameters $\lambda_s$ and $\lambda_\eta$, which are chosen with trade-off curves (Figure S1).
-Our goal here is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in Section \ref{sec:FullInversion}.
+Our goal is to get a prior constraint on $\eta_{\mathrm{eff}}$ to minimize the amount of searching we have to do when describing the postseismic deformation over the full five years, which we do in Section \ref{sec:FullInversion}.
 Estimates of $s$ made here will not be used in Section \ref{sec:FullInversion}, and so the motivation behind adding regularization to $s$ is to ensure that the slip driving viscoelastic relaxation in eq.
@@
 When fault slip is simultaneously estimated with viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.5\times10^{9}\ \mathrm{m}^3$ when we assume the crust and upper mantle are elastic.
-The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation at depths greater than $60$ km.
+The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation.
 The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
@@
 It is important to remember that the presented effective viscosities were estimated with a smoothing regularization constraint and so the uncertainties are almost certainly underestimated \citep{Aster2011}.
-The uncertainties are shown to give the reader a sense of the relative confidence between layers.
 Indeed, many viscosity profiles which are outside of the shown confidence intervals can just as adequately described the first 0.8 years of postseismic deformation.
-The solution in (Figure \ref{fig:EffectiveViscosity}) should be interpreted as the smoothest effective viscosity profile which is capable of describing the data.
+Our solution in Figure \ref{fig:EffectiveViscosity} should be interpreted as the smoothest effective viscosity profile which is capable of describing the data.
 This means that any  sharp viscosity transitions will be tapered out, which we demonstrate with a synthetic test in Figure S2.
@@
 We find that the viscosity below 60 km depth needs to be ${\sim}10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
-The viscosity of the lower crust is the least well constrained because there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
+The viscosity of the lower crust has the largest uncertainties because there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
 
@@
 We find that a shear moduli ratio of 0.375 yields the best prediction to the observed postseismic displacements with a misfit of $\bar\chi^2=31.2$ (Figure \ref{fig:ShearModulusRatio}).
-The improvement in the Zener model over the Maxwell model can be clearly seen in the fit to the far-field data (Figure \ref{fig:RecordSectionMain}) where the Zener model does a significantly better job at explaining the transient rate of deformation throughout the five years considered in this study.
+The improvement in the Zener model over the Maxwell model can be seen in the fit to the far-field data (Figure \ref{fig:RecordSectionMain}) where the Zener model does a significantly better job at explaining the transient rate of deformation throughout the five years considered in this study.
+The rheologic parameters for our preferred Zener model are summarized in Table 1.
 
@@
 The regularized inference of coseismic slip and afterslip for our preferred Zener model is shown in Figure \ref{fig:FinalSlip}.
-The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw=7.26 earthquake, and most of the slip is shallow and on the Sierra Cucapah fault segment.
+The inferred coseismic potency is $3.0\times10^{9}\ \mathrm{m}^3$, equivalent to a Mw=7.26 earthquake, where most of the slip is shallow and on the Sierra Cucapah fault segment.
 The potency of five years of afterslip is $1.1\times10^{9}\ \mathrm{m}^3$.
@@
 
-The postseismic displacements predicted by our preferred model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
-Overall, the trends in the near-field and far-field transient deformation are accurately described.
-In particular, the trends in far-field deformation are much better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle (Figure \ref{fig:RecordSectionMain}).
-There are a few areas where we have notable misfit.
-Most of our misfit is for the near-field stations in the Imperial Valley, and we attribute this misfit to our relatively simple fault geometry, which does not account for potential fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
-In particular, we are unable to model the sustained, rapid rate of deformation at station P496, which suggests that this station could be influenced by a more localized deformation mechanism than is considered in this study.
+The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
+Overall, the trends in the near-field and far-field deformation is better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle.
+The largest residuals occur within the Imperial Valley and these residuals do not appear to have any systematic trend.
+This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
+We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.
+As discussed in section \ref{sec:Data}, our method for data processing is not able to completely remove the seasonal signal in the GPS data and this results in regionally uniform oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.
 Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.

### 2016-07-02 JGRRevision/2016JB013114.tex
lasted edits before sending to Eric

@@
 \begin{abstract}
-
 We analyze five years of Southern California GPS data following the Mw=7.2 El Mayor-Cucapah earthquake.
 We observed transient postseismic deformation which persists for three years at epicentral distances greater than ${\sim}200$ km.
-In the near-field, rapid postseismic transience decays to a sustained rate which exceeds its pre-earthquake trend.
+In the near-field, rapid postseismic transience decays to a sustained rate which exceeds its preseismic trend.
 We attempt to determine the mechanisms driving this deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
@@
 The interpretations of postseismic deformation are not always conclusive because multiple postseismic deformation mechanisms, such as afterslip or viscoelastic relaxation in the lower crust and upper mantle, can have qualitatively similar surface expressions \citep[e.g.][]{Savage1990}.
-This complication can potentially be remedied by having a sufficient number of well positioned observations of the postseismic displacement field \citep{Hearn2003}.
+This non-uniqueness complication can potentially be remedied if the postseismic deformation occurs in an area that is sufficiently well instrumented with GPS stations \citep{Hearn2003}.
 Owing to the dense geodetic network deployed throughout the 2000s as part of the Plate Boundary Observatory, the postseismic deformation following the April 4, 2010, Mw=7.2 El Mayor-Cucapah earthquake in Baja California was observed at more GPS stations than any other earthquake in California to date (see \citet{Hauksson2011} and \citet{Fletcher2014} for a detailed description of this earthquake and its seismotectonic context).
-With such a large collection of data, we attempt to discern the mechanisms driving postseismic deformation following the El Mayor-Cucapah earthquake.
+With such a large collection of data, we attempt to discern the mechanisms driving the postseismic deformation.
 
@@
 One can also assume that afterslip does not persist for more than a few months and then model the later postseismic deformation assuming it to be the result of only viscoelastic relaxation \citep[e.g.][]{Pollitz2012,Spinler2015}.
-However, postseismic afterslip in similar tectonic settings has been observed to persist for decades following earthquakes \citep{Cakir2012,Cetin2014}.
+However, afterslip in similar tectonic settings has been observed to persist for decades following earthquakes \citep{Cakir2012,Cetin2014}.
 Indeed, the preferred viscoelastic model from \citet{Pollitz2012} significantly underestimates deformation in the Imperial Valley, which could be indicative of unmodeled continued afterslip.
@@
 We consider the GPS position time series, $u_\mathrm{obs}(t)$, to be the combination of $u_\mathrm{post}(t)$, secular tectonic deformation, annual and semi-annual oscillations, and coseismic offsets from significant earthquakes over the time span of this study.
-The June 14, 2010, Mw=5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw=5.5 and an Mw=5.4 event on August 26, 2012, (Figure \ref{fig:ContextMap}) are the only earthquakes that produced noticeable displacements in any of the time series.
+The June 14, 2010, Mw=5.8 Ocotillo earthquake and the Brawley swarm, which included an Mw=5.5 and an Mw=5.4 event on August 26, 2012 (Figure \ref{fig:ContextMap}), are the only earthquakes that produced noticeable displacements in any of the time series.
 We treat the displacements resulting from the Brawley swarm as a single event because the daily solutions provided by UNAVCO cannot resolve the separate events.
@@
 Red lines indicate the times of the El Mayor-Cucapah and Ocotillo earthquake.
-The right panels show estimated coseismic and postseismic displacements $u_\mathrm{post}$ which are extracted from the predicted displacements.
+The right panels show estimated coseismic and postseismic displacements, $u_\mathrm{post}$, which are extracted from the predicted displacements.
 The 68\% confidence interval is shown in light blue.}
@@
 Field studies \citep{Fletcher2014} and LIDAR observations \citep{Oskin2012} have revealed a significantly more complicated fault geometry than what was inferred by \citet{Wei2011}, especially within the Sierra Cucapah.
-However, we find that a relatively simple coseismic fault geometry based on \citep{Wei2011} is adequate because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture zone that they are insensitive to the details in the fault geometry found by \citet{Fletcher2014} and \citet{Oskin2012}.
+However, we find that a relatively simple coseismic fault geometry based on \citep{Wei2011} is adequate because most of the stations used in this study are sufficiently far from the El Mayor-Cucapah rupture that they are insensitive to the details in the fault geometry found by \citet{Fletcher2014} and \citet{Oskin2012}.
 The fault geometry used in this study (Figure \ref{fig:ContextMap}) consists of the two main fault segments inferred by \citet{Wei2011}, where the northern segment runs through the Sierra Cucapah up to the US-Mexico border and the southern segment is the Indiviso fault which extends down to the Gulf of California.
 Both segments extend from the surface to 15 km depth.
-We extend the northern segment by 40 km to the northwest, motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
+We extend the northern segment by 40 km to the northwest, which is motivated by the clustering of aftershocks on the northern tip of the coseismic rupture zone \citep{Hauksson2011,Kroll2013}.
 This extended fault segment was also found to be necessary by \citet{Rollins2015} and \citet{Pollitz2012} in order to describe the postseismic deformation.
@@
 The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.
-Using a subset of the GPS stations considered in this study, \citet{Rollins2015} found that three years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
+\citet{Rollins2015} used a subset of the GPS stations considered in this study and found that three years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
 We also perform an elastic slip inversion, but we use GPS stations within a larger radius about the El Mayor-Cucapah epicenter (400 km instead of ${\sim}200$ km).
@@
 Our coseismic slip and afterslip solutions are shown in Figure \ref{fig:ElasticSlip}.
-As with \citet{Rollins2015}, we find that a large amount of afterslip on the Indiviso fault segment is required to explain the observations.
+Similar to \citet{Rollins2015}, we find that a large amount of afterslip on the Indiviso fault segment is required to explain the observations.
 The potency of our inferred coseismic slip is $3.2\times10^9\ \mathrm{m}^3$, equivalent to a Mw=7.28 earthquake when assuming a shear modulus of 32 GPa.
@@
 \includegraphics[scale=0.9]{Figures/ElasticSlip}
-\caption{Coseismic slip and cumulative afterslip over the indicated intervals for the elastic model from Section \ref{sec:ElasticInversion}.
+\caption{Coseismic slip and cumulative afterslip over the indicated time intervals when assuming the crust and mantle are elastic.
 Color indicates the magnitude of slip while arrows indicate the motion of the hanging wall.}
@@
 The observed postseismic displacements, $u_\mathrm{post}$ are shown in black with gray indicating the 68\% confidence interval.
-The displacements predicted by the best fitting elastic model $u_\mathrm{pred}$ are shown in red.
+The displacements predicted by the best fitting elastic model are shown in red.
 The blue and green lines are the predicted postseismic displacements for the models discussed in Section 3.3.
@@
 (\ref{InitialRate}) with eq.
-(\ref{GeneralForward}) to get a first order approximation for early postseismic deformation,
+(\ref{GeneralForward}) to get a first-order approximation for early postseismic deformation,
 
@@
 (\ref{ApproxForward}) is used to estimate $s$ and $\eta_\mathrm{eff}$ from postseismic deformation can be found in \citet{Hines2016}.
-A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner akin to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
+A non-linear Kalman filter based inverse method can also be used to estimate $s$ and $\eta_{\mathrm{eff}}$ in a manner similar to \citet{Segall1997} or \citet{McGuire2003}, in which we would not have to explicitly impose a time dependent parametrization of $s$.
 We have thoroughly explored Kalman filter based approaches, but we ultimately prefer the method described in \citet{Hines2016} because of its relative simplicity.
-Moreover, we believe the piecewise continuous representation of slip with respect to time to be sufficiently general for the resolving power of these GPS data.
+Moreover, we believe the piecewise continuous representation of slip with respect to time is sufficiently general for the resolving power of these GPS data.
 
 We estimate coseismic slip and afterslip with the same spatial and temporal discretization as in Section \ref{sec:ElasticInversion}.
-Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, as well as from 150 km to the bottom of our numerical model domain at 800 km.
+Simultaneously, we estimate $\eta_{\mathrm{eff}}$ within six vertically stratified layers which have depths ranging from 15-30 km, 30-60 km, 60-90 km, 90-120 km, 120-150 km, and from 150 km to the bottom of our numerical model domain at 800 km.
 We again restrict fault slip to occur between 0 and 15 km depth, which is done in order to help eliminate inevitable non-uniqueness in the inversion.
@@
 The highlighted area on the fault extends from 15 to 30 km depth and indicates where 1 meter of right-lateral slip was imposed.
-The elastic properties of the crust and mantle are the same as in Table \ref{tab:MaterialProperties}, and $\eta_\mathrm{eff}$  is $10^{18}$ Pa s in the lower crust.
+The elastic properties of the crust and mantle are the same as in Table 1, and $\eta_\mathrm{eff}$  is $10^{18}$ Pa s in the lower crust.
 Vertical displacements are interpolated between station locations.}
@@
 When fault slip is simultaneously estimated with viscosity, the potency of inferred afterslip over the first 0.8 years after the earthquake is $0.85\times 10^9\ \mathrm{m}^3$, compared to $3.5\times10^{9}\ \mathrm{m}^3$ when we assume the crust and upper mantle are elastic.
-The significant amount of afterslip inferred on the Indiviso fault seems to be compensating for unmodeled viscoelastic relaxation.
+The significant amount of afterslip inferred on the Indiviso fault in Section \ref{sec:ElasticInversion} seems to be compensating for unmodeled viscoelastic relaxation.
 The fact that there is still an appreciable amount of afterslip inferred on the Indiviso fault raises the question of whether it is compensating for viscoelastic relaxation that is more localized than what we allow for since we only estimate depth dependent variations in viscosity.
@@
 (\ref{InitialRate}) is linear with respect to fluidity and so the fluidity indicates the amplitude of the viscoelastic signal coming from each layer.
-We use bootstrapping to find the 95\% confidence intervals for our estimated effective viscosities which are shown in Figure \ref{fig:EffectiveViscosity}.
+We use bootstrapping to find the 95\% confidence intervals for our estimated effective viscosities which are shown as shaded regions in Figure \ref{fig:EffectiveViscosity}.
 It is important to remember that the presented effective viscosities were estimated with a smoothing regularization constraint and so the uncertainties are almost certainly underestimated \citep{Aster2011}.
@@
 Our solution in Figure \ref{fig:EffectiveViscosity} should be interpreted as the smoothest effective viscosity profile which is capable of describing the data.
-This means that any  sharp viscosity transitions will be tapered out, which we demonstrate with a synthetic test in Figure S2.
+This means that any  sharp viscosity transitions will be tapered out in the inversion, which we demonstrate with a synthetic test in Figure S2.
 Nonetheless, a robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
 This transitional depth is also consistent with the the viscosity structure required to explain far-field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
-We find that the viscosity below 60 km depth needs to be ${\sim}10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
+We find that the viscosity below 60 km depth needs to be ${\sim}1\times10^{18}$ Pa s to describe the early rate of postseismic deformation at far-field stations while the lower crust and uppermost mantle need to be relatively stronger.
 The viscosity of the lower crust has the largest uncertainties because there is no evidence of relaxation in that layer, meaning that it is effectively elastic over the first 0.8 years after the earthquake.
@@
 (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.
-95\% confidence intervals, estimated from bootstrapping, are indicated by color fields.}
+95\% confidence intervals, estimated from bootstrapping, are indicated by shaded regions.}
 \label{fig:EffectiveViscosity}
@@
 The Maxwell viscoelastic model has a larger misfit because it tends to overestimate the rate of deformation after about three years (Figure \ref{fig:RecordSectionMain}).
-Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle.
-However, decreasing the viscosity only increases the misfit.
+Since our initial estimates of $\eta_\mathrm{eff}$ may be biased towards overestimating viscosities, we have also performed the slip inversion where we use uniformly lower viscosities in the crust and mantle; however, decreasing the viscosity only increases the misfit.
 Although, the viscosities used here are consistent with the successful Maxwell viscoelastic models found by \citet{Rollins2015} and \citet{Spinler2015}, which had mantle viscosities on the order of $10^{18}$ Pa s and relatively higher lower crustal viscosities, we find that such a model is incapable of describing the entire postseismic time series.
@@
 The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
-Overall, the trends in the near-field and far-field deformation is better described by our preferred Zener model than either an elastic model or a model with a Maxwell viscoelastic mantle.
-The largest residuals occur within the Imperial Valley and these residuals do not appear to have any systematic trend.
+The largest misfit occur within the Imperial Valley and there does not appear to be any systematic trend in the residuals.
 This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
 We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.
-As discussed in section \ref{sec:Data}, our method for data processing is not able to completely remove the seasonal signal in the GPS data and this results in regionally uniform oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.
-Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation resulting from those earthquakes.
-Lastly, there are clear discrepancies between the observed and predicted vertical deformation following the first year after the El Mayor Cucapah earthquake.
-We observe a broad uplift throughout Southern California, which is inconsistent with any postseismic model.
+We do notice regionally uniform seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.
+This is the result of our method for data processing which is not able to completely remove the seasonal signal in the GPS data, which was discussed in Section \ref{sec:Data}.
+Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation following those earthquakes.
+Lastly, there are clear discrepancies between the observed and predicted vertical displacements following the first year after the El Mayor-Cucapah earthquake.
+We observe a broad uplift throughout Southern California which is inconsistent with any postseismic model.
 
@@
 Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km.
-Beneath that depth, a transient viscosity of ${\sim}10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the five years considered in this study.
+Beneath that depth, a transient viscosity of ${\sim}1\times10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the five years considered in this study.
 By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.

### 2016-07-06 JGRRevision/2016JB013114.tex
changed figure 4 caption
renamed figures

@@
 We find that early, rapid, near-field deformation can be explained with afterslip on the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of ${\sim}10^{19}$ Pa s.
-The trend in far-field deformation is best explained with a transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle.
+The later postseismic deformation in the far-field is best explained with a transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle.
 We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay in postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
@@
 
-\citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} have explored viscoelastic relaxation in the lower crust and upper mantle as a potential postseismic deformation mechanism.
+\citet{Pollitz2012}, \citet{Rollins2015} and \citet{Spinler2015} explored viscoelastic relaxation in the lower crust and upper mantle as a potential postseismic deformation mechanism.
 The rheology of the crust and mantle is largely unknown and so modeling postseismic deformation with viscoelastic relaxation requires one to assume a rheologic model and then find the best fitting rheologic parameters.
@@
 In this case, our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.
-We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.
+We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models which we test against the five years of postseismic data available to date.
 Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and viscoelastic relaxation in a Zener rheology upper mantle with a transient viscosity on the order of $10^{18}$ Pa s.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Figures/ContextMap} 
+\includegraphics[scale=0.8]{Figures/2016jb013114-p01} 
 \caption{Map of the region considered in this study.
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/FilterP496}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p02}
 \centering
@@
 \begin{figure}
-\noindent\includegraphics[scale=0.9]{Figures/FilterP619}
+\noindent\includegraphics[scale=0.9]{Figures/2016jb013114-p03}
 \centering
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/MapViewNearField}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p04}
 \centering 
 \caption{Near-field coseismic and cumulative postseismic displacements over the indicated time periods (black) and predicted displacements for our preferred model from Section \ref{sec:FullInversion} (green).
+The black error ellipses show the 68\% confidence interval for the observed horizontal displacements.
 Observed vertical displacements are shown as an interpolated field and predicted vertical displacements are shown within the green circles.
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/MapViewFarField}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p05}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/ElasticSlip}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p06}
 \caption{Coseismic slip and cumulative afterslip over the indicated time intervals when assuming the crust and mantle are elastic.
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/RecordSectionFinal}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p07}
 \caption{Scaled radial component of postseismic displacements.
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/rheology}
+\includegraphics[scale=0.9]{Figures/2016jb013114-f08}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/Cancellation}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p09}
 \caption{Displacements resulting from fault slip at lower crustal depths (a), and initial velocities resulting from subsequent relaxation of a viscoelastic lower crust (b).
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/RecordSectionDuration}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p10}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/InitialSlip}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p11}
 \caption{Coseismic slip and afterslip inferred by fitting eq. (\ref{ApproxForward}) to the first 0.8 years of postseismic displacements.}
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/EffectiveViscosity}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p12}
 \centering 
@@
 
-Instead of exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, the transient viscosity, $\eta_{K}$, and transient shear modulus, $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces one additional unknown parameter, $\mu_{K}$.
+Instead of exploring a Burgers rheology mantle, which introduces two new parameters that need to be estimated, the transient viscosity, $\eta_{K}$, and transient shear modulus, $\mu_{K}$, we first consider a Zener rheology for the mantle, which only introduces one unknown model parameter, $\mu_{K}$.
 We assume that the lower crust still has a Maxwell rheology.
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/RatioMisfit}
+\includegraphics[scale=0.9]{Figures/2016jb013114-f13}
 \centering 
@@
 \begin{figure}
-\includegraphics[scale=0.9]{Figures/FinalSlip}
+\includegraphics[scale=0.9]{Figures/2016jb013114-p14}
 \centering 
@@
 The similarity of the horizontal postseismic deformation results in a non-uniqueness in inferences of afterslip or viscoelastic relaxation.
-In contrast, the spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}.
+The spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}.
 It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981,Hetland2014}.
@@
 One could explain the early transient postseismic deformation with fault creep and the later phase with relaxation in a Maxwell viscoelastic lower crust and upper mantle \citep[e.g][]{Hearn2009,Johnson2009}.
-However, postseismic deformation at distances greater than ${\sim}200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSectionMain}).
+However, postseismic deformation at distances greater than ${\sim}200$ km from the El Mayor-Cucapah epicenter can only be attributed to viscoelastic relaxation \citep[e.g.][]{Freed2007a} and we have demonstrated that the far-field deformation cannot be explained with a Maxwell rheology (Figure \ref{fig:RecordSectionMain}).
 
@@
 
-Of course, a Zener rheology provides an incomplete descriptions of the asthenosphere, as it does not have the fluid-like behavior required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
+Of course, a Zener rheology provides an incomplete description of the asthenosphere because it does not have the fluid-like behavior required to explain isostatic rebound or convection in the mantle \citep{OConnell1971}.
 \citet{Yuen1982} proposed a Burgers rheology with a low transient viscosity ($\eta_K\approx10^{16}$ Pa s) and high steady-state viscosity ($\eta_M\approx10^{21}$ Pa s) to describe both seismic attenuation and long term geologic processes.
@@
 We thank Andy Freed for an illuminating discussion on the data used in this study.
+We also thank F.
+Pollitz and an anonymous reviewer for comments that improved this manuscript, and Editor Martha Savage.
 This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.

### 2016-07-06 JGRRevision/2016JB013114.tex
added elastic/viscoelastic partition supplementary figures

@@
 We attempt to determine the mechanisms driving this deformation, where we consider afterslip at seismogenic depths and viscoelastic relaxation in the lower crust and upper mantle as candidate mechanisms.
-We find that early, rapid, near-field deformation can be explained with afterslip on the fault that ruptured coseismically, while the later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of ${\sim}10^{19}$ Pa s.
+We find that early, rapid, near-field deformation can be explained with afterslip on the fault that ruptured coseismically.
+The later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of ${\sim}10^{19}$ Pa s.
 The later postseismic deformation in the far-field is best explained with a transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle.
@@
 \end{equation}
-This process is repeated for each of the $N$ time epochs at which point we use Rauch-Tung-Striebel smoothing \citep{Rauch1965} to find $\mathbf{X}_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates GPS observation for all $N$ time epochs.
+This process is repeated for each of the $N$ time epochs.
+We then use Rauch-Tung-Striebel smoothing \citep{Rauch1965} to find $\mathbf{X}_{i|N}$, which is an estimate of the state at time $t_i$ that incorporates GPS observation for all $N$ time epochs.
 Our final estimates of $u_\mathrm{post}(t)$ are used in subsequent analysis, while the remaining components of the state vector are considered nuisance parameters.
@@
 Setting $\sigma^2$ equal to zero will effectively result in modeling $u_\mathrm{post}(t)$ as a straight line which is insufficient to describe the expected transient behavior in postseismic deformation.
-The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ over fitting the data.
+The other end member, where $\sigma^2$ is infinitely large, will result in $u_\mathrm{pred}(t)$ overfitting the data.
 While one can use a maximum likelihood based approach for picking $\sigma^2$ \citep[e.g.][]{Segall1997}, we instead take a subjective approach and choose a value for $\sigma^2$ that is just large enough to faithfully describe the observed deformation at the most near-field station in our study, P496, which exhibits the most rapid changes in velocity.
@@
 
-We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field postseismic displacements accumulated over the time intervals 0-1 years, 1-3 years, and 3-5 years, as well as the coseismic displacements.
+We show in Figures \ref{fig:NearField} and \ref{fig:FarField} the near and far-field coseismic displacements and the postseismic displacements accumulated over the time intervals 0-1 years, 1-3 years, and 3-5 years.
 Stations at epicentral distances beyond ${\sim}200$ km have an elevated rate of deformation for the first three years following the earthquake.
@@
 The simplest rheologic model is to consider them to be effectively elastic and isotropic.
-In such case, the rheologic parameters consist of the Lam\'e parameters, $\lambda$ and $\mu$, which are reasonably well known and we use the same values used by \citet{Wei2011} throughout this paper (Table 1).
-The only unknown is the distribution of fault slip, which can be easily estimated from postseismic deformation through linear least squares.
+In such case, the rheologic parameters consist of the reasonably well known Lam\'e parameters, $\lambda$ and $\mu$, and we use the same values used by \citet{Wei2011} throughout this paper (Table 1).
+The only unknown is the distribution of fault slip, which can be estimated from postseismic deformation through linear least squares.
 \citet{Rollins2015} used a subset of the GPS stations considered in this study and found that three years of postseismic deformation following the El Mayor-Cucapah earthquake can be explained with afterslip on the coseismic fault plane without requiring any viscoelastic relaxation.
@@
 \caption{Coseismic slip and cumulative afterslip over the indicated time intervals when assuming the crust and mantle are elastic.
-Color indicates the magnitude of slip while arrows indicate the motion of the hanging wall.}
+Color indicates the magnitude of slip and arrows indicate the motion of the hanging wall.}
 \label{fig:ElasticSlip}
@@
 We eliminate this null space by allowing only one mechanism in the lower crust, which we choose to be viscoelastic relaxation.
-This is not to say that we do not believe deep afterslip to be a possibility; rather, we restrict slip to seismogenic depths as a modeling necessity.
+This is not to say that we do not believe deep afterslip is a possibility; rather, we restrict slip to seismogenic depths as a modeling necessity.
 Although, it has been noted that the pattern of vertical postseismic deformation following the El Mayor-Cucpah earthquake indicates that a significant amount of afterslip must be shallow \citep{Rollins2015}.
@@
 This means that any  sharp viscosity transitions will be tapered out in the inversion, which we demonstrate with a synthetic test in Figure S2.
-Nonetheless, a robust feature that we see is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
+Nonetheless, a robust feature that we see with a variety of choices for $\lambda_s$, $\lambda_\eta$, and $t_\mathrm{bd}$ is that the largest jump in fluidity is at 60 km depth, which is consistent with the range of lithosphere-asthenosphere boundary depths inferred by \citet{Lekic2011}.
 This transitional depth is also consistent with the the viscosity structure required to explain far-field postseismic deformation following the Hector Mine earthquake \citep{Freed2007a}.
@@
 Most of the afterslip in our preferred model occurs within the first year after the earthquake and coincides with the location of our inferred coseismic slip.
-Inferred afterslip within the first year is accounting for the most rapid near-field transient deformation.
-After one year, afterslip is inferred to be deeper down on the Sierra Cucapah segment, which is describing much of the sustained near-field postseismic deformation.
+Inferred afterslip within the first year is accounting for the most rapid near-field transient deformation (Figure S3).
+After one year, afterslip is inferred to be deeper down on the Sierra Cucapah segment, which is describing some of the sustained near-field postseismic deformation.
 We emphasize, that the GPS station closest to where we infer afterslip, P496, is still about 30 km away, which is too far for us to conclusively argue for sustained localized deformation rather than shallow distributed deformation.
@@
 \caption{Inferred coseismic slip and afterslip when assuming a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.
-The transient viscosity $\eta_K$ in the mantle and steady-state viscosity $\eta_M$ in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}.
-We set $\frac{\mu_K}{\mu}=0.375$ in the upper mantle.}
+The transient viscosity, $\eta_K$, in the mantle and steady-state viscosity, $\eta_M$, in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}.
+We use $\frac{\mu_K}{\mu}=0.375$ in the upper mantle.}
 \label{fig:FinalSlip}

### 2016-07-07 JGRRevision/2016JB013114.tex
a few more edits

@@
 We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.
-We do notice regionally uniform seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.
+We do notice regional scale seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.
 This is the result of our method for data processing which is not able to completely remove the seasonal signal in the GPS data, which was discussed in Section \ref{sec:Data}.
@@
 We thank Andy Freed for an illuminating discussion on the data used in this study.
-We also thank F.
-Pollitz and an anonymous reviewer for comments that improved this manuscript, and Editor Martha Savage.
+We thank Fred Pollitz and an anonymous reviewer for comments that improved this manuscript.
+We also thank the editor, Martha Savage.
 This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No.

### 2016-07-07 JGRRevision/2016JB013114.tex
removed tiny ellipses in S4 and fixed the bib

@@
 % \documentclass{AGUJournal}
-
 \journalname{JGR-Solid Earth}
@@
 \begin{document}
-
 \title{Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
-
 \authors{T. T. Hines\affil{1}, E. A. Hetland\affil{1}}
-
 \affiliation{1}{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, Michigan, USA.}
-
 \correspondingauthor{T. T. Hines}{hinest@umich.edu}
-
-%% Keypoints, final entry on title page.
-
-% Example: 
-% \begin{keypoints}
-% \item	List up to three key points (at least one is required)
-% \item	Key Points summarize the main points and conclusions of the article
-% \item	Each must be 100 characters or less with no special characters or punctuation 
-% \end{keypoints}
-
-%  List up to three key points (at least one is required)
-%  Key Points summarize the main points and conclusions of the article
-%  Each must be 100 characters or less with no special characters or punctuation
 
@@
 \item Transient postseismic deformation can be observed following the El Mayor-Cucapah earthquake at epicentral distances of up to 400 km
-
 \item Near-field postseismic deformation exhibits early transience that decays to a sustained rate which is elevated above the preseismic trend 
-
 \item Far-field postseismic deformation can be explained with a Zener or Burgers rheology upper mantle 
-
 \end{keypoints}
@@
 The values for $\eta_\mathrm{eff}$ are estimated in Section \ref{sec:InitialInversion}, and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.}
-
 \end{table}
+
 We seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake and we consider afterslip and viscoelastic relaxation as candidate mechanisms.
@@
 \subsection{Full Postseismic Inversion}\label{sec:FullInversion} 
-
 In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation.
@@
 \section{Discussion}\label{Discussion}
-
 It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001, Hearn2003, Feigl2006}.
@@
 \section{Conclusion}
-
 We have extracted a smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.
@@
 
-\bibitem[{\textit{Argus et~al.}(2005)\textit{Argus, Heflin, Peltzer,
-  Cramp{\'{e}}, and Webb}}]{Argus2005}
-Argus, D.~F., M.~B. Heflin, G.~Peltzer, F.~Cramp{\'{e}}, and F.~H. Webb (2005),
-  {Interseismic strain accumulation and anthropogenic motion in metropolitan
-  Los Angeles}, \textit{Journal of Geophysical Research: Solid Earth},
-  \textit{110}(4), 1--26, \doi{10.1029/2003JB002934}.
-
-\bibitem[{\textit{Aster et~al.}(2011)\textit{Aster, Borchers, and
-  Thurber}}]{Aster2011}
-Aster, R.~C., B.~Borchers, and C.~H. Thurber (2011), {Parameter
-  Estimation and Inverse Problems}, vol. 90, Academic Press.
-
-\bibitem[{\textit{Bawden et~al.}(2001)\textit{Bawden, Thatcher, Stein, Hudnut,
-  and Peltzer}}]{Bawden2001}
-Bawden, G.~W., W.~Thatcher, R.~S. Stein, K.~W. Hudnut, and G.~Peltzer (2001),
-  {Tectonic contraction across Los Angeles after removal of groundwater pumping
-  effects.}, \textit{Nature}, \textit{412}(August), 812--815,
-  \doi{10.1038/35090558}.
+\bibitem[{\textit{Argus et~al.}(2005)\textit{Argus, Heflin, Peltzer, Cramp{\'{e}}, and Webb}}]{Argus2005}
+Argus, D.~F., M.~B.
+Heflin, G.~Peltzer, F.~Cramp{\'{e}}, and F.~H.
+Webb (2005), {Interseismic strain accumulation and anthropogenic motion in metropolitan Los Angeles}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B04401), 1--26, \doi{10.1029/2003JB002934}.
+
+\bibitem[{\textit{Aster et~al.}(2011)\textit{Aster, Borchers, and Thurber}}]{Aster2011}
+Aster, R.~C., B.~Borchers, and C.~H. Thurber (2011), {Parameter Estimation and Inverse Problems}, vol. 90, Academic Press.
+
+\bibitem[{\textit{Bawden et~al.}(2001)\textit{Bawden, Thatcher, Stein, Hudnut, and Peltzer}}]{Bawden2001}
+Bawden, G.~W., W.~Thatcher, R.~S.
+Stein, K.~W.
+Hudnut, and G.~Peltzer (2001), {Tectonic contraction across Los Angeles after removal of groundwater pumping effects.}, \textit{Nature}, \textit{412}, 812--815, \doi{10.1038/35090558}.
 
 \bibitem[{\textit{Bills and May}(1987)}]{Bills1987}
-Bills, B.~G., and G.~M. May (1987), {Lake Bonneville: Constraints on
-  Lithospheric Thickness and Upper Mantle Viscosity From Isostatic Warping of
-  Bonneville, Provo, and Gilbert Stage Shorelines}, \textit{Journal of
-  Geophysical Research-Solid Earth and Planets}, \textit{92}(B11),
-  11,493--11,508, \doi{10.1029/JB092iB11p11493}.
-
-\bibitem[{\textit{{\c{C}}akir et~al.}(2012)\textit{{\c{C}}akir, Ergintav,
-  {\"{O}}zener, Dogan, Akoglu, Meghraoui, and Reilinger}}]{Cakir2012}
-{\c{C}}akir, Z., S.~Ergintav, H.~{\"{O}}zener, U.~Dogan, A.~M. Akoglu,
-  M.~Meghraoui, and R.~Reilinger (2012), {Onset of aseismic creep on major
-  strike-slip faults}, \textit{Geology}, \textit{40}(12), 1115--1118,
-  \doi{10.1130/G33522.1}.
-
-\bibitem[{\textit{Cavali{\'{e}} et~al.}(2007)\textit{Cavali{\'{e}}, Doin,
-  Lasserre, and Briole}}]{Cavalie2007}
-Cavali{\'{e}}, O., M.~P. Doin, C.~Lasserre, and P.~Briole (2007), {Ground
-  motion measurement in the Lake Mead area, Nevada, by differential synthetic
-  aperture radar interferometry time series analysis: Probing the lithosphere
-  rheological structure}, \textit{Journal of Geophysical Research: Solid
-  Earth}, \textit{112}(3), 1--18, \doi{10.1029/2006JB004344}.
-
-\bibitem[{\textit{Cetin et~al.}(2014)\textit{Cetin, Cakir, Meghraoui, Ergintav,
-  and Akoglu}}]{Cetin2014}
-Cetin, E., Z.~Cakir, M.~Meghraoui, S.~Ergintav, and A.~M. Akoglu (2014),
-  {Extent and distribution of aseismic slip on the Ismetpasa segment of the
-  North Anatolian Fault (Turkey) from Persistent Scatterer InSAR},
-  \textit{Geochemistry, Geophysics, Geosystems}, \textit{15},
-  \doi{10.1002/2014GC005307.Received}.
+Bills, B.~G., and G.~M.
+May (1987), {Lake Bonneville: Constraints on Lithospheric Thickness and Upper Mantle Viscosity From Isostatic Warping of Bonneville, Provo, and Gilbert Stage Shorelines}, \textit{Journal of Geophysical Research-Solid Earth and Planets}, \textit{92}(B11), 11, 11493--11508, \doi{10.1029/JB092iB11p11493}.
+
+\bibitem[{\textit{{\c{C}}akir et~al.}(2012)\textit{{\c{C}}akir, Ergintav, {\"{O}}zener, Dogan, Akoglu, Meghraoui, and Reilinger}}]{Cakir2012}
+{\c{C}}akir, Z., S.~Ergintav, H.~{\"{O}}zener, U.~Dogan, A.~M.
+Akoglu, M.~Meghraoui, and R.~Reilinger (2012), {Onset of aseismic creep on major strike-slip faults}, \textit{Geology}, \textit{40}(12), 1115--1118, \doi{10.1130/G33522.1}.
+
+\bibitem[{\textit{Cavali{\'{e}} et~al.}(2007)\textit{Cavali{\'{e}}, Doin, Lasserre, and Briole}}]{Cavalie2007}
+Cavali{\'{e}}, O., M.~P.
+Doin, C.~Lasserre, and P.~Briole (2007), {Ground motion measurement in the Lake Mead area, Nevada, by differential synthetic aperture radar interferometry time series analysis: Probing the lithosphere rheological structure}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{112}(B03403), 1--18, \doi{10.1029/2006JB004344}.
+
+\bibitem[{\textit{Cetin et~al.}(2014)\textit{Cetin, Cakir, Meghraoui, Ergintav, and Akoglu}}]{Cetin2014}
+Cetin, E., Z.~Cakir, M.~Meghraoui, S.~Ergintav, and A.~M.
+Akoglu (2014), {Extent and distribution of aseismic slip on the Ismetpasa segment of the North Anatolian Fault (Turkey) from Persistent Scatterer InSAR}, \textit{Geochemistry, Geophysics, Geosystems}, \textit{15}, \doi{10.1002/2014GC005307}.
 
 \bibitem[{\textit{Chopra}(1997)}]{Chopra1997}
-Chopra, P.~N. (1997), {High-temperature transient creep in olivine rocks},
-  \textit{Tectonophysics}, \textit{279}, 93--111,
-  \doi{10.1016/S0040-1951(97)00134-0}.
+Chopra, P.~N. (1997), {High-temperature transient creep in olivine rocks}, \textit{Tectonophysics}, \textit{279}, 93--111, \doi{10.1016/S0040-1951(97)00134-0}.
 
 \bibitem[{\textit{Crittenden}(1967)}]{Crittenden1967}
-Crittenden, M. (1967), {Viscosity and Finite Strength of the Mantle as
-  Determined from Water and Ice Loads*}, \textit{Geophysical Journal of the
-  Royal Astronomical {\ldots}}, pp. 261--279,
-  \doi{10.1111/j.1365-246X.1967.tb06243.x}.
-
-\bibitem[{\textit{Davis et~al.}(2012)\textit{Davis, Wernicke, and
-  Tamisiea}}]{Davis2012}
-Davis, J.~L., B.~P. Wernicke, and M.~E. Tamisiea (2012), {On seasonal signals
-  in geodetic time series}, \textit{Journal of Geophysical Research: Solid
-  Earth}, \textit{117}(1), 1--10, \doi{10.1029/2011JB008690}.
+Crittenden, M.
+(1967), {Viscosity and Finite Strength of the Mantle as Determined from Water and Ice Loads}, \textit{Geophysical Journal of the Royal Astronomical Society}, 261--279, \doi{10.1111/j.1365-246X.1967.tb06243.x}.
+
+\bibitem[{\textit{Davis et~al.}(2012)\textit{Davis, Wernicke, and Tamisiea}}]{Davis2012}
+Davis, J.~L., B.~P.
+Wernicke, and M.~E.
+Tamisiea (2012), {On seasonal signals in geodetic time series}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{117}(B01403), 1--10, \doi{10.1029/2011JB008690}.
 
 \bibitem[{\textit{Feigl and Thatcher}(2006)}]{Feigl2006}
-Feigl, K.~L., and W.~Thatcher (2006), {Geodetic observations of post-seismic
-  transients in the context of the earthquake deformation cycle},
-  \textit{Comptes Rendus - Geoscience}, \textit{338}, 1012--1028,
-  \doi{10.1016/j.crte.2006.06.006}.
-
-\bibitem[{\textit{Fletcher et~al.}(2014)\textit{Fletcher, Teran, Rockwell,
-  Oskin, Hudnut, Mueller, Spelz, Akciz, Masana, Faneros, Fielding, Leprince,
-  Morelan, Stock, Lynch, Elliott, Gold, Liu-Zeng, Gonz{\'{a}}lez-Ortega,
-  Hinojosa-Corona, and Gonz{\'{a}}lez-Garc{\'{i}}a}}]{Fletcher2014}
-Fletcher, J.~M., O.~J. Teran, T.~K. Rockwell, M.~E. Oskin, K.~W. Hudnut, K.~J.
-  Mueller, R.~M. Spelz, S.~O. Akciz, E.~Masana, G.~Faneros, E.~J. Fielding,
-  S.~Leprince, A.~E. Morelan, J.~Stock, D.~K. Lynch, A.~J. Elliott, P.~Gold,
-  J.~Liu-Zeng, A.~Gonz{\'{a}}lez-Ortega, A.~Hinojosa-Corona, and
-  J.~Gonz{\'{a}}lez-Garc{\'{i}}a (2014), {Assembly of a large earthquake from a
-  complex fault system: Surface rupture kinematics of the 4 April 2010 El
-  Mayor-Cucapah (Mexico) Mw 7.2 earthquake}, \textit{Geosphere},
-  \textit{10}(4), 797--827, \doi{10.1130/GES00933.1}.
-
-\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais,
-  Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
-Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and
-  S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002
-  Denali, Alaska, earthquake for postseismic relaxation processes and
-  lithospheric rheology}, \textit{Journal of Geophysical Research: Solid
-  Earth}, \textit{111}, 1--23, \doi{10.1029/2005JB003894}.
-
-\bibitem[{\textit{Freed et~al.}(2007)\textit{Freed, B{\"{u}}rgmann, and
-  Herring}}]{Freed2007a}
-Freed, A.~M., R.~B{\"{u}}rgmann, and T.~Herring (2007), {Far-reaching transient
-  motions after Mojave earthquakes require broad mantle flow beneath a strong
-  crust}, \textit{Geophysical Research Letters}, \textit{34}, 1--5,
-  \doi{10.1029/2007GL030959}.
-
-\bibitem[{\textit{Gonzalez-Ortega et~al.}(2014)\textit{Gonzalez-Ortega, Fialko,
-  Sandwell, Nava-pichardo, Fletcher, Gonzalez-garcia, Lipovsky, Floyd, and
-  Funning}}]{Gonzalez-ortega2014}
-Gonzalez-Ortega, A., Y.~Fialko, D.~Sandwell, F.~A. Nava-pichardo, J.~Fletcher,
-  J.~Gonzalez-garcia, B.~Lipovsky, M.~Floyd, and G.~Funning (2014), {El
-  Mayor-Cucapah (Mw7.2) earthquake: early near-field postseismic deformation
-  from InSar and GPS observations}, \textit{Journal of Geophysical Research},
-  \textit{119}, 1482--1497, \doi{10.1002/2013JB010193.Received}.
-
-\bibitem[{\textit{Hauksson et~al.}(2011)\textit{Hauksson, Stock, Hutton, Yang,
-  Vidal-Villegas, and Kanamori}}]{Hauksson2011}
-Hauksson, E., J.~Stock, K.~Hutton, W.~Yang, J.~A. Vidal-Villegas, and
-  H.~Kanamori (2011), {The 2010 Mw 7.2 El mayor-cucapah earthquake sequence,
-  Baja California, Mexico and Southernmost California, USA: Active
-  seismotectonics along the Mexican pacific margin}, \textit{Pure and Applied
-  Geophysics}, \textit{168}(3918), 1255--1277, \doi{10.1007/s00024-010-0209-7}.
+Feigl, K.~L., and W.~Thatcher (2006), {Geodetic observations of post-seismic transients in the context of the earthquake deformation cycle}, \textit{Comptes Rendus - Geoscience}, \textit{338}, 1012--1028, \doi{10.1016/j.crte.2006.06.006}.
+
+\bibitem[{\textit{Fletcher et~al.}(2014)\textit{Fletcher, Teran, Rockwell, Oskin, Hudnut, Mueller, Spelz, Akciz, Masana, Faneros, Fielding, Leprince, Morelan, Stock, Lynch, Elliott, Gold, Liu-Zeng, Gonz{\'{a}}lez-Ortega, Hinojosa-Corona, and Gonz{\'{a}}lez-Garc{\'{i}}a}}]{Fletcher2014}
+Fletcher, J.~M., O.~J.
+Teran, T.~K.
+Rockwell, M.~E.
+Oskin, K.~W.
+Hudnut, K.~J.
+Mueller, R.~M.
+Spelz, S.~O.
+Akciz, E.~Masana, G.~Faneros, E.~J.
+Fielding, S.~Leprince, A.~E.
+Morelan, J.~Stock, D.~K.
+Lynch, A.~J.
+Elliott, P.~Gold, J.~Liu-Zeng, A.~Gonz{\'{a}}lez-Ortega, A.~Hinojosa-Corona, and J.~Gonz{\'{a}}lez-Garc{\'{i}}a (2014), {Assembly of a large earthquake from a complex fault system: Surface rupture kinematics of the 4 April 2010 El Mayor-Cucapah (Mexico) Mw 7.2 earthquake}, \textit{Geosphere}, \textit{10}(4), 797--827, \doi{10.1130/GES00933.1}.
+
+\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais, Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
+Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002 Denali, Alaska, earthquake for postseismic relaxation processes and lithospheric rheology}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{111}{B01401}, 1--23, \doi{10.1029/2005JB003894}.
+
+\bibitem[{\textit{Freed et~al.}(2007)\textit{Freed, B{\"{u}}rgmann, and Herring}}]{Freed2007a}
+Freed, A.~M., R.~B{\"{u}}rgmann, and T.~Herring (2007), {Far-reaching transient motions after Mojave earthquakes require broad mantle flow beneath a strong crust}, \textit{Geophysical Research Letters}, \textit{34}(L19302), 1--5, \doi{10.1029/2007GL030959}.
+
+\bibitem[{\textit{Gonzalez-Ortega et~al.}(2014)\textit{Gonzalez-Ortega, Fialko, Sandwell, Nava-pichardo, Fletcher, Gonzalez-garcia, Lipovsky, Floyd, and Funning}}]{Gonzalez-ortega2014}
+Gonzalez-Ortega, A., Y.~Fialko, D.~Sandwell, F.~A.
+Nava-pichardo, J.~Fletcher, J.~Gonzalez-garcia, B.~Lipovsky, M.~Floyd, and G.~Funning (2014), {El Mayor-Cucapah (Mw7.2) earthquake: early near-field postseismic deformation from InSar and GPS observations}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{119}, 1482--1497, \doi{10.1002/2013JB010193}.
+
+\bibitem[{\textit{Hauksson et~al.}(2011)\textit{Hauksson, Stock, Hutton, Yang, Vidal-Villegas, and Kanamori}}]{Hauksson2011}
+Hauksson, E., J.~Stock, K.~Hutton, W.~Yang, J.~A.
+Vidal-Villegas, and H.~Kanamori (2011), {The 2010 Mw 7.2 El mayor-cucapah earthquake sequence, Baja California, Mexico and Southernmost California, USA: Active seismotectonics along the Mexican pacific margin}, \textit{Pure and Applied Geophysics}, \textit{168}, 1255--1277, \doi{10.1007/s00024-010-0209-7}.
 
 \bibitem[{\textit{Hearn}(2003)}]{Hearn2003}
-Hearn, E.~H. (2003), {What can GPS data tell us about the dynamics of
-  post-seismic deformation ?}, (2003), 753--777.
-
-\bibitem[{\textit{Hearn et~al.}(2009)\textit{Hearn, McClusky, Ergintav, and
-  Reilinger}}]{Hearn2009}
-Hearn, E.~H., S.~McClusky, S.~Ergintav, and R.~E. Reilinger (2009), {Izmit
-  earthquake postseismic deformation and dynamics of the North Anatolian Fault
-  Zone}, \textit{Journal of Geophysical Research: Solid Earth},
-  \textit{114}(August 2008), 1--21, \doi{10.1029/2008JB006026}.
+Hearn, E.~H.
+(2003), {What can GPS data tell us about the dynamics of post-seismic deformation}, \textit{Geophysical Journal International}, \textit{115}, 753--777, \doi{10.1111/j.1365-246X.2003.02030.x}.
+
+\bibitem[{\textit{Hearn et~al.}(2009)\textit{Hearn, McClusky, Ergintav, and Reilinger}}]{Hearn2009} 
+Hearn, E.~H., S.~McClusky, S.~Ergintav, and R.~E.
+Reilinger (2009), {Izmit earthquake postseismic deformation and dynamics of the North Anatolian Fault Zone}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{114}(B08405), 1--21, \doi{10.1029/2008JB006026}.
 
 \bibitem[{\textit{Hetland}(2003)}]{Hetland2003}
-Hetland, E.~A. (2003), {Postseismic relaxation across the Central Nevada
-  Seismic Belt}, \textit{Journal of Geophysical Research}, \textit{108}(Figure
-  2), 1--13, \doi{10.1029/2002JB002257}.
+Hetland, E.~A. (2003), {Postseismic relaxation across the Central Nevada Seismic Belt}, \textit{Journal of Geophysical Research}, \textit{108}(B8), 1--13, \doi{10.1029/2002JB002257}.
 
 \bibitem[{\textit{Hetland and Zhang}(2014)}]{Hetland2014}
-Hetland, E.~A., and G.~Zhang (2014), {Effect of shear zones on post-seismic
-  deformation with application to the 1997 Mw 7.6 manyi earthquake},
-  \textit{Geophysical Journal International}, \textit{198}, 259--269,
-  \doi{10.1093/gji/ggu127}.
+Hetland, E.~A., and G.~Zhang (2014), {Effect of shear zones on post-seismic deformation with application to the 1997 Mw 7.6 manyi earthquake}, \textit{Geophysical Journal International}, \textit{206}(2), 1--11, \doi{10.1093/gji/ggu127}.
 
 \bibitem[{\textit{Hines and Hetland}(2013)}]{Hines2013}
-Hines, T.~T., and E.~A. Hetland (2013), {Bias in estimates of lithosphere
-  viscosity from interseismic deformation}, \textit{Geophysical Research
-  Letters}, \textit{40}(16), 4260--4265, \doi{10.1002/grl.50839}.
+Hines, T.~T., and E.~A.
+Hetland (2013), {Bias in estimates of lithosphere viscosity from interseismic deformation}, \textit{Geophysical Research Letters}, \textit{40}(16), 4260--4265, \doi{10.1002/grl.50839}.
 
 \bibitem[{\textit{Hines and Hetland}(2016)}]{Hines2016}
-Hines, T.~T., and E.~A. Hetland (2016), {Rapid and simultaneous estimation of
-  fault slip and heterogeneous lithospheric viscosity from post-seismic
-  deformation}, \textit{Geophysical Journal International}, \textit{204}(1),
-  569--582, \doi{10.1093/gji/ggv477}.
-
-\bibitem[{\textit{Jacobs et~al.}(2002)\textit{Jacobs, Sandwell, Fialko, and
-  Sichoix}}]{Jacobs2002}
-Jacobs, A., D.~Sandwell, Y.~Fialko, and L.~Sichoix (2002), {The 1999 (Mw7.1)
-  Hector Mine, California, Earthquake: Near-Field Postseismic Deformation from
-  ERS Interferometry}, \textit{Bulletin of the Seismological Society of
-  America}, \textit{92}(May), 1433--1442.
+Hines, T.~T., and E.~A.
+Hetland (2016), {Rapid and simultaneous estimation of fault slip and heterogeneous lithospheric viscosity from post-seismic deformation}, \textit{Geophysical Journal International}, \textit{204}(1), 569--582, \doi{10.1093/gji/ggv477}.
+
+\bibitem[{\textit{Jacobs et~al.}(2002)\textit{Jacobs, Sandwell, Fialko, and Sichoix}}]{Jacobs2002}
+Jacobs, A., D.~Sandwell, Y.~Fialko, and L.~Sichoix (2002), {The 1999 (Mw7.1) Hector Mine, California, Earthquake: Near-Field Postseismic Deformation from ERS Interferometry}, \textit{Bulletin of the Seismological Society of America}, \textit{92}(4), 1433--1442.
 
 \bibitem[{\textit{Johnson and Segall}(2004)}]{Johnson2004}
-Johnson, K.~M., and P.~Segall (2004), {Viscoelastic earthquake cycle models
-  with deep stress-driven creep along the San Andreas fault system},
-  \textit{Journal of Geophysical Research: Solid Earth}, \textit{109}, 1--19,
-  \doi{10.1029/2004JB003096}.
-
-\bibitem[{\textit{Johnson et~al.}(2009)\textit{Johnson, B{\"{u}}rgmann, and
-  Freymueller}}]{Johnson2009}
-Johnson, K.~M., R.~B{\"{u}}rgmann, and J.~T. Freymueller (2009), {Coupled
-  afterslip and viscoelastic flow following the 2002 Denali Fault, Alaska
-  earthquake}, \textit{Geophysical Journal International}, \textit{176}(3),
-  670--682, \doi{10.1111/j.1365-246X.2008.04029.x}.
-
-\bibitem[{\textit{J{\'{o}}nsson et~al.}(2003)\textit{J{\'{o}}nsson, Segall,
-  Pedersen, and Bjornsson}}]{Jonsson2003}
-J{\'{o}}nsson, S., P.~Segall, R.~Pedersen, and G.~Bjornsson (2003),
-  {Post-earthquake ground movements correlated to pore-pressure transients},
-  \textit{Nature}, \textit{424}(July), 179--183, \doi{10.1038/nature01758.1.}
+Johnson, K.~M., and P.~Segall (2004), {Viscoelastic earthquake cycle models with deep stress-driven creep along the San Andreas fault system}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{109}(B10403), 1--19, \doi{10.1029/2004JB003096}.
+
+\bibitem[{\textit{Johnson et~al.}(2009)\textit{Johnson, B{\"{u}}rgmann, and Freymueller}}]{Johnson2009}
+Johnson, K.~M., R.~B{\"{u}}rgmann, and J.~T.
+Freymueller (2009), {Coupled afterslip and viscoelastic flow following the 2002 Denali Fault, Alaska earthquake}, \textit{Geophysical Journal International}, \textit{176}(3), 670--682, \doi{10.1111/j.1365-246X.2008.04029.x}.
+
+\bibitem[{\textit{J{\'{o}}nsson et~al.}(2003)\textit{J{\'{o}}nsson, Segall, Pedersen, and Bjornsson}}]{Jonsson2003}
+J{\'{o}}nsson, S., P.~Segall, R.~Pedersen, and G.~Bjornsson (2003), {Post-earthquake ground movements correlated to pore-pressure transients}, \textit{Nature}, \textit{424}, 179--183, \doi{10.1038/nature01758.1.}
 
 \bibitem[{\textit{Kaufmann and Amelung}(2000)}]{Kaufmann2000}
-Kaufmann, G., and F.~Amelung (2000), {Reservoir-induced deformation and
-  continental rheology in vicinity of Lake Mead, Nevada}, \textit{Journal of
-  Geophysical Research}, \textit{105}(B7), 16,341, \doi{10.1029/2000JB900079}.
-
-\bibitem[{\textit{Kroll et~al.}(2013)\textit{Kroll, Cochran, Richards-Dinger,
-  and Sumy}}]{Kroll2013}
-Kroll, K.~A., E.~S. Cochran, K.~B. Richards-Dinger, and D.~F. Sumy (2013),
-  {Aftershocks of the 2010 Mw 7.2 El Mayor-Cucapah earthquake reveal complex
-  faulting in the Yuha Desert, California}, \textit{Journal of Geophysical
-  Research: Solid Earth}, \textit{118}(October), 6146--6164,
-  \doi{10.1002/2013JB010529}.
-
-\bibitem[{\textit{Lekic et~al.}(2011)\textit{Lekic, French, and
-  Fischer}}]{Lekic2011}
-Lekic, V., S.~W. French, and K.~M. Fischer (2011), {Lithospheric Thinning
-  Beneath Rifted Regions of Southern California}, \textit{Science},
-  \textit{334}(November), 783--787.
-
-\bibitem[{\textit{Liu et~al.}(1976)\textit{Liu, Anderson, and
-  Kanamori}}]{Liu1976}
-Liu, H.-P., D.~L. Anderson, and H.~Kanamori (1976), {Velocity dispersion due to
-  anelasticity; implications for seismology and mantle composition},
-  \textit{Geophysical Journal International}, \textit{47}(1), 41--58,
-  \doi{10.1111/j.1365-246X.1976.tb01261.x}.
-
-\bibitem[{\textit{Lundgren et~al.}(2009)\textit{Lundgren, Hetland, Liu, and
-  Fielding}}]{Lundgren2009}
-Lundgren, P., E.~A. Hetland, Z.~Liu, and E.~J. Fielding (2009), {Southern San
-  Andreas-San Jacinto fault system slip rates estimated from earthquake cycle
-  models constrained by GPS and interferometric synthetic aperture radar
-  observations}, \textit{Journal of Geophysical Research: Solid Earth},
-  \textit{114}(2), 1--18, \doi{10.1029/2008JB005996}.
+Kaufmann, G., and F.~Amelung (2000), {Reservoir-induced deformation and continental rheology in vicinity of Lake Mead, Nevada}, \textit{Journal of Geophysical Research}, \textit{105}(B7), 16,341, \doi{10.1029/2000JB900079}.
+
+\bibitem[{\textit{Kroll et~al.}(2013)\textit{Kroll, Cochran, Richards-Dinger, and Sumy}}]{Kroll2013}
+Kroll, K.~A., E.~S.
+Cochran, K.~B.
+Richards-Dinger, and D.~F.
+Sumy (2013), {Aftershocks of the 2010 Mw 7.2 El Mayor-Cucapah earthquake reveal complex faulting in the Yuha Desert, California}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{118}, 6146--6164, \doi{10.1002/2013JB010529}.
+
+\bibitem[{\textit{Lekic et~al.}(2011)\textit{Lekic, French, and Fischer}}]{Lekic2011}
+Lekic, V., S.~W. French, and K.~M. Fischer (2011), {Lithospheric Thinning Beneath Rifted Regions of Southern California}, \textit{Science} \textit{334}, 783--787.
+
+\bibitem[{\textit{Liu et~al.}(1976)\textit{Liu, Anderson, and Kanamori}}]{Liu1976}
+Liu, H.-P., D.~L.
+Anderson, and H.~Kanamori (1976), {Velocity dispersion due to anelasticity; implications for seismology and mantle composition} \textit{Geophysical Journal of the Royal Astronomical Society}, \textit{47}, 41--58, \doi{10.1111/j.1365-246X.1976.tb01261.x}.
+
+\bibitem[{\textit{Lundgren et~al.}(2009)\textit{Lundgren, Hetland, Liu, and Fielding}}]{Lundgren2009}
+Lundgren, P., E.~A.
+Hetland, Z.~Liu, and E.~J.
+Fielding (2009), {Southern San Andreas-San Jacinto fault system slip rates estimated from earthquake cycle models constrained by GPS and interferometric synthetic aperture radar observations}, \textit{Journal of Geophysical Research: Solid Earth} \textit{114}(B02403), 1--18, \doi{10.1029/2008JB005996}.
 
 \bibitem[{\textit{McGuire and Segall}(2003)}]{McGuire2003}
-McGuire, J.~J., and P.~Segall (2003), {Imaging of aseismic fault slip
-  transients recorded by dense geodetic networks}, \textit{Geophysical Journal
-  International}, \textit{155}(3), 778--788,
-  \doi{10.1111/j.1365-246X.2003.02022.x}.
+McGuire, J.~J., and P.~Segall (2003), {Imaging of aseismic fault slip transients recorded by dense geodetic networks}, \textit{Geophysical Journal International}, \textit{155}, 778--788, \doi{10.1111/j.1365-246X.2003.02022.x}.
 
 \bibitem[{\textit{Meade and Hager}(2005)}]{Meade2005}
-Meade, B.~J., and B.~H. Hager (2005), {Block models of crustal motion in
-  southern California constrained by GPS measurements}, \textit{Journal of
-  Geophysical Research B: Solid Earth}, \textit{110}, 1--19,
-  \doi{10.1029/2004JB003209}.
+Meade, B.~J., and B.~H.
+Hager (2005), {Block models of crustal motion in southern California constrained by GPS measurements}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B03403), 1--19, \doi{10.1029/2004JB003209}.
 
 \bibitem[{\textit{Murray and Segall}(2005)}]{Murray2005}
-Murray, J.~R., and P.~Segall (2005), {Spatiotemporal evolution of a transient
-  slip event on the San Andreas fault near Parkfield, California},
-  \textit{Journal of Geophysical Research : Solid Earth}, \textit{110}(9),
-  1--12, \doi{10.1029/2005JB003651}.
+Murray, J.~R., and P.~Segall (2005), {Spatiotemporal evolution of a transient slip event on the San Andreas fault near Parkfield, California}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B09407), 1--12, \doi{10.1029/2005JB003651}.
 
 \bibitem[{\textit{Nur and Mavko}(1974)}]{Nur1974}
-Nur, A., and G.~Mavko (1974), {Postseismic viscoelastic rebound},
-  \textit{Science}, \textit{183}(4121), 204--206, \doi{10.1038/098448b0}.
+Nur, A., and G.~Mavko (1974), {Postseismic viscoelastic rebound}, \textit{Science}, \textit{183}(4121), 204--206, \doi{10.1038/098448b0}.
 
 \bibitem[{\textit{O'Connell}(1971)}]{OConnell1971}
-O'Connell, R.~J. (1971), {Rheology of the Mantle}, \textit{EOS, Transactions,
-  American Geophysical Union}, \textit{52}, 140--142.
-
-\bibitem[{\textit{Oskin et~al.}(2012)\textit{Oskin, Arrowsmith, {Hinojosa
-  Corona}, Elliott, Fletcher, Fielding, Gold, {Gonzalez Garcia}, Hudnut,
-  Liu-Zeng, and Teran}}]{Oskin2012}
-Oskin, M.~E., J.~R. Arrowsmith, A.~{Hinojosa Corona}, A.~J. Elliott, J.~M.
-  Fletcher, E.~J. Fielding, P.~O. Gold, J.~J. {Gonzalez Garcia}, K.~W. Hudnut,
-  J.~Liu-Zeng, and O.~J. Teran (2012), {Near-field deformation from the El
-  Mayor-Cucapah earthquake revealed by differential LIDAR}, \textit{Science},
-  \textit{335}(6069), 702--705, \doi{10.1126/science.1213778}.
-
-\bibitem[{\textit{Pollitz et~al.}(2001)\textit{Pollitz, Wicks, and
-  Thatcher}}]{Pollitz2001}
-Pollitz, F., C.~Wicks, and W.~Thatcher (2001), {Mantle Flow Beneath a
-  Continental Strike-Slip Fault : Postseismic Deformation After the 1999 Hector
-  Mine Earthquake}, \textit{Science}, \textit{1814}(2001), 1814--1818,
-  \doi{10.1126/science.1061361}.
+O'Connell, R.~J. (1971), {Rheology of the Mantle}, \textit{EOS, Transactions, American Geophysical Union}, \textit{52}, 140--142.
+
+\bibitem[{\textit{Oskin et~al.}(2012)\textit{Oskin, Arrowsmith, {Hinojosa Corona}, Elliott, Fletcher, Fielding, Gold, {Gonzalez Garcia}, Hudnut, Liu-Zeng, and Teran}}]{Oskin2012}
+Oskin, M.~E., J.~R.
+Arrowsmith, A.~{Hinojosa Corona}, A.~J.
+Elliott, J.~M.
+Fletcher, E.~J.
+Fielding, P.~O.
+Gold, J.~J.
+{Gonzalez Garcia}, K.~W.
+Hudnut, J.~Liu-Zeng, and O.~J.
+Teran (2012), {Near-field deformation from the El Mayor-Cucapah earthquake revealed by differential LIDAR}, \textit{Science}, \textit{335}, 702--705, \doi{10.1126/science.1213778}.
+
+\bibitem[{\textit{Pollitz et~al.}(2001)\textit{Pollitz, Wicks, and Thatcher}}]{Pollitz2001}
+Pollitz, F., C.~Wicks, and W.~Thatcher (2001), {Mantle Flow Beneath a Continental Strike-Slip Fault: Postseismic Deformation After the 1999 Hector Mine Earthquake}, \textit{Science}, \textit{293}, 1814--1818, \doi{10.1126/science.1061361}.
 
 \bibitem[{\textit{Pollitz}(2003)}]{Pollitz2003}
-Pollitz, F.~F. (2003), {Transient rheology of the uppermost mantle beneath the
-  Mojave Desert, California}, \textit{Earth and Planetary Science Letters},
-  \textit{215}, 89--104, \doi{10.1016/S0012-821X(03)00432-1}.
-
-\bibitem[{\textit{Pollitz et~al.}(2000)\textit{Pollitz, Peltzer, and
-  B{\"{u}}rgmann}}]{Pollitz2000}
-Pollitz, F.~F., G.~Peltzer, and R.~B{\"{u}}rgmann (2000), {Mobility of
-  continental mantle: Evidence from postseismic geodetic observations following
-  the 1992 Landers earthquake}, \textit{Journal of Geophysical Research},
-  \textit{105}(1999), 8035, \doi{10.1029/1999JB900380}.
-
-\bibitem[{\textit{Pollitz et~al.}(2012)\textit{Pollitz, B{\"{u}}rgmann, and
-  Thatcher}}]{Pollitz2012} 
-  Pollitz, F.~F., R.~B{\"{u}}rgmann, and W.~Thatcher (2012), {Illumination of
-  rheological mantle heterogeneity by the M7.2 2010 El Mayor-Cucapah
-  earthquake}, \textit{Geochemistry, Geophysics, Geosystems}, \textit{13}(6),
-  1--17, \doi{10.1029/2012GC004139}.
+Pollitz, F.~F.
+(2003), {Transient rheology of the uppermost mantle beneath the Mojave Desert, California}, \textit{Earth and Planetary Science Letters}, \textit{215}, 89--104, \doi{10.1016/S0012-821X(03)00432-1}.
+
+\bibitem[{\textit{Pollitz et~al.}(2000)\textit{Pollitz, Peltzer, and B{\"{u}}rgmann}}]{Pollitz2000}
+Pollitz, F.~F., G.~Peltzer, and R.~B{\"{u}}rgmann (2000), {Mobility of continental mantle: Evidence from postseismic geodetic observations following the 1992 Landers earthquake}, \textit{Journal of Geophysical Research}, \textit{105}(B4), 8035--8054, \doi{10.1029/1999JB900380}.
+
+\bibitem[{\textit{Pollitz et~al.}(2012)\textit{Pollitz, B{\"{u}}rgmann, and Thatcher}}]{Pollitz2012} 
+Pollitz, F.~F., R.~B{\"{u}}rgmann, and W.~Thatcher (2012), {Illumination of rheological mantle heterogeneity by the M7.2 2010 El Mayor-Cucapah earthquake}, \textit{Geochemistry, Geophysics, Geosystems}, \textit{13}(6), 1--17, \doi{10.1029/2012GC004139}.
 
@@
 (2015).
-{Postearthquake relaxation evidence for laterally variable viscoelastic structure and water content in the Southern California mantle}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{120},2672--2696, \doi{10.1002/2014JB011603}.
-
-\bibitem[{\textit{Rauch et~al.}(1965)\textit{Rauch, Tung, and
-  Striebel}}]{Rauch1965}
-Rauch, H.~E., F.~Tung, and C.~T. Striebel (1965), {Maximum likelihood estimates
-  of linear dynamic systems}, \textit{AIAA Journal}, \textit{3}(8), 1445--1450.
+{Postearthquake relaxation evidence for laterally variable viscoelastic structure and water content in the Southern California mantle}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{120}, 2672--2696, \doi{10.1002/2014JB011603}.
+
+\bibitem[{\textit{Rauch et~al.}(1965)\textit{Rauch, Tung, and Striebel}}]{Rauch1965}
+Rauch, H.~E., F.~Tung, and C.~T. Striebel (1965), {Maximum likelihood estimates of linear dynamic systems}, \textit{AIAA Journal}, \textit{3}(8), 1445--1450.
 
 \bibitem[{\textit{Riva and Govers}(2009)}]{Riva2009}
-Riva, R. E.~M., and R.~Govers (2009), {Relating viscosities from postseismic
-  relaxation to a realistic viscosity structure for the lithosphere},
-  \textit{Geophysical Journal International}, \textit{176}, 614--624,
-  \doi{10.1111/j.1365-246X.2008.04004.x}.
-
-\bibitem[{\textit{Rollins et~al.}(2015)\textit{Rollins, Barbot, and
-  Avouac}}]{Rollins2015}
-Rollins, C., S.~Barbot, and J.-P. Avouac (2015), {Postseismic Deformation
-  Following the 2010 M7.2 El Mayor-Cucapah Earthquake : Observations ,
-  Kinematic Inversions , and Dynamic Models}, \textit{Pure and Applied
-  Geophysics}, \doi{10.1007/s00024-014-1005-6}.
+Riva, R.
+E.~M., and R.~Govers (2009), {Relating viscosities from postseismic relaxation to a realistic viscosity structure for the lithosphere}, \textit{Geophysical Journal International}, \textit{176}, 614--624, \doi{10.1111/j.1365-246X.2008.04004.x}.
+
+\bibitem[{\textit{Rollins et~al.}(2015)\textit{Rollins, Barbot, and Avouac}}]{Rollins2015}
+Rollins, C., S.~Barbot, and J.-P.
+Avouac (2015), {Postseismic Deformation Following the 2010 M7.2 El Mayor-Cucapah Earthquake: Observations, Kinematic Inversions, and Dynamic Models}, \textit{Pure and Applied Geophysics}, \textit{172}(5), 1305-1358, \doi{10.1007/s00024-014-1005-6}.
 
 \bibitem[{\textit{Savage}(1990)}]{Savage1990}
-Savage, J.~C. (1990), {Equivalent strike-slip earthquake cycles in half-space
-  and lithosphere-asthenosphere earth models}, \textit{Journal of Geophysical
-  Research}, \textit{95}, 4873, \doi{10.1029/JB095iB04p04873}.
+Savage, J.~C.
+(1990), {Equivalent strike-slip earthquake cycles in half-space and lithosphere-asthenosphere earth models}, \textit{Journal of Geophysical Research}, \textit{95}(B4), 4873--4879, \doi{10.1029/JB095iB04p04873}.
 
 \bibitem[{\textit{Savage and Svarc}(2009)}]{Savage2009}
-Savage, J.~C., and J.~L. Svarc (2009), {Postseismic relaxation following the
-  1992 M 7.3 Landers and 1999 M 7.1 Hector Mine earthquakes , southern
-  California}, \textit{Journal of Geophysical Research}, \textit{114}(B01401),
-  \doi{10.1029/2008JB005938}.
-
-\bibitem[{\textit{Savage et~al.}(2005)\textit{Savage, Svarc, and
-  Yu}}]{Savage2005a}
-Savage, J.~C., J.~L. Svarc, and S.~B. Yu (2005), {Postseismic relaxation and
-  transient creep}, \textit{Journal of Geophysical Research: Solid Earth},
-  \textit{110}, 1--14, \doi{10.1029/2005JB003687}.
+Savage, J.~C., and J.~L.
+Svarc (2009), {Postseismic relaxation following the 1992 M7.3 Landers and 1999 M7.1 Hector Mine earthquakes, southern California}, \textit{Journal of Geophysical Research}, \textit{114}(B01401), \doi{10.1029/2008JB005938}.
+
+\bibitem[{\textit{Savage et~al.}(2005)\textit{Savage, Svarc, and Yu}}]{Savage2005a}
+Savage, J.~C., J.~L.
+Svarc, and S.~B.
+Yu (2005), {Postseismic relaxation and transient creep}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B11402), 1--14, \doi{10.1029/2005JB003687}.
 
 \bibitem[{\textit{Segall and Mathews}(1997)}]{Segall1997}
-Segall, P., and M.~Mathews (1997), {Time dependent inversion of geodetic data},
-  \textit{Journal of Geophysical Research}, \textit{102}.
-
-\bibitem[{\textit{Spinler et~al.}(2015)\textit{Spinler, Bennett, Walls, Shawn,
-  and Garcia}}]{Spinler2015}
-Spinler, J.~C., R.~A. Bennett, C.~Walls, L.~Shawn, and J.~J.~G. Garcia (2015),
-  {Assessing long-term postseismic deformation following the M7.2 4 April 2010,
-  El Mayor-Cucapah earthquake with implications for lithospheric rheology in
-  the Salton Trough}, \textit{Journal of Geophysical Research: Solid Earth},
-  \textit{120}, 3664--3679, \doi{10.1002/2014JB011613.Received}.
-
-\bibitem[{\textit{Wei et~al.}(2011{\natexlab{a}})\textit{Wei, Sandwell, Fialko,
-  and Bilham}}]{Wei2011a}
-Wei, M., D.~Sandwell, Y.~Fialko, and R.~Bilham (2011{\natexlab{a}}), {Slip on
-  faults in the Imperial Valley triggered by the 4 April 2010 Mw 7.2 El
-  Mayor-Cucapah earthquake revealed by InSAR}, \textit{Geophysical Research
-  Letters}, \textit{38}(January), 1--6, \doi{10.1029/2010GL045235}.
-
-\bibitem[{\textit{Wei et~al.}(2015)\textit{Wei, Liu, Kaneko, Mcguire, and
-  Bilham}}]{Wei2015}
-Wei, M., Y.~Liu, Y.~Kaneko, J.~J. Mcguire, and R.~Bilham (2015), {Dynamic
-  triggering of creep events in the Salton Trough, Southern California by
-  regional M≥5.4 earthquakes constrained by geodetic observations and
-  numerical simulations}, \textit{Earth and Planetary Science Letters},
-  \textit{427}, 1--10, \doi{10.1016/j.epsl.2015.06.044}.
-
-\bibitem[{\textit{Wei et~al.}(2011{\natexlab{b}})\textit{Wei, Fielding,
-  Leprince, Sladen, Avouac, Helmberger, Hauksson, Chu, Simons, Hudnut, Herring,
-  and Briggs}}]{Wei2011}
-Wei, S., E.~Fielding, S.~Leprince, A.~Sladen, J.-P. Avouac, D.~Helmberger,
-  E.~Hauksson, R.~Chu, M.~Simons, K.~Hudnut, T.~Herring, and R.~Briggs
-  (2011{\natexlab{b}}), {Superficial simplicity of the 2010 El Mayor–Cucapah
-  earthquake of Baja California in Mexico}, \textit{Nature Geoscience},
-  \textit{4}(9), 615--618, \doi{10.1038/ngeo1213}.
+Segall, P., and M.~Mathews (1997), {Time dependent inversion of geodetic data}, \textit{Journal of Geophysical Research}, \textit{102}(B10). 22391--22409
+
+\bibitem[{\textit{Spinler et~al.}(2015)\textit{Spinler, Bennett, Walls, Shawn, and Garcia}}]{Spinler2015}
+Spinler, J.~C., R.~A.
+Bennett, C.~Walls, L.~Shawn, and J.~J.~G.
+Garcia (2015), {Assessing long-term postseismic deformation following the M7.2 4 April 2010, El Mayor-Cucapah earthquake with implications for lithospheric rheology in the Salton Trough}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{120}, 3664--3679, \doi{10.1002/2014JB011613}.
+
+\bibitem[{\textit{Wei et~al.}(2011{\natexlab{a}})\textit{Wei, Sandwell, Fialko, and Bilham}}]{Wei2011a}
+Wei, M., D.~Sandwell, Y.~Fialko, and R.~Bilham (2011{\natexlab{a}}), {Slip on faults in the Imperial Valley triggered by the 4 April 2010 Mw 7.2 El Mayor-Cucapah earthquake revealed by InSAR}, \textit{Geophysical Research Letters}, \textit{38}(L01308), 1--6 \doi{10.1029/2010GL045235}.
+
+\bibitem[{\textit{Wei et~al.}(2015)\textit{Wei, Liu, Kaneko, Mcguire, and Bilham}}]{Wei2015}
+Wei, M., Y.~Liu, Y.~Kaneko, J.~J.
+Mcguire, and R.~Bilham (2015), {Dynamic triggering of creep events in the Salton Trough, Southern California by regional M≥5.4 earthquakes constrained by geodetic observations and numerical simulations}, \textit{Earth and Planetary Science Letters}, \textit{427}, 1--10, \doi{10.1016/j.epsl.2015.06.044}.
+
+\bibitem[{\textit{Wei et~al.}(2011{\natexlab{b}})\textit{Wei, Fielding, Leprince, Sladen, Avouac, Helmberger, Hauksson, Chu, Simons, Hudnut, Herring, and Briggs}}]{Wei2011}
+Wei, S., E.~Fielding, S.~Leprince, A.~Sladen, J.-P.
+Avouac, D.~Helmberger, E.~Hauksson, R.~Chu, M.~Simons, K.~Hudnut, T.~Herring, and R.~Briggs,(2011{\natexlab{b}}), {Superficial simplicity of the 2010 El Mayor–Cucapah earthquake of Baja California in Mexico}, \textit{Nature Geoscience}, \textit{4}, 615--618, \doi{10.1038/ngeo1213}.
 
@@
 \bibitem[{\textit{Yuen and Peltier}(1982)}]{Yuen1982}
-Yuen, D.~A., and W.~R. Peltier (1982), {Normal modes of the viscoelastic
-  earth}, \textit{Geophysical Journal of the Royal Astronomical Society},
-  \textit{69}, 495--526, \doi{10.1111/j.1365-246X.1982.tb04962.x}.
+Yuen, D.~A., and W.~R.
+Peltier (1982), {Normal modes of the viscoelastic earth}, \textit{Geophysical Journal of the Royal Astronomical Society}, \textit{69}, 495--526, \doi{10.1111/j.1365-246X.1982.tb04962.x}.
 
 \end{thebibliography}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Track Changes:
-% To add words, \added{<word added>}
-% To delete words, \deleted{<word deleted>}
-% To replace words, \replace{<word to be replaced>}{<replacement word>}
-% To explain why change was made: \explain{<explanation>} This will put
-% a comment into the right margin.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% At the end of the document, use \listofchanges, which will list the
-% changes and the page and line number where the change was made.
-
-% When final version, \listofchanges will not produce anything,
-% \added{<word or words>} word will be printed, \deleted{<word or words} will take away the word,
-% \replaced{<delete this word>}{<replace with this word>} will print only the replacement word.
-%  In the final version, \explain will not print anything.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Supporting Information
-%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
-%% for Supporting Information.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-More Information and Advice:
-
-%% ------------------------------------------------------------------------ %%
-%
-%  SECTION HEADS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Capitalize the first letter of each word (except for
-% prepositions, conjunctions, and articles that are
-% three or fewer letters).
-
-% AGU follows standard outline style; therefore, there cannot be a section 1 without
-% a section 2, or a section 2.3.1 without a section 2.3.2.
-% Please make sure your section numbers are balanced.
-% ---------------
-% Level 1 head
-%
-% Use the \section{} command to identify level 1 heads;
-% type the appropriate head wording between the curly
-% brackets, as shown below.
-%
-%An example:
-%\section{Level 1 Head: Introduction}
-%
-% ---------------
-% Level 2 head
-%
-% Use the \subsection{} command to identify level 2 heads.
-%An example:
-%\subsection{Level 2 Head}
-%
-% ---------------
-% Level 3 head
-%
-% Use the \subsubsection{} command to identify level 3 heads
-%An example:
-%\subsubsection{Level 3 Head}
-%
-%---------------
-% Level 4 head
-%
-% Use the \subsubsubsection{} command to identify level 3 heads
-% An example:
-%\subsubsubsection{Level 4 Head} An example.
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  IN-TEXT LISTS
-%
-%% ------------------------------------------------------------------------ %%
-%
-% Do not use bulleted lists; enumerated lists are okay.
-% \begin{enumerate}
-% \item
-% \item
-% \item
-% \end{enumerate}
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATIONS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Single-line equations are centered.
-% Equation arrays will appear left-aligned.
-
-Math coded inside display math mode \[ ...\]
- will not be numbered, e.g.,:
- \[ x^2=y^2 + z^2\]
-
- Math coded inside \begin{equation} and \end{equation} will
- be automatically numbered, e.g.,:
- \begin{equation}
- x^2=y^2 + z^2
- \end{equation}
-
-% To create multiline equations, use the
-% \begin{eqnarray} and \end{eqnarray} environment
-% as demonstrated below.
-\begin{eqnarray}
-  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
-        && + (y - y_{0}) \sin \Theta  \nonumber \\
-  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
-        && + (y - y_{0}) \cos \Theta.
-\end{eqnarray}
-
-%If you don't want an equation number, use the star form:
-%\begin{eqnarray*}...\end{eqnarray*}
-
-% Break each line at a sign of operation
-% (+, -, etc.) if possible, with the sign of operation
-% on the new line.
-
-% Indent second and subsequent lines to align with
-% the first character following the equal sign on the
-% first line.
-
-% Use an \hspace{} command to insert horizontal space
-% into your equation if necessary. Place an appropriate
-% unit of measure between the curly braces, e.g.
-% \hspace{1in}; you may have to experiment to achieve
-% the correct amount of space.
-
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATION NUMBERING: COUNTER
-%
-%% ------------------------------------------------------------------------ %%
-
-% You may change equation numbering by resetting
-% the equation counter or by explicitly numbering
-% an equation.
-
-% To explicitly number an equation, type \eqnum{}
-% (with the desired number between the brackets)
-% after the \begin{equation} or \begin{eqnarray}
-% command.  The \eqnum{} command will affect only
-% the equation it appears with; LaTeX will number
-% any equations appearing later in the manuscript
-% according to the equation counter.
-%
-
-% If you have a multiline equation that needs only
-% one equation number, use a \nonumber command in
-% front of the double backslashes (\\) as shown in
-% the multiline equation above.
-
-% If you are using line numbers, remember to surround
-% equations with \begin{linenomath*}...\end{linenomath*}
-
-%  To add line numbers to lines in equations:
-%  \begin{linenomath*}
-%  \begin{equation}
-%  \end{equation}
-%  \end{linenomath*}

### 2016-07-07 JGRRevision/2016JB013114.tex
commit before going home for the night

@@
 We find that early, rapid, near-field deformation can be explained with afterslip on the fault that ruptured coseismically.
-The later, sustained, near-field deformation can be explained with either continued afterslip in an effectively elastic lower crust, or lower crustal viscoelastic relaxation with a steady-state viscosity of ${\sim}10^{19}$ Pa s.
+The later, sustained, near-field deformation can be explained with viscoelastic relaxation in the lower crust with a steady-state viscosity of ${\sim}10^{19}$ Pa s and possibly continued afterslip.
 The later postseismic deformation in the far-field is best explained with a transient viscosity of ${\sim}10^{18}$ Pa s in the upper mantle.
-We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay in postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time-scales.
+We argue that a transient rheology in the mantle is preferable over a Maxwell rheology because it better predicts the decay in postseismic deformation, and also because it does not conflict with the generally higher, steady-state viscosities inferred from studies of geophysical processes occurring over longer time scales.
 \end{abstract}
@@
 The blue lines show the predicted displacements for the model with a Maxwell viscoelastic lower crust and upper mantle.
-The green line shows the predicted displacements for the model with a Maxwell viscoelastic lower crust and a Zener viscoelastic upper mantle.
+The green line shows the predicted displacements for our preferred model, which has a Maxwell viscoelastic lower crust and a Zener viscoelastic upper mantle.
 The effective viscosities are the same for both models and are shown in Figure \ref{fig:EffectiveViscosity}.}
@@
 Inferred afterslip within the first year is accounting for the most rapid near-field transient deformation (Figure S3).
-After one year, afterslip is inferred to be deeper down on the Sierra Cucapah segment, which is describing some of the sustained near-field postseismic deformation.
-We emphasize, that the GPS station closest to where we infer afterslip, P496, is still about 30 km away, which is too far for us to conclusively argue for sustained localized deformation rather than shallow distributed deformation.
-The deep afterslip inferred after one year could potentially be describing deformation resulting from lower crustal flow.
+After one year, afterslip is inferred to be deeper down on the Sierra Cucapah segment.
+The sustained near-field postseismic deformation is being explained by this continued afterslip as well as viscoelastic relaxation in the lower crust.
+We emphasize, that the GPS station closest to where we infer afterslip, P496, is still about 30 km away, which is too far for us to conclusively discern deep afterslip from viscoelastic relaxation in the lower crust.
+The deep afterslip inferred after one year could potentially be compensating for an overestimated lower crustal viscosity.
 To test this, we have modified our preferred model by decreasing the lower crustal viscosity from $5.91\times10^{19}$ Pa s to $1\times10^{19}$ Pa s, which is still consistent with our viscosity inference from Section \ref{sec:InitialInversion}, and we inverted for fault slip.
 We find that a model with a weaker lower crust adequately describes the postseismic displacements without any afterslip after one year, while still requiring about the same amount of afterslip over the first year.
-We do believe that the early, shallow afterslip on the Sierra Cucapah segment is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
+We do believe that the early afterslip on the Sierra Cucapah segment is a robust feature in our preferred model, while we are not confident in our inference of later deep afterslip.
 
@@
 \centering 
-\caption{Inferred coseismic slip and afterslip when assuming a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.
+\caption{Inferred coseismic slip and afterslip for our preferred model, which has a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.
 The transient viscosity, $\eta_K$, in the mantle and steady-state viscosity, $\eta_M$, in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}.
@@
 Near-field deformation exhibits transience that decays to a sustained, elevated rate after about one or two years.
-We found that near-field transient deformation can be explained with shallow afterslip, and the sustained rate of near-field deformation can either be explained with continued afterslip or viscoelastic relaxation in the lower crust.
+We found that near-field transient deformation can be explained with shallow afterslip.
+The sustained rate of near-field deformation can be explained with viscoelastic relaxation in the lower crust and possibly continued afterslip.
 Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km.

### 2016-07-08 JGRAnnotatedRevision/new.tex
made a directory containing submission materials

--- 2016-07-07 JGRRevision/2016JB013114.tex
@@
 \centering 
-\caption{Mean chi-squared value for the best fitting slip model as a function of the transient shear modulus relative to the elastic shear modulus in a Zener upper mantle.
-Large dot indicates our preferred ratio.}
+\caption{Mean chi-squared value as a function of the transient shear modulus relative to the elastic shear modulus in a Zener rheology upper mantle. Large dot indicates our preferred ratio.}
 \label{fig:ShearModulusRatio}
@@
 The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.
-The largest misfit occur within the Imperial Valley and there does not appear to be any systematic trend in the residuals.
+The largest misfit occur within the Imperial Valley where there does not appear to be any systematic trend in the residuals.
 This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Or, to use BibTeX:
-%
-% Follow these steps
-%
-% 1. Type in \bibliography{<name of your .bib file>} 
-%    Run LaTeX on your LaTeX file.
-%
-% 2. Run BiBTeX on your LaTeX file.
-%
-% 3. Open the new .bbl file containing the reference list and
-%   copy all the contents into your LaTeX file here.
-%
-% 4. Run LaTeX on your new file which will produce the citations.
-%
-% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.
-
 %% After you run BibTeX, Copy in the contents of the .bbl file here:
@@
 \bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais, Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
-Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002 Denali, Alaska, earthquake for postseismic relaxation processes and lithospheric rheology}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{111}{B01401}, 1--23, \doi{10.1029/2005JB003894}.
+Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002 Denali, Alaska, earthquake for postseismic relaxation processes and lithospheric rheology}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{111}(B01401), 1--23, \doi{10.1029/2005JB003894}.
 

### 2016-07-08 JGRRevision/Rebuttal/RebuttalLetter.tex
manuscript submitted

\documentclass[10pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\begin{document}

\signature{Trever T. Hines}

\begin{letter}{}
\opening{Dear Editor,}

We were pleased with the positive comments from you and the reviewers, and we feel that the comments brought up valid concerns. We hope that we have addressed these concerns sufficiently in our revision. In order to fully address the comments, we have included a supplementary material document.  We have also made some changes to the manuscript which were not specifically requested by the reviewers.  Most of these changes were stylistic and do not change the content of the manuscript.  One of the more substantial changes was that we merged Figures 7 and 14, which are both showing observed and predicted radial components of postseismic displacements, facilitating direct comparison of the figures.

We added supporting figures S3 and S4, which break down the predicted displacements of our preferred model into an elastic and viscoelastic component.  We feel that these figures help support our discussion on lines 509 to 523, where we attribute inferences of fault slip and viscoelastic relaxation to different aspects of the observed postseismic displacements.

On line 500 to 502 of our previous version of this manuscript we make the claim that “After one year, afterslip is inferred to be deeper down on the Sierra Cucapah segment, which is describing much of the sustained near-field postseismic deformation.”  This sentence is not accurate of the preferred model we present in the manuscript. As can be clearly seen in the new figures S3-S4, afterslip is describing some of the later near-field deformation, although most of it is being described by viscoelastic relaxation.  We have reworded this passage and updated the introduction and conclusion to accurately describe our interpretations of the mechanisms driving later near-field deformation.  This does not significantly alter the main conclusions of our manuscript, because we are very clear, both in the original and revised versions, that the deformation mechanism driving later near-field deformation cannot be definitively resolved with these data.

Each of the reviewer comments are included below followed by our response and a description of how these comments were addressed in this revised manuscript.

\textbf{Reviewer \#1 Evaluations:}\newline
\textbf{Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.}\newline
\textbf{Supported: Yes}\newline
\textbf{Referencing: Yes}\newline
\textbf{Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.}\newline
\textbf{Data: Yes}

\textbf{Reviewer \#1 (Formal Review for Authors (shown to authors)):}\newline
\textbf{In this manuscript, the authors carry out an in-depth analysis of deformation time-series following the 2010 El Mayor-Cucapah earthquake, modeling simultaneously coseismic effects, afterslip and viscoelastic relaxation. Their modeling approach is technically sound and well discussed. In particular, I appreciated that the authors clearly explain which steps of their approach are subjective decisions.}

\textbf{I think that this work is of potential interest for a broad range of researchers and therefore I recommend its publication on JGR. I have just a few minor comments, which I believe that will further improve the manuscript.}

\textbf{- The only aspect of the modeling that is not discussed is the resolution of the inversions. For both coseismic slip and afterslip, faults are discretized with a 4km step, but the real resolving power of the dataset is likely to be lower. I suggest showing a checkerboard test, maybe as additional material to avoid introducing too much clutter in the main text. A brief discussion the resolution on viscosity values would also be helpful.}

We have included the results of a synthetic test as Figure S2 in the supplementary information which illustrates the resolvability of fault slip and lithospheric viscosity for the inversion in Section 3.2.  In this synthetic test, we generate displacements resulting from a checkerboard pattern of coseismic slip and viscoelastic relaxation in an elastic lithosphere overlying a uniformly low viscosity asthenosphere.  Our checkerboard test illustrates the effect of regularization on our solution and we believe that it should provide the reader with a better sense of the uncertainty in our solution.  In lines 416-418 and 437 to 440, we comment on the synthetic test and use it to explain how the reader should interpret our inferred solution in Section 3.2.

\textbf{- I think that it would be useful to show the regularization tradeoff curves for both elastic and full-postseismic inversion, in order to quantify the effect of the penalty parameters. These curves could be shown as additional material.}

We include the trade-off curves as Figure S1 in the supplementary information and we explain how we used the tradeoff curves to infer the two penalty parameters from Section 3.2.

\textbf{- The introduction of a Zener rheology undoubtedly improves the agreement with data, but in many stations the model still fails to explain the observed signal. It would be useful to give a statistical measure of the significance of misfit reduction in relation to the additional model parameters, to ensure that the lower chi-square is meaningful and not just an over-fitting.}

We do not know of a statistical measure that would be appropriate for demonstrating the statistical significance of using a Zener rheology instead of a Maxwell or elastic rheology.  The Zener model includes one extra model parameter compared to the Maxwell model, while  the total number of model parameters is on the order of a few hundred, resulting in very small, arguably trivial, change to the degrees of freedom. We do not feel that an F-test would be appropriate because the uncertainty on our data is likely underestimated, which we discuss in Section 2, and combined with the fact that only one model parameter was added, this results in an F-tests which we feel is overly confident.  We performed the F-test to see how significant the Zener model is over the Maxwell model, and the F-test suggests that we can reject the null hypothesis with effectively 100\% confidence. We think that comparing the models with an F-test can be misleading and we instead think that a visual comparison between the observed and predicted displacements, which are presented in Figures 4, 5, and 7, is a more honest means of appraisal.  Alternatively, we could compare the Zener model to the Maxwell or elastic model with the Akaike Information Criterion (AIC).  The AIC is a function of the number of model parameters and the chi-squared misfit.  The number of model parameters remains effectively constant for the Zener and Maxwell model, and thus comparing the AIC of the models does not offer any more information than comparing their chi-squared values, which we present in the text.

\textbf{Minor points:}

\textbf{- I suggest adding a paragraph in the introduction to describe the earthquake and its seismo-tectonic context.}

We do not describe the seismo-tectonic context of the El Mayor-Cucapah earthquake because we do not feel that such general background information is necessary to understand our paper. Likewise, our postseismic results do not yield deeper understanding of the seismo-tectonics of the area. Others have already described the El Mayor in context of the seismo-tectonics of the region, and on line 39 we now point the reader to two papers doing so.

\textbf{- Magnitudes would read better if the notation "Mw=7.2" or "Mw$>$7" is used instead of "Mw7.2" or "$>$Mw7".}

We have made the suggested changes.

\textbf{- In eqs. (1) and (2), it is not explicitly stated that t is expressed in years.}

We added a sentence stating this on line 116.

\textbf{- line 202: I suggest to quantify the "elevated rate"}

The text has been changed so that we quantify this elevated rate as “a few millimeters per year” on line 204.

\textbf{- Figures 4 ad 5: add a symbol to mark the epicenter}

We have added focal mechanisms at the El Mayor-Cucapah epicenter for Figure 4.  We do not change Figure 5 because the epicenter is not in the frame.

\textbf{- lines 259-260: "Table 3" should read "Table 1"}

We have made the suggested changes.

\textbf{- Figures 6, 12 and 15: a label with the two fault names would be useful. White arrows for the slip direction are difficult to see, maybe it is better to use a more contrasting color (I would try red)}

We have increased the size of the slip vectors on these figures. We also added the fault segment names to these figures.

\textbf{- line 513: `the' should be `The'}

We have made the suggested changes.

\textbf{Reviewer \#2 Evaluations:}\newline
\textbf{Significant: Yes, the paper is a significant contribution and worthy of prompt publication.}\newline
\textbf{Supported: Yes}\newline
\textbf{Referencing: Mostly yes, but some additions are necessary.}\newline
\textbf{Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.}\newline
\textbf{Data: Yes}

\textbf{Reviewer \#2 (Formal Review for Authors (shown to authors)):}

\textbf{This is a timely study of the mechanisms of postseismic relaxation following the 2010 M7.2 El Mayor-Cucapah earthquake. The authors make use of ~5 years of postseismic time series and model the time-dependent crustal motions with joint afterslip and lower crust/upper mantle viscoelastic relaxation. This approach is well motivated by observations of both processes following past earthquakes in both megathrust and continental strike-slip settings. The authors leverage the power of several years of observations and perform a careful search of model parameter space to infer rheological parameters. They make the case for non-Maxwellian rheology in the upper mantle. The resulting estimate of Zener-rheology mantle viscosity is consistent with the transient or Maxwell viscosity obtained from other western US postseismic relaxation studies and lacustrine lake unloading studies.}

\textbf{Specific comments}

\textbf{Figures 4 and 5. I cannot figure out what the predicted vertical displacements are. "... shown within the circles at the base of each vector." - are these the black circles? Should the reader be looking at the size of these circles? How do I tell the sign of the predicted vertical displacement? At many stations I don't even see these circles! Also, do the observed horizontal displacements include error ellipses?}

The Figure 4 caption in the previous version of the text was ambiguous and we changed it to read “The black error ellipses show the 68\% confidence interval for the observed horizontal displacements.  Observed vertical displacements are shown as an interpolated field and predicted vertical displacements are shown within the green circles.”  We believe this addresses the reviewers confusion.

\textbf{Figure 11. The confidence intervals for viscosity seem remarkably tight given the likely small sensitivity to viscosity at, say, the 150-180 km depth interval. Please elaborate on how these uncertainties were determined.}

We appreciate that the reviewer brought up this point and we feel that it is important to emphasize in the text that the uncertainty is likely underestimated due to our added regularization constraints.  We modified the text to further stress this point in lines 433 to 440.  The uncertainties were calculated using the standard bootstrapping technique, which we state.

\textbf{Section 3.3. After about line 479, remind the reader where the parameters of the preferred rheology model are summarized (Table 1).}

We changed the text as suggested on line 493.

\textbf{Last paragraph of section 3.3. Is there anything in the fits of Figures 4 and 5 that would suggest any systematic pattern in the residuals? I have in mind possible differences between the Salton trough and surrounding regions, which may be expected from the relatively high heat flow in the Salton trough.}

We do not observe any systematic residuals in the Salton Trough that would suggest lateral heterogeneity in the material properties.  We modified the text to state this in lines 525 to 530.

\textbf{Last paragraph of Discussion. Please note that Pollitz (2003) has been superseded by Pollitz (2015), which models post-Hector Mine motions with joint afterslip and viscoelastic relaxation. Pollitz (2015) interprets the early post-Hector Mine motions as predominantly afterslip, and the estimated transient and Maxwell viscosities are ~10 times higher than those of Pollitz (2003).}

We thank the reviewer for pointing out this paper, which nicely complements our work.  We modified the discussion to note the contribution by Pollitz (2015) on line 624 to 627.

\textbf{Reference}

\textbf{Pollitz, F.F., Post-earthquake relaxation evidence for laterally variable viscoelastic structure and water content in the southern California mantle, J. Geophys. Res., 120, 2672-2696, (2015).}

\closing{thank you for your consideration,}
\end{letter}
\end{document}
